### 2017-05-29 thesis_report/draft_thesis.tex
LaTeX file: Theoretic background (75%)

\documentclass[12pt]{report}

\title{Topic modeling bla bla}

\renewcommand{\thesection}{\arabic{section}}

\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}
\begin{document}
\maketitle
\tableofcontents

\begin{abstract}
This is a simple paragraph at the beginning of the 
document. A brief introduction about the main subject.
\end{abstract}

\section{Introduction}
This is where you tell people why they should bother reading your article.
\vspace{10mm}

\section{Theoretic background}

\vspace{5mm}

In this chapter we will present some basic theoretic background about topic modeling. To deal with extensive text body, machine learning researchers have developed topic modeling: a suite of methods that analyze the words of the original text to discover the themes that run through the data and detect hidden semantic structures by analyzing a corpus. By marking up the documents using these topics and by using the resulting structure, the model can be used for organization, finding similar documents, or any other similar tasks. A topic is here defined as a probability distribution of words, meaning that certain words are more likely within a certain topic. Since the topics emerge from the analysis of the original texts, topic modeling algorithms do not require any prior annotations or labeling of the documents.\par

\vspace{3mm}

In order to apply a topic model to our data, the first question we must answer is how to represent documents. For understanding of natural language one must obviously preserve the order of the words in documents. However, for many large-scale data mining tasks, it is sufficient to use a simple representation that loses all information about word order. Given a collection of documents, the first task to perform is to identify the set of all words used at least once in at least one document. This set is called the vocabulary. Often, we reduce the size of the vocabulary by keeping only words that are used in at least a small percentage of the documents. Words that are found only once are often misspellings or other mistakes. Although the vocabulary is a set, we fix an arbitrary ordering for it so we can refer to word 1 through word $m$ where $m$ is the size of the vocabulary. Once the vocabulary has been fixed, each document is represented as a vector with integer entries of length $m$. If this vector is $x$ then its $j$-th component $x_j$ is the number of appearances of word $j$ in the document. The length of the document is $n=\sum\limits_{j=1}^m x^j$.\par

\vspace{3mm}

Many applications of if topic modeling also eliminate from the vocabulary so-called “stop” words. These are words that are common in most documents and do not correspond to any particular subject matter. They include pronouns (you, he, it), connectives (and, because, however), prepositions (to, of, before), and auxiliaries (have, been, can, should).  Stop words may also include generic nouns (amount, part, nothing) and verbs (do, have). A collection of documents is represented as a two-dimensional matrix where each row describes a document and each column corresponds to a word. Each entry in this matrix is an integer count; most entries are zero. It makes sense to view each column as a feature.\par

\vspace{3mm}

Some further common concepts and terms in topic modeling:

- A word is defined as an item from a vocabulary indexed from ${1, ..., V}$, where V is the size of the vocabulary. All words are represented as unit-basis vectors with one component equal to one and the rest equal to zero.

- A document is a collection of words denoted by $w = {w_1, ..., w_N}$, where $w_n$ is the $n$th word and $N$ is the total number of words in the collection.

- A corpus is a collection of documents in a dataset. It is denoted $D = {w_1, ..., w_M}$, where $w_m$ is the $m$th document in the corpus and $M$ is the total number of documents.

- Latent variables are variables that may not be directly observed, unlike observable variables. Latent variables can instead be inferred from other observable variables.

- Polysemy is the capacity for a word to have multiple related meanings. An example of this is the word “plant” which can mean a living organism of the kind exemplified by trees, herbs etc., or a place where an industrial or manufacturing process takes place.

- Synonymy is the capacity for several words to have similar meanings such as the words “buy” and “purchase”.

\vspace{10mm}

\subsection{The Multinomial Distribution}

\vspace{5mm}

Once we have a representation for individual documents, the natural next step is to select a model for a set of documents. It is important to understand the difference between a representation and a model.  A representation is a way of encoding an entity as a data structure. A model is an abstraction of a set of entities, for example a probability distribution.  Given a training set of documents, we will choose values for the parameters of a probabilistic model that make the training documents have high probability. Then, given a test document, we can evaluate its probability according to the model. The higher this probability is, the more similar the test document is to the training set.

\vspace{3mm}

The probability distribution that we use is the multinomial. Mathematically, this distribution is:

\begin{equation}
p(x;\theta) = \left(\frac{n!}{\prod\limits_{j=1}^m x^j!}\right)\left(\prod\limits_{j=1}^m \theta_j^{x_j}\right)
\end{equation}

\vspace{3mm}

where the data $x$ are a vector of non-negative integers and the parameters $\theta$ are a real-valued vector. Both vectors have the same length $m$. Intuitively, $\theta_j$ is the probability of word $j$ while $x_j$ is the count of word $j$. Each time word $j$ appears in the document it contributes an amount $\theta_j$ to the total probability, hence the term $\theta_j^{x_j}$. The components of $\theta$ are non-negative and have unit $\sum\limits_{j=1}^m \theta_j = 1$. A vector with these properties is called a unit vector.\par

\vspace{3mm}

Like any discrete distribution, a multinomial has to sum to one, where the sum is over all possible data points. Here, a data point is a document containing $n$ words.

\vspace{10mm}

\subsection{Generative process}

\vspace{5mm}

Suppose that we have a collection of documents, and we want to find an organization for these, i.e. we want to do unsupervised learning. A common way to do unsupervised learning is to assume that the data were generated by some probabilistic process, and then to infer the parameters of this process. The generative process is a specification of a parametrized family of distributions. Learning is based on the principle of maximum likelihood, or some refinement of this principle such as maximum a posterior probability.\par

\vspace{3mm}

\begin{enumerate}
  \item Fix a multinomial distribution with parameter vector $\phi$ of length $V$
  \item for each word in the document:
  \begin{itemize}
  draw a word $w$ according to $\phi$
  \end{itemize}
\end{enumerate}

\vspace{3mm}

Above, step 1 sets up the probability distributions that are then used in step 2 to produce the observed training data. A single multinomial distribution can only represent a category of closely related documents. For a collection of documents of multiple categories/topics, a simple
generative process is

\vspace{3mm}

\begin{enumerate}
\item Fix a multinomial $\alpha$ over categories $1$ to $K$\\
for category number $1$ to category number $K$:
\begin{itemize}
fix a multinomial with parameter vector $\phi_k$
\end{itemize}

\item for document number $1$ to document number $M$:
\begin{itemize}
draw a category $z$ according to $\alpha$\\
for each word in the document:\\
  	\begin{itemize}
  		draw a word $w$ according to $\phi_z$
  	\end{itemize}
\end{itemize}
\end{enumerate}
\vspace{3mm}

Note that $z$ is an integer between $1$ and $K$. For each document, the value of $z$ is hidden, meaning that it exists conceptually, but it is never known, not even for training data. The generative process above gives the following global probability distribution\par
\vspace{3mm}

\begin{equation}
f(x) = \sum\limits_{k=1}^K \alpha_k f(x;\phi_k)
\end{equation}

\vspace{3mm}

where $x$ is a document and $\phi_k$ is the parameter vector of the $k$-th multinomial. In general, $x$ could be a data point of any type and $\phi_k$ could be the parameters of any appropriate distribution. $K$ is called the number of components in the mixture model. For each $k$, $f (x; \theta_k)$ is the distribution of component number $k$. The scalar $\alpha_k$ is the proportion of component number $k$. A distribution like this is called a mixture distribution. In general, the components can be probability density functions, for example Gaussians, or probability mass functions, for example multinomials. We will see later how to do maximum likelihood estimation for mixture distributions, using a technique called expectation-maximization.\par

\vspace{10mm}
\subsection{Basic models in topic modeling}

\vspace{5mm}

First, we’ll introduce some basic models for topic modeling. The Latent Semantic Indexing, or LSI, was presented by Deerwester et al. in 1990. The model manages to deal with the problem that multiple terms can refer to the same meaning, i.e. synonymy. However, it is not as successful regarding polysemy. The reason is that every term is represented as just one
point in the so-called latent semantic space. Furthermore, a word that can mean two or more different things is represented as a weighted average of the different meanings.\par

\vspace{3mm}

After LSI was introduced, Hofmann presented the Probabilistic Latent Semantic Indexing, or PLSI model. PLSI is a so-called topic model where each word in a document is generated from a single “topic” which results in that each document in a corpus can be represented with a topic distribution. Later, in 2003 Blei et al. presented the Latent Dirichlet Allocation, or LDA.
As opposed to PLSI, LDA is a statistically generative model for documents where each word in a document can be generated by all topics.\par
\vspace{10mm}

\subsubsection{Latent Semantic Indexing (LSI)}

\vspace{5mm}

Latent Semantic Indexing was one of the earliest methods for finding relationships between documents and the words that occur in them. In LSI a term-document matrix is created by analyzing the corpus, where the rows correspond to words and columns to documents. Each element in this sparse matrix describes the number of times a word occurs in a document but this term count can also be weighted with for instance TF-IDF. Letting each word represent a dimension in a very high dimensional space, a document can be seen as a vector with components corresponding to its weighted term counts.\par

\vspace{3mm}

A low-rank approximation of the term-document matrix is created using Single Value Decomposition, SVD, which creates new dimensions, called concepts, as linear combinations of the original words. This allows similarity measures and clustering methods by reducing the volume of the word space and thus making this space more densely populated.\par

\vspace{3mm}

The drawbacks with LSI are mainly the lack of a statistical foundation in the model. LSI is based on linear algebra instead of probabilistic modeling leaving it with a small toolbox for what can be achieved using the model.\par

\vspace{10mm}
\subsubsection{Probabilistic Latent Semantic Indexing (PLSI)}
\vspace{5mm}

Probabilistic Latent Semantic Indexing evolved from LSI and uses the same concept of finding a lower rank approximation of the term-document occurrence matrix. The difference is that instead of being based on linear algebra, PLSI is based on a mixture decomposition using a latent class model. PLSI associates an unobserved class variable $z$ with each document-word observation pair $(w, w)$. This $z$ can be seen as a topic, since it is a probability distribution over words. As a generative model, PLSI can be defined in the following way for a corpus $D$:

\vspace{3mm}

\begin{enumerate}
\item Pick a document $w$ with probability $p(w)$
\item For each of the $N$ words in $w$:
\begin{itemize}
(a) Pick a topic $z$ with probability $p(z|w)$
\end{itemize}
\begin{itemize}
(b) Generate a word $w$ with probability $p(w|z)$
\end{itemize}
\end{enumerate}

\vspace{3mm}

The result from PLSI is that every document is represented as mixing proportions for the topics, given by $p(z|w)$. Even though PLSI is generative for the analyzed corpus, it is not generative for new documents, which means is that there is no clear way of assigning probability to a document that is not part of the training data. Another problem is that the number of parameters in the model grows linearly with the number of documents.\par

\vspace{10mm}
\subsubsection{Latent Dirichlet Allocation (LDA)}
\vspace{5mm}

LDA is a topic model that was first presented as a graphical model for topic discovery by David Blei, Andrew Ng, and Michael I. Jordan in 2003. The basic idea is that documents exhibit multiple topics. LDA is a generative statistical model that allows sets of observations to be explained by unobserved groups that explain why some parts of the data are similar. For example, if observations are words collected into documents, it posits that each document is a mixture of a small number of topics and that each word's occurrence is attributable to one of the document's topics. This is similar to PLSI, except that in LDA the topic distribution is assumed to have a Dirichlet prior (see 2.x.x). In practice, this results in more reasonable mixtures of topics in a document. The reduced document description result in PLSI is a vector where each element describes the mixing proportion for a topic. A limitation with PLSI is that there is no generative (see 2.x) model for these proportions, making it difficult to handle unseen documents. The Latent Dirichlet Allocation model tries to solve this limitation by setting a Dirichlet prior on the topic distribution.\par

\vspace{3mm}

The basic idea in LDA is that  we define a topic to be a Dirichlet distribution over a fixed vocabulary. Technically, the model assumes that the topics are generated first, before the documents. Now for each document in the collection, we generate the words in a two-stage process:

\vspace{3mm}

\begin{enumerate}
\item Randomly choose a distribution over topics.
\item For each word in the document:
\begin{itemize}
(a) Randomly choose a topic from the distribution over topics in step #1.
\end{itemize}
\begin{itemize}
(b) Randomly choose a word from the corresponding distribution over the vocabulary.
\end{itemize}
\end{enumerate}

\vspace{3mm}

This statistical model reflects the intuition that documents exhibit multiple topics. Each document exhibits the topics with different proportion (step #1); each word in each document is drawn from one of the topics (step #2b), where the selected topic is chosen from the per-document distribution over topics (step #2a). All the documents in the corpus share the same set of topics, but each document exhibits those topics with different proportion - that’s the distinguishing characteristic of LDA.
A more detailed explanation of the model follows in section 2.x.x.\par

\vspace{10mm}

\paragraph{Dirichlet distribution}

\vspace{5mm}

The Dirichlet distribution is a way to model random probability mass functions (PMFs)\footnote{If you roll 1000 dice, the theoretical odds of any particular number showing up (i.e. a 1, 2, 3, 4, 5, or 6) are 1/6. However, you won’t get that exact distribution in a real experiment due to manufacturing defects. If you have ten dice, each die will have its own probability mass function (PMF).} for finite sets. It is also sometimes used as a prior in Bayesian statistics. The Dirichlet is the multivariate generalization of the beta distribution. It is an extension of the beta distribution for modeling probabilities for two or more events; when the result of the event has only 2 values, the Dirichlet distribution is equal to the beta distribution.\par

\vspace{3mm}

The Dirichlet distribution is a prior for the multinomial distribution. This means that if the prior distribution of the multinomial parameters is Dirichlet then the posterior distribution is also a Dirichlet distribution (with parameters different from those of the prior).\\
The Dirichlet process is a way to model randomness of a probability mass function (PMF) with unlimited options (e.g. an unlimited amount of dice in a bag). The process is similar Polya’s Urn, only instead of having a set number of ball colors you have an unlimited amount:

\vspace{10mm}

\paragraph{Model}

\vspace{5mm}

In LDA, each document is represented by a mixture of the topics, with weight θ2w for topic z in document w. These weight have a Dirichlet prior, parameterized by a hyper-parameter α. Each topic is a probability distribution over the vocabulary, with probability βwz for word w in topic z.

\vspace{10mm}

\paragraph{Expectation Maximization}

\vspace{5mm}
bla
\vspace{10mm}

\paragraph{Variational Inference}

\vspace{5mm}
bla bla

\vspace{10mm}

\section{Related work}

\section{Methodology}

\section{Analysis and results}

\section{Conclusion}

\section{Future work}

\end{document}

### 2017-05-30 thesis_report/draft_thesis.tex
Minor fixes in formating

@@
   \item for each word in the document:
-  \begin{itemize}
-  draw a word $w$ according to $\phi$
-  \end{itemize}
+  \begin{description}
+  \item draw a word $w$ according to $\phi$
+  \end{description}
 \end{enumerate}
@@
 for category number $1$ to category number $K$:
-\begin{itemize}
-fix a multinomial with parameter vector $\phi_k$
-\end{itemize}
+\begin{description}
+\item   fix a multinomial with parameter vector $\phi_k$
+\end{description}
 
 \item for document number $1$ to document number $M$:
-\begin{itemize}
-draw a category $z$ according to $\alpha$\\
-for each word in the document:\\
-  	\begin{itemize}
-  		draw a word $w$ according to $\phi_z$
-  	\end{itemize}
-\end{itemize}
+\begin{description}
+\item draw a category $z$ according to $\alpha$
+\item for each word in the document:
+  	\begin{description}
+  	\item	draw a word $w$ according to $\phi_z$
+  	\end{description}
+\end{description}
 \end{enumerate}
@@
 \item For each of the $N$ words in $w$:
-\begin{itemize}
-(a) Pick a topic $z$ with probability $p(z|w)$
-\end{itemize}
-\begin{itemize}
-(b) Generate a word $w$ with probability $p(w|z)$
-\end{itemize}
+\begin{description}
+\item (a) Pick a topic $z$ with probability $p(z|w)$
+\end{description}
+\begin{description}
+\item (b) Generate a word $w$ with probability $p(w|z)$
+\end{description}
 \end{enumerate}
@@
 \item For each word in the document:
-\begin{itemize}
-(a) Randomly choose a topic from the distribution over topics in step #1.
-\end{itemize}
-\begin{itemize}
-(b) Randomly choose a word from the corresponding distribution over the vocabulary.
-\end{itemize}
+\begin{description}
+	\item (a) Randomly choose a topic from the distribution over topics in step 1.
+\end{description}
+\begin{description}
+	\item (b) Randomly choose a word from the corresponding distribution over the vocabulary.
+\end{description}
 \end{enumerate}
@@
 This statistical model reflects the intuition that documents exhibit multiple topics.
-Each document exhibits the topics with different proportion (step #1); each word in each document is drawn from one of the topics (step #2b), where the selected topic is chosen from the per-document distribution over topics (step #2a).
+Each document exhibits the topics with different proportion (step 1); each word in each document is drawn from one of the topics (step 2b), where the selected topic is chosen from the per-document distribution over topics (step 2a).
 All the documents in the corpus share the same set of topics, but each document exhibits those topics with different proportion - that’s the distinguishing characteristic of LDA.

### 2017-05-31 thesis_report/draft_thesis.tex
Fix: line per sentence

@@
 \setcounter{tocdepth}{5}
+
 \begin{document}
+
 \maketitle
@@
 This is a simple paragraph at the beginning of the 
-document. A brief introduction about the main subject.
+document. 
+A brief introduction about the main subject.
 \end{abstract}
@@
 This is where you tell people why they should bother reading your article.
-\vspace{10mm}
 
@@
 
-\vspace{5mm}
-
 In this chapter we will present some basic theoretic background about topic modeling. 
-To deal with extensive text body, machine learning researchers have developed topic modeling: a suite of methods that analyze the words of the original text to discover the themes that run through the data and detect hidden semantic structures by analyzing a corpus.
+To deal with extensive text body, machine learning researchers have developed topic modeling: 
+a suite of methods that analyze the words of the original text to discover the themes that run through the data and detect hidden semantic structures by analyzing a corpus. 
 By marking up the documents using these topics and by using the resulting structure, the model can be used for organization, finding similar documents, or any other similar tasks. 
 A topic is here defined as a probability distribution of words, meaning that certain words are more likely within a certain topic. 
-Since the topics emerge from the analysis of the original texts, topic modeling algorithms do not require any prior annotations or labeling of the documents.\par
-
-\vspace{3mm}
+Since the topics emerge from the analysis of the original texts, topic modeling algorithms do not require any prior annotations or labeling of the documents.
 
@@
 If this vector is $x$ then its $j$-th component $x_j$ is the number of appearances of word $j$ in the document. 
-The length of the document is $n=\sum\limits_{j=1}^m x^j$.\par
-
-\vspace{3mm}
+The length of the document is $n=\sum\limits_{j=1}^m x^j$.
 
@@
 Each entry in this matrix is an integer count; most entries are zero. 
-It makes sense to view each column as a feature.\par
-
-\vspace{3mm}
+It makes sense to view each column as a feature.
 
@@
 
-- A corpus is a collection of documents in a dataset. It is denoted $D = {w_1, ..., w_M}$, where $w_m$ is the $m$th document in the corpus and $M$ is the total number of documents.
+- A corpus is a collection of documents in a dataset. 
+It is denoted $D = {w_1, ..., w_M}$, where $w_m$ is the $m$th document in the corpus and $M$ is the total number of documents.
 
-- Latent variables are variables that may not be directly observed, unlike observable variables. Latent variables can instead be inferred from other observable variables.
+- Latent variables are variables that may not be directly observed, unlike observable variables. 
+Latent variables can instead be inferred from other observable variables.
 
@@
 
-\vspace{10mm}
-
 \subsection{The Multinomial Distribution}
-
-\vspace{5mm}
 
@@
 
-\vspace{3mm}
-
-The probability distribution that we use is the multinomial. Mathematically, this distribution is:
+The probability distribution that we use is the multinomial. 
+Mathematically, this distribution is:
 
@@
 \end{equation}
-
-\vspace{3mm}
 
@@
 The components of $\theta$ are non-negative and have unit $\sum\limits_{j=1}^m \theta_j = 1$. 
-A vector with these properties is called a unit vector.\par
+A vector with these properties is called a unit vector.
 
-\vspace{3mm}
-
-Like any discrete distribution, a multinomial has to sum to one, where the sum is over all possible data points. Here, a data point is a document containing $n$ words.
-
-\vspace{10mm}
+Like any discrete distribution, a multinomial has to sum to one, where the sum is over all possible data points. 
+Here, a data point is a document containing $n$ words.
 
@@
 
-\vspace{5mm}
-
-Suppose that we have a collection of documents, and we want to find an organization for these, i.e.
-we want to do unsupervised learning.
+Suppose that we have a collection of documents, and we want to find an organization for these, i.e. we want to do unsupervised learning. 
 A common way to do unsupervised learning is to assume that the data were generated by some probabilistic process, and then to infer the parameters of this process. 
 The generative process is a specification of a parametrized family of distributions. 
-Learning is based on the principle of maximum likelihood, or some refinement of this principle such as maximum a posterior probability.\par
-
-\vspace{3mm}
+Learning is based on the principle of maximum likelihood, or some refinement of this principle such as maximum a posterior probability.
 
@@
 
-\vspace{3mm}
-
 Above, step 1 sets up the probability distributions that are then used in step 2 to produce the observed training data. 
@@
 generative process is
-
-\vspace{3mm}
 
@@
 \end{enumerate}
-\vspace{3mm}
 
@@
 For each document, the value of $z$ is hidden, meaning that it exists conceptually, but it is never known, not even for training data. 
-The generative process above gives the following global probability distribution\par
-\vspace{3mm}
+The generative process above gives the following global probability distribution
 
@@
 In general, the components can be probability density functions, for example Gaussians, or probability mass functions, for example multinomials. 
-We will see later how to do maximum likelihood estimation for mixture distributions, using a technique called expectation-maximization.\par
+We will see later how to do maximum likelihood estimation for mixture distributions, using a technique called expectation-maximization.
 
-\vspace{10mm}
 \subsection{Basic models in topic modeling}
 
-\vspace{5mm}
-
 First, we’ll introduce some basic models for topic modeling. 
-The Latent Semantic Indexing, or LSI, was presented by Deerwester et al.
-in 1990.
-The model manages to deal with the problem that multiple terms can refer to the same meaning, i.e.
-synonymy.
+The Latent Semantic Indexing, or LSI, was presented by Deerwester et al. in 1990. 
+The model manages to deal with the problem that multiple terms can refer to the same meaning, i.e. synonymy. 
 However, it is not as successful regarding polysemy. 
-The reason is that every term is represented as just one
-point in the so-called latent semantic space. Furthermore, a word that can mean two or more different things is represented as a weighted average of the different meanings.\par
-
-\vspace{3mm}
+The reason is that every term is represented as just one point in the so-called latent semantic space. 
+Furthermore, a word that can mean two or more different things is represented as a weighted average of the different meanings.
 
@@
 PLSI is a so-called topic model where each word in a document is generated from a single “topic” which results in that each document in a corpus can be represented with a topic distribution. 
-Later, in 2003 Blei et al.
-presented the Latent Dirichlet Allocation, or LDA.
-As opposed to PLSI, LDA is a statistically generative model for documents where each word in a document can be generated by all topics.\par
-\vspace{10mm}
+Later, in 2003 Blei et al. presented the Latent Dirichlet Allocation, or LDA.
+As opposed to PLSI, LDA is a statistically generative model for documents where each word in a document can be generated by all topics.
 
 \subsubsection{Latent Semantic Indexing (LSI)}
-
-\vspace{5mm}
 
@@
 Each element in this sparse matrix describes the number of times a word occurs in a document but this term count can also be weighted with for instance TF-IDF. 
-Letting each word represent a dimension in a very high dimensional space, a document can be seen as a vector with components corresponding to its weighted term counts.\par
-
-\vspace{3mm}
+Letting each word represent a dimension in a very high dimensional space, a document can be seen as a vector with components corresponding to its weighted term counts.
 
 A low-rank approximation of the term-document matrix is created using Single Value Decomposition, SVD, which creates new dimensions, called concepts, as linear combinations of the original words. 
-This allows similarity measures and clustering methods by reducing the volume of the word space and thus making this space more densely populated.\par
-
-\vspace{3mm}
+This allows similarity measures and clustering methods by reducing the volume of the word space and thus making this space more densely populated.
 
 The drawbacks with LSI are mainly the lack of a statistical foundation in the model. 
-LSI is based on linear algebra instead of probabilistic modeling leaving it with a small toolbox for what can be achieved using the model.\par
+LSI is based on linear algebra instead of probabilistic modeling leaving it with a small toolbox for what can be achieved using the model.
 
-\vspace{10mm}
 \subsubsection{Probabilistic Latent Semantic Indexing (PLSI)}
-\vspace{5mm}
 
@@
 As a generative model, PLSI can be defined in the following way for a corpus $D$:
-
-\vspace{3mm}
 
@@
 
-\vspace{3mm}
-
 The result from PLSI is that every document is represented as mixing proportions for the topics, given by $p(z|w)$. 
 Even though PLSI is generative for the analyzed corpus, it is not generative for new documents, which means is that there is no clear way of assigning probability to a document that is not part of the training data.
-Another problem is that the number of parameters in the model grows linearly with the number of documents.\par
+Another problem is that the number of parameters in the model grows linearly with the number of documents.
 
-\vspace{10mm}
 \subsubsection{Latent Dirichlet Allocation (LDA)}
-\vspace{5mm}
 
-LDA is a topic model that was first presented as a graphical model for topic discovery by David Blei, Andrew Ng, and Michael I.
-Jordan in 2003.
+LDA is a topic model that was first presented as a graphical model for topic discovery by David Blei, Andrew Ng, and Michael I. Jordan in 2003. 
 The basic idea is that documents exhibit multiple topics. 
@@
 A limitation with PLSI is that there is no generative (see 2.x) model for these proportions, making it difficult to handle unseen documents. 
-The Latent Dirichlet Allocation model tries to solve this limitation by setting a Dirichlet prior on the topic distribution.\par
-
-\vspace{3mm}
+The Latent Dirichlet Allocation model tries to solve this limitation by setting a Dirichlet prior on the topic distribution.
 
@@
 Now for each document in the collection, we generate the words in a two-stage process:
-
-\vspace{3mm}
 
@@
 
-\vspace{3mm}
-
 This statistical model reflects the intuition that documents exhibit multiple topics. 
-Each document exhibits the topics with different proportion (step 1); each word in each document is drawn from one of the topics (step 2b), where the selected topic is chosen from the per-document distribution over topics (step 2a).
+Each document exhibits the topics with different proportion (step 1); 
+each word in each document is drawn from one of the topics (step 2b), where the selected topic is chosen from the per-document distribution over topics (step 2a). 
 All the documents in the corpus share the same set of topics, but each document exhibits those topics with different proportion - that’s the distinguishing characteristic of LDA.
-A more detailed explanation of the model follows in section 2.x.x.\par
-
-\vspace{10mm}
+A more detailed explanation of the model follows in section 2.x.x.
 
 \paragraph{Dirichlet distribution}
-
-\vspace{5mm}
 
@@
 The Dirichlet is the multivariate generalization of the beta distribution. 
-It is an extension of the beta distribution for modeling probabilities for two or more events; when the result of the event has only 2 values, the Dirichlet distribution is equal to the beta distribution.\par
-
-\vspace{3mm}
+It is an extension of the beta distribution for modeling probabilities for two or more events; 
+when the result of the event has only 2 values, the Dirichlet distribution is equal to the beta distribution.
 
 The Dirichlet distribution is a prior for the multinomial distribution. 
-This means that if the prior distribution of the multinomial parameters is Dirichlet then the posterior distribution is also a Dirichlet distribution (with parameters different from those of the prior).\\
-The Dirichlet process is a way to model randomness of a probability mass function (PMF) with unlimited options (e.g.
-an unlimited amount of dice in a bag).
+This means that if the prior distribution of the multinomial parameters is Dirichlet then the posterior distribution is also a Dirichlet distribution (with parameters different from those of the prior).
+
+The Dirichlet process is a way to model randomness of a probability mass function (PMF) with unlimited options (e.g. an unlimited amount of dice in a bag). 
 The process is similar Polya’s Urn, only instead of having a set number of ball colors you have an unlimited amount:
 
-\vspace{10mm}
-
 \paragraph{Model}
-
-\vspace{5mm}
 
@@
 
-\vspace{10mm}
-
 \paragraph{Expectation Maximization}
 
-\vspace{5mm}
 bla
-\vspace{10mm}
 
@@
 
-\vspace{5mm}
 bla bla
-
-\vspace{10mm}
 

### 2017-05-31 thesis_report/draft_thesis.tex
Fixes: lines & LDA description

@@
 
+\usepackage{amsfonts}
+\usepackage{graphicx}
+
 \begin{document}
-
 \maketitle
@@
 In this chapter we will present some basic theoretic background about topic modeling. 
-To deal with extensive text body, machine learning researchers have developed topic modeling: 
-a suite of methods that analyze the words of the original text to discover the themes that run through the data and detect hidden semantic structures by analyzing a corpus. 
-By marking up the documents using these topics and by using the resulting structure, the model can be used for organization, finding similar documents, or any other similar tasks. 
-A topic is here defined as a probability distribution of words, meaning that certain words are more likely within a certain topic. 
-Since the topics emerge from the analysis of the original texts, topic modeling algorithms do not require any prior annotations or labeling of the documents.
+To deal with extensive text body, machine learning researchers have developed topic 
+modeling: a suite of methods that analyze the words of the original text to discover 
+the themes that run through the data and detect hidden semantic structures by 
+analyzing a corpus. By marking up the documents using these topics and by using the  resulting structure, the model can be used for organization, finding similar 
+documents, or any other similar tasks. A topic is here defined as a probability 
+distribution of words, meaning that certain words are more likely within a certain 
+topic. Since the topics emerge from the analysis of the original texts, topic 
+modeling algorithms do not require any prior annotations or labeling of the documents.
 
-In order to apply a topic model to our data, the first question we must answer is how to represent documents. 
-For understanding of natural language one must obviously preserve the order of the words in documents. 
-However, for many large-scale data mining tasks, it is sufficient to use a simple representation that loses all information about word order. 
-Given a collection of documents, the first task to perform is to identify the set of all words used at least once in at least one document. 
-This set is called the vocabulary. 
-Often, we reduce the size of the vocabulary by keeping only words that are used in at least a small percentage of the documents. 
-Words that are found only once are often misspellings or other mistakes. 
-Although the vocabulary is a set, we fix an arbitrary ordering for it so we can refer to word 1 through word $m$ where $m$ is the size of the vocabulary. 
-Once the vocabulary has been fixed, each document is represented as a vector with integer entries of length $m$. 
-If this vector is $x$ then its $j$-th component $x_j$ is the number of appearances of word $j$ in the document. 
-The length of the document is $n=\sum\limits_{j=1}^m x^j$.
+In order to apply a topic model to our data, the first question we must answer is 
+how to represent documents. For understanding of natural language one must 
+obviously preserve the order of the words in documents. However, for many 
+large-scale data mining tasks, it is sufficient to use a simple representation that 
+loses all information about word order. Given a collection of documents, the first 
+task to perform is to identify the set of all words used at least once in at least 
+one document. This set is called the vocabulary. Often, we reduce the size of the 
+vocabulary by keeping only words that are used in at least a small percentage of 
+the documents. Words that are found only once are often misspellings or other 
+mistakes. Although the vocabulary is a set, we fix an arbitrary ordering for it 
+so we can refer to word 1 through word $m$ where $m$ is the size of the vocabulary. 
+Once the vocabulary has been fixed, each document is represented as a vector with integer entries of length $m$. If this vector is $x$ then its $j$-th component 
+$x_j$ is the number of appearances of word $j$ in the document. The length of the 
+document is $n=\sum\limits_{j=1}^m x^j$.
 
-Many applications of if topic modeling also eliminate from the vocabulary so-called “stop” words. 
-These are words that are common in most documents and do not correspond to any particular subject matter. 
-They include pronouns (you, he, it), connectives (and, because, however), prepositions (to, of, before), and auxiliaries (have, been, can, should). 
-Stop words may also include generic nouns (amount, part, nothing) and verbs (do, have). 
-A collection of documents is represented as a two-dimensional matrix where each row describes a document and each column corresponds to a word. 
-Each entry in this matrix is an integer count; most entries are zero. 
-It makes sense to view each column as a feature.
+Many applications of if topic modeling also eliminate from the vocabulary so-called 
+“stop” words. These are words that are common in most documents and do not correspond 
+to any particular subject matter. They include pronouns (you, he, it), connectives 
+(and, because, however), prepositions (to, of, before), and auxiliaries 
+(have, been, can, should). Stop words may also include generic nouns 
+(amount, part, nothing) and verbs (do, have). A collection of documents is 
+represented as a two-dimensional matrix where each row describes a document 
+and each column corresponds to a word. Each entry in this matrix is an integer count; 
+most entries are zero. It makes sense to view each column as a feature.
 
@@
 
-- A word is defined as an item from a vocabulary indexed from ${1, ..., V}$, where V is the size of the vocabulary. 
-All words are represented as unit-basis vectors with one component equal to one and the rest equal to zero.
+- A word is defined as an item from a vocabulary indexed from ${1, ..., V}$, 
+where V is the size of the vocabulary. All words are represented as unit-basis 
+vectors with one component equal to one and the rest equal to zero.
 
-- A document is a collection of words denoted by $w = {w_1, ..., w_N}$, where $w_n$ is the $n$th word and $N$ is the total number of words in the collection.
+- A document is a collection of words denoted by $w = {w_1, ..., w_N}$, where 
+$w_n$ is the $n$th word and $N$ is the total number of words in the collection.
 
-- A corpus is a collection of documents in a dataset. 
-It is denoted $D = {w_1, ..., w_M}$, where $w_m$ is the $m$th document in the corpus and $M$ is the total number of documents.
+- A corpus is a collection of documents in a dataset. It is denoted 
+$D = {w_1, ..., w_M}$, where $w_m$ is the $m$th document in the corpus and $M$ 
+is the total number of documents.
 
-- Latent variables are variables that may not be directly observed, unlike observable variables. 
-Latent variables can instead be inferred from other observable variables.
+- Latent variables are variables that may not be directly observed, unlike 
+observable variables. Latent variables can instead be inferred from other 
+observable variables.
 
-- Polysemy is the capacity for a word to have multiple related meanings. 
-An example of this is the word “plant” which can mean a living organism of the kind exemplified by trees, herbs etc., or a place where an industrial or manufacturing process takes place.
+- Polysemy is the capacity for a word to have multiple related meanings. An example 
+of this is the word “plant” which can mean a living organism of the kind exemplified 
+by trees, herbs etc., or a place where an industrial or manufacturing process 
+takes place.
 
-- Synonymy is the capacity for several words to have similar meanings such as the words “buy” and “purchase”.
+- Synonymy is the capacity for several words to have similar meanings such as the 
+words “buy” and “purchase”.
 
@@
 
-Once we have a representation for individual documents, the natural next step is to select a model for a set of documents. 
-It is important to understand the difference between a representation and a model. 
-A representation is a way of encoding an entity as a data structure. 
-A model is an abstraction of a set of entities, for example a probability distribution. 
-Given a training set of documents, we will choose values for the parameters of a probabilistic model that make the training documents have high probability. 
-Then, given a test document, we can evaluate its probability according to the model. 
-The higher this probability is, the more similar the test document is to the training set.
+Once we have a representation for individual documents, the natural next step 
+is to select a model for a set of documents. It is important to understand the 
+difference between a representation and a model. A representation is a way of 
+encoding an entity as a data structure. A model is an abstraction of a set of 
+entities, for example a probability distribution. Given a training set of documents, 
+we will choose values for the parameters of a probabilistic model that make the 
+training documents have high probability. Then, given a test document, we can 
+evaluate its probability according to the model. The higher this probability is, 
+the more similar the test document is to the training set.
 
-The probability distribution that we use is the multinomial. 
-Mathematically, this distribution is:
+The probability distribution that we use is the multinomial. Mathematically, 
+this distribution is:
 
@@
 
-where the data $x$ are a vector of non-negative integers and the parameters $\theta$ are a real-valued vector. 
-Both vectors have the same length $m$. 
-Intuitively, $\theta_j$ is the probability of word $j$ while $x_j$ is the count of word $j$. 
-Each time word $j$ appears in the document it contributes an amount $\theta_j$ to the total probability, hence the term $\theta_j^{x_j}$. 
-The components of $\theta$ are non-negative and have unit $\sum\limits_{j=1}^m \theta_j = 1$. 
-A vector with these properties is called a unit vector.
+where the data $x$ are a vector of non-negative integers and the parameters 
+$\theta$ are a real-valued vector. Both vectors have the same length $m$. 
+Intuitively, $\theta_j$ is the probability of word $j$ while $x_j$ is the count 
+of word $j$. Each time word $j$ appears in the document it contributes an amount 
+$\theta_j$ to the total probability, hence the term $\theta_j^{x_j}$. 
+The components of $\theta$ are non-negative and have unit 
+$\sum\limits_{j=1}^m \theta_j = 1$. A vector with these properties is called 
+a unit vector.
 
-Like any discrete distribution, a multinomial has to sum to one, where the sum is over all possible data points. 
-Here, a data point is a document containing $n$ words.
-
-\subsection{Generative process}
-
-Suppose that we have a collection of documents, and we want to find an organization for these, i.e. we want to do unsupervised learning. 
-A common way to do unsupervised learning is to assume that the data were generated by some probabilistic process, and then to infer the parameters of this process. 
-The generative process is a specification of a parametrized family of distributions. 
-Learning is based on the principle of maximum likelihood, or some refinement of this principle such as maximum a posterior probability.
-
-\begin{enumerate}
-  \item Fix a multinomial distribution with parameter vector $\phi$ of length $V$
-  \item for each word in the document:
-  \begin{description}
-  \item draw a word $w$ according to $\phi$
-  \end{description}
-\end{enumerate}
-
-Above, step 1 sets up the probability distributions that are then used in step 2 to produce the observed training data. 
-A single multinomial distribution can only represent a category of closely related documents. 
-For a collection of documents of multiple categories/topics, a simple
-generative process is
-
-\begin{enumerate}
-\item Fix a multinomial $\alpha$ over categories $1$ to $K$\\
-for category number $1$ to category number $K$:
-\begin{description}
-\item   fix a multinomial with parameter vector $\phi_k$
-\end{description}
-
-\item for document number $1$ to document number $M$:
-\begin{description}
-\item draw a category $z$ according to $\alpha$
-\item for each word in the document:
-  	\begin{description}
-  	\item	draw a word $w$ according to $\phi_z$
-  	\end{description}
-\end{description}
-\end{enumerate}
-
-Note that $z$ is an integer between $1$ and $K$. 
-For each document, the value of $z$ is hidden, meaning that it exists conceptually, but it is never known, not even for training data. 
-The generative process above gives the following global probability distribution
-
-\begin{equation}
-f(x) = \sum\limits_{k=1}^K \alpha_k f(x;\phi_k)
-\end{equation}
-
-where $x$ is a document and $\phi_k$ is the parameter vector of the $k$-th multinomial. 
-In general, $x$ could be a data point of any type and $\phi_k$ could be the parameters of any appropriate distribution. 
-$K$ is called the number of components in the mixture model. 
-For each $k$, $f (x; \theta_k)$ is the distribution of component number $k$. 
-The scalar $\alpha_k$ is the proportion of component number $k$. 
-A distribution like this is called a mixture distribution. 
-In general, the components can be probability density functions, for example Gaussians, or probability mass functions, for example multinomials. 
-We will see later how to do maximum likelihood estimation for mixture distributions, using a technique called expectation-maximization.
+Like any discrete distribution, a multinomial has to sum to one, where the 
+sum is over all possible data points. Here, a data point is a document 
+containing $n$ words.
 
@@
 
-First, we’ll introduce some basic models for topic modeling. 
-The Latent Semantic Indexing, or LSI, was presented by Deerwester et al. in 1990. 
-The model manages to deal with the problem that multiple terms can refer to the same meaning, i.e. synonymy. 
-However, it is not as successful regarding polysemy. 
-The reason is that every term is represented as just one point in the so-called latent semantic space. 
-Furthermore, a word that can mean two or more different things is represented as a weighted average of the different meanings.
+First, we’ll introduce some basic models for topic modeling. The Latent Semantic 
+Indexing, or LSI, was presented by Deerwester et al. in 1990. The model manages to 
+deal with the problem that multiple terms can refer to the same meaning, i.e. 
+synonymy. However, it is not as successful regarding polysemy. The reason is that 
+every term is represented as just one point in the so-called latent semantic space. 
+Furthermore, a word that can mean two or more different things is represented as 
+a weighted average of the different meanings.
 
-After LSI was introduced, Hofmann presented the Probabilistic Latent Semantic Indexing, or PLSI model. 
-PLSI is a so-called topic model where each word in a document is generated from a single “topic” which results in that each document in a corpus can be represented with a topic distribution. 
-Later, in 2003 Blei et al. presented the Latent Dirichlet Allocation, or LDA.
-As opposed to PLSI, LDA is a statistically generative model for documents where each word in a document can be generated by all topics.
+After LSI was introduced, Hofmann presented the Probabilistic Latent Semantic 
+Indexing, or PLSI model. PLSI is a so-called topic model where each word in a 
+document is generated from a single “topic” which results in that each document 
+in a corpus can be represented with a topic distribution. Later, in 2003 Blei et 
+al. presented the Latent Dirichlet Allocation, or LDA. As opposed to PLSI, LDA is 
+a statistically generative model for documents where each word in a document can 
+be generated by all topics.
 
@@
 
-Latent Semantic Indexing was one of the earliest methods for finding relationships between documents and the words that occur in them. 
-In LSI a term-document matrix is created by analyzing the corpus, where the rows correspond to words and columns to documents. 
-Each element in this sparse matrix describes the number of times a word occurs in a document but this term count can also be weighted with for instance TF-IDF. 
-Letting each word represent a dimension in a very high dimensional space, a document can be seen as a vector with components corresponding to its weighted term counts.
+Latent Semantic Indexing was one of the earliest methods for finding relationships 
+between documents and the words that occur in them. In LSI a term-document matrix 
+is created by analyzing the corpus, where the rows correspond to words and columns 
+to documents. Each element in this sparse matrix describes the number of times a 
+word occurs in a document but this term count can also be weighted with for 
+instance TF-IDF. Letting each word represent a dimension in a very high dimensional 
+space, a document can be seen as a vector with components corresponding to its 
+weighted term counts.
 
-A low-rank approximation of the term-document matrix is created using Single Value Decomposition, SVD, which creates new dimensions, called concepts, as linear combinations of the original words. 
-This allows similarity measures and clustering methods by reducing the volume of the word space and thus making this space more densely populated.
+A low-rank approximation of the term-document matrix is created using Single Value 
+Decomposition, SVD, which creates new dimensions, called concepts, as linear 
+combinations of the original words. This allows similarity measures and clustering  methods by reducing the volume of the word space and thus making this space more 
+densely populated.
 
 The drawbacks with LSI are mainly the lack of a statistical foundation in the model. 
-LSI is based on linear algebra instead of probabilistic modeling leaving it with a small toolbox for what can be achieved using the model.
+LSI is based on linear algebra instead of probabilistic modeling leaving it with 
+a small toolbox for what can be achieved using the model.
 
@@
 
-Probabilistic Latent Semantic Indexing evolved from LSI and uses the same concept of finding a lower rank approximation of the term-document occurrence matrix. 
-The difference is that instead of being based on linear algebra, PLSI is based on a mixture decomposition using a latent class model. 
-PLSI associates an unobserved class variable $z$ with each document-word observation pair $(w, w)$. 
-This $z$ can be seen as a topic, since it is a probability distribution over words. 
-As a generative model, PLSI can be defined in the following way for a corpus $D$:
+Probabilistic Latent Semantic Indexing evolved from LSI and uses the same concept of 
+finding a lower rank approximation of the term-document occurrence matrix. 
+The difference is that instead of being based on linear algebra, PLSI is based on a 
+mixture decomposition using a latent class model. PLSI associates an unobserved 
+class variable $z$ with each document-word observation pair $(w, w)$. This $z$ can be seen as a topic, since it is a probability distribution over words. As a generative 
+model, PLSI can be defined in the following way for a corpus $D$:
 
@@
 
-The result from PLSI is that every document is represented as mixing proportions for the topics, given by $p(z|w)$. 
-Even though PLSI is generative for the analyzed corpus, it is not generative for new documents, which means is that there is no clear way of assigning probability to a document that is not part of the training data.
-Another problem is that the number of parameters in the model grows linearly with the number of documents.
+The result from PLSI is that every document is represented as mixing proportions for 
+the topics, given by $p(z|w)$. Even though PLSI is generative for the analyzed corpus, 
+it is not generative for new documents, which means is that there is no clear way of 
+assigning probability to a document that is not part of the training data. Another 
+problem is that the number of parameters in the model grows linearly with the number 
+of documents.
 
@@
 
-LDA is a topic model that was first presented as a graphical model for topic discovery by David Blei, Andrew Ng, and Michael I. Jordan in 2003. 
-The basic idea is that documents exhibit multiple topics. 
-LDA is a generative statistical model that allows sets of observations to be explained by unobserved groups that explain why some parts of the data are similar. 
-For example, if observations are words collected into documents, it posits that each document is a mixture of a small number of topics and that each word's occurrence is attributable to one of the document's topics.
-This is similar to PLSI, except that in LDA the topic distribution is assumed to have a Dirichlet prior (see 2.x.x). 
-In practice, this results in more reasonable mixtures of topics in a document. 
-The reduced document description result in PLSI is a vector where each element describes the mixing proportion for a topic. 
-A limitation with PLSI is that there is no generative (see 2.x) model for these proportions, making it difficult to handle unseen documents. 
-The Latent Dirichlet Allocation model tries to solve this limitation by setting a Dirichlet prior on the topic distribution.
+LDA is a topic model that was first presented as a graphical model for topic discovery 
+by David Blei, Andrew Ng, and Michael I. Jordan in 2003. The basic idea is that 
+documents exhibit multiple topics. LDA is a generative statistical model that allows 
+sets of observations to be explained by unobserved groups that explain why some parts 
+of the data are similar. For example, if observations are words collected into 
+documents, it posits that each document is a mixture of a small number of topics and 
+that each word's occurrence is attributable to one of the document's topics. This is 
+similar to PLSI, except that in LDA the topic distribution is assumed to have a 
+Dirichlet prior (see 2.3.3.1). In practice, this results in more reasonable mixtures 
+of topics in a document. The reduced document description result in PLSI is a vector 
+where each element describes the mixing proportion for a topic. A limitation with 
+PLSI is that there is no generative model for these proportions, making it difficult 
+to handle unseen documents. The Latent Dirichlet Allocation model tries to solve 
+this limitation by setting a Dirichlet prior on the topic distribution.
 
-The basic idea in LDA is that  we define a topic to be a Dirichlet distribution over a fixed vocabulary. 
-Technically, the model assumes that the topics are generated first, before the documents. 
-Now for each document in the collection, we generate the words in a two-stage process:
+Suppose that we have a collection of documents, and we want to find an organization 
+for these, i.e. we want to do unsupervised learning. A common way to do unsupervised 
+learning is to assume that the data were generated by some probabilistic process, 
+and then to infer the parameters of this process. The generative process is a 
+specification of a parametrized family of distributions. Learning is based on the 
+principle of maximum likelihood, or some refinement of this principle such as maximum 
+a posterior probability.
+
+The basic idea in LDA is that  we define a topic to be a Dirichlet distribution over 
+a fixed vocabulary. Technically, the model assumes that the topics are generated 
+first, before the documents. Now for each document in the collection, we generate 
+the words in a two-stage process:
 
@@
 This statistical model reflects the intuition that documents exhibit multiple topics. 
-Each document exhibits the topics with different proportion (step 1); 
-each word in each document is drawn from one of the topics (step 2b), where the selected topic is chosen from the per-document distribution over topics (step 2a). 
-All the documents in the corpus share the same set of topics, but each document exhibits those topics with different proportion - that’s the distinguishing characteristic of LDA.
-A more detailed explanation of the model follows in section 2.x.x.
+Each document exhibits the topics with different proportion (step 1); each word in 
+each document is drawn from one of the topics (step 2b), where the selected topic is 
+chosen from the per-document distribution over topics (step 2a). All the documents 
+in the corpus share the same set of topics, but each document exhibits those topics 
+with different proportion - that’s the distinguishing characteristic of LDA. A more 
+detailed explanation of the model follows in section 2.3.3.2.
 
@@
 
-The Dirichlet distribution is a way to model random probability mass functions (PMFs)\footnote{If you roll 1000 dice, the theoretical odds of any particular number showing up (i.e.
-a 1, 2, 3, 4, 5, or 6) are 1/6.
-However, you won’t get that exact distribution in a real experiment due to manufacturing defects. 
-If you have ten dice, each die will have its own probability mass function (PMF).} for finite sets. 
-It is also sometimes used as a prior in Bayesian statistics. 
-The Dirichlet is the multivariate generalization of the beta distribution. 
-It is an extension of the beta distribution for modeling probabilities for two or more events; 
-when the result of the event has only 2 values, the Dirichlet distribution is equal to the beta distribution.
+The Dirichlet distribution is a way to model random probability mass functions 
+(PMFs)\footnote{If you roll 1000 dice, the theoretical odds of any particular 
+number showing up (i.e. a 1, 2, 3, 4, 5, or 6) are 1/6. However, you won’t get 
+that exact distribution in a real experiment due to manufacturing defects. If you 
+have ten dice, each die will have its own probability mass function (PMF).} for 
+finite sets. It is also sometimes used as a prior in Bayesian statistics. The 
+Dirichlet is the multivariate generalization of the beta distribution. It is an 
+extension of the beta distribution for modeling probabilities for two or more events; 
+when the result of the event has only 2 values, the Dirichlet distribution is equal 
+to the beta distribution.
 
-The Dirichlet distribution is a prior for the multinomial distribution. 
-This means that if the prior distribution of the multinomial parameters is Dirichlet then the posterior distribution is also a Dirichlet distribution (with parameters different from those of the prior).
+The Dirichlet distribution is a prior for the multinomial distribution. This means 
+that if the prior distribution of the multinomial parameters is Dirichlet then the 
+posterior distribution is also a Dirichlet distribution (with parameters different 
+from those of the prior).
 
-The Dirichlet process is a way to model randomness of a probability mass function (PMF) with unlimited options (e.g. an unlimited amount of dice in a bag). 
-The process is similar Polya’s Urn, only instead of having a set number of ball colors you have an unlimited amount:
+The Dirichlet process is a way to model randomness of a probability mass function 
+(PMF) with unlimited options (e.g. an unlimited amount of dice in a bag). 
+The process is similar Polya’s Urn, only instead of having a set number of ball 
+colors you have an unlimited amount:
+
+\begin{itemize}
+\item Start out with an empty urn.
+\item Randomly pick a colored ball and place it in the urn.
+\item Then choose one option:
+\begin{enumerate}
+\item Randomly pick a colored ball and place it in the urn.
+\item Randomly remove a colored ball from the urn, then put it back with another 
+ball of the same color.
+\end{enumerate}
+\end{itemize}
+
+As the number of balls in the urn increase, the probability of picking a new color 
+decreases. The proportion of balls in the urn after an infinite amount of draws is 
+a Dirichlet process.
 
@@
 
-In LDA, each document is represented by a mixture of the topics, with weight θ2w for topic z in document w. 
-These weight have a Dirichlet prior, parameterized by a hyper-parameter α. 
-Each topic is a probability distribution over the vocabulary, with probability βwz for word w in topic z.
+In LDA, each document is represented by a mixture of the topics, with weight 
+$\theta_w^2$ for topic $z$ in document $w$. These weight have a Dirichlet prior, 
+parameterized by a hyper-parameter $\alpha$. Each topic is a probability 
+distribution over the vocabulary, with probability $\beta^w_z$ for word $w$ in 
+topic $z$.
+
+For each document $w$, in corpus $D$, the LDA generative process is as follows:
+
+\begin{enumerate}
+	\item Draw topic distribution  $\theta_w \sim Dir(\alpha)$
+	\item For each of the $N$ words $w_n$:
+	\begin{description}
+	\item (a) Draw a specific topic $z_n \sim Multinomial(\theta)$
+	\item (b) Draw a word $w_n \sim Multinomial(\beta_{zn})$
+	\end{description}
+\end{enumerate}
+
+As seen in step 1, each document contains topics in different proportions, determined 
+by the scaling parameter $\alpha$. The individual words are drawn from one of the $k$ 
+topics in step (b), where the probability of each word within a topic is parameterized 
+by a $k \times V$ matrix , where $V$ is the size of the specified vocabulary. The 
+most probable words in each topic could be used to identify the topic and gives an 
+intuitive description for the topic.
+
+The key difference in LDA compared to PLSI is that the process outlined above actually 
+is generative for documents. This means that, given a new document, one can use the 
+parameters learned previously to estimate the topic distribution $\theta$ for this 
+new document.
+
+A limitation with the standard LDA model is the fix vocabulary. This means that new 
+words cannot enter the model and that you have to know a priori what words will model 
+the corpus effectively. A setting where this could be problematic is when analyzing 
+twitter data where new words in the form of slang, names and hashtags emerge over 
+time. Another limitation is the fact that one has to state the number of topics 
+the model should use. This is not a big issue, but could lead to some of the 
+resulting topics to be insignificant.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{LDA_standard_model.png}
+\caption{Plate notation of the standard LDA model}
+\end{figure}
 
@@
 
-bla
+The Expectation Maximization, or EM, algorithm is an approach to deriving an algorithm 
+for approximately obtaining maximum likelihood of variables in a statistical model. 
+Normally one obtains a maximum likelihood solution by taking partial derivatives of 
+the likelihood function with respect to all variables, setting these derivatives to 
+zero and solving the equations simultaneously.
+
+Due to latent variables it is not always possible to solve the equations directly and 
+instead one typically gets two sets of equations that depend on each other. The EM 
+algorithm uses the idea that one could choose starting values for the latent variables 
+in the first set of equations, use the result in the second set of equations, and then 
+alternate between the two sets until convergence.
+
+Consider a statistical model accompanied by a set of observed data $X$, a set of 
+latent data $Z$, a set of latent variables $\theta$ and a likelihood function 
+$L(\theta \mid X, Z)$. The marginal likelihood of the observed data is then
+
+\begin{equation}
+L(\theta \mid X) = p(X \mid \theta) = \sum\limits_{Z} p(X, Z \mid \theta)
+\end{equation}
+
+which determines the maximum likelihood estimate of the latent variables. The sum is 
+however often intractable and the EM algorithm solves this problem by iterating the 
+following two steps:
+
+\begin{itemize}
+\item \textbf{Expectation step (E - step)}: For the current estimate of the parameters 
+$\theta^t$, calculate the expected value of the log likelihood function:
+\begin{equation}
+Q(\theta \mid \theta^t) \leftarrow \mathbb{E}_{Z \mid X, \theta^t} [\log(L(\theta \mid X, Z))]
+\end{equation}
+\item \textbf{Maximization step (M - step)} Maximize the expected value function 
+with regard to the parameters:
+\begin{equation}
+\theta^{t + 1} \leftarrow arg \max\limits_{\theta} Q(\theta \mid \theta^t)
+\end{equation}
+\end{itemize}
 
@@
 
-bla bla
+Variational inference can be seen as an extension of the EM algorithm and is used to 
+approximate intractable integrals. The goal of variational inference is to approximate 
+an intractable probability distribution $p$, with a tractable one $q$, in a way that 
+makes them as close as possible given a similarity measure. In this thesis, 
+variational inference is used to approximate the posterior distribution of latent 
+variables.
+
+For a bayesian model where x = x 1:n are observations and z = z 1:m are 
+latent variables, the posterior distribution is
+
+\begin{equation}
+p(x \mid z) = \frac{p(x \mid z) p(z)}{\int\limits_{z} p(x \mid z)p(z)}
+\end{equation}
+
+For many models, this distribution is intractable due to the integral in the 
+denominator. The posterior can be computed up to a constant, but the normalization 
+constant cannot be computed. Variational inference methods can be used to approximate 
+this integral. Applying variational inference to posterior distributions is sometimes 
+called variational Bayes but is only an instance of a more general problem that 
+variational inference solves.
 

### 2017-06-03 thesis_report/draft_thesis.tex
Auto wrap

@@
 \begin{abstract}
-This is a simple paragraph at the beginning of the 
-document. 
+This is a simple paragraph at the beginning of the document. 
 A brief introduction about the main subject.
@@
 
-In this chapter we will present some basic theoretic background about topic modeling. 
-To deal with extensive text body, machine learning researchers have developed topic 
-modeling: a suite of methods that analyze the words of the original text to discover 
-the themes that run through the data and detect hidden semantic structures by 
-analyzing a corpus. By marking up the documents using these topics and by using the  resulting structure, the model can be used for organization, finding similar 
-documents, or any other similar tasks. A topic is here defined as a probability 
-distribution of words, meaning that certain words are more likely within a certain 
-topic. Since the topics emerge from the analysis of the original texts, topic 
-modeling algorithms do not require any prior annotations or labeling of the documents.
+In this chapter we will present some basic theoretic background about topic
+modeling. To deal with extensive text body, machine learning researchers have
+developed topic modeling: a suite of methods that analyze the words of the
+original text to discover the themes that run through the data and detect
+hidden semantic structures by analyzing a corpus. By marking up the documents
+using these topics and by using the resulting structure, the model can be used
+for organization, finding similar documents, or any other similar tasks. A
+topic is here defined as a probability distribution of words, meaning that
+certain words are more likely within a certain topic. Since the topics emerge
+from the analysis of the original texts, topic modeling algorithms do not
+require any prior annotations or labeling of the documents.
 
-In order to apply a topic model to our data, the first question we must answer is 
-how to represent documents. For understanding of natural language one must 
+In order to apply a topic model to our data, the first question we must answer
+is how to represent documents. For understanding of natural language one must
 obviously preserve the order of the words in documents. However, for many
-large-scale data mining tasks, it is sufficient to use a simple representation that 
-loses all information about word order. Given a collection of documents, the first 
-task to perform is to identify the set of all words used at least once in at least 
-one document. This set is called the vocabulary. Often, we reduce the size of the 
-vocabulary by keeping only words that are used in at least a small percentage of 
-the documents. Words that are found only once are often misspellings or other 
-mistakes. Although the vocabulary is a set, we fix an arbitrary ordering for it 
-so we can refer to word 1 through word $m$ where $m$ is the size of the vocabulary. 
-Once the vocabulary has been fixed, each document is represented as a vector with integer entries of length $m$. If this vector is $x$ then its $j$-th component 
-$x_j$ is the number of appearances of word $j$ in the document. The length of the 
-document is $n=\sum\limits_{j=1}^m x^j$.
+large-scale data mining tasks, it is sufficient to use a simple representation
+that loses all information about word order. Given a collection of documents,
+the first task to perform is to identify the set of all words used at least
+once in at least one document. This set is called the vocabulary. Often, we
+reduce the size of the vocabulary by keeping only words that are used in at
+least a small percentage of the documents. Words that are found only once are
+often misspellings or other mistakes. Although the vocabulary is a set, we fix
+an arbitrary ordering for it so we can refer to word 1 through word $m$ where
+$m$ is the size of the vocabulary. Once the vocabulary has been fixed, each
+document is represented as a vector with integer entries of length $m$. If this
+vector is $x$ then its $j$-th component $x_j$ is the number of appearances of
+word $j$ in the document. The length of the document is $n=\sum\limits_{j=1}^m
+x^j$.
 
-Many applications of if topic modeling also eliminate from the vocabulary so-called 
-“stop” words. These are words that are common in most documents and do not correspond 
-to any particular subject matter. They include pronouns (you, he, it), connectives 
-(and, because, however), prepositions (to, of, before), and auxiliaries 
-(have, been, can, should). Stop words may also include generic nouns 
-(amount, part, nothing) and verbs (do, have). A collection of documents is 
-represented as a two-dimensional matrix where each row describes a document 
-and each column corresponds to a word. Each entry in this matrix is an integer count; 
-most entries are zero. It makes sense to view each column as a feature.
+Many applications of if topic modeling also eliminate from the vocabulary so-
+called “stop” words. These are words that are common in most documents and do
+not correspond to any particular subject matter. They include pronouns (you,
+he, it), connectives (and, because, however), prepositions (to, of, before),
+and auxiliaries (have, been, can, should). Stop words may also include generic
+nouns (amount, part, nothing) and verbs (do, have). A collection of documents
+is represented as a two-dimensional matrix where each row describes a document
+and each column corresponds to a word. Each entry in this matrix is an integer
+count; most entries are zero. It makes sense to view each column as a feature.
 
@@
 
-- A corpus is a collection of documents in a dataset. It is denoted 
-$D = {w_1, ..., w_M}$, where $w_m$ is the $m$th document in the corpus and $M$ 
-is the total number of documents.
+- A corpus is a collection of documents in a dataset. It is denoted $D = {w_1,
+..., w_M}$, where $w_m$ is the $m$th document in the corpus and $M$ is the
+total number of documents.
 
@@
 
-- Polysemy is the capacity for a word to have multiple related meanings. An example 
-of this is the word “plant” which can mean a living organism of the kind exemplified 
-by trees, herbs etc., or a place where an industrial or manufacturing process 
-takes place.
+- Polysemy is the capacity for a word to have multiple related meanings. An
+example of this is the word “plant” which can mean a living organism of the
+kind exemplified by trees, herbs etc., or a place where an industrial or
+manufacturing process takes place.
 
-- Synonymy is the capacity for several words to have similar meanings such as the 
-words “buy” and “purchase”.
+- Synonymy is the capacity for several words to have similar meanings such as
+the words “buy” and “purchase”.
 
 \subsection{The Multinomial Distribution}
-
 Once we have a representation for individual documents, the natural next step
@@
 encoding an entity as a data structure. A model is an abstraction of a set of
-entities, for example a probability distribution. Given a training set of documents, 
-we will choose values for the parameters of a probabilistic model that make the 
-training documents have high probability. Then, given a test document, we can 
-evaluate its probability according to the model. The higher this probability is, 
-the more similar the test document is to the training set.
+entities, for example a probability distribution. Given a training set of
+documents, we will choose values for the parameters of a probabilistic model
+that make the training documents have high probability. Then, given a test
+document, we can evaluate its probability according to the model. The higher
+this probability is, the more similar the test document is to the training set.
 
@@
 \begin{equation}
-p(x;\theta) = \left(\frac{n!}{\prod\limits_{j=1}^m x^j!}\right)\left(\prod\limits_{j=1}^m \theta_j^{x_j}\right)
+p(x;\theta) = \left(\frac{n!}{\prod\limits_{j=1}^m x^j!}\right)\left
+(\prod\limits_{j=1}^m \theta_j^{x_j}\right)
 \end{equation}
@@
 of word $j$. Each time word $j$ appears in the document it contributes an amount
-$\theta_j$ to the total probability, hence the term $\theta_j^{x_j}$. 
-The components of $\theta$ are non-negative and have unit 
-$\sum\limits_{j=1}^m \theta_j = 1$. A vector with these properties is called 
-a unit vector.
+$\theta_j$ to the total probability, hence the term $\theta_j^{x_j}$. The
+components of $\theta$ are non-negative and have unit $\sum\limits_{j=1}^m
+\theta_j = 1$. A vector with these properties is called a unit vector.
 
-Like any discrete distribution, a multinomial has to sum to one, where the 
-sum is over all possible data points. Here, a data point is a document 
-containing $n$ words.
+Like any discrete distribution, a multinomial has to sum to one, where the sum
+is over all possible data points. Here, a data point is a document containing
+$n$ words.
 
@@
 First, we’ll introduce some basic models for topic modeling. The Latent Semantic
-Indexing, or LSI, was presented by Deerwester et al. in 1990. The model manages to 
-deal with the problem that multiple terms can refer to the same meaning, i.e. 
-synonymy. However, it is not as successful regarding polysemy. The reason is that 
-every term is represented as just one point in the so-called latent semantic space. 
-Furthermore, a word that can mean two or more different things is represented as 
-a weighted average of the different meanings.
+Indexing, or LSI, was presented by Deerwester et al. in 1990. The model manages
+to deal with the problem that multiple terms can refer to the same meaning,
+i.e. synonymy. However, it is not as successful regarding polysemy. The reason
+is that every term is represented as just one point in the so-called latent
+semantic space. Furthermore, a word that can mean two or more different things
+is represented as a weighted average of the different meanings.
 
@@
 in a corpus can be represented with a topic distribution. Later, in 2003 Blei et
-al. presented the Latent Dirichlet Allocation, or LDA. As opposed to PLSI, LDA is 
-a statistically generative model for documents where each word in a document can 
-be generated by all topics.
+al. presented the Latent Dirichlet Allocation, or LDA. As opposed to PLSI, LDA
+is a statistically generative model for documents where each word in a document
+can be generated by all topics.
 
@@
 
-Latent Semantic Indexing was one of the earliest methods for finding relationships 
-between documents and the words that occur in them. In LSI a term-document matrix 
-is created by analyzing the corpus, where the rows correspond to words and columns 
-to documents. Each element in this sparse matrix describes the number of times a 
-word occurs in a document but this term count can also be weighted with for 
-instance TF-IDF. Letting each word represent a dimension in a very high dimensional 
-space, a document can be seen as a vector with components corresponding to its 
-weighted term counts.
+Latent Semantic Indexing was one of the earliest methods for finding
+relationships between documents and the words that occur in them. In LSI a
+term-document matrix is created by analyzing the corpus, where the rows
+correspond to words and columns to documents. Each element in this sparse
+matrix describes the number of times a word occurs in a document but this term
+count can also be weighted with for instance TF-IDF. Letting each word
+represent a dimension in a very high dimensional space, a document can be seen
+as a vector with components corresponding to its weighted term counts.
 
-A low-rank approximation of the term-document matrix is created using Single Value 
-Decomposition, SVD, which creates new dimensions, called concepts, as linear 
-combinations of the original words. This allows similarity measures and clustering  methods by reducing the volume of the word space and thus making this space more 
-densely populated.
+A low-rank approximation of the term-document matrix is created using Single
+Value Decomposition, SVD, which creates new dimensions, called concepts, as
+linear combinations of the original words. This allows similarity measures and
+clustering methods by reducing the volume of the word space and thus making
+this space more densely populated.
 
-The drawbacks with LSI are mainly the lack of a statistical foundation in the model. 
-LSI is based on linear algebra instead of probabilistic modeling leaving it with 
-a small toolbox for what can be achieved using the model.
+The drawbacks with LSI are mainly the lack of a statistical foundation in the
+model. LSI is based on linear algebra instead of probabilistic modeling leaving
+it with a small toolbox for what can be achieved using the model.
 
@@
 
-Probabilistic Latent Semantic Indexing evolved from LSI and uses the same concept of 
-finding a lower rank approximation of the term-document occurrence matrix. 
-The difference is that instead of being based on linear algebra, PLSI is based on a 
-mixture decomposition using a latent class model. PLSI associates an unobserved 
-class variable $z$ with each document-word observation pair $(w, w)$. This $z$ can be seen as a topic, since it is a probability distribution over words. As a generative 
-model, PLSI can be defined in the following way for a corpus $D$:
+Probabilistic Latent Semantic Indexing evolved from LSI and uses the same
+concept of finding a lower rank approximation of the term-document occurrence
+matrix. The difference is that instead of being based on linear algebra, PLSI
+is based on a mixture decomposition using a latent class model. PLSI associates
+an unobserved class variable $z$ with each document-word observation pair $(w,
+w)$. This $z$ can be seen as a topic, since it is a probability distribution
+over words. As a generative model, PLSI can be defined in the following way for
+a corpus $D$:
 
@@
 
-The result from PLSI is that every document is represented as mixing proportions for 
-the topics, given by $p(z|w)$. Even though PLSI is generative for the analyzed corpus, 
-it is not generative for new documents, which means is that there is no clear way of 
-assigning probability to a document that is not part of the training data. Another 
-problem is that the number of parameters in the model grows linearly with the number 
-of documents.
+The result from PLSI is that every document is represented as mixing proportions
+for the topics, given by $p(z|w)$. Even though PLSI is generative for the
+analyzed corpus, it is not generative for new documents, which means is that
+there is no clear way of assigning probability to a document that is not part
+of the training data. Another problem is that the number of parameters in the
+model grows linearly with the number of documents.
 
@@
 
-LDA is a topic model that was first presented as a graphical model for topic discovery 
-by David Blei, Andrew Ng, and Michael I. Jordan in 2003. The basic idea is that 
-documents exhibit multiple topics. LDA is a generative statistical model that allows 
-sets of observations to be explained by unobserved groups that explain why some parts 
-of the data are similar. For example, if observations are words collected into 
-documents, it posits that each document is a mixture of a small number of topics and 
-that each word's occurrence is attributable to one of the document's topics. This is 
-similar to PLSI, except that in LDA the topic distribution is assumed to have a 
-Dirichlet prior (see 2.3.3.1). In practice, this results in more reasonable mixtures 
-of topics in a document. The reduced document description result in PLSI is a vector 
-where each element describes the mixing proportion for a topic. A limitation with 
-PLSI is that there is no generative model for these proportions, making it difficult 
-to handle unseen documents. The Latent Dirichlet Allocation model tries to solve 
-this limitation by setting a Dirichlet prior on the topic distribution.
+LDA is a topic model that was first presented as a graphical model for topic
+discovery by David Blei, Andrew Ng, and Michael I. Jordan in 2003. The basic
+idea is that documents exhibit multiple topics. LDA is a generative statistical
+model that allows sets of observations to be explained by unobserved groups
+that explain why some parts of the data are similar. For example, if
+observations are words collected into documents, it posits that each document
+is a mixture of a small number of topics and that each word's occurrence is
+attributable to one of the document's topics. This is similar to PLSI, except
+that in LDA the topic distribution is assumed to have a Dirichlet prior (see
+2.3.3.1). In practice, this results in more reasonable mixtures of topics in a
+document. The reduced document description result in PLSI is a vector where
+each element describes the mixing proportion for a topic. A limitation with
+PLSI is that there is no generative model for these proportions, making it
+difficult to handle unseen documents. The Latent Dirichlet Allocation model
+tries to solve this limitation by setting a Dirichlet prior on the topic
+distribution.
 
-Suppose that we have a collection of documents, and we want to find an organization 
-for these, i.e. we want to do unsupervised learning. A common way to do unsupervised 
-learning is to assume that the data were generated by some probabilistic process, 
-and then to infer the parameters of this process. The generative process is a 
-specification of a parametrized family of distributions. Learning is based on the 
-principle of maximum likelihood, or some refinement of this principle such as maximum 
-a posterior probability.
+Suppose that we have a collection of documents, and we want to find an
+organization for these, i.e. we want to do unsupervised learning. A common way
+to do unsupervised learning is to assume that the data were generated by some
+probabilistic process, and then to infer the parameters of this process. The
+generative process is a specification of a parametrized family of
+distributions. Learning is based on the principle of maximum likelihood, or
+some refinement of this principle such as maximum a posterior probability.
 
-The basic idea in LDA is that  we define a topic to be a Dirichlet distribution over 
-a fixed vocabulary. Technically, the model assumes that the topics are generated 
-first, before the documents. Now for each document in the collection, we generate 
-the words in a two-stage process:
+The basic idea in LDA is that we define a topic to be a Dirichlet distribution
+over a fixed vocabulary. Technically, the model assumes that the topics are
+generated first, before the documents. Now for each document in the collection,
+we generate the words in a two-stage process:
 
@@
 \begin{description}
-	\item (b) Randomly choose a word from the corresponding distribution over the vocabulary.
+	\item (b) Randomly choose a word from the corresponding distribution over the 
+	vocabulary.
 \end{description}
@@
 
-This statistical model reflects the intuition that documents exhibit multiple topics. 
-Each document exhibits the topics with different proportion (step 1); each word in 
-each document is drawn from one of the topics (step 2b), where the selected topic is 
-chosen from the per-document distribution over topics (step 2a). All the documents 
-in the corpus share the same set of topics, but each document exhibits those topics 
-with different proportion - that’s the distinguishing characteristic of LDA. A more 
-detailed explanation of the model follows in section 2.3.3.2.
+This statistical model reflects the intuition that documents exhibit multiple
+topics. Each document exhibits the topics with different proportion (step 1);
+each word in each document is drawn from one of the topics (step 2b), where the
+selected topic is chosen from the per-document distribution over topics (step
+2a). All the documents in the corpus share the same set of topics, but each
+document exhibits those topics with different proportion - that’s the
+distinguishing characteristic of LDA. A more detailed explanation of the model
+follows in section 2.3.3.2.
 
@@
 number showing up (i.e. a 1, 2, 3, 4, 5, or 6) are 1/6. However, you won’t get
-that exact distribution in a real experiment due to manufacturing defects. If you 
-have ten dice, each die will have its own probability mass function (PMF).} for 
-finite sets. It is also sometimes used as a prior in Bayesian statistics. The 
-Dirichlet is the multivariate generalization of the beta distribution. It is an 
-extension of the beta distribution for modeling probabilities for two or more events; 
-when the result of the event has only 2 values, the Dirichlet distribution is equal 
-to the beta distribution.
+that exact distribution in a real experiment due to manufacturing defects. If
+you have ten dice, each die will have its own probability mass function (PMF).}
+for finite sets. It is also sometimes used as a prior in Bayesian statistics.
+The Dirichlet is the multivariate generalization of the beta distribution. It
+is an extension of the beta distribution for modeling probabilities for two or
+more events; when the result of the event has only 2 values, the Dirichlet
+distribution is equal to the beta distribution.
 
-The Dirichlet distribution is a prior for the multinomial distribution. This means 
-that if the prior distribution of the multinomial parameters is Dirichlet then the 
-posterior distribution is also a Dirichlet distribution (with parameters different 
-from those of the prior).
+The Dirichlet distribution is a prior for the multinomial distribution. This
+means that if the prior distribution of the multinomial parameters is Dirichlet
+then the posterior distribution is also a Dirichlet distribution (with
+parameters different from those of the prior).
 
-The Dirichlet process is a way to model randomness of a probability mass function 
-(PMF) with unlimited options (e.g. an unlimited amount of dice in a bag). 
-The process is similar Polya’s Urn, only instead of having a set number of ball 
-colors you have an unlimited amount:
+The Dirichlet process is a way to model randomness of a probability mass
+function (PMF) with unlimited options (e.g. an unlimited amount of dice in a
+bag). The process is similar Polya’s Urn, only instead of having a set number
+of ball colors you have an unlimited amount:
 
@@
 
-As the number of balls in the urn increase, the probability of picking a new color 
-decreases. The proportion of balls in the urn after an infinite amount of draws is 
-a Dirichlet process.
+As the number of balls in the urn increase, the probability of picking a new
+color decreases. The proportion of balls in the urn after an infinite amount of
+draws is a Dirichlet process.
 
@@
 
-As seen in step 1, each document contains topics in different proportions, determined 
-by the scaling parameter $\alpha$. The individual words are drawn from one of the $k$ 
-topics in step (b), where the probability of each word within a topic is parameterized 
-by a $k \times V$ matrix , where $V$ is the size of the specified vocabulary. The 
-most probable words in each topic could be used to identify the topic and gives an 
-intuitive description for the topic.
+As seen in step 1, each document contains topics in different proportions,
+determined by the scaling parameter $\alpha$. The individual words are drawn
+from one of the $k$ topics in step (b), where the probability of each word
+within a topic is parameterized by a $k \times V$ matrix , where $V$ is the
+size of the specified vocabulary. The most probable words in each topic could
+be used to identify the topic and gives an intuitive description for the topic.
 
-The key difference in LDA compared to PLSI is that the process outlined above actually 
-is generative for documents. This means that, given a new document, one can use the 
-parameters learned previously to estimate the topic distribution $\theta$ for this 
-new document.
+The key difference in LDA compared to PLSI is that the process outlined above
+actually is generative for documents. This means that, given a new document,
+one can use the parameters learned previously to estimate the topic
+distribution $\theta$ for this new document.
 
-A limitation with the standard LDA model is the fix vocabulary. This means that new 
-words cannot enter the model and that you have to know a priori what words will model 
-the corpus effectively. A setting where this could be problematic is when analyzing 
-twitter data where new words in the form of slang, names and hashtags emerge over 
-time. Another limitation is the fact that one has to state the number of topics 
-the model should use. This is not a big issue, but could lead to some of the 
-resulting topics to be insignificant.
+A limitation with the standard LDA model is the fix vocabulary. This means that
+new words cannot enter the model and that you have to know a priori what words
+will model the corpus effectively. A setting where this could be problematic is
+when analyzing twitter data where new words in the form of slang, names and
+hashtags emerge over time. Another limitation is the fact that one has to state
+the number of topics the model should use. This is not a big issue, but could
+lead to some of the resulting topics to be insignificant.
 
@@
 
-The Expectation Maximization, or EM, algorithm is an approach to deriving an algorithm 
-for approximately obtaining maximum likelihood of variables in a statistical model. 
-Normally one obtains a maximum likelihood solution by taking partial derivatives of 
-the likelihood function with respect to all variables, setting these derivatives to 
-zero and solving the equations simultaneously.
+The Expectation Maximization, or EM, algorithm is an approach to deriving an
+algorithm for approximately obtaining maximum likelihood of variables in a
+statistical model. Normally one obtains a maximum likelihood solution by taking
+partial derivatives of the likelihood function with respect to all variables,
+setting these derivatives to zero and solving the equations simultaneously.
 
-Due to latent variables it is not always possible to solve the equations directly and 
-instead one typically gets two sets of equations that depend on each other. The EM 
-algorithm uses the idea that one could choose starting values for the latent variables 
-in the first set of equations, use the result in the second set of equations, and then 
-alternate between the two sets until convergence.
+Due to latent variables it is not always possible to solve the equations
+directly and instead one typically gets two sets of equations that depend on
+each other. The EM algorithm uses the idea that one could choose starting
+values for the latent variables in the first set of equations, use the result
+in the second set of equations, and then alternate between the two sets until
+convergence.
 
@@
 
-which determines the maximum likelihood estimate of the latent variables. The sum is 
-however often intractable and the EM algorithm solves this problem by iterating the 
-following two steps:
+which determines the maximum likelihood estimate of the latent variables. The
+sum is however often intractable and the EM algorithm solves this problem by
+iterating the following two steps:
 
@@
 \begin{equation}
-Q(\theta \mid \theta^t) \leftarrow \mathbb{E}_{Z \mid X, \theta^t} [\log(L(\theta \mid X, Z))]
+Q(\theta \mid \theta^t) \leftarrow \mathbb{E}_{Z \mid X, \theta^t}
+ [\log(L(\theta \mid X, Z))]
 \end{equation}
@@
 
-Variational inference can be seen as an extension of the EM algorithm and is used to 
-approximate intractable integrals. The goal of variational inference is to approximate 
-an intractable probability distribution $p$, with a tractable one $q$, in a way that 
-makes them as close as possible given a similarity measure. In this thesis, 
-variational inference is used to approximate the posterior distribution of latent 
-variables.
+Variational inference can be seen as an extension of the EM algorithm and is
+used to approximate intractable integrals. The goal of variational inference is
+to approximate an intractable probability distribution $p$, with a tractable
+one $q$, in a way that makes them as close as possible given a similarity
+measure. In this thesis, variational inference is used to approximate the
+posterior distribution of latent variables.
 
-For a bayesian model where x = x 1:n are observations and z = z 1:m are 
-latent variables, the posterior distribution is
+For a bayesian model where x = x 1:n are observations and z = z 1:m are latent
+variables, the posterior distribution is
 
@@
 For many models, this distribution is intractable due to the integral in the
-denominator. The posterior can be computed up to a constant, but the normalization 
-constant cannot be computed. Variational inference methods can be used to approximate 
-this integral. Applying variational inference to posterior distributions is sometimes 
-called variational Bayes but is only an instance of a more general problem that 
-variational inference solves.
+denominator. The posterior can be computed up to a constant, but the
+normalization constant cannot be computed. Variational inference methods can be
+used to approximate this integral. Applying variational inference to posterior
+distributions is sometimes called variational Bayes but is only an instance of
+a more general problem that variational inference solves.
 

### 2017-06-05 thesis_report/draft_thesis.tex
Edit: LDA model

@@
 \usepackage{graphicx}
+\usepackage{biblatex}
+\addbibresource{sample.bib}
 
@@
 \subsection{The Multinomial Distribution}
+
 Once we have a representation for individual documents, the natural next step
@@
 
+LDA is a probabilistic model of text documents, which assumes a collection of 
+K topics. Each topic defines a multinomial distribution over the vocabulary 
+and is assumed to have been drawn from a Dirichlet 
+$\beta_k \sim Dirichlet(\eta)$.
+
 In LDA, each document is represented by a mixture of the topics, with weight
@@
 be used to identify the topic and gives an intuitive description for the topic.
+
+We can analyze a corpus of documents with LDA by examining the posterior 
+distribution of topics $\beta$, topic proportions $\theta$ and topic 
+assignments $z$ conditioned on the documents. This reveals latent structure 
+in the collection that can be used for prediction or data exploration. This 
+posterior can't be computed directly; it is usually approximated using Markov 
+Chain Monte Carlo (MCMC) or variational inference. Both methods are effective, 
+but also present significant computational challenges in large data sets \cite{onlineLDAvb}. In our implementation, we're using the online variational 
+LDA model, which is described in section 2.2.3.4.
 

### 2017-06-06 thesis_report/draft_thesis.tex
Fix: variational inference

@@
 \usepackage{graphicx}
-\usepackage{biblatex}
-\addbibresource{sample.bib}
+\usepackage{cite}
+\usepackage{algorithm2e}
 
 \begin{document}
+
 \maketitle
@@
 distribution of topics $\beta$, topic proportions $\theta$ and topic
-assignments $z$ conditioned on the documents. This reveals latent structure 
-in the collection that can be used for prediction or data exploration. This 
+assignments $z$ conditioned on the documents. This reveals latent structure in
+the collection that can be used for prediction or data exploration. This
 posterior can't be computed directly; it is usually approximated using Markov
 Chain Monte Carlo (MCMC) or variational inference. Both methods are effective,
-but also present significant computational challenges in large data sets \cite{onlineLDAvb}. In our implementation, we're using the online variational 
+but also present significant computational challenges in large data sets
+~\cite{onlineLDAvb}. In our implementation, we're using the online variational
 LDA model, which is described in section 2.2.3.4.
@@
 \begin{itemize}
-\item \textbf{Expectation step (E - step)}: For the current estimate of the parameters 
-$\theta^t$, calculate the expected value of the log likelihood function:
+\item \textbf{Expectation step (E - step)}: For the current estimate of the 
+parameters $\theta^t$, calculate the expected value of the log likelihood function:
 \begin{equation}
@@
 
-Variational inference can be seen as an extension of the EM algorithm and is
-used to approximate intractable integrals. The goal of variational inference is
-to approximate an intractable probability distribution $p$, with a tractable
-one $q$, in a way that makes them as close as possible given a similarity
-measure. In this thesis, variational inference is used to approximate the
-posterior distribution of latent variables.
+Learning the various distributions (the set of topics, their associated word
+probabilities, the topic of each word, and the particular topic mixture of each
+document) is a problem of Bayesian inference. In the original paper it's being
+used a variational Bayes approximation of the posterior distribution;
+~\cite{blei2003latent} alternative inference techniques use Gibbs sampling and
+expectation propagation. The goal of variational inference is to approximate an
+intractable probability distribution $p$, with a tractable one $q$, in a way
+that makes them as close as possible given a similarity measure. In this thesis,
+variational inference is used to approximate the posterior distribution of
+latent variables. A new distribution over the hidden variables $q(z, \beta)$
+(called the variational distribution) is  introduced. This new distribution has
+properties such that it can be efficiently computed.
 
-For a bayesian model where x = x 1:n are observations and z = z 1:m are latent
-variables, the posterior distribution is
+The variational distribution is a function of a set of free parameters that are optimized such that the variational distribution is as close as possible to the 
+actual target posterior distribution where closeness is measured in terms of KL divergence.
+Minimizing the KL divergence between the variational distribution and the target
+posterior is equivalent to maximizing the Evidence Lower BOund (ELBO) which is
 
 \begin{equation}
-p(x \mid z) = \frac{p(x \mid z) p(z)}{\int\limits_{z} p(x \mid z)p(z)}
+L(q) = E_q [log p(x, z, \beta)] -  E_q [log q(z, \beta)]  
 \end{equation}
 
-For many models, this distribution is intractable due to the integral in the
-denominator. The posterior can be computed up to a constant, but the
-normalization constant cannot be computed. Variational inference methods can be
-used to approximate this integral. Applying variational inference to posterior
-distributions is sometimes called variational Bayes but is only an instance of
-a more general problem that variational inference solves.
+The variational distribution has the property that it can be efficiently
+computed. This is done by making each hidden variable independent of each other.
+
+\begin{equation}
+q(z, \beta) = q(\beta \mid \lambda) \prod\limits_{n=1}^N \prod\limits_{j=1}^J q(z_{nj} \mid \phi_{nj})   
+\end{equation}
+
+The posterior over the per-word topic assignments $z$ is parameterized by
+$\phi$, the posterior over per-document topic weights $\theta$ is parameterized
+by $\gamma$, and the posterior over the topics $\beta$ is parameterized by
+$\lambda$. Furthermore, each hidden variable is governed by its own variational
+parameter so the variational parameters $\lambda$ governs the global variables
+$\beta$ and the variational parameters $\phi_n$ govern the local variables $z_n
+q(\beta \mid \lambda)$ and $q(z_{nj} \mid \phi_{nj})$ take the same form as the
+complete conditionals $p(\beta \mid x, z, \alpha)$ and $p(z_{nj} \mid x_n, z_{n,
+-j}, \beta)$, but the natural parameters are now $\lambda$ and $\phi_{nj}$,
+respectively to give
+
+\begin{equation}
+q(\beta \mid \lambda) = h(\beta) exp(\lambda^T t(\beta) - \alpha_g(\lambda))
+\end{equation}
+\begin{equation}
+q(z_{nj} \mid \phi_{nj}) = h(z_{nj}) exp(\phi_{nj}^T t(z_{nj}) - \alpha_l(\phi_{nj}))
+\end{equation}
+
+Where $h(.)$ is called the base measure, $\alpha(.)$ is called the log-
+normalizer, $\eta(.)$ is called the natural parameter, and $t(.)$ is called the
+sufficient statistics. Furthermore, we also assume that the prior distribution
+over $\beta$ is part of the exponential family. We maximize the ELBO objective
+function with a coordinate ascent procedure. We find its gradient with respect
+to the global variational parameter $\lambda$ and find the value of $\lambda$
+that sets the gradient to zero. We do the same thing for the local parameters
+$\phi_n$. We iterate between these updates until we converge to the maximum of
+the ELBO. The updates are given without proof, but the general procedure is to
+write the ELBO in terms of parameter of interest (either $\lambda$ or $\phi_n$)
+then take the gradient and set it to zero.
+
+\begin{equation}
+\lambda = E_q[\eta_g(x, z, \alpha)]
+\end{equation}
+\begin{equation}
+\phi_{nj} = E_q[\eta_l(x_n, z{n, -j}, \beta)]
+\end{equation}
+
+Therefore the updates of each variational parameter are equal to the expected
+value of the natural parameters of the complete conditionals. A simple outline 
+of the algorithm ~\cite{alexminnar} is given below
+
+\begin{algorithm}[H] 
+\SetAlgoLined
+
+Initialize $\lambda^{(0)}$ randomly.
+\Repeat{the ELBO converges}{
+	\For{each local variational parameter $\phi_{nj}$}{\label{forins}
+		Update $\phi_{nj}^{(t)} = \mathbb{E}_{q^{(t - 1)}}[\eta_{l,j}(x_n, z_{n,-j}, \beta)]$.
+	}
+	Update the global variational parameters, $\lambda^{(t)} = \mathbb{E}_{q^{(t)}}[\eta_g (z_{1:N}, x_{1:N})]$.
+}
+\caption{Variational Bayes for LDA} 
+\end{algorithm}
+
+As you can see, in the local parameter update (in the $for$ loop), we have to
+iterate over every data point in the data set which is computationally
+expensive. The algorithm above has constant memory requirements and empirically
+converges faster than collapsed Gibbs sampling. However, it still requires a
+full pass through the entire corpus in each iteration. It can be slow to apply
+to very large datasets. An online variational inference algorithm is proposed by
+Hoffman et all. ~\cite{onlineLDAvb} for fitting $\lambda$, the parameters to the
+variational posterior over the topic distributions $\beta$. The "online LDA" is
+nearly as simple as the variational algorithm, but converges much faster for
+large datasets.
 
@@
 
+\bibliography{references}{}
+\bibliographystyle{plain}
+
 \end{document}

### 2017-06-06 thesis_report/draft_thesis.tex
Add references

@@
 is over all possible data points. Here, a data point is a document containing
-$n$ words.
+$n$ words ~\cite{Huang_maximumlikelihood}.
 
@@
 represent a dimension in a very high dimensional space, a document can be seen
-as a vector with components corresponding to its weighted term counts.
+as a vector with components corresponding to its weighted term counts ~\cite{Deerwester90indexingby}.
 
@@
 matrix. The difference is that instead of being based on linear algebra, PLSI
-is based on a mixture decomposition using a latent class model. PLSI associates
+is based on a mixture decomposition using a latent class model 
+~\cite{Hofmann:1999:PLS:312624.312649}. PLSI associates
 an unobserved class variable $z$ with each document-word observation pair $(w,
@@
 tries to solve this limitation by setting a Dirichlet prior on the topic
-distribution.
+distribution ~\cite{blei2003latent}.
 
@@
 over a fixed vocabulary. Technically, the model assumes that the topics are
-generated first, before the documents. Now for each document in the collection,
+generated first, before the documents ~\cite{Blei11introductionto}. Now for each document in the collection,
 we generate the words in a two-stage process:
@@
 partial derivatives of the likelihood function with respect to all variables,
-setting these derivatives to zero and solving the equations simultaneously.
+setting these derivatives to zero and solving the equations simultaneously 
+~\cite{Myung:2003}.
 
@@
 (called the variational distribution) is  introduced. This new distribution has
-properties such that it can be efficiently computed.
+properties such that it can be efficiently computed ~\cite{Fox2011ATO}.
 

### 2017-06-06 thesis_report/draft_thesis.tex
Add Methodology description

@@
 
-\setcounter{secnumdepth}{5}
-\setcounter{tocdepth}{5}
+\setcounter{secnumdepth}{4}
+\setcounter{tocdepth}{4}
+
+\setlength{\parskip}{1em}
 
@@
 
+\begin{center}
 \begin{figure}
@@
 \end{figure}
+\end{center}
 
@@
 
+In this section, we explain the procedure that we followed in n order to apply the LDA model in our dataset.
+The dataset consists of two datasets: the one that contains all the information about EU projects founded for research and innovation under the FP4-H2020 and the dataset from USA about the awards/projects that got approved from 1994-2017.
+We consider the projects' description/abstract as the documents in LDA.
+
+\subsection{EU dataset}
+
+CORDIS (Community Research and Development Information Service) is the European Commission's primary public repository and portal to disseminate information on all EU-funded research projects and their results in the broadest sense.
+The website includes all public information held by the Commission (project factsheets, publishable reports and deliverables), editorial content to support communication and exploitation (news, events, success stories, magazines) and comprehensive links to external sources such as open access publications and websites.
+CORDIS is managed by the Publications Office of the European Union, on behalf of the European Commission's research Directorates-General and Agencies.
+CORDIS content dates back to the origin of the service in 1990 and the website has been online since 1994.
+
+Below, we provide the general topics of the EU projects as listed in the EU Open Data Portal \footnote{https://data.europa.eu/euodp/en/data}:
+\begin{itemize}
+\item Agriculture, Fisheries and Food
+	\begin{description}
+	\item Agriculture, Food safety, Maritime affairs and fisheries
+	\end{description}
+\item Business
+	\begin{description}
+	\item Competition, Enterprise, Single market, Trade
+	\end{description}
+\item Culture and Education
+	\begin{description}
+	\item Audiovisual and media, Culture, Education training and youth, Multiligualism
+	\end{description}
+\item Customs and Tax
+	\begin{description}
+	\item Customs, Taxation
+	\end{description}
+\item Development and Humanitarian aid
+	\begin{description}
+	\item Development and cooperation, Humanitarian aid and Civil protection, Human rights
+	\end{description}
+\item Economy and Finance
+	\begin{description}
+	\item Budget, Economic and monetary affairs, Fraud prevention
+	\end{description}
+\item Employment and Social affairs
+\item Enlargement and Foreign affairs
+\item Environment and Energy
+	\begin{description}
+	\item Climate action, Energy, Environment
+	\end{description}
+\item EU institutions
+	\begin{description}
+	\item Institutional affairs
+	\end{description}
+\item Health
+	\begin{description}
+	\item Health, Sport
+	\end{description}
+\item Justice and Citizens’ rights
+	\begin{description}
+	\item EU citizenship, Consumers, Justice and Home affairs
+	\end{description}
+\item Regions and Local development
+	\begin{description}
+	\item Regional policy
+	\end{description}
+\item Science and Technology
+	\begin{description}
+	\item Space, Digital Economy and Society, Research and Innovation
+	\end{description}
+\item Transport and Travel
+\end{itemize}
+
+The data that are provided by CORDIS (via the EU Open Data Portal) are open, free and can be used in research, applications, commercial or non-commercial purposes.
+The dataset that we chose for the following analysis contains information about all the projects funded by the European Union from 1994 to 2017.
+These projects got approved under the framework programme (FP4-H2020) for research and technological development.
+For each project it is provided information, such as: reference, acronym, dates, funding, programmes, participant countries, subjects and objectives.
+
+In the provided dataset, the information is splitted into CSV files, based on the framework program that each project belongs. The frameworks from 1994 to 2020 are listed below:
+
+\begin{itemize}
+\item FP4: fourth framework programme (1994-1998)
+\item FP5: fifth framework programme (1998–2002)
+\item FP6: sixth framework programme (2002–2006)
+\item FP7: seventh framework programme (2007–2013)
+\item H2020: Horizon 2020 framework programme (2014-2020)
+\end{itemize}
+
+\subparagraph{Data preparation}
+
+Data cleaning is absolutely crucial for generating a useful topic model.
+We implemented the following steps, which are common to most natural language processing methods, in order to obtain the final corpus for the analysis:
+
+\begin{itemize}
+\item Remove punctuation and numbers
+\item Tokenize documents
+\item Remove stopwords
+\item Create a dictionary
+\item Filter out the most frequent and some rare words of the dictionary
+\end{itemize}
+
+To obtain the collection of the documents, we consider as ‘documents’ in LDA the project objectives, which is an accurate description for the project.
+We also added the ‘title’ value of each project to the objectives-documents, to increase the probability of finding accurate topics.
+For the majority of the projects the ‘start date’ and ‘end date’ value was null, so we kept the splitting of the dataset per framework, in order to keep the correlation to the time.
+We followed the same format in the dataset of USA awards.
+
+\begin{center}
+\begin{tabular}{l*{6}{c}r}
+Framework & Years & No of docs & No of unique tokens & No of words in the corpus \\
+\hline
+FP4 & 1994-1998 & 14567 & 7293 & 364263 \\
+FP5 & 1998-2002 & 17202 & 15756 & 1617232 \\
+FP6 & 2002-2006 & 10091 & 15521 & 1437607 \\
+FP7 & 2007-2013 & 25607 & 26499 & 3789837 \\
+H2020 & 2014-2017 & 9055 & 15835 & 1342882 \\
+\end{tabular}
+\end{center}
+
+As stopwords, we used the list that is provided by the Gensim Python library\footnote{http://radimrehurek.com/gensim/} and we added following very common words in the existing dataset: 'data', 'based', 'new', 'project', 'university', 'student', 'students', 'research', 'study', 'program', 'development', 'study', 'studies', 'provide', 'use'.
+We also removed the rare words that appear less than 5 times in the collection.
+Finally, we obtained a smaller corpus per framework (see the table above)
+
+In this section, we explain the procedure that we followed in n order to apply the LDA model in our dataset.
+The dataset consists of two datasets: the one that contains all the information about EU projects founded for research and innovation under the FP4-H2020 and the dataset from USA about the awards/projects that got approved from 1994-2017.
+We consider the projects' description/abstract as the documents in LDA.
+
+\subsection{USA dataset}
+
+The National Science Foundation (NSF) is a United States government agency that supports fundamental research and education in all the non-medical fields of science and engineering.
+Its medical counterpart is the National Institutes of Health.
+The NSF funds approximately 24\% of all federally supported basic research conducted by the United States' colleges and universities.
+In some fields, such as mathematics, computer science, economics, and the social sciences, the NSF is the major source of federal backing.
+
+The NSF organizes its research and education support through seven directorates, each encompassing several disciplines:
+
+\begin{itemize}
+\item Biological Sciences
+\begin{description}
+\item Molecular, Cellular and Organismal biology, Environmental science
+\end{description}
+\item Computer and Information Science and Engineering
+\begin{description}
+\item Fundamental computer science, Computer and networking systems, 
+Artificial Intelligence
+\end{description}
+\item Engineering
+\begin{description}
+\item Bioengineering, Environmental systems, Civil and Mechanical systems, 
+Chemical and Transport systems, Electrical and Communications systems, Design
+ and Manufacturing
+\end{description}
+\item Geosciences
+\begin{description}
+\item Geological, Atmospheric and Ocean sciences
+\end{description}
+\item Mathematical and Physical Sciences
+\begin{description}
+\item Mathematics, Astronomy, Physics, Chemistry and Materials science
+\end{description}
+\item Social, Behavioral and Economic Sciences
+\begin{description}
+\item Neuroscience, Management, Psychology, Sociology, Anthropology, 
+Linguistics, Science of science policy and economics
+\end{description}
+\item Education and Human Resources
+\begin{description}
+\item Science, Technology, Engineering and mathematics education at every level
+\end{description}
+\end{itemize}
+
+The data about the awards \footnote{https://www.nsf.gov/awardsearch/download.jsp} are open, free and can be used in research and applications.
+The dataset that we chose for the following analysis contains information about all the projects that got funded by the NSF from 1994 to 2017.
+
+In the provided dataset, the information is splitted into XML files, separated per year, from 1994 - 2017.
+In order to keep the correlation to time and be able to compare the two datasets later, we splitted the projects based on the year they were initialized (see Table below).
+
+\subparagraph{Data preparation}
+
+Just like the EU dataset, we followed the same preprocessing steps to obtain the final corpus.
+As stopwords, we used the list that is provided by the Gensim Python library and we removed following very common words in the existing dataset: 'data', 'work', 'based', 'new', 'project', 'university', 'student', 'students', 'research', 'study', 'program', 'development', 'study', 'studies', 'provide', 'use', 'understanding', 'important', 'support', 'proposed'.
+We also removed the rare words that appear less than 5 times in the collection.
+Finally, we obtained a smaller corpus per framework (see Table below).
+
+\begin{center}
+\begin{tabular}{l*{6}{c}r}
+Framework         & Years & No of docs & No of unique tokens & No of words in the corpus \\
+\hline
+FP4 & 1994-1997 & 36752 & 28038 & 4346604 \\
+FP5 & 1998-2001 & 37674 & 30728 & 5166316 \\
+FP6 & 2002-2006 & 54212 & 38476 & 8837298 \\
+FP7 & 2007-2013 & 87341 & 48277 & 15673424 \\
+H2020 & 2014-2017 & 35581 & 32268 & 7379219 \\
+\end{tabular}
+\end{center}
+
+\subsection{Model inference}
+
+Details about the implementation, system specs etc.
+
 \section{Analysis and results}

### 2017-06-08 eu_gensim/eu_all_wordclouds.py
Topics for the whole EU dataset

@@ -1,0 +1,118 @@
+# coding: utf-8
+
+import pandas as pd
+import numpy as np
+import re
+import pickle
+import gensim
+
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+from time import time
+from wordcloud import WordCloud
+from gensim import corpora
+from gensim import models
+from gensim.corpora.dictionary import Dictionary
+from collections import defaultdict
+from gensim.parsing.preprocessing import STOPWORDS
+
+import string
+import logging
+
+df4 = pd.read_pickle('dfs/' + 'FP4')
+df5 = pd.read_pickle('dfs/' + 'FP5')
+df6 = pd.read_pickle('dfs/' + 'FP6')
+df7 = pd.read_pickle('dfs/' + 'FP7')
+df20 = pd.read_pickle('dfs/' + 'H2020')
+
+def get_merged_docs(df):
+    df = df[['title','objective']]
+    df = df.dropna(how='any')
+    df['merged'] = df['title'] + ' ' + df['objective']
+    return df['merged']
+
+objectives = pd.concat([get_merged_docs(df) for df in [df4, df5, df6, df7, df20] ])
+
+
+RE_PUNCTUATION = '|'.join([re.escape(x) for x in string.punctuation])
+
+objectives = objectives.str.lower().str.replace('%l', '').str.replace(RE_PUNCTUATION, ' ')
+
+objectives_split = objectives.str.strip().str.split()
+objectives_split = objectives_split.apply(lambda tokens: [token for token in tokens if len(token) > 2])
+objectives_split = objectives_split.apply(lambda tokens: [token for token in tokens if not(token.isdigit())])
+objectives_split.head(2)
+
+
+list_stopwords = ['data','will', 'develop', 'development', 'project', 'research', 'new', 'use', 'europe', 'european', 'based']
+# if dfname == 'FP4':
+#     list_stopwords.append('des')
+
+additional_stopwords = set(list_stopwords)
+stopwords = set(STOPWORDS) | additional_stopwords
+
+objectives_split = objectives_split.apply(lambda tokens: [token for token in tokens if token not in stopwords])
+
+
+frequency = defaultdict(int)
+for text in objectives_split:
+    for token in text:
+        frequency[token] += 1
+
+objectives_split = objectives_split.apply(lambda tokens: [token for token in tokens if (frequency[token] > 5)])
+
[…]

### 2017-06-08 eu_gensim/test_merge_dfs.py

@@ -1,0 +1,144 @@
+# coding: utf-8
+
+import pandas as pd
+import numpy as np
+import re
+import pickle
+import gensim
+import itertools
+
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+
+from time import time
+from wordcloud import WordCloud
+from gensim import corpora
+from gensim import models
+from gensim.corpora.dictionary import Dictionary
+from collections import defaultdict
+from gensim.parsing.preprocessing import STOPWORDS
+
+import string
+import logging
+
+# df4 = pd.read_pickle('dfs/' + 'FP4')
+# df5 = pd.read_pickle('dfs/' + 'FP5')
+# df6 = pd.read_pickle('dfs/' + 'FP6')
+# df7 = pd.read_pickle('dfs/' + 'FP7')
+# df20 = pd.read_pickle('dfs/' + 'H2020')
+
+# def get_merged_docs(df):
+#     df = df[['title','objective', 'framework_programme']]
+#     df = df.dropna(how='any')
+#     df['merged'] = df['title'] + ' ' + df['objective']
+#     df1 = df[['merged', 'framework_programme']]
+#     return df1
+
+# objectives = pd.concat([get_merged_docs(df) for df in [df4, df5, df6, df7, df20] ])
+
+# print objectives.columns
+# print objectives.shape
+
+# objectives.to_pickle('df_all')
+
+df_all = pd.read_pickle('dfs/df_all')
+
+# print df_all.columns
+# print df_all.shape
+# print df_all.head(3)
+# print
+
+RE_PUNCTUATION = '|'.join([re.escape(x) for x in string.punctuation])
+
+df_all['merged'] = df_all['merged'].str.lower().str.replace('%l', '').str.replace(RE_PUNCTUATION, ' ')
+
+df_all['merged'] = df_all['merged'].str.strip().str.split()
+df_all['merged'] = df_all['merged'].apply(lambda tokens: [token for token in tokens if len(token) > 2])
+df_all['merged'] = df_all['merged'].apply(lambda tokens: [token for token in tokens if not(token.isdigit())])
+df_all['merged'].head(2)
+
+
+list_stopwords = ['data','will', 'develop', 'development', 'project', 'research', 'new', 'use', 'europe', 'european', 'based']
+# if dfname == 'FP4':
+#     list_stopwords.append('des')
+
+additional_stopwords = set(list_stopwords)
[…]

### 2017-06-09 thesis_report/draft_thesis.tex
Update: some probability concepts

@@
 
-\title{Topic modeling bla bla}
+\title{Topic modeling on EU and the USA research projects}
+\author{Maria Iliadi}
 
@@
 
-\subsection{The Multinomial Distribution}
+\subsection{Some probability concepts}
+
+\subparagraph{Prior and posterior distributions}
+
+When introducing the Latent Dirichlet Allocation in section 2.x.x, we will be
+using the terms prior and posterior probabilities and likelihood function:
+
+\begin{itemize}
+\item The prior probability distribution of and uncertain quantity is the 
+probability distribution that express the value of this quantity before 
+some evidence is taken into account.
+\item The posterior probability is the conditional probability after some 
+evidence is taken into account.
+\item The likelihood function of a set of parameters given some outcome 
+is equal to the probability of observing said outcome given those 
+parameter values.
+\end{itemize}
+
+If the prior and the posterior distributions are in the same distribution
+family, then the prior and posterior are called conjugate distributions and the
+prior is called a conjugate prior for the likelihood funtion.
+
+Given a prior $p(\theta)$ and observations x with the likelihood 
+$p(x \mid \theta)$, the posterior is defined as:
+
+\begin{equation}
+p(\theta \mid x) = \frac{p(x \mid \theta) p(\theta)}{p(x)}
+\end{equation}
+
+\subparagraph{Jensen Inequality}
+
+In the context of probabilities, the Jensen Inequality is stated as follows: 
+If X is a random variable and f a convex function then:
+
+\begin{equation}
+f(\mathbb{E}[X]) \leq \mathbb{E}[f(X)]
+\end{equation}
+
+And, if f is a concave function the inequality turns:
+
+\begin{equation}
+f(\mathbb{E}[X]) \geq \mathbb{E}[f(X)]
+\end{equation}
+
+\subparagraph{Kullback-Leibler (KL) divergence}
+
+When formulating the optimization problem in Latent Dirichlet Allocation we 
+will use the KL divergence to express the optimization problem. The KL divergence 
+is a measure of the difference between two probability distributions $P$ and $Q$. 
+It is important to note
+that the KL divergence is not symmetrical in $P$ and $Q$ so it’s not a metric.
+
+The KL divergence can be interpreted as a way to express the amount of 
+information lost when $Q$ is used to approximate $P$.
+
+Given two continuous distributions $P$ and $Q$ the KL divergence is defined as follows:
+
+\begin{equation}
+D_{KL}(P \mid \mid Q) = \int_{-\infty}^{+\infty} p(x) log\frac{p(x)}{q(x)}dx
+\end{equation}
+
+This can also be expressed using the definition of expectation (and expressing the 
+log of a division as difference of log) as:
+
+\begin{equation}
+D_{KL}(P \mid \mid Q) = \mathbb{E}_{p}[log p(x)] - \mathbb{E}_{p}[log q(x)]
+\end{equation}
+
+This is the expression we will use later on instead of the definition. We present 
+now the two probability distributions we will be using when we define the different 
+models in this work: the \textbf{Multinomial} and the \textbf{Dirichlet} distributions.
+
+\subparagraph{Multinomial Distribution}
 
@@
 $n$ words ~\cite{Huang_maximumlikelihood}.
+
+\subparagraph{Dirichlet distribution}
+
+The Dirichlet distribution is a way to model random probability mass functions
+(PMFs)\footnote{If you roll 1000 dice, the theoretical odds of any particular
+number showing up (i.e. a 1, 2, 3, 4, 5, or 6) are 1/6. However, you won’t get
+that exact distribution in a real experiment due to manufacturing defects. If
+you have ten dice, each die will have its own probability mass function (PMF).}
+for finite sets. It is also sometimes used as a prior in Bayesian statistics.
+The Dirichlet is the multivariate generalization of the beta distribution. It
+is an extension of the beta distribution for modeling probabilities for two or
+more events; when the result of the event has only 2 values, the Dirichlet
+distribution is equal to the beta distribution.
+
+The Dirichlet distribution is a prior for the multinomial distribution. This
+means that if the prior distribution of the multinomial parameters is Dirichlet
+then the posterior distribution is also a Dirichlet distribution (with
+parameters different from those of the prior).
+
+The Dirichlet process is a way to model randomness of a probability mass
+function (PMF) with unlimited options (e.g. an unlimited amount of dice in a
+bag). The process is similar Polya’s Urn, only instead of having a set number
+of ball colors you have an unlimited amount:
+
+\begin{itemize}
+\item Start out with an empty urn.
+\item Randomly pick a colored ball and place it in the urn.
+\item Then choose one option:
+\begin{enumerate}
+\item Randomly pick a colored ball and place it in the urn.
+\item Randomly remove a colored ball from the urn, then put it back with another 
+ball of the same color.
+\end{enumerate}
+\end{itemize}
+
+As the number of balls in the urn increase, the probability of picking a new
+color decreases. The proportion of balls in the urn after an infinite amount of
+draws is a Dirichlet process.
 
@@
 distinguishing characteristic of LDA. A more detailed explanation of the model
-follows in section 2.3.3.2.
-
-\paragraph{Dirichlet distribution}
-
-The Dirichlet distribution is a way to model random probability mass functions
-(PMFs)\footnote{If you roll 1000 dice, the theoretical odds of any particular
-number showing up (i.e. a 1, 2, 3, 4, 5, or 6) are 1/6. However, you won’t get
-that exact distribution in a real experiment due to manufacturing defects. If
-you have ten dice, each die will have its own probability mass function (PMF).}
-for finite sets. It is also sometimes used as a prior in Bayesian statistics.
-The Dirichlet is the multivariate generalization of the beta distribution. It
-is an extension of the beta distribution for modeling probabilities for two or
-more events; when the result of the event has only 2 values, the Dirichlet
-distribution is equal to the beta distribution.
-
-The Dirichlet distribution is a prior for the multinomial distribution. This
-means that if the prior distribution of the multinomial parameters is Dirichlet
-then the posterior distribution is also a Dirichlet distribution (with
-parameters different from those of the prior).
-
-The Dirichlet process is a way to model randomness of a probability mass
-function (PMF) with unlimited options (e.g. an unlimited amount of dice in a
-bag). The process is similar Polya’s Urn, only instead of having a set number
-of ball colors you have an unlimited amount:
-
-\begin{itemize}
-\item Start out with an empty urn.
-\item Randomly pick a colored ball and place it in the urn.
-\item Then choose one option:
-\begin{enumerate}
-\item Randomly pick a colored ball and place it in the urn.
-\item Randomly remove a colored ball from the urn, then put it back with another 
-ball of the same color.
-\end{enumerate}
-\end{itemize}
-
-As the number of balls in the urn increase, the probability of picking a new
-color decreases. The proportion of balls in the urn after an infinite amount of
-draws is a Dirichlet process.
+follows in section 2.3.3.1.
 

### 2017-06-09 thesis_report/draft_thesis.tex
Update: Theoretic background - vb and online vb LDA

@@
 full pass through the entire corpus in each iteration. It can be slow to apply
-to very large datasets. An online variational inference algorithm is proposed by
-Hoffman et all. ~\cite{onlineLDAvb} for fitting $\lambda$, the parameters to the
-variational posterior over the topic distributions $\beta$. The "online LDA" is
-nearly as simple as the variational algorithm, but converges much faster for
-large datasets.
+to very large datasets.
+
+\paragraph{Online variational LDA}
+
+An online variational inference algorithm is proposed by Hoffman et all.
+~\cite{onlineLDAvb} for fitting $\lambda$, the parameters to the variational
+posterior over the topic distributions $\beta$. The "online LDA" is nearly as
+simple as the variational algorithm, but converges much faster for large
+datasets. Variational inference requires to pass through the whole dataset for
+each iteration, and that can be a problem when working with big datasets and is
+not an option to use cases where the data is arriving constantly. The Online
+Variational Inference algorithm aims to solve both problems without compromising
+the quality of the obtained topics and with an algorithm nearly as simple as
+Variational Inference. For this algorithm we will only highlight the differences
+respect the Variational Inference and the resulting algorithm. The key
+difference is the way to fit the variational parameter $\lambda$ respect the
+Variational Inference explained in the previous section.
+
+The $t$-th document (or equivalently a vector of words counts) we perform the
+E-step like Variational inference to find locally optimal values for $\gamma_t$
+and $\phi_t$ while holding $]\lambda$ fixed. And then (the M-step) compute the
+optimal value for $\lambda$ if the whole document corpus consisted of this
+$t$-th document repeated $M$ times (M: the number of documents in the corpus).
+After we have the optimal value of $\lambda$ for the   document, $\lambda$*, we
+update the value of $\lambda$ using a weighted average of its previous value and
+$\lambda_d$∗. The weight given to $\lambda$∗ is given by 
+$\rho_t = (\tau_{0} + t)^{-\kappa}$, with $\kappa \in (0.5, 1]$. 
+$\kappa$ controls the importance we give to most recents values of $\lambda$∗.
+
+In short, we approximate the true distribution by a simple distribution $q$, and
+associate parameters $\phi,\gamma,\lambda$ with the original parameters $z,\theta,
+\beta$ respectively. Recall that $z$ gives the topic assignments for each
+word in each document, $\theta$ gives the topic composition of each document, 
+and $\beta$ gives the word-topic probabilities for each word and each topic.
+
+Our goal is to estimate $\phi, \gamma, \lambda$. In both variational 
+and online variational LDA, we alternate between two steps:
+
+\begin{enumerate}
+\item E-Step: Estimate $\phi, \gamma$ using the current value of $\lambda$
+\item M-Step: Update $\lambda$, using the current value of $\phi$
+\end{enumerate}
+
+Algorithm 2 shows the inference process given a vector of word counts. The
+explicit formulas for $\mathbb{E}_q[log \theta_{tk}]$ and $\mathbb{E}_q[log
+\beta_{kw}]$ are:
+
+\begin{equation}
+\mathbb{E}_q[log \theta_{tk}] = \Psi(\gamma_{tk}) - \Psi(\sum_{i=1}^K \gamma_{ti})
+\end{equation}
+
+\begin{equation}
+\mathbb{E}_q[log \beta_{kw}] = \Psi(\lambda_{kw}) - \Psi(\sum_{i=1}^W \lambda_{ki})
+\end{equation}
+
+Where $\Psi$ denotes the derivative of the logarithm of the gamma function.
+
+\begin{algorithm}
+\SetAlgoLined
+Define $\rho_t = (\tau_{0} + t)^{-\kappa}$
+
+Initialize $\lambda$ randomly.
+
+\For{$t = 0 to \infty$}{\label{forins}
+	E step:
+
+	Initialize $\gamma_{tk} = 1$
+
+	\Repeat{$\frac{1}{K} \sum_k$ |change in $\gamma_{tk}$| $< 0.00001$}{
+		Set $\phi_{twk} \propto exp${$\mathbb{E}_q[log \theta_{tk}]$ + $\mathbb{E}_q[log\beta_{kw}]$}
+
+		Set $\gamma_{tk} = \alpha + \sum_w \phi_{twk}n_{tw}$
+	}
+	M step:
+
+	Compute $\lambda_{kw}* = \eta + Dn_{tw}\phi_{twk}$
+
+	Set $\lambda = (1 - \rho_t)\lambda + \rho_{t}\lambda*$
+}
+
+We can see that unlike variational LDA, in online LDA we only need to hold a
+small chunk of the data at a time, and once we’re done analyzing it, we never
+need it again. As with batch, once we’ve estimated $\lambda$, we can find the 
+most probable words for each topic by looking at the word probabilities in 
+each row of $\lambda$.
+
+\caption{Online Variational Bayes for LDA} 
+\end{algorithm}
 

### 2017-06-10 eu_gensim/test_merge_dfs.py
Topic evolution in EU

@@ -36,13 +36,13 @@ import logging
 #     df1 = df[['merged', 'framework_programme']]
 #     return df1
 
-# objectives = pd.concat([get_merged_docs(df) for df in [df4, df5, df6, df7, df20] ])
+# df_all = pd.concat([get_merged_docs(df) for df in [df4, df5] ])
 
 # print objectives.columns
 # print objectives.shape
 
 # objectives.to_pickle('df_all')
-
+# ######################################################3
 df_all = pd.read_pickle('dfs/df_all')
 
 # print df_all.columns
@@ -130,15 +130,28 @@ print("done in %0.3fs." % (time() - t0))
 
 # corpus_lda = lda[objectives_corpus]
 
-l_merged = df_all['merged'].tolist()
 
+# for doc in df_all['merged']:
+#     print doc
+#     topic_doc_list = lda.get_document_topics(objectives_dictionary.doc2bow(doc))
+#     print topic_doc_list
+#     top_topic = sorted(topic_doc_list,key=lambda x: x[1], reverse=True)[0]
+#     print top_topic
+#     print
+def get_top_probability(doc):
+    topic_doc_list = lda.get_document_topics(objectives_dictionary.doc2bow(doc))
+    top_topic = sorted(topic_doc_list,key=lambda x: x[1], reverse=True)[0]
+    return top_topic[1]
 
-for i in range(2):
-    print l_merged[i]
-    print lda.get_document_topics(l_merged[i])
-    print lda.get_document_topics(l_merged[i], per_word_topics=True)
+def get_top_topic(doc):
+    topic_doc_list = lda.get_document_topics(objectives_dictionary.doc2bow(doc))
+    top_topic = sorted(topic_doc_list,key=lambda x: x[1], reverse=True)[0]
+    return top_topic[0]
 
+# for doc in df_all['merged']:
+df_all['top_prob_topic'] = df_all['merged'].apply(lambda docs: get_top_probability(docs))
+df_all['top_topic'] = df_all['merged'].apply(lambda docs: get_top_topic(docs))
 
+print df_all.shape
 
-# # ************************************
-# # get_document_topics ???
+df_all.to_pickle('dfs/df_topics')

### 2017-06-10 eu_gensim/test_merge_dfs.py
Code for word-topic df - USA

@@ -130,14 +130,6 @@ print("done in %0.3fs." % (time() - t0))
 
 # corpus_lda = lda[objectives_corpus]
 
-
-# for doc in df_all['merged']:
-#     print doc
-#     topic_doc_list = lda.get_document_topics(objectives_dictionary.doc2bow(doc))
-#     print topic_doc_list
-#     top_topic = sorted(topic_doc_list,key=lambda x: x[1], reverse=True)[0]
-#     print top_topic
-#     print
 def get_top_probability(doc):
     topic_doc_list = lda.get_document_topics(objectives_dictionary.doc2bow(doc))
     top_topic = sorted(topic_doc_list,key=lambda x: x[1], reverse=True)[0]

### 2017-06-10 usa_gensim/usa_merge_dfs.py

@@ -1,0 +1,135 @@
+# coding: utf-8
+
+import pandas as pd
+import numpy as np
+import re
+import pickle
+import gensim
+import itertools
+
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+
+from time import time
+from wordcloud import WordCloud
+from gensim import corpora
+from gensim import models
+from gensim.corpora.dictionary import Dictionary
+from collections import defaultdict
+from gensim.parsing.preprocessing import STOPWORDS
+
+import string
+import logging
+
+# df4 = pd.read_pickle('pickle_data/usa' + 'FP4')
+# df5 = pd.read_pickle('pickle_data/usa' + 'FP5')
+# df6 = pd.read_pickle('pickle_data/usa' + 'FP6')
+# df7 = pd.read_pickle('pickle_data/usa' + 'FP7')
+# df20 = pd.read_pickle('pickle_data/usa' + 'H2020')
+
+# def get_merged_docs(df):
+#     df = df[['title','objective', 'framework_programme']]
+#     df = df.dropna(how='any')
+#     df['merged'] = df['title'] + ' ' + df['objective']
+#     df1 = df[['merged', 'framework_programme']]
+#     return df1
+
+# dfusa = pd.concat([get_merged_docs(df) for df in [df4, df5, df6, df7, df20] ])
+
+# print dfusa.columns
+# print dfusa.shape
+
+# dfusa.to_pickle('pickle_data/df_usa_all')
+dfusa = pd.read_pickle('pickle_data/df_usa_all')
+
+RE_PUNCTUATION = '|'.join([re.escape(x) for x in string.punctuation])
+
+dfusa['merged'] = dfusa['merged'].str.lower().str.replace(RE_PUNCTUATION, ' ')
+
+dfusa['merged'] = dfusa['merged'].str.strip().str.split()
+dfusa['merged'] = dfusa['merged'].apply(lambda tokens: [token for token in tokens if len(token) > 2])
+dfusa['merged'] = dfusa['merged'].apply(lambda tokens: [token for token in tokens if not(token.isdigit())])
+
+list_stopwords = ['data', 'work', 'based', 'new', 'project', 'university', 'student', 'students', 'research', 
+                'study', 'program', 'development', 'study', 'studies', 'provide', 'use', 'understanding', 'important',
+                'support', 'proposed']
+
+additional_stopwords = set(list_stopwords)
+stopwords = set(STOPWORDS) | additional_stopwords
+
[…]

### 2017-06-10 eu_gensim/test_merge_dfs.py
Fixed: topics over time plot with normalized values

@@ -23,6 +23,7 @@ from gensim.parsing.preprocessing import STOPWORDS
 import string
 import logging
 
+# Code for merging into one dataframe all projects from each framework programme
 # df4 = pd.read_pickle('dfs/' + 'FP4')
 # df5 = pd.read_pickle('dfs/' + 'FP5')
 # df6 = pd.read_pickle('dfs/' + 'FP6')
@@ -38,17 +39,9 @@ import logging
 
 # df_all = pd.concat([get_merged_docs(df) for df in [df4, df5] ])
 
-# print objectives.columns
-# print objectives.shape
+# df_all.to_pickle('df_all')
 
-# objectives.to_pickle('df_all')
-# ######################################################3
 df_all = pd.read_pickle('dfs/df_all')
-
-# print df_all.columns
-# print df_all.shape
-# print df_all.head(3)
-# print
 
 RE_PUNCTUATION = '|'.join([re.escape(x) for x in string.punctuation])
 
@@ -104,8 +97,6 @@ class ObjectivesCorpus(corpora.textcorpus.TextCorpus):
 
 objectives_corpus = ObjectivesCorpus(df_all['merged'])
 
-# print df_all['merged'].head(1)
-
 t0 = time()
 lda = gensim.models.ldamodel.LdaModel(corpus = objectives_corpus, 
                                         id2word = objectives_dictionary, 
@@ -115,6 +106,7 @@ lda = gensim.models.ldamodel.LdaModel(corpus = objectives_corpus,
 
 print("done in %0.3fs." % (time() - t0))
 
+# Code for visualizing topics to Wordclouds
 
 # for t in range(lda.num_topics):
 #     words = dict(lda.show_topic(t, 20))
@@ -125,22 +117,23 @@ print("done in %0.3fs." % (time() - t0))
 #     t = t + 1
 #     plt.title("Topic #" + str(t))
 #     # plt.savefig('EU' + df_name + '_topic' + str(t) + '_' + str(iterations) + '.png')
-#     plt.savefig('EU' + '_topic' + str(t) + '_all_docs' + '.png')
+#     plt.savefig('eu_all_wordclouds/EU' + '_topic' + str(t) + '_all_docs' + '.png')
 #     plt.close()
 
-# corpus_lda = lda[objectives_corpus]
 
+# Get the probability of the topic with the highest probability for each doc
 def get_top_probability(doc):
[…]

### 2017-06-11 thesis_report/draft_thesis.tex
Fixed: "Some probability concepts" subsection in Theoretic background

@@
 \usepackage{algorithm2e}
+\usepackage{url}
 
@@
 
-Many applications of if topic modeling also eliminate from the vocabulary so-
+Many applications of topic modeling also eliminate from the vocabulary so-
 called “stop” words. These are words that are common in most documents and do
@@
 Once we have a representation for individual documents, the natural next step
-is to select a model for a set of documents. It is important to understand the
-difference between a representation and a model. A representation is a way of
-encoding an entity as a data structure. A model is an abstraction of a set of
-entities, for example a probability distribution. Given a training set of
+is to select a model for a set of documents. Given a training set of
 documents, we will choose values for the parameters of a probabilistic model
@@
 
-The probability distribution that we use is the multinomial. Mathematically,
-this distribution is:
+The probability distribution that we use is the multinomial. In probability 
+theory, the multinomial distribution is a generalization of the binomial 
+distribution. For example, it models the probability of counts for rolling 
+a k-sided dice n times. For n independent trials each of which leads to a 
+success for exactly one of k categories, with each category having a given 
+fixed success probability, the multinomial distribution gives the 
+probability of any particular combination of numbers of successes for the 
+various categories \footnote{\url{https://en.wikipedia.org/wiki/Multinomial_distribution}}.
+
+Mathematically, this distribution is:
 
@@
 components of $\theta$ are non-negative and have unit $\sum\limits_{j=1}^m
-\theta_j = 1$. A vector with these properties is called a unit vector.
+\theta_j = 1$.
 
@@
 function (PMF) with unlimited options (e.g. an unlimited amount of dice in a
-bag). The process is similar Polya’s Urn, only instead of having a set number
+bag). The process is similar Polya’s Urn \footnote{\url{http://www.statisticshowto.com/dirichlet-distribution/}}, only instead of having a set number
 of ball colors you have an unlimited amount:

### 2017-06-11 usa_data_load_merged.py
some fixes for USA merged dfs

@@ -1,0 +1,58 @@
+import os
+import zipfile
+import cjson
+import pandas as pd
+import numpy as np
+import xmltodict, json
+import pickle
+
+from xml.dom.minidom import parse
+
+filenames = os.listdir('USA_data')
+
+raw_text = {}
+
+usa_all = []
+
+for zipfilename in filenames:
+    with zipfile.ZipFile('USA_data/'+zipfilename) as z:
+        for filename in z.namelist():
+            if not os.path.isdir(filename):
+                try:
+                    with z.open(filename) as f:
+                        raw_text[filename[:-4]] = json.dumps(xmltodict.parse(f))
+                except:
+                    print filename
+                    pass
+
+for key, val in raw_text.items():
+    usa_dict = {}
+
+    value = cjson.decode(val)
+    new_val = value['rootTag']['Award']
+
+    # usa_dict['id'] = new_val['AwardID']
+    # usa_dict['title'] = new_val['AwardTitle']
+    # usa_dict['objective'] = new_val['AbstractNarration']
+    try:
+        usa_dict['merged'] = new_val['AwardTitle'] + new_val['AbstractNarration']
+    except:
+        pass
+
+    if key[:2] in ['94', '95', '96', '97', '98', '99']:
+    	usa_dict['year'] = int('19' + key[:2])
+    else:
+    	usa_dict['year'] = int('20' + key[:2])
+    usa_all.append(usa_dict)
+
+
+df_usa = pd.DataFrame(usa_all)
+df_usa = df_usa.dropna(how='any')
+
+print df_usa.columns
+print df_usa.shape
+print df_usa.head(2)
+
+
+
+df_usa.to_pickle('usa_gensim/pickle_data/dfUSA')

### 2017-06-11 usa_gensim/usa_merge_dfs.py

@@ -42,7 +42,8 @@ import logging
 # print dfusa.shape
 
 # dfusa.to_pickle('pickle_data/df_usa_all')
-dfusa = pd.read_pickle('pickle_data/df_usa_all')
+
+dfusa = pd.read_pickle('pickle_data/dfUSA')
 
 RE_PUNCTUATION = '|'.join([re.escape(x) for x in string.punctuation])
 
@@ -113,7 +114,7 @@ for t in range(lda.num_topics):
     t = t + 1
     plt.title("Topic #" + str(t))
     # plt.savefig('USA' + df_name + '_topic' + str(t) + '_' + str(i) + '_' + str(iterations) + '.png')
-    plt.savefig('USA' + '_topic' + str(t) + '_8000.png')
+    plt.savefig('usa_all_wordclouds/USA' + '_topic' + str(t) + '_8000_all_docs.png')
     plt.close()
 
 def get_top_probability(doc):
@@ -132,4 +133,4 @@ dfusa['top_topic'] = dfusa['merged'].apply(lambda docs: get_top_topic(docs))
 
 print dfusa.shape
 
-dfusa.to_pickle('df_usa_topics')
+dfusa.to_pickle('pickle_data/df_usa_topics')

### 2017-06-11 usa_gensim/get_year_topic_prop.py
Topic evolution of the USA dataset

@@ -1,0 +1,38 @@
+import pandas as pd
+import numpy as np
+import pickle
+import matplotlib.pyplot as plt
+
+df = pd.read_pickle('pickle_data/df_usa_topics')
+print df.head(2)
+
+print df.columns
+print df.shape
+
+df['year'] = df['year'].astype('str')
+
+sz = df.groupby(["top_topic", 'year']).size()
+sz = sz.reset_index()
+sz = sz.rename(columns = {0:'count'})
+
+print 'sz'
+print sz.shape
+print sz.columns
+
+print sz.head(2)
+
+sz['normalized'] = np.where(sz['year']=='1994', 
+                    (sz['count']/sz.loc[sz['year'] == '1994', 'count'].sum())*100, sz['count'])
+
+years = ['1995', '1996', '1997', '1998', '1999', '2000', '2001', '2002', '2003', '2004', '2005', '2006',
+			'2007', '2008', '2009', '2010', '2011', '2012', '2013', '2014', '2015', '2016', '2017']
+for year in years:
+	sz['normalized'] = np.where(sz['year']==year, 
+                    (sz['count']/sz.loc[sz['year'] == year, 'count'].sum())*100, sz['normalized'])
+
+top_year = sz.pivot(index='year', columns='top_topic', values='normalized')
+
+print
+print top_year
+print top_year
+top_year.to_pickle('pickle_data/df_year_topic')

### 2017-06-12 thesis_report/draft_thesis.tex
small fixes in theoretic background & citations

@@
 \setlength{\parskip}{1em}
-
+\usepackage[justification=centering]{caption}
 \usepackage{amsfonts}
@@
 from the analysis of the original texts, topic modeling algorithms do not
-require any prior annotations or labeling of the documents.
+require any prior annotations or labeling of the documents.\cite{Blei:2012:PTM:2133806.2133826}
 
@@
 Some further common concepts and terms in topic modeling: 
-
-- A word is defined as an item from a vocabulary indexed from ${1, ..., V}$,
-where V is the size of the vocabulary. All words are represented as unit-basis
-vectors with one component equal to one and the rest equal to zero.
-
-- A document is a collection of words denoted by $w = {w_1, ..., w_N}$, where
-$w_n$ is the $n$th word and $N$ is the total number of words in the collection.
-
-- A corpus is a collection of documents in a dataset. It is denoted $D = {w_1,
-..., w_M}$, where $w_m$ is the $m$th document in the corpus and $M$ is the
-total number of documents.
-
-- Latent variables are variables that may not be directly observed, unlike
-observable variables. Latent variables can instead be inferred from other
-observable variables.
-
-- Polysemy is the capacity for a word to have multiple related meanings. An
-example of this is the word “plant” which can mean a living organism of the
-kind exemplified by trees, herbs etc., or a place where an industrial or
+\begin{itemize}
+\item[] A \textit{word} is defined as an item from a vocabulary indexed from 
+${1, ..., V}$, where V is the size of the vocabulary. All words are 
+represented as unit-basis vectors with one component equal to one and 
+the rest equal to zero.
+\item[] A \textit{document} is a collection of words denoted by $w = {w_1, ..., w_N}$, 
+where $w_n$ is the $n$th word and $N$ is the total number of words in the 
+collection.
+\item[] A \textit{corpus} is a collection of documents in a dataset. It is denoted 
+$D = {w_1,..., w_M}$, where $w_m$ is the $m$th document in the corpus and 
+$M$ is the total number of documents.
+\item[] \textit{Latent variables} are variables that may not be directly observed, 
+unlike observable variables. Latent variables can instead be inferred 
+from other observable variables.
+\item[] \textit{Polysemy} is the capacity for a word to have multiple related meanings. 
+An example of this is the word “plant” which can mean a living organism of 
+the kind exemplified by trees, herbs etc., or a place where an industrial or
 manufacturing process takes place.
-
-- Synonymy is the capacity for several words to have similar meanings such as
+\item[] \textit{Synonymy} is the capacity for several words to have similar meanings such as
 the words “buy” and “purchase”.
+\end{itemize}
 
@@
 
-When introducing the Latent Dirichlet Allocation in section 2.x.x, we will be
-using the terms prior and posterior probabilities and likelihood function:
+When introducing the Latent Dirichlet Allocation in section 2.2.3, we 
+will be using the terms prior and posterior probabilities and 
+likelihood function:
 
@@
 probability of any particular combination of numbers of successes for the 
-various categories \footnote{\url{https://en.wikipedia.org/wiki/Multinomial_distribution}}.
+various categories\footnote{\url{https://en.wikipedia.org/wiki/Multinomial_distribution}}.
 
@@
 is over all possible data points. Here, a data point is a document containing
-$n$ words ~\cite{Huang_maximumlikelihood}.
+$n$ words.\cite{Huang_maximumlikelihood}
 
@@
 function (PMF) with unlimited options (e.g. an unlimited amount of dice in a
-bag). The process is similar Polya’s Urn \footnote{\url{http://www.statisticshowto.com/dirichlet-distribution/}}, only instead of having a set number
+bag). The process is similar Polya’s Urn\footnote{\url{http://www.statisticshowto.com/dirichlet-distribution/}}, only instead of having a set number
 of ball colors you have an unlimited amount:
@@
 After LSI was introduced, Hofmann presented the Probabilistic Latent Semantic
-Indexing, or PLSI model. PLSI is a so-called topic model where each word in a
-document is generated from a single “topic” which results in that each document
+Indexing, or PLSI model. PLSI is a topic model where each word in a
+document is generated from a single topic which results in that each document
 in a corpus can be represented with a topic distribution. Later, in 2003 Blei et
@@
 Latent Semantic Indexing was one of the earliest methods for finding
-relationships between documents and the words that occur in them. In LSI a
+relationships between documents and the words that occur in them.\cite{Deerwester90indexingby} In LSI a
 term-document matrix is created by analyzing the corpus, where the rows
@@
 represent a dimension in a very high dimensional space, a document can be seen
-as a vector with components corresponding to its weighted term counts ~\cite{Deerwester90indexingby}.
+as a vector with components corresponding to its weighted term counts.
+\cite{Salton:1988:TAA:54259.54260}
 
@@
 matrix. The difference is that instead of being based on linear algebra, PLSI
-is based on a mixture decomposition using a latent class model 
-~\cite{Hofmann:1999:PLS:312624.312649}. PLSI associates
-an unobserved class variable $z$ with each document-word observation pair $(w,
+is based on a mixture decomposition using a latent class model.
+~\cite{Hofmann:1999:PLS:312624.312649} PLSI associates an unobserved class 
+variable $z$ with each document-word observation pair (\textbf{w},$
 w)$. This $z$ can be seen as a topic, since it is a probability distribution
-over words. As a generative model, PLSI can be defined in the following way for
-a corpus $D$:
+over words. As a generative model, PLSI can be defined in the following way 
+for a corpus $D$:
 
 \begin{enumerate}
-\item Pick a document $w$ with probability $p(w)$
-\item For each of the $N$ words in $w$:
+\item Pick a document \textbf{w} with probability $p($\textbf{w}$)$
+\item For each of the $N$ words in \textbf{w}:
 \begin{description}
-\item (a) Pick a topic $z$ with probability $p(z|w)$
+\item (a) Pick a topic $z$ with probability $p(z|$\textbf{w}$)$
 \end{description}
@@
 \end{enumerate}
-
+\begin{center}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\textwidth, natwidth=548,natheight=201]{figs/PLSI_plate_notation.png}
+\caption{Plate notation representing the PLSI model. \textbf{w} is the document index, $z$ is the topic drawn for the word $w$ from the topic distribution of the document}
+\end{figure}
+\end{center}
 The result from PLSI is that every document is represented as mixing proportions
-for the topics, given by $p(z|w)$. Even though PLSI is generative for the
-analyzed corpus, it is not generative for new documents, which means is that
+for the topics, given by $p(z|$\textbf{w}$)$. Even though PLSI is generative for 
+the analyzed corpus, it is not generative for new documents, which means is that
 there is no clear way of assigning probability to a document that is not part
-of the training data. Another problem is that the number of parameters in the
-model grows linearly with the number of documents.
+of the training data.\cite{blei2003latent} Another problem is that the number 
+of parameters in the model grows linearly with the number of documents.
 
@@
 is a mixture of a small number of topics and that each word's occurrence is
-attributable to one of the document's topics. This is similar to PLSI, except
-that in LDA the topic distribution is assumed to have a Dirichlet prior (see
-2.3.3.1). In practice, this results in more reasonable mixtures of topics in a
+attributable to one of the document's topics.\cite{Blei:2012:PTM:2133806.2133826}
+
+This is similar to PLSI, except
+that in LDA the topic distribution is assumed to have a Dirichlet prior. 
+In practice, this results in more reasonable mixtures of topics in a
 document. The reduced document description result in PLSI is a vector where
@@
 tries to solve this limitation by setting a Dirichlet prior on the topic
-distribution ~\cite{blei2003latent}.
+distribution.\cite{blei2003latent}
 
@@
 over a fixed vocabulary. Technically, the model assumes that the topics are
-generated first, before the documents ~\cite{Blei11introductionto}. Now for each document in the collection,
-we generate the words in a two-stage process:
+generated first, before the documents.\cite{Blei11introductionto} Now for 
+each document in the collection, we generate the words in a two-stage process:
 
-\begin{enumerate}
-\item Randomly choose a distribution over topics.
-\item For each word in the document:
-\begin{description}
-	\item (a) Randomly choose a topic from the distribution over topics in step 1.
-\end{description}
-\begin{description}
-	\item (b) Randomly choose a word from the corresponding distribution over the 
-	vocabulary.
-\end{description}
-\end{enumerate}
+\begin{algorithm}[H]
+\SetAlgoNoLine
+1. Randomly choose a distribution over topics.
+
+2. 
+\For{each word in the document}{
+	(a) Randomly choose a topic from the distribution over topics in 
+	step 1
+
+	(b) Randomly choose a word from the corresponding distribution over 
+	the vocabulary
+}
+\end{algorithm}
 
@@
 distinguishing characteristic of LDA. A more detailed explanation of the model
-follows in section 2.3.3.1.
+follows in section 2.2.3.1.
 
@@
 distribution over the vocabulary, with probability $\beta^w_z$ for word $w$ in
-topic $z$.
+topic $z$. We define the following variables and notation:
+\begin{itemize}
+  \item[] $k$ is the number of topics.
+  \item[] $V$ is the number of unique words in the vocabulary.
+  \item[] $\theta$  is the topic distribution (of length $k$) for a document,
+   drawn from a uniform Dirichlet distribution with parameter $\alpha$.
+  \item[] $z_{n}$ is a topic assignment for $word w_{n}$, sampled from 
+  $p(z_{n} = i|\theta) = \theta_{i}$.
+  \item[] \textbf{w}$ = (w_{1}, ... , w_{N})$ is a document with $N$ words.
+  \item[] $w_{n}^{i} = 1$ means that the word $w_{n}$ is the $i$-th word 
+  of the vocabulary.
+  \item[] $\beta$  is a $k \times V$ matrix, where each row $\beta_{i}$ 
+  is the multinomial distribution for the $i$-th topic. That is, 
+  $\beta_{ij} = p(w^{j} = 1 | z_{j} = i)$.
+\end{itemize}
 
-For each document $w$, in corpus $D$, the LDA generative process is as follows:
+For each document $w$, in corpus $D$, the LDA generative process is as follows, 
+with corresponding plate notation in Figure 2:
 
-\begin{enumerate}
-	\item Draw topic distribution $\theta_w \sim Dir(\alpha)$
-	\item For each of the $N$ words $w_n$:
-	\begin{description}
-	\item (a) Draw a specific topic $z_n \sim Multinomial(\theta)$
-	\item (b) Draw a word $w_n \sim Multinomial(\beta_{zn})$
-	\end{description}
-\end{enumerate}
+\begin{algorithm}[H]
+\SetAlgoNoLine
+1. Draw topic distribution $\theta_w \sim Dir(\alpha)$
+
+2. 
+\For{each of the $N$ words $w_n$}{
+	(a) Draw a specific topic $z_n \sim Multinomial(\theta)$
+
+	(b) Draw a word $w_n \sim Multinomial(\beta_{zn})$
+}
+\end{algorithm}
 
@@
 will model the corpus effectively. A setting where this could be problematic is
-when analyzing twitter data where new words in the form of slang, names and
-hashtags emerge over time. Another limitation is the fact that one has to state
+when analyzing data where new words in the form of slang or names emerge over 
+time. Another limitation is the fact that one has to state
 the number of topics the model should use. This is not a big issue, but could
 lead to some of the resulting topics to be insignificant.
-
 \begin{center}
-\begin{figure}
+\begin{figure}[h]
 \centering
-\includegraphics[width=0.6\textwidth]{LDA_standard_model.png}
+\includegraphics[width=0.6\textwidth, natwidth=561,natheight=197]{figs/LDA_standard_model.png}
 \caption{Plate notation of the standard LDA model}
@@
 partial derivatives of the likelihood function with respect to all variables,
-setting these derivatives to zero and solving the equations simultaneously 
-~\cite{Myung:2003}.
+setting these derivatives to zero and solving the equations simultaneously.
+\cite{Myung:2003}
 
@@
 document) is a problem of Bayesian inference. In the original paper it's being
-used a variational Bayes approximation of the posterior distribution;
-~\cite{blei2003latent} alternative inference techniques use Gibbs sampling and
+used a variational Bayes approximation of the posterior distribution;\cite{blei2003latent} alternative inference techniques use Gibbs sampling and
 expectation propagation. The goal of variational inference is to approximate an
@@
 (called the variational distribution) is  introduced. This new distribution has
-properties such that it can be efficiently computed ~\cite{Fox2011ATO}.
+properties such that it can be efficiently computed.\cite{Fox2011ATO}
 
@@
 
-An online variational inference algorithm is proposed by Hoffman et all.
-~\cite{onlineLDAvb} for fitting $\lambda$, the parameters to the variational
+An online variational inference algorithm is proposed by Hoffman et all.\cite{onlineLDAvb} for fitting $\lambda$, the parameters to the variational
 posterior over the topic distributions $\beta$. The "online LDA" is nearly as

### 2017-06-13 thesis_report/draft_thesis.tex
Rewrite VB and online VB LDA

@@
 
-We can analyze a corpus of documents with LDA by examining the posterior
-distribution of topics $\beta$, topic proportions $\theta$ and topic
-assignments $z$ conditioned on the documents. This reveals latent structure in
-the collection that can be used for prediction or data exploration. This
+We can see that this does in fact generate a document based on the topic 
+mixture $\theta$, the topic-word assignments $z$, and the probability 
+matrix $\beta$. Then, we can analyze a corpus of documents with LDA by 
+examining $\beta$, which is the posterior distribution of topics, $\theta$ 
+and $z$ conditioned on the documents. This reveals latent structure in
+the collection that can be used for prediction or data exploration.
+
+Hence, we observe the document, and must infer the latent topic mixture 
+$\theta$ and topic-word assignments $z$. LDA aims to infer:
+
+\begin{equation}
+p(\theta, \textbf{z} |\textbf{w}, \alpha, \beta)
+\end{equation}
+
+This
 posterior can't be computed directly; it is usually approximated using Markov
@@
 
-Consider a statistical model accompanied by a set of observed data $X$, a set of
-latent data $Z$, a set of latent variables $\theta$ and a likelihood function
-$L(\theta \mid X, Z)$. The marginal likelihood of the observed data is then
+The general idea behind the Expectation-Maximization algorithm is this:
 
-\begin{equation}
-L(\theta \mid X) = p(X \mid \theta) = \sum\limits_{Z} p(X, Z \mid \theta)
-\end{equation}
-
-which determines the maximum likelihood estimate of the latent variables. The
-sum is however often intractable and the EM algorithm solves this problem by
-iterating the following two steps:
-
-\begin{itemize}
-\item \textbf{Expectation step (E - step)}: For the current estimate of the 
-parameters $\theta^t$, calculate the expected value of the log likelihood function:
-\begin{equation}
-Q(\theta \mid \theta^t) \leftarrow \mathbb{E}_{Z \mid X, \theta^t}
- [\log(L(\theta \mid X, Z))]
-\end{equation}
-\item \textbf{Maximization step (M - step)} Maximize the expected value function 
-with regard to the parameters:
-\begin{equation}
-\theta^{t + 1} \leftarrow arg \max\limits_{\theta} Q(\theta \mid \theta^t)
-\end{equation}
-\end{itemize}
+\begin{enumerate}
+\item Start with an initial estimate of what each parameter might be.
+\item \textbf{E step}: Compute the likelihood that each parameter produces 
+the data point.
+\item Calculate weights for each data point based on the likelihood of it 
+being produced by a parameter.
+\item \textbf{M step}: Combine these weights together with the data to 
+compute a better estimate for the parameters.
+\item Repeat steps 2 to 4 until the parameter estimate converges.
+\end{enumerate}
 
@@
 
-Learning the various distributions (the set of topics, their associated word
-probabilities, the topic of each word, and the particular topic mixture of each
-document) is a problem of Bayesian inference. In the original paper it's being
-used a variational Bayes approximation of the posterior distribution;\cite{blei2003latent} alternative inference techniques use Gibbs sampling and
+In LDA, our ultimate goal is to find the posterior distribution of latent topic variables after observing training data.
+However, computing this distribution is intractable, so we’re forced to approximate.
+One approximation approach is to
+use an optimization method called Variational Bayes. In the original paper it's 
+being used a variational Bayes approximation of the posterior distribution;\cite{blei2003latent} alternative inference techniques use Gibbs sampling and
 expectation propagation. The goal of variational inference is to approximate an
@@
 
-The variational distribution is a function of a set of free parameters that are optimized such that the variational distribution is as close as possible to the 
-actual target posterior distribution where closeness is measured in terms of KL divergence.
-Minimizing the KL divergence between the variational distribution and the target
-posterior is equivalent to maximizing the Evidence Lower BOund (ELBO) which is
+In short, we approximate the true distribution by a simple distribution $q$, and associate parameters $\phi$, $\gamma$, $\lambda$ with the original parameters 
+$z$, $\theta$, $\beta$ respectively. Recall that $z$ gives the topic assignments 
+for each word in each document, $\theta$ gives the topic composition of each 
+document, and $\beta$ gives the word-topic probabilities for each word and each 
+topic. The variational distribution is a function of a set of free parameters that 
+are optimized such that the variational distribution is as close as possible to 
+the actual target posterior distribution where closeness is measured in terms of 
+KL divergence.
 
+Specifically, we have:
 \begin{equation}
-L(q) = E_q [log p(x, z, \beta)] -  E_q [log q(z, \beta)]  
+q(z_{di}=k) = \phi_{dw_{di}k}
 \end{equation}
-
-The variational distribution has the property that it can be efficiently
-computed. This is done by making each hidden variable independent of each other.
-
 \begin{equation}
-q(z, \beta) = q(\beta \mid \lambda) \prod\limits_{n=1}^N \prod\limits_{j=1}^J q(z_{nj} \mid \phi_{nj})   
+q(\theta_{d}) = dirichlet(\theta_{d}; \gamma_{d})
+\end{equation}
+\begin{equation}
+q(\beta_{k}) = dirichlet(\beta_{k}; \lambda_{k})
 \end{equation}
@@
 by $\gamma$, and the posterior over the topics $\beta$ is parameterized by
-$\lambda$. Furthermore, each hidden variable is governed by its own variational
-parameter so the variational parameters $\lambda$ governs the global variables
-$\beta$ and the variational parameters $\phi_n$ govern the local variables $z_n
-q(\beta \mid \lambda)$ and $q(z_{nj} \mid \phi_{nj})$ take the same form as the
-complete conditionals $p(\beta \mid x, z, \alpha)$ and $p(z_{nj} \mid x_n, z_{n,
--j}, \beta)$, but the natural parameters are now $\lambda$ and $\phi_{nj}$,
-respectively to give
+$\lambda$.
 
+Our goal is to estimate $\phi$, $\gamma$ and $\lambda$. In both VB and 
+online VB LDA, we alternate between two steps:
+\begin{enumerate}
+\item E-Step: Estimate $\phi$, $\gamma$ using the current value of $\lambda$
+\item M-Step: Update $\lambda$, using the current value of $\phi$
+\end{enumerate}
+
+In Variational Bayes, we perform multiple passes over the entire dataset, 
+checking each time for convergence. During each pass, the algorithm does an 
+E-Step using the entire dataset and an M-Step, which updates $\lambda$ using 
+$\phi$ values from every document. At a high level:
+
+\begin{algorithm}
+\SetAlgoNoLine
+E Step:
+
+\For{$d = 1$ to $numDocs$}{
+	initialize $\gamma$
+
+    \Repeat{change in $\phi < \epsilon$}{
+        update $\phi$
+        update $\gamma$
+     }
+}
+M Step:
+
+update $\lambda$
+\end{algorithm}
+
+The specific updates are:
 \begin{equation}
-q(\beta \mid \lambda) = h(\beta) exp(\lambda^T t(\beta) - \alpha_g(\lambda))
+\phi_{d,word_{i},k} \propto e^{E_{q}(log \theta_{d,k})+E_{q}(log\beta_{k,word_{i}})}
 \end{equation}
 \begin{equation}
-q(z_{nj} \mid \phi_{nj}) = h(z_{nj}) exp(\phi_{nj}^T t(z_{nj}) - \alpha_l(\phi_{nj}))
-\end{equation}
-
-Where $h(.)$ is called the base measure, $\alpha(.)$ is called the log-
-normalizer, $\eta(.)$ is called the natural parameter, and $t(.)$ is called the
-sufficient statistics. Furthermore, we also assume that the prior distribution
-over $\beta$ is part of the exponential family. We maximize the ELBO objective
-function with a coordinate ascent procedure. We find its gradient with respect
-to the global variational parameter $\lambda$ and find the value of $\lambda$
-that sets the gradient to zero. We do the same thing for the local parameters
-$\phi_n$. We iterate between these updates until we converge to the maximum of
-the ELBO. The updates are given without proof, but the general procedure is to
-write the ELBO in terms of parameter of interest (either $\lambda$ or $\phi_n$)
-then take the gradient and set it to zero.
-
-\begin{equation}
-\lambda = E_q[\eta_g(x, z, \alpha)]
+\gamma_{d,k} = \alpha + \sum_{word_{i}}\phi_{d,word_{i},k}n_{d,word_{i}}
 \end{equation}
 \begin{equation}
-\phi_{nj} = E_q[\eta_l(x_n, z{n, -j}, \beta)]
+\lambda_{k,word_{i}}=\eta +\sum_{d}n_{d,word_{i}}\phi_{d,word_{i},k}
 \end{equation}
-
-Therefore the updates of each variational parameter are equal to the expected
-value of the natural parameters of the complete conditionals. A simple outline 
-of the algorithm ~\cite{alexminnar} is given below
-
-\begin{algorithm}[H] 
-\SetAlgoLined
-
-Initialize $\lambda^{(0)}$ randomly.
-\Repeat{the ELBO converges}{
-	\For{each local variational parameter $\phi_{nj}$}{\label{forins}
-		Update $\phi_{nj}^{(t)} = \mathbb{E}_{q^{(t - 1)}}[\eta_{l,j}(x_n, z_{n,-j}, \beta)]$.
-	}
-	Update the global variational parameters, $\lambda^{(t)} = \mathbb{E}_{q^{(t)}}[\eta_g (z_{1:N}, x_{1:N})]$.
-}
-\caption{Variational Bayes for LDA} 
-\end{algorithm}
-
-As you can see, in the local parameter update (in the $for$ loop), we have to
-iterate over every data point in the data set which is computationally
-expensive. The algorithm above has constant memory requirements and empirically
+Where $n_{d,word_{i}}$ is the number of occurrences of $word_{i}$ in document $d$.
+The algorithm above has constant memory requirements and empirically
 converges faster than collapsed Gibbs sampling. However, it still requires a
@@
 
-The $t$-th document (or equivalently a vector of words counts) we perform the
-E-step like Variational inference to find locally optimal values for $\gamma_t$
-and $\phi_t$ while holding $]\lambda$ fixed. And then (the M-step) compute the
-optimal value for $\lambda$ if the whole document corpus consisted of this
-$t$-th document repeated $M$ times (M: the number of documents in the corpus).
-After we have the optimal value of $\lambda$ for the   document, $\lambda$*, we
-update the value of $\lambda$ using a weighted average of its previous value and
-$\lambda_d$∗. The weight given to $\lambda$∗ is given by 
-$\rho_t = (\tau_{0} + t)^{-\kappa}$, with $\kappa \in (0.5, 1]$. 
-$\kappa$ controls the importance we give to most recents values of $\lambda$∗.
-
 In short, we approximate the true distribution by a simple distribution $q$, and
 associate parameters $\phi,\gamma,\lambda$ with the original parameters $z,\theta,
-\beta$ respectively. Recall that $z$ gives the topic assignments for each
+\beta$ respectively, as in VB. Recall that $z$ gives the topic assignments for each
 word in each document, $\theta$ gives the topic composition of each document, 
@@
 
-Algorithm 2 shows the inference process given a vector of word counts. The
-explicit formulas for $\mathbb{E}_q[log \theta_{tk}]$ and $\mathbb{E}_q[log
-\beta_{kw}]$ are:
+In online Variational Bayes, we only make a single sweep of the entire dataset, analyzing a chunk of documents at a time. A chunk could be a single document, 
+50 documents, or even the entire dataset. Let’s let a chunk be 1000 documents.
 
-\begin{equation}
-\mathbb{E}_q[log \theta_{tk}] = \Psi(\gamma_{tk}) - \Psi(\sum_{i=1}^K \gamma_{ti})
-\end{equation}
-
-\begin{equation}
-\mathbb{E}_q[log \beta_{kw}] = \Psi(\lambda_{kw}) - \Psi(\sum_{i=1}^W \lambda_{ki})
-\end{equation}
-
-Where $\Psi$ denotes the derivative of the logarithm of the gamma function.
+The online E-Step only uses the current chunk; instead of holding all the 
+documents we now only have to hold 1000 in memory. The E-Step finds locally 
+optimal values for $\phi$ and $\gamma$, while in the M-Step, we first compute 
+$\lambda^{*}$, which is the value of $\lambda$ if we imagined that the entire 
+dataset is made up of $\frac{numDocs}{chunkSize}$ copies of the current chunk. 
+Then $\lambda$ is updated using a weighted sum of $\lambda^{*}$ and $\lambda$:
 
 \begin{algorithm}
-\SetAlgoLined
-Define $\rho_t = (\tau_{0} + t)^{-\kappa}$
+\SetAlgoNoLine
+E Step:
 
-Initialize $\lambda$ randomly.
+initialize $\gamma$
 
-\For{$t = 0 to \infty$}{\label{forins}
-	E step:
+\Repeat{change in $\phi < \epsilon$}{
+        update $\phi$
 
-	Initialize $\gamma_{tk} = 1$
+        update $\gamma$
+}
+M Step:
 
-	\Repeat{$\frac{1}{K} \sum_k$ |change in $\gamma_{tk}$| $< 0.00001$}{
-		Set $\phi_{twk} \propto exp${$\mathbb{E}_q[log \theta_{tk}]$ + $\mathbb{E}_q[log\beta_{kw}]$}
+compute $\lambda^{*}$
 
-		Set $\gamma_{tk} = \alpha + \sum_w \phi_{twk}n_{tw}$
-	}
-	M step:
-
-	Compute $\lambda_{kw}* = \eta + Dn_{tw}\phi_{twk}$
-
-	Set $\lambda = (1 - \rho_t)\lambda + \rho_{t}\lambda*$
-}
+update $\lambda$
+\end{algorithm}
 
@@
 most probable words for each topic by looking at the word probabilities in 
-each row of $\lambda$.
-
-\caption{Online Variational Bayes for LDA} 
-\end{algorithm}
+each row of $\lambda$.\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}
 

### 2017-06-14 thesis_report/draft_thesis.tex
Related work: part (1/2)

@@
 
+\section{Related work}
+
+This chapter surveys previous work in topic modeling on scientific data. Topic
+modeling algorithms provides a suite of algorithms to discover hidden thematic
+structure in large collections of texts and can be adapted to many kinds of
+data. These algorithms can be used to summarize, visualize and explore a
+collection of documents. The papers listed below are applying a Latend Dirichlet
+Allocation model in an interesting approach on their corpus.
+
+D.Blei's research focuses on probabilistic topic models, Bayesian methods and
+approximate posterior inference. In his work "Introduction to Probabilistic
+Topic Models",\cite{Blei11introductionto} he describes the basic ideas behind
+LDA and applies the model to articles from the journal "Science". The model
+assumes that the topics are generated first, before the documents and that the
+documents axhibit multiple topics, but each one of them exhibit those topics in
+different proportion. In our implementation we also use the LDA model and we
+follow a similar approach, since we don't use any previous information about the
+subjects that run through our dataset and the documents are not labeled with
+keywords or topics. The topic distributions arise by computing the hidden
+structure that resembles the thematic structure of the collection.
+
+The paper that mostly infuenced our work is "Finding Scientific Topics", by
+T.Griffiths and M.Steyvers.\cite{griffiths_steyvers04} They investigated
+abstract data from articles published in the Proceedings of the National Academy
+of Sciences (PNAS) from 1991 to 2001 and compared research topics obtained from
+topic modeling with existing categories. We also use the abstacts of the
+projects as documents for the model. (to be continued)
+
 \section{Theoretic background}
@@
 from the analysis of the original texts, topic modeling algorithms do not
-require any prior annotations or labeling of the documents.\cite{Blei:2012:PTM:2133806.2133826}
+require any prior annotations or labeling of the documents.\cite{Blei11introductionto}
 
@@
 is a mixture of a small number of topics and that each word's occurrence is
-attributable to one of the document's topics.\cite{Blei:2012:PTM:2133806.2133826}
+attributable to one of the document's topics.\cite{Blei11introductionto}
 
@@
 
-\section{Related work}
-
 \section{Methodology}

### 2017-06-14 thesis_report/draft_thesis.tex
Related work: part (2/2)

@@
 projects as documents for the model. (to be continued)
+
+Griffiths and Steyvers describe LDA and present a Marckv Chain Monte Carlo
+algorithm for inference in the model, illustrating the operation of the
+suggested algorithm on a small dataset, and then on a larger corpus of PNAS
+abstracts. Finally, they define the dynamics of the topics as a means of gaining
+insight into the dynamics of science. As "hot" topics are identified the topics
+that appear more frequently over the years (positive linear trend), and as
+"cold" the ones that appear less frequently (negative linear trends over time).
+We also analyze the topics over time, in order to highlight potential trends in
+scientific research in EU and USA.
+
+Inspired by Griffiths and Steyvers, L.Sun and Y.Yin wrote a paper, "Discovering
+themes and trends in transportation research using topic modeling",
+\cite{Sun201749} about topic modeling in transportation research. 
+Considering approximately 17000 abstracts of articles published on 22 
+leading journals in transportation research as documents, they infer 50 
+topics by using LDA. Compared to "Finding scientific topics", Sun and 
+Yin use more than one journal (22 popular journals) and they
+investigate the journal-topic distribution and journal similarity. In our
+analysis, we assume that EU and USA are 2 countries (like 2 different journals),
+with different proportions of documents-projects, and we visualize the topic
+similarity of the two countries per framework programme.
+
+To best of our knowledge, there is no work done in the field of topic modeling
+on scientific projects between EU and USA. There is limited information from
+European Commission about the evolution and the results of the projects provided
+by the official website.
 

### 2017-06-15 thesis_report/draft_thesis.tex
minor fixes in Related work on the thesis report

@@
 investigate the journal-topic distribution and journal similarity. In our
-analysis, we assume that EU and USA are 2 countries (like 2 different journals),
+analysis, we identify the EU and the USA as 2 regions (like 2 different journals),
 with different proportions of documents-projects, and we visualize the topic
-similarity of the two countries per framework programme.
+similarity of the two regions per framework programme.
 
@@
 
-Details about the implementation, system specs etc.
+For the implementation, we used the Gensim package (Radim Řehůřek,
+2009)\cite{rehurek_lrec} which implements an efficient online LDA algorithm, to
+extract the topics of a given corpus. Gensim uses a fast implementation of
+online LDA parameter estimation based on "Online Learning for Latent Dirichlet
+Allocation".\cite{onlineLDAvb} The algorithm runs in constant memory, which
+means that the size of the training corpus does not affect memory footprint, so
+it can process corpus larger than RAM.
+
+The LDA model requires some basic input parameters; for both datasets we chose
+the number of topics $K=10$. The hyperparameter $\alpha$, which affects the
+sparsity of the document-topic distribution $\theta$, is by default a symmetric
+$\frac{1.0}{num_topics} = 0.1$ prior. We left the default value of $chunksize=2000$. We
+started with 50 iterations and later we increased the number of iterations,
+until the training converged. We used 7000 iterations for each framework
+programme of the EU dataset and 8000 for each framework of the USA dataset. In
+the USA dataset, we used $passes=1$, while in the EU dataset we switched to
+$passes=2$, because the training could not converge, despite the large number of
+the iterations.
+
+The implementation was run on a computer with an Intel® Xeon® Processor E5-1410
+(10MB Cache, 2.8 GHz, 4 cores, 8 threads) and RAM=12 GB.
 
 \section{Analysis and results}
+
+In this section, we show our main results. We focus on finding differents
+between the two datasets in terms of topic distribution and later we 
+investigate the evolution of the topics over time of each dataset separately.
+
+\subsection{Discovering topics on EU and USA projects}
+
+wordclouds per FP?
+
+\subsection{Topic evolution over time}
 

### 2017-06-17 usa_gensim/get_year_topic_prop.py
Removed year 2017 from USA topic evolution diagram

@@ -25,7 +25,7 @@ sz['normalized'] = np.where(sz['year']=='1994',
                     (sz['count']/sz.loc[sz['year'] == '1994', 'count'].sum())*100, sz['count'])
 
 years = ['1995', '1996', '1997', '1998', '1999', '2000', '2001', '2002', '2003', '2004', '2005', '2006',
-			'2007', '2008', '2009', '2010', '2011', '2012', '2013', '2014', '2015', '2016', '2017']
+			'2007', '2008', '2009', '2010', '2011', '2012', '2013', '2014', '2015', '2016']
 for year in years:
 	sz['normalized'] = np.where(sz['year']==year, 
                     (sz['count']/sz.loc[sz['year'] == year, 'count'].sum())*100, sz['normalized'])

### 2017-06-17 usa_gensim/usa_merge_dfs.py

@@ -23,27 +23,10 @@ from gensim.parsing.preprocessing import STOPWORDS
 import string
 import logging
 
-# df4 = pd.read_pickle('pickle_data/usa' + 'FP4')
-# df5 = pd.read_pickle('pickle_data/usa' + 'FP5')
-# df6 = pd.read_pickle('pickle_data/usa' + 'FP6')
-# df7 = pd.read_pickle('pickle_data/usa' + 'FP7')
-# df20 = pd.read_pickle('pickle_data/usa' + 'H2020')
-
-# def get_merged_docs(df):
-#     df = df[['title','objective', 'framework_programme']]
-#     df = df.dropna(how='any')
-#     df['merged'] = df['title'] + ' ' + df['objective']
-#     df1 = df[['merged', 'framework_programme']]
-#     return df1
-
-# dfusa = pd.concat([get_merged_docs(df) for df in [df4, df5, df6, df7, df20] ])
-
-# print dfusa.columns
-# print dfusa.shape
-
-# dfusa.to_pickle('pickle_data/df_usa_all')
 
 dfusa = pd.read_pickle('pickle_data/dfUSA')
+
+print dfusa[dfusa['year'].astype(str).str.contains('2017')]
 
 RE_PUNCTUATION = '|'.join([re.escape(x) for x in string.punctuation])
 
@@ -95,12 +78,14 @@ class ObjectivesCorpus(corpora.textcorpus.TextCorpus):
 
 objectives_corpus = ObjectivesCorpus(dfusa['merged'])
 
+iterations = 8000
+# passes = 10
 t0 = time()
-
+logging.basicConfig(format='%(levelname)s : %(message)s', level=logging.INFO)
 lda = gensim.models.ldamodel.LdaModel(corpus = objectives_corpus, 
                                         id2word = objectives_dictionary, 
                                         num_topics = 10,
-                                        iterations = 8000,
+                                        iterations = iterations,
                                         random_state=np.random.seed(42))
 
 print("done in %0.3fs." % (time() - t0))
@@ -111,10 +96,9 @@ for t in range(lda.num_topics):
     plt.figure()
     plt.imshow(elements)
     plt.axis("off")
-    t = t + 1
     plt.title("Topic #" + str(t))
     # plt.savefig('USA' + df_name + '_topic' + str(t) + '_' + str(i) + '_' + str(iterations) + '.png')
[…]

### 2017-06-17 thesis_report/draft_thesis.tex
Topic evolution over time in EU (1/2)

@@
 \usepackage{url}
+\usepackage{subfig}
 
@@
 
+One of our goals is to identify trends in scientific research in EU and USA, in
+order to give some insights to researchers and scientists regarding potential
+trends. Fot this analysis, we run the model for the whole dataset, instead of
+running the model per FP), for the EU and the USA, respectively. The outcome was
+10 topics for each region from 1994 to 2017 for the EU and from 1994 to 2016 for
+the USA.\footnote{in this implementation we removed the projects of the year
+2017 from the USA dataset, because the amount of projects-documents was too
+small compared to the other years and it was affecting the result of the trend
+for eact topic.}
+
+\subparagraph{Trends in the EU}
+
+In figure x we show the 10 topics that consists of the 20 top words with the
+highest posterior probability of belonging to the topic. The size of each word
+is in proportion to each probability; the bigger the word, the higher the
+probability. Each wordcloud describes a topic, which we can find intuitevely.
+Below are listed the topics that we found corresponding to the words that
+describe them:
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic0_all.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic1_all.png}} &
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic2_all.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic3_all.png}} &
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic4_all.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic5_all.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic6_all.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic7_all.png}} &
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic8_all.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic9_all.png}} &
+\end{tabular}
+\caption{Wordclouds of topics of the EU dataset (1994-2017)}
+\end{figure}
+\end{center}
+
+\subparagraph{Trends in the USA	}
+
 \section{Conclusion}

### 2017-06-18 thesis_report/draft_thesis.tex
Fixed: topics in USA, wordclouds & figs

@@
 
+\begin{center}
+\begin{figure}
+\centering
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic0_12000_all_docs.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic1_12000_all_docs.png}} &
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic2_12000_all_docs.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic3_12000_all_docs.png}} &
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic4_12000_all_docs.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic5_12000_all_docs.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic6_12000_all_docs.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic7_12000_all_docs.png}} &
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic8_12000_all_docs.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic9_12000_all_docs.png}} &
+\end{tabular}
+\caption{Wordclouds of topics of the USA dataset (1994-2016)}
+\end{figure}
+\end{center}
+
 \section{Conclusion}

### 2017-06-18 thesis_report/draft_thesis.tex
Update: Topic evolution in USA

@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic0_all.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic1_all.png}} &
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic2_all.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic3_all.png}} &
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic4_all.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic5_all.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic6_all.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic7_all.png}} &
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic8_all.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/EU_topic9_all.png}} &
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic0_all.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic1_all.png}} &
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic2_all.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic3_all.png}} &
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic4_all.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic5_all.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic6_all.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic7_all.png}} &
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic8_all.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic9_all.png}} &
 \end{tabular}
@@
 \subparagraph{Trends in the USA	}
+
+Just like the EU dataset, we found the 10 topics of the USA dataset from 1994 to
+2016. Since, we're looking for the topic distribution over time, in this
+implementation we took the projects per year (instead of using the separation of
+the dataset per FP), to visualize the evolution of each topic per year. We ran
+the LDA model with 12000 iterations and the dame value of the rest of the
+parameters, as described in section 4.3.
+
+Each one of the wordclouds in figure X represents a topic. The topics that are
+described in the wordclouds are listed below:
+
+\begin{itemize}
+\item[] Topic 0: Material science and High energy physics
+\item[] Topic 1: Mathematics
+\item[] Topic 2: (Molecular) biology, Genetics
+\item[] Topic 3: Science of social policy and economics
+\item[] Topic 4: International research and conferences
+\item[] Topic 5: Chemistry and Materials science
+\item[] Topic 6: STEM education
+\item[] Topic 7: Climatology, Atmospheric and Ocean sciences
+\item[] Topic 8: Molecular biology 
+\item[] Topic 9: Mechanical engineering
+\end{itemize}
+
+!!!Write what you computed to get the results
 
@@
 
+\begin{center}
+\begin{figure}
+\includegraphics[width=1.0\textwidth, natwidth=707,natheight=483]
+{figs/topic-evolution-usa.png}
+\caption{Topics over time in USA}
+\end{figure}
+\end{center}
+
 \section{Conclusion}

### 2017-06-18 thesis_report/draft_thesis.tex
Update: Topic evolution in USA

@@
 
+In figure X we plot the topic distribition over time. We can easily observe that
+the topic 6, which refers to STEM education, is becoming a trend in the United
+States over the years, while most of the other topics' evolution doesn't show up
+such a high increace. Topics 5 and 8, which refer to Chemistry \& Materials
+science and Molecular biology, respectively, show a small decreace over the
+years.  +++
+
+In general, the STEM (science, technology, engineering and math) related
+research and education is becoming more and more popular, which is not
+surprising, since the National Science Foundation itself estimates that 80/% of
+the jobs available during the next decade will require math and science skills.
+Even the concept of STEM was first introduced by Judith A. Ramaley, the former
+director of the National Science Foundation’s education and human resources
+division.
+
 \begin{center}

### 2017-06-19 thesis_report/draft_thesis.tex
Update: Description of the computation of topic distribution over time

@@
 
+In order to find the topic distribution over time, we need the topic
+distribution of each project-document. As we mentioned before, LDA assumes that
+each document exhibits multiple topics. After running the model to our dataset,
+we get the document-topic distribution and we keep the topic with the highest
+probability (the one that most likely belongs to this document). Then, we
+calculate the proportion of each topic per FP, using the following equation:
+\begin{equation}
+topicProportion(k, fp) = \frac{\sum num of docs_{k,fp}}{\sum num of docs_{fp}} * 100
+\end{equation}
+where $k$ is the number of the topic id, $fp$ is the framework programme,
+$fp \in [FP4, FP5, FP6, FP7, H2020]$. The topic proportion of each topic in 
+the FP equals to the sum of the number of the documents assigned to this 
+topic during the FP, nomralized by the number of the documents-projects 
+occuring in this FP. In figure X we plot the results of the topic proportion 
+over time.
+
 \subparagraph{Trends in the USA	}
@@
 \end{itemize}
-
-!!!Write what you computed to get the results
 
@@
 
+Just like the computation in the EU dataset, we calculate the topic 
+distribution over time for the USA dataset. We get the document-topic 
+distribution, we keep the topic with the highest probability and finally 
+we calculate the proportion of each topic per
+year (instead of FP), using the following equation:
+
+\begin{equation}
+topicProportion(k, y) = \frac{\sum num of docs_{k,y}}{\sum num of docs_{y}} * 100
+\end{equation}
+
+where $k$ is the number of the topic id, $y$ is the year between 1994-2016. The
+topic proportion of each topic per year equals to the sum of the number of the
+documents assigned to this topic during the year, nomralized by the number of
+the documents-projects  occuring in this year.
+
 In figure X we plot the topic distribition over time. We can easily observe that
@@
 science and Molecular biology, respectively, show a small decreace over the
-years.  +++
+years. Topics 9 and 0 (Mechanical Engineering, Materiac Science and High energy
+physics) show a small increase over the last 5 years. Mathematics' evolution
+over time (Topic 1) looks stable on average and shows up as a popular subject
+over the last 22 years, while Social Sciences and International Research (Topic
+3 and 4) show a small decrease over the last 3 years.  Molecular biology and
+Genetics (Topic 2) has an increasing polularity from 1994 to 2001 and later is
+starting to stabilize. Climatology, Atmospheric and Ocean sciences look stable
+the first years, while from 2006 up to date it is gradually becoming less
+popular over the years.
 

### 2017-06-19 eu_gensim/eu_iterations.py
Update: EU topics and saved LDA model

@@ -8,6 +8,7 @@ import gensim
 
 import matplotlib
 matplotlib.use('Agg')
+
 import matplotlib.pyplot as plt
 
 from wordcloud import WordCloud
@@ -18,7 +19,7 @@ from gensim.corpora.dictionary import Dictionary
 from collections import defaultdict
 from gensim.parsing.preprocessing import STOPWORDS
 from time import time
-
+import json
 import string
 import logging
 # logging.basicConfig(format='%(levelname)s : %(message)s', level=logging.INFO)
@@ -75,6 +76,7 @@ for text in objectives_split:
 objectives_split = objectives_split.apply(lambda tokens: [token for token in tokens if (frequency[token] > 5)])
 
 objectives_dictionary = Dictionary(objectives_split)
+# objectives_dictionary.save('./lda_saved/dict_eu' + df_name + '.dict')
 
 print (objectives_dictionary)
 print
@@ -103,6 +105,7 @@ class ObjectivesCorpus(corpora.textcorpus.TextCorpus):
             
 
 objectives_corpus = ObjectivesCorpus(objectives_split)
+# corpora.MmCorpus.serialize('./lda_saved/corpus_eu' + df_name + '.mm', objectives_corpus)
 
 print'Corpus size: ', (objectives_corpus)
 
@@ -121,7 +124,11 @@ for i in range(1):
     #     text_file.write(str(lda.print_topics(num_topics=10, num_words=15)))
     #     text_file.close()
 
+
 print("done in %0.3fs." % (time() - t0))
+
+lda.save('./lda_saved/lda_eu' + df_name + '.model')
+
 
 for t in range(lda.num_topics):
     words = dict(lda.show_topic(t, 15))
@@ -129,7 +136,6 @@ for t in range(lda.num_topics):
     plt.figure()
     plt.imshow(elements)
     plt.axis("off")
-    t = t + 1
     plt.title("Topic #" + str(t))
     # plt.savefig('EU' + df_name + '_topic' + str(t) + '_' + str(iterations) + '.png')
     plt.savefig('eu_'+ df_name + '_wordclouds/EU' + df_name + '_topic' + str(t) + '_' + str(args.iterations) + '.png')

### 2017-06-19 compare_FPs_topics.py
Code for comparing the datasets per FP (with JSD)

@@ -1,0 +1,86 @@
+# coding: utf-8
+
+import pandas as pd
+import numpy as np
+import gensim
+import argparse
+import pickle
+import scipy.stats as stats
+
+from gensim import corpora, models, similarities, matutils
+from gensim.corpora.dictionary import Dictionary
+
+from scipy.stats import entropy
+from numpy.linalg import norm
+
+parser = argparse.ArgumentParser()
+
+parser.add_argument('dataset',
+                    action='store',
+                    choices=['FP4', 'FP5', 'FP6', 'FP7', 'H2020'],
+                    help='input dataset')
+
+args = parser.parse_args()
+
+df = args.dataset
+
+# Load the LDA model of the two datasets
+ldaEU = gensim.models.ldamodel.LdaModel.load('./eu_gensim/lda_saved/lda_eu'+ df +'.model')
+ldaUSA = gensim.models.ldamodel.LdaModel.load('./usa_gensim/lda_saved/lda_usa'+ df +'.model')
+
+def get_topic_vectors(topic_eu_id, topic_usa_id):
+	# get the words and their probabilities per topic
+	get_topic_terms_eu = ldaEU.show_topic(topic_eu_id, topn=ldaEU.num_terms)
+	get_topic_terms_usa = ldaUSA.show_topic(topic_usa_id, topn=ldaUSA.num_terms)
+
+	# keep the words in a list as a dictionary
+	eu_list = [x[0] for x in get_topic_terms_eu]
+	usa_list = [x[0] for x in get_topic_terms_usa]
+
+	# add the words that don't exist in one of them, with probability = 0.0
+	for i in get_topic_terms_eu:
+		if i[0] not in usa_list:
+			get_topic_terms_usa.append((i[0], 0.0))
+
+	for j in get_topic_terms_usa:
+		if j[0] not in eu_list:
+			get_topic_terms_eu.append((j[0], 0.0))
+
+	# sort the list of the tuples (word, probability) in alphabetic order
+	get_topic_terms_eu = sorted(get_topic_terms_eu, key=lambda x: x[0])
+	get_topic_terms_usa = sorted(get_topic_terms_usa, key=lambda x: x[0])
+
+	# get only the probabilities as vectors
+	topicEUvec = [x[1] for x in get_topic_terms_eu]
[…]

### 2017-06-20 thesis_report/draft_thesis.tex
Fixed: misspellings in the Related work section

@@
 assumes that the topics are generated first, before the documents and that the
-documents axhibit multiple topics, but each one of them exhibit those topics in
+documents exhibit multiple topics, but each one of them exhibit those topics in
 different proportion. In our implementation we also use the LDA model and we
@@
 of Sciences (PNAS) from 1991 to 2001 and compared research topics obtained from
-topic modeling with existing categories. We also use the abstacts of the
-projects as documents for the model. (to be continued)
-
-Griffiths and Steyvers describe LDA and present a Marckv Chain Monte Carlo
+topic modeling with existing categories. In our implementation, we also use 
+the abstacts of the projects as documents for the model.
+
+Griffiths and Steyvers describe LDA and present a Markov Chain Monte Carlo
 algorithm for inference in the model, illustrating the operation of the

### 2017-06-20 eu_gensim/test_merge_dfs.py
Update: EU topics & wordclouds in the whole dataset

@@ -39,9 +39,11 @@ import logging
 
 # df_all = pd.concat([get_merged_docs(df) for df in [df4, df5] ])
 
-# df_all.to_pickle('df_all')
+# df_all.to_pickle('dfs/df_all')
 
 df_all = pd.read_pickle('dfs/df_all')
+
+print df_all.shape
 
 RE_PUNCTUATION = '|'.join([re.escape(x) for x in string.punctuation])
 
@@ -52,8 +54,9 @@ df_all['merged'] = df_all['merged'].apply(lambda tokens: [token for token in tok
 df_all['merged'] = df_all['merged'].apply(lambda tokens: [token for token in tokens if not(token.isdigit())])
 df_all['merged'].head(2)
 
-
-list_stopwords = ['data','will', 'develop', 'development', 'project', 'research', 'new', 'use', 'europe', 'european', 'based']
+# , 'study', 'propose', '•'
+list_stopwords = ['data','will', 'develop', 'development', 'project', 'research', 'new', 'use', 'europe', 'european', 'based', 
+                    'study', '•']
 # if dfname == 'FP4':
 #     list_stopwords.append('des')
 
@@ -97,28 +100,31 @@ class ObjectivesCorpus(corpora.textcorpus.TextCorpus):
 
 objectives_corpus = ObjectivesCorpus(df_all['merged'])
 
+# random seed = 1, 42
+# ,random_state = np.random.seed(42)
 t0 = time()
+logging.basicConfig(format='%(levelname)s : %(message)s', level=logging.INFO)
+
 lda = gensim.models.ldamodel.LdaModel(corpus = objectives_corpus, 
                                         id2word = objectives_dictionary, 
-                                        num_topics = 10,
-                                        random_state = np.random.seed(42),
-                                        iterations = 7000)
+                                        num_topics = 12,
+                                        passes = 3,
+                                        iterations = 10000)
 
 print("done in %0.3fs." % (time() - t0))
 
 # Code for visualizing topics to Wordclouds
 
-# for t in range(lda.num_topics):
-#     words = dict(lda.show_topic(t, 20))
-#     elements = WordCloud(background_color='white', width=300, height=180, max_font_size=36, colormap='winter', prefer_horizontal=1.0).fit_words(words)
-#     plt.figure()
-#     plt.imshow(elements)
-#     plt.axis("off")
-#     t = t + 1
[…]

### 2017-06-20 thesis_report/draft_thesis.tex
Add: appendix

@@
 
-Many applications of topic modeling also eliminate from the vocabulary so-
+Many applications of topic modeling also eliminate from the vocabulary so
 called “stop” words. These are words that are common in most documents and do
@@
 \subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic9_all.png}} &
+\subfloat[Topic 10]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic10_all.png}} &
+\subfloat[Topic 11]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic11_all.png}}\\
 \end{tabular}
@@
 
+\clearpage
+\appendix
+
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic0_7000.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic1_7000.png}}&
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic2_7000.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic3_7000.png}}&
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic4_7000.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic5_7000.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic6_7000.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic7_7000.png}}&
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic8_7000.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic9_7000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the EU FP4 (1994-1998)}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic0_7000.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic1_7000.png}}&
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic2_7000.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic6_7000.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic7_7000.png}}&
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic8_7000.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic9_7000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the EU FP5 (1998-2002)}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic0_7000.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic1_7000.png}}&
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic2_7000.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic3_7000.png}}&
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic4_7000.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic5_7000.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic6_7000.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic7_7000.png}}&
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic8_7000.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic9_7000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the EU FP6 (2002-2006)}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic0_7000.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic1_7000.png}}&
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic2_7000.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic3_7000.png}}&
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic4_7000.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic5_7000.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic6_7000.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic7_7000.png}}&
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic8_7000.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic9_7000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the EU FP7 (2007-2013)}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic0_20000.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic1_20000.png}}&
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic2_20000.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic3_20000.png}}&
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic4_20000.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic5_20000.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic6_20000.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic7_20000.png}}&
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic8_20000.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic9_20000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the EU H2020 (2014-2020)}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the USA (1994-1997)}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic0_8000.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic1_8000.png}}&
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic2_8000.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic3_8000.png}}&
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic4_8000.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic5_8000.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic6_8000.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic7_8000.png}}&
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic8_8000.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic9_8000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the USA (1998-2001)}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic0_8000.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic1_8000.png}}&
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic2_8000.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic3_8000.png}}&
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic4_8000.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic5_8000.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic6_8000.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic7_8000.png}}&
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic8_8000.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic9_8000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the USA (2002-2006)}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic0_9000.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic1_9000.png}}&
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic2_9000.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic3_9000.png}}&
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic4_9000.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic5_9000.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic6_9000.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic7_9000.png}}&
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic8_9000.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic9_9000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the USA (2007-2013)}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}
+\begin{tabular}{rcl}
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic0_8000.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic1_8000.png}}&
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic2_8000.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic3_8000.png}}&
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic4_8000.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic5_8000.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic6_8000.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic7_8000.png}}&
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic8_8000.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic9_8000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the USA (2014-2017)}
+\end{figure}
+\end{center}
+
 \end{document}

### 2017-06-20 thesis_report/draft_thesis.tex
Appendix wordclouds (2/10)

@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic0_7000.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic1_7000.png}}&
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic2_7000.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic3_7000.png}}&
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic4_7000.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic5_7000.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic6_7000.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic7_7000.png}}&
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic8_7000.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic9_7000.png}}&
+\subfloat[Quality Management Systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic0_7000.png}} &
+\subfloat[Agriculture, Fisheries and Food]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic1_7000.png}}&
+\subfloat[Molecular biology, Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic2_7000.png}}\\
+\subfloat[EU transport]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic3_7000.png}}&
+\subfloat[Digital systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic4_7000.png}} &
+\subfloat[Materials processing]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic5_7000.png}}\\
+\subfloat[Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic6_7000.png}} &
+\subfloat[Policy for environmental sustainability]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic7_7000.png}}&
+\subfloat[Energy technologies]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic8_7000.png}}\\
+\subfloat[Applications in mobile networks]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic9_7000.png}}&
 \end{tabular}
@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic0_7000.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic1_7000.png}}&
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic2_7000.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic6_7000.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic7_7000.png}}&
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic8_7000.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic9_7000.png}}&
+\subfloat[Management software]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic0_7000.png}} &
+\subfloat[Hydropower / Energy production]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic1_7000.png}}&
+\subfloat[Information technologies]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic2_7000.png}}\\
+\subfloat[Quality control systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
+\subfloat[Healthcare / Medical genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
+\subfloat[Environmental sustainability and policies]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\
+\subfloat[Molecular biology (genes)]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic6_7000.png}} &
+\subfloat[Optical quantum computing]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic7_7000.png}}&
+\subfloat[Education in Nuclear physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic8_7000.png}}\\
+\subfloat[Education, training]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic9_7000.png}}&
 \end{tabular}

### 2017-06-21 thesis_report/draft_thesis.tex
Appendix wordclouds (5/10)

@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic0_7000.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic1_7000.png}}&
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic2_7000.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic3_7000.png}}&
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic4_7000.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic5_7000.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic6_7000.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic7_7000.png}}&
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic8_7000.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic9_7000.png}}&
+\subfloat[International research]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic0_7000.png}} &
+\subfloat[Biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic1_7000.png}}&
+\subfloat[Embedded systems design]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic2_7000.png}}\\
+\subfloat[Molecular biology, genes]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic3_7000.png}}&
+\subfloat[Evolution / Formation]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic4_7000.png}} &
+\subfloat[Sustainable production / Energy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic5_7000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic6_7000.png}} &
+\subfloat[Environmental management services]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic7_7000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic8_7000.png}}\\
+\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic9_7000.png}}&
 \end{tabular}
@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic0_7000.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic1_7000.png}}&
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic2_7000.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic3_7000.png}}&
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic4_7000.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic5_7000.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic6_7000.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic7_7000.png}}&
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic8_7000.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic9_7000.png}}&
+\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic0_7000.png}} &
+\subfloat[(High energy) physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic1_7000.png}}&
+\subfloat[Energy production]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic2_7000.png}}\\
+\subfloat[Social Sciences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic3_7000.png}}&
+\subfloat[Molecular Biology / Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic4_7000.png}} &
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic5_7000.png}}\\
+\subfloat[International research]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic6_7000.png}} &
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic7_7000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic8_7000.png}}\\
+\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic9_7000.png}}&
 \end{tabular}
@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic0_20000.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic1_20000.png}}&
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic2_20000.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic3_20000.png}}&
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic4_20000.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic5_20000.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic6_20000.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic7_20000.png}}&
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic8_20000.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic9_20000.png}}&
+\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic0_20000.png}} &
+\subfloat[Environmental sustainability \& food production]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic1_20000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic2_20000.png}}\\
+\subfloat[?]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic3_20000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic4_20000.png}} &
+\subfloat[Environmental sustainability / Green energy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic5_20000.png}}\\
+\subfloat[Physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic6_20000.png}} &
+\subfloat[Business \& Innovation]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic7_20000.png}}&
+\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic8_20000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic9_20000.png}}&
 \end{tabular}

### 2017-06-21 thesis_report/draft_thesis.tex
Appendix wordclouds (10/10)

@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
+\subfloat[Software engineering]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
+\subfloat[Climate change]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
+\subfloat[International research \& Education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
+\subfloat[Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
+\subfloat[Economic \& Social science]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
+\subfloat[Molecular biology / Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
+\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
+\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
 \end{tabular}
@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic0_8000.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic1_8000.png}}&
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic2_8000.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic3_8000.png}}&
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic4_8000.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic5_8000.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic6_8000.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic7_8000.png}}&
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic8_8000.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic9_8000.png}}&
+\subfloat[Applied Sciences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic0_8000.png}} &
+\subfloat[Environment \& Climate change]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic1_8000.png}}&
+\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic2_8000.png}}\\
+\subfloat[Biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic3_8000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic4_8000.png}} &
+\subfloat[STEM education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic5_8000.png}}\\
+\subfloat[Systems ?]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic6_8000.png}} &
+\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic7_8000.png}}&
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic8_8000.png}}\\
+\subfloat[International conferences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic9_8000.png}}&
 \end{tabular}
@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic0_8000.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic1_8000.png}}&
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic2_8000.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic3_8000.png}}&
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic4_8000.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic5_8000.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic6_8000.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic7_8000.png}}&
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic8_8000.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic9_8000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic0_8000.png}} &
+\subfloat[Education (in engineering)]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic1_8000.png}}&
+\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic2_8000.png}}\\
+\subfloat[International conferences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic3_8000.png}}&
+\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic4_8000.png}} &
+\subfloat[Green transportation]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic5_8000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic6_8000.png}} &
+\subfloat[Climate change]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic7_8000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic8_8000.png}}\\
+\subfloat[Physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic9_8000.png}}&
 \end{tabular}
@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic0_9000.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic1_9000.png}}&
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic2_9000.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic3_9000.png}}&
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic4_9000.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic5_9000.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic6_9000.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic7_9000.png}}&
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic8_9000.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic9_9000.png}}&
+\subfloat[STEM education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic0_9000.png}} &
+\subfloat[Computer \& Networking systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic1_9000.png}}&
+\subfloat[Chemistry \& Materials science]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic2_9000.png}}\\
+\subfloat[Climate change \ Environmental science]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic3_9000.png}}&
+\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic4_9000.png}} &
+\subfloat[Atmospheric \& Ocean sciences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic5_9000.png}}\\
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic6_9000.png}} &
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic7_9000.png}}&
+\subfloat[(Molecular) biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic8_9000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic9_9000.png}}&
 \end{tabular}
@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic0_8000.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic1_8000.png}}&
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic2_8000.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic3_8000.png}}&
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic4_8000.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic5_8000.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic6_8000.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic7_8000.png}}&
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic8_8000.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic9_8000.png}}&
+\subfloat[Biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic0_8000.png}} &
+\subfloat[Climate Change / Geology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic1_8000.png}}&
+\subfloat[Sociology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic2_8000.png}}\\
+\subfloat[STEM education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic3_8000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic4_8000.png}} &
+\subfloat[Chemical \& transport systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic5_8000.png}}\\
+\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic6_8000.png}} &
+\subfloat[Materials \& Mechanical engineering]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic7_8000.png}}&
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic8_8000.png}}\\
+\subfloat[International research]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic9_8000.png}}&
 \end{tabular}

### 2017-06-21 compare_FPs_topics.py
JSD

@@ -6,10 +6,11 @@ import gensim
 import argparse
 import pickle
 import scipy.stats as stats
+import dit
 
 from gensim import corpora, models, similarities, matutils
 from gensim.corpora.dictionary import Dictionary
-
+from dit.divergences import jensen_shannon_divergence
 from scipy.stats import entropy
 from numpy.linalg import norm
 
@@ -53,14 +54,22 @@ def get_topic_vectors(topic_eu_id, topic_usa_id):
 	# get only the probabilities as vectors
 	topicEUvec = [x[1] for x in get_topic_terms_eu]
 	topicUSAvec = [x[1] for x in get_topic_terms_usa]
+
+
+	topicEUvec = dit.ScalarDistribution([x[0] for x in get_topic_terms_eu], [x[1] for x in get_topic_terms_eu])
+	topicUSAvec = dit.ScalarDistribution([x[0] for x in get_topic_terms_usa], [x[1] for x in get_topic_terms_usa])
+
 	return topicEUvec, topicUSAvec
 
 # Function for calculating the Jensen Shannon Divergence
 def JSD(P, Q):
-    _P = P / norm(P, ord=1)
-    _Q = Q / norm(Q, ord=1)
+    # _P = P / norm(P, ord=1)
+    # _Q = Q / norm(Q, ord=1)
+    _P = np.array(P)
+    _Q = np.array(Q)
     _M = 0.5 * (_P + _Q)
     return 0.5 * (entropy(_P, _M) + entropy(_Q, _M))
+# check if it computes the KL
 
 # print JSD(topicEUvec, topicUSAvec)
 
@@ -71,16 +80,24 @@ eu = [i for i in range(10)]
 usa = [i for i in range(10)]
 dfJSD = pd.DataFrame(index=eu, columns=usa)
 
-for eu_topic in range(ldaEU.num_topics):
-	for usa_topic in range(ldaUSA.num_topics):
-		topicEUvec, topicUSAvec = get_topic_vectors(eu_topic, usa_topic)
+
+# for eu_topic in range(ldaEU.num_topics):
+# 	for usa_topic in range(ldaUSA.num_topics):
+# 		topicEUvec, topicUSAvec = get_topic_vectors(eu_topic, usa_topic)
 		# print 'EU topic: ', eu_topic, ' USA topic: ', usa_topic,
[…]

### 2017-06-21 thesis_report/draft_thesis.tex
Update: EU topics in the whole dataset
Discovering topics on the EU projects

@@
 
-\subsection{Discovering topics on EU and USA projects}
-
-wordclouds per FP?
+\subsection{Discovering topics on the EU projects}
+
+In general, the most popular subject in European Union over the years is
+Information systems. In our dataset we fount projects related to almost all
+kinds of information systems, and especially Quality managemest systems
+(1994-2002), Management information systems, Network information systems and
+Information systems as a service to all kinds of organizations, including
+universities and companies. Since technology has an impact in every aspect
+nowadays, it is normal to have such polularity over the years and it's becoming
+popular in education, as well. The same period of time, Innovation in Business
+emerged as a trending topic, with projects related to new technologies and
+software systems in the industry and how they assist the businesses and the
+market. In addition, until 2002 a very popular subject related to Information
+systems, was Applications in mobile networks, embedded and broadband systems,
+which nowadays has lost part of its popularity in research.
+
+Another popular subject that appears the last 22 years is Materials research;
+the projects related to material research are mostly related to the discovery
+and design of new materials, with an emphasis on solids. Matelials properties
+and performace are used in many disciplines, like chemistry, physics and
+engineering.
+
+The third most polular subject is Molecular biology and Genetics. These projects
+are related to the cellular molecules that carry out the biological processes
+essential for the cell's functions and maintenance. These affect many aspects of
+our lives, including evolution, nutrition and the spread of diseases. Especially
+from 1998 up to day, there is a focus in Healthcare and Diagnostics, and fot the
+last decade researchers are studying the cancer detection and treatment, which
+is a common cause of death in EU and the second most common cause of death in
+USA.
+
+Moreover, Environmental, Social and Economic Sustainability is a subject very
+important to the research community and many researchers work on this up to day.
+In short, sustainability takes into account how we might live in harmony with
+the natural world around us, protecting it from damage and destruction. Many
+projects are related to one of the Three Pillars of Sustainability\footnote{http
+://www.thwink.org/sustain/glossary/ThreePillarsOfSustainability.htm}. The
+European Union is considered by some to have the most extensive environmental
+laws of any international organisation, started by the  European Economic
+Community (EEC), which is the beginning of the EU's environmental policy. Social
+and Econimic policies are also popular in the EU region over the last decate.
+Also, the last two decades there is a focus on the Green energy production, like
+hydropower, solar and nuclear energy.
+
+During the 6th and the 7th framework programme, International Research and
+conferences came up in our dataset as a trending topic. Researchers have a great
+interest to collaborate with other colleagues from all over the world and share
+their knowledge. A big part of the projects funded by the EU that is related to
+international research, is also related to Physics, in general, and High energy
+physics in EU (see Appendix: Wordclouds of topics of the EU).
+
+\subsection{Discovering topics on the USA projects}
 
@@
 describe them:
+\begin{itemize}
+\item[] Topic 0: Molecular biology
+\item[] Topic 1: Marerials \& Manufacturing
+\item[] Topic 2: Social policy
+\item[] Topic 3: Disease detection \& treatment
+\item[] Topic 4: Materials science / Physics
+\item[] Topic 5: Transport \& Energy
+\item[] Topic 6: Business \& Innovation
+\item[] Topic 7: Climate change / Environment
+\item[] Topic 8: Molecular mechanisms
+\item[] Topic 9: Information systems
+\item[] Topic 10: International research
+\item[] Topic 11: Energy production
+\end{itemize}
 \begin{center}
@@
 \end{center}
-
 In order to find the topic distribution over time, we need the topic

### 2017-06-21 compare_FPs_topics.py
clean up and accelerate

@@ -10,7 +10,7 @@ import dit
 
 from gensim import corpora, models, similarities, matutils
 from gensim.corpora.dictionary import Dictionary
-from dit.divergences import jensen_shannon_divergence
+import dit.divergences as dd
 from scipy.stats import entropy
 from numpy.linalg import norm
 
@@ -26,68 +26,61 @@ args = parser.parse_args()
 df = args.dataset
 
 # Load the LDA model of the two datasets
-ldaEU = gensim.models.ldamodel.LdaModel.load('./eu_gensim/lda_saved/lda_eu'+ df +'.model')
-ldaUSA = gensim.models.ldamodel.LdaModel.load('./usa_gensim/lda_saved/lda_usa'+ df +'.model')
+ldaEU = gensim.models.ldamodel.LdaModel.load('./eu_gensim/lda_saved/lda_eu'
+                                             + df +'.model')
+ldaUSA = gensim.models.ldamodel.LdaModel.load('./usa_gensim/lda_saved/lda_usa'
+                                              + df +'.model')
 
 def get_topic_vectors(topic_eu_id, topic_usa_id):
-	# get the words and their probabilities per topic
-	get_topic_terms_eu = ldaEU.show_topic(topic_eu_id, topn=ldaEU.num_terms)
-	get_topic_terms_usa = ldaUSA.show_topic(topic_usa_id, topn=ldaUSA.num_terms)
 
-	# keep the words in a list as a dictionary
-	eu_list = [x[0] for x in get_topic_terms_eu]
-	usa_list = [x[0] for x in get_topic_terms_usa]
+    # get the words and their probabilities for the topic
+    eu_topic_terms_tuples = ldaEU.show_topic(topic_eu_id,
+                                             topn=ldaEU.num_terms)
+    us_topic_terms_tuples = ldaUSA.show_topic(topic_usa_id,
+                                              topn=ldaUSA.num_terms)
 
-	# add the words that don't exist in one of them, with probability = 0.0
-	for i in get_topic_terms_eu:
-		if i[0] not in usa_list:
-			get_topic_terms_usa.append((i[0], 0.0))
+    # keep the words in set
+    eu_topic_terms = { x[0] for x in eu_topic_terms_tuples }
[…]

### 2017-06-21 compare_FPs_topics.py
remove unneeded imports

@@ -6,11 +6,9 @@ import gensim
 import argparse
 import pickle
 import scipy.stats as stats
-import dit
 
 from gensim import corpora, models, similarities, matutils
 from gensim.corpora.dictionary import Dictionary
-import dit.divergences as dd
 from scipy.stats import entropy
 from numpy.linalg import norm
 

### 2017-06-22 compare_FPs_topics.py
Heatmaps for comparing the datasets per FP

@@ -68,26 +68,18 @@ def calc_jsd(P, Q):
 
 print('Framework Programme ' +  df)
 
-eu = [i for i in range(10)]
-usa = [i for i in range(10)]
+eu = [('eu' + str(i)) for i in range(10)]
+usa = [('usa' + str(i)) for i in range(10)]
 dfJSD = pd.DataFrame(index=eu, columns=usa)
 
-# for eu_topic in range(ldaEU.num_topics):
-#       for usa_topic in range(ldaUSA.num_topics):
-#               topicEUvec, topicUSAvec = get_topic_vectors(eu_topic, usa_topic)
-                # print 'EU topic: ', eu_topic, ' USA topic: ', usa_topic,
-                # print ' --> JSD = ', JSD(topicEUvec, topicUSAvec)
-                # dfJSD.set_value(index=eu_topic, col=usa_topic, value=JSD(topicEUvec, topicUSAvec))
-                # dfJSD.set_value(index=eu_topic, col=usa_topic, value=jensen_shannon_divergence([topicEUvec, topicUSAvec]))
+for eu_topic in range(ldaEU.num_topics):
+	for usa_topic in range(ldaUSA.num_topics):
+		eu_topic_probs, us_topic_probs = get_topic_vectors(eu_topic, usa_topic)
+		dfJSD.set_value(index=('eu'+ str(eu_topic)), col=('usa'+ str(usa_topic)), value=calc_jsd(eu_topic_probs, us_topic_probs))
 
-# dfJSD.to_pickle('compared_FPs/JSD_' + df)
+dfJSD.to_pickle('compared_FPs/JSD_' + df)
 
-# print dfJSD.head(1)
-
-# # Caluculates symmetric Kullback-Leibler divergence.
-# def symmetric_kl_divergence(p, q):
-#       return numpy.sum([stats.entropy(p, q), stats.entropy(q, p)])
-
-
-eu_topic_probs, us_topic_probs = get_topic_vectors(0, 0)
-print(calc_jsd(eu_topic_probs, us_topic_probs))
+print dfJSD.index
+print dfJSD.columns
+# eu_topic_probs, us_topic_probs = get_topic_vectors(0, 0)
+# print(calc_jsd(eu_topic_probs, us_topic_probs))

### 2017-06-23 thesis_report/draft_thesis.tex
Discovering topics on the USA projects

@@
 \includegraphics[width=0.6\textwidth, natwidth=548,natheight=201]{figs/PLSI_plate_notation.png}
-\caption{Plate notation representing the PLSI model. \textbf{w} is the document index, $z$ is the topic drawn for the word $w$ from the topic distribution of the document}
+\caption{Plate notation representing the PLSI model. \textbf{w} is the document 
+index, $z$ is the topic drawn for the word $w$ from the topic distribution of 
+the document}
 \end{figure}
@@
 
-In LDA, our ultimate goal is to find the posterior distribution of latent topic variables after observing training data.
-However, computing this distribution is intractable, so we’re forced to approximate.
-One approximation approach is to
+In LDA, our ultimate goal is to find the posterior distribution of latent topic 
+variables after observing training data. However, computing this distribution 
+is intractable, so we’re forced to approximate. One approximation approach is to 
 use an optimization method called Variational Bayes. In the original paper it's 
-being used a variational Bayes approximation of the posterior distribution;\cite{blei2003latent} alternative inference techniques use Gibbs sampling and
+being used a variational Bayes approximation of the posterior distribution;
+\cite{blei2003latent} alternative inference techniques use Gibbs sampling and
 expectation propagation. The goal of variational inference is to approximate an
@@
 
-In short, we approximate the true distribution by a simple distribution $q$, and associate parameters $\phi$, $\gamma$, $\lambda$ with the original parameters 
+In short, we approximate the true distribution by a simple distribution $q$, and 
+associate parameters $\phi$, $\gamma$, $\lambda$ with the original parameters 
 $z$, $\theta$, $\beta$ respectively. Recall that $z$ gives the topic assignments 
@@
 
-In online Variational Bayes, we only make a single sweep of the entire dataset, analyzing a chunk of documents at a time. A chunk could be a single document, 
+In online Variational Bayes, we only make a single sweep of the entire dataset, 
+analyzing a chunk of documents at a time. A chunk could be a single document, 
 50 documents, or even the entire dataset. Let’s let a chunk be 1000 documents.
@@
 
-In this section, we explain the procedure that we followed in n order to apply the LDA model in our dataset.
-The dataset consists of two datasets: the one that contains all the information about EU projects founded for research and innovation under the FP4-H2020 and the dataset from USA about the awards/projects that got approved from 1994-2017.
-We consider the projects' description/abstract as the documents in LDA.
+In this section, we explain the procedure that we followed in n order to apply
+the LDA model in our dataset. The dataset consists of two datasets: the one that
+contains all the information about EU projects founded for research and
+innovation under the FP4-H2020 and the dataset from USA about the
+awards/projects that got approved from 1994-2017. We consider the projects'
+description/abstract as the documents in LDA.
 
@@
 
-CORDIS (Community Research and Development Information Service) is the European Commission's primary public repository and portal to disseminate information on all EU-funded research projects and their results in the broadest sense.
-The website includes all public information held by the Commission (project factsheets, publishable reports and deliverables), editorial content to support communication and exploitation (news, events, success stories, magazines) and comprehensive links to external sources such as open access publications and websites.
-CORDIS is managed by the Publications Office of the European Union, on behalf of the European Commission's research Directorates-General and Agencies.
-CORDIS content dates back to the origin of the service in 1990 and the website has been online since 1994.
-
-Below, we provide the general topics of the EU projects as listed in the EU Open Data Portal \footnote{https://data.europa.eu/euodp/en/data}:
+CORDIS (Community Research and Development Information Service) is the European
+Commission's primary public repository and portal to disseminate information on
+all EU-funded research projects and their results in the broadest sense. The
+website includes all public information held by the Commission (project
+factsheets, publishable reports and deliverables), editorial content to support
+communication and exploitation (news, events, success stories, magazines) and
+comprehensive links to external sources such as open access publications and
+websites. CORDIS is managed by the Publications Office of the European Union, on
+behalf of the European Commission's research Directorates-General and Agencies.
+CORDIS content dates back to the origin of the service in 1990 and the website
+has been online since 1994.
+
+Below, we provide the general topics of the EU projects as listed in the EU 
+Open Data Portal \footnote{https://data.europa.eu/euodp/en/data}:
 \begin{itemize}
@@
 
-The data that are provided by CORDIS (via the EU Open Data Portal) are open, free and can be used in research, applications, commercial or non-commercial purposes.
-The dataset that we chose for the following analysis contains information about all the projects funded by the European Union from 1994 to 2017.
-These projects got approved under the framework programme (FP4-H2020) for research and technological development.
-For each project it is provided information, such as: reference, acronym, dates, funding, programmes, participant countries, subjects and objectives.
-
-In the provided dataset, the information is splitted into CSV files, based on the framework program that each project belongs. The frameworks from 1994 to 2020 are listed below:
+The data that are provided by CORDIS (via the EU Open Data Portal) are open,
+free and can be used in research, applications, commercial or non-commercial
+purposes. The dataset that we chose for the following analysis contains
+information about all the projects funded by the European Union from 1994 to
+2017. These projects got approved under the framework programme (FP4-H2020) for
+research and technological development. For each project it is provided
+information, such as: reference, acronym, dates, funding, programmes,
+participant countries, subjects and objectives.
+
+In the provided dataset, the information is splitted into CSV files, based on
+the framework program that each project belongs. The frameworks from 1994 to
+2020 are listed below:
 
@@
 Data cleaning is absolutely crucial for generating a useful topic model. 
-We implemented the following steps, which are common to most natural language processing methods, in order to obtain the final corpus for the analysis:
+We implemented the following steps, which are common to most natural 
+language processing methods, in order to obtain the final corpus for the 
+analysis:
 
@@
 
-To obtain the collection of the documents, we consider as ‘documents’ in LDA the project objectives, which is an accurate description for the project.
-We also added the ‘title’ value of each project to the objectives-documents, to increase the probability of finding accurate topics.
-For the majority of the projects the ‘start date’ and ‘end date’ value was null, so we kept the splitting of the dataset per framework, in order to keep the correlation to the time.
-We followed the same format in the dataset of USA awards.
+To obtain the collection of the documents, we consider as ‘documents’ in LDA the
+project objectives, which is an accurate description for the project. We also
+added the ‘title’ value of each project to the objectives-documents, to increase
+the probability of finding accurate topics. For the majority of the projects the
+‘start date’ and ‘end date’ value was null, so we kept the splitting of the
+dataset per framework, in order to keep the correlation to the time. We followed
+the same format in the dataset of USA awards.
 
@@
 
-As stopwords, we used the list that is provided by the Gensim Python library\footnote{http://radimrehurek.com/gensim/} and we added following very common words in the existing dataset: 'data', 'based', 'new', 'project', 'university', 'student', 'students', 'research', 'study', 'program', 'development', 'study', 'studies', 'provide', 'use'.
-We also removed the rare words that appear less than 5 times in the collection.
-Finally, we obtained a smaller corpus per framework (see the table above)
-
-In this section, we explain the procedure that we followed in n order to apply the LDA model in our dataset.
-The dataset consists of two datasets: the one that contains all the information about EU projects founded for research and innovation under the FP4-H2020 and the dataset from USA about the awards/projects that got approved from 1994-2017.
-We consider the projects' description/abstract as the documents in LDA.
+As stopwords, we used the list that is provided by the Gensim Python
+library\footnote{http://radimrehurek.com/gensim/} and we added following very
+common words in the existing dataset: 'data', 'based', 'new', 'project',
+'university', 'student', 'students', 'research', 'study', 'program',
+'development', 'study', 'studies', 'provide', 'use'. We also removed the rare
+words that appear less than 5 times in the collection. Finally, we obtained a
+smaller corpus per framework (see the table above)
+
+In this section, we explain the procedure that we followed in n order to apply
+the LDA model in our dataset. The dataset consists of two datasets: the one that
+contains all the information about EU projects founded for research and
+innovation under the FP4-H2020 and the dataset from USA about the
+awards/projects that got approved from 1994-2017. We consider the projects'
+description/abstract as the documents in LDA.
 
@@
 
-The National Science Foundation (NSF) is a United States government agency that supports fundamental research and education in all the non-medical fields of science and engineering.
-Its medical counterpart is the National Institutes of Health.
-The NSF funds approximately 24\% of all federally supported basic research conducted by the United States' colleges and universities.
-In some fields, such as mathematics, computer science, economics, and the social sciences, the NSF is the major source of federal backing.
-
-The NSF organizes its research and education support through seven directorates, each encompassing several disciplines:
+The National Science Foundation (NSF) is a United States government agency that
+supports fundamental research and education in all the non-medical fields of
+science and engineering. Its medical counterpart is the National Institutes of
+Health. The NSF funds approximately 24\% of all federally supported basic
+research conducted by the United States' colleges and universities. In some
+fields, such as mathematics, computer science, economics, and the social
+sciences, the NSF is the major source of federal backing.
+
+The NSF organizes its research and education support through seven 
+directorates, each encompassing several disciplines:
 
@@
 
-The data about the awards \footnote{https://www.nsf.gov/awardsearch/download.jsp} are open, free and can be used in research and applications.
-The dataset that we chose for the following analysis contains information about all the projects that got funded by the NSF from 1994 to 2017.
-
-In the provided dataset, the information is splitted into XML files, separated per year, from 1994 - 2017.
-In order to keep the correlation to time and be able to compare the two datasets later, we splitted the projects based on the year they were initialized (see Table below).
+The data about the awards
+\footnote{https://www.nsf.gov/awardsearch/download.jsp} are open, free and can
+be used in research and applications. The dataset that we chose for the
+following analysis contains information about all the projects that got funded
+by the NSF from 1994 to 2017.
+
+In the provided dataset, the information is splitted into XML files, separated
+per year, from 1994 - 2017. In order to keep the correlation to time and be able
+to compare the two datasets later, we splitted the projects based on the year
+they were initialized (see Table below).
 
@@
 
-Just like the EU dataset, we followed the same preprocessing steps to obtain the final corpus.
-As stopwords, we used the list that is provided by the Gensim Python library and we removed following very common words in the existing dataset: 'data', 'work', 'based', 'new', 'project', 'university', 'student', 'students', 'research', 'study', 'program', 'development', 'study', 'studies', 'provide', 'use', 'understanding', 'important', 'support', 'proposed'.
-We also removed the rare words that appear less than 5 times in the collection.
-Finally, we obtained a smaller corpus per framework (see Table below).
+Just like the EU dataset, we followed the same preprocessing steps to obtain the
+final corpus. As stopwords, we used the list that is provided by the Gensim
+Python library and we removed following very common words in the existing
+dataset: 'data', 'work', 'based', 'new', 'project', 'university', 'student',
+'students', 'research', 'study', 'program', 'development', 'study', 'studies',
+'provide', 'use', 'understanding', 'important', 'support', 'proposed'. We also
+removed the rare words that appear less than 5 times in the collection. Finally,
+we obtained a smaller corpus per framework (see Table below).
 
@@
 \begin{tabular}{l*{6}{c}r}
-Framework         & Years & No of docs & No of unique tokens & No of words in the corpus \\
+Framework& Years & No of docs & No of unique tokens & No of words in the corpus \\
 \hline
@@
 \subsection{Discovering topics on the USA projects}
+
+The National Science Foundation mostly supports fundamental research and
+education in the non-medicalin science and engineering. Its medical counterpart
+is the National Institutes of Health.\footnote{\url{https://en.wikipedia.org/wik
+i/National_Science_Foundation}} With STEM being the top priority in USA, most of
+the projects founded by NSF are related to engineering, computer science,
+mathematics and information systems, in general. The subjects STEM \& Education,
+Software engineering, Information systems and Mathematics, arise as topics in
+all these years, from 1994-2017.
+
+While NSF promotes the progress of science, it also enhances the effords to
+maintain the national health, prosperity, and welfare. Over the last 22 years,
+many projects are related to the environment effects of climate change. Topics
+like Environmental Science, Atmospheric \& Ocean sciences, Geology, Climate
+change and its impact in the United States emerge during all these years. The
+last three years there is a focus on the Green energy production, like
+hydropower and wind power. Among with climate change, there is many research
+related to Biology and Evolution. A less popular subject that appears during the
+years 1994-1997 and 2007-2013 is Molecular, Cellular \& Organismal biology and
+Genetics. These projects mostly refer to applied genetics, as well as cell
+functionality. Topics include receptor biology, regulation of gene expression,
+biomedical engineering, patterns of inheritance and molecular genetics.
+
+Another popular subject that appears the last 22 years is Materials and
+Chemistry; the projects related to material research are mostly refer to the
+materials' properties and applications in engineering. The last 3 years,
+researchers from the USA focus on materials applications and desing in
+mechanical engineering, bioengineering and chemical \& transport systems. In
+2002-2006 many projects are related to the subject of transport that is
+sustainable in the senses of social, environmental and climate impacts (Green
+transportation).
+
+From 1994-2006 and the last three years, International Research and conferences
+came up as a trending topic. Re- searchers have a great interest to collaborate
+with other colleagues from all over the world and share their knowledge. A big
+part of the projects funded by the EU that is related to international research,
+is also related to Physics, in general, and High energy physics in EU (see
+Appendix: Wordclouds of topics of the EU).
+
+NSF shows a great interest in international activities across all NSF supported
+disciplines. The goal of these projects is to support high quality research and
+education, which could not occur without international collaboration. NSF seeks
+to catalyze a higher level of international engagement in the U.S. science and
+engineering community by promoting International conferences and university
+projects and partnerships. An interesting fact regarding international
+partnerships is that the European Commission and the Government of the United
+States of America concluded on 17 October 2016 an Implementing Arrangement that
+simplifies the cooperation between Horizon 2020 projects and US entities.
+European and American researchers will be able to work together more closely on
+projects funded under Horizon 2020, the European Union's research and innovation
+programme.\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}
+
+From 2002 up to day, Economic and Social Sciences emerge as a topic in our
+dataset. Researchers show a great interest in identifying policies which help
+the communities and they also do lots of Qualitative and Quantitative research
+to investigate the size or extent of particular issues or trends in society.
+
+Finally, a topic that used to be popular in the past, in 1994-1997 and
+2007-2013, is High energy Physics in USA, which has lost its popularity
+nowadays. The last 5 years, there is an interest around STEM and its
+applications in manufacturing and engineering.
 
@@
 
+\begin{center}
+\begin{figure}
+\includegraphics[width=1.0\textwidth, natwidth=707,natheight=483]
+{figs/eu-topic-evolution.png}
+\caption{Topics over time in EU}
+\end{figure}
+\end{center}
+
 \subparagraph{Trends in the USA	}
@@
 
+\subsection{Comparison of the two regions per framework programme}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth, natwidth=1080,natheight=720]
+{figs/heatmaps/heatmapFP4.png}
+\caption{Heatmap of the similarity of the two regions during 1994-1997}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth, natwidth=1080,natheight=720]
+{figs/heatmaps/heatmapFP5.png}
+\caption{Heatmap of the similarity of the two regions during 1998-2001}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth, natwidth=1080,natheight=720]
+{figs/heatmaps/heatmapFP6.png}
+\caption{Heatmap of the similarity of the two regions during 2002-2006}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth, natwidth=1080,natheight=720]
+{figs/heatmaps/heatmapFP7.png}
+\caption{Heatmap of the similarity of the two regions during 2007-2013}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth, natwidth=1080,natheight=720]
+{figs/heatmaps/heatmapH2020.png}
+\caption{Heatmap of the similarity of the two regions during 2014-2017}
+\end{figure}
+
 \section{Conclusion}

### 2017-06-23 thesis_report/draft_thesis.tex
Spelling

@@
 data. These algorithms can be used to summarize, visualize and explore a
-collection of documents. The papers listed below are applying a Latend Dirichlet
+collection of documents. The papers listed below are applying a Latent Dirichlet
 Allocation model in an interesting approach on their corpus.
@@
 
-The paper that mostly infuenced our work is "Finding Scientific Topics", by
+The paper that mostly influenced our work is "Finding Scientific Topics", by
 T.Griffiths and M.Steyvers.\cite{griffiths_steyvers04} They investigated
@@
 topic modeling with existing categories. In our implementation, we also use 
-the abstacts of the projects as documents for the model.
+the abstracts of the projects as documents for the model.
 
@@
 family, then the prior and posterior are called conjugate distributions and the
-prior is called a conjugate prior for the likelihood funtion.
+prior is called a conjugate prior for the likelihood function.
 
@@
 $\theta_w^2$ for topic $z$ in document $w$. These weight have a Dirichlet prior,
-parameterized by a hyper-parameter $\alpha$. Each topic is a probability
+parametrized by a hyper-parameter $\alpha$. Each topic is a probability
 distribution over the vocabulary, with probability $\beta^w_z$ for word $w$ in
@@
 from one of the $k$ topics in step (b), where the probability of each word
-within a topic is parameterized by a $k \times V$ matrix , where $V$ is the
+within a topic is parametrized by a $k \times V$ matrix , where $V$ is the
 size of the specified vocabulary. The most probable words in each topic could
@@
 \begin{equation}
-q(\theta_{d}) = dirichlet(\theta_{d}; \gamma_{d})
+q(\theta_{d}) = Dirichlet(\theta_{d}; \gamma_{d})
 \end{equation}
 \begin{equation}
-q(\beta_{k}) = dirichlet(\beta_{k}; \lambda_{k})
+q(\beta_{k}) = Dirichlet(\beta_{k}; \lambda_{k})
 \end{equation}
 
-The posterior over the per-word topic assignments $z$ is parameterized by
-$\phi$, the posterior over per-document topic weights $\theta$ is parameterized
-by $\gamma$, and the posterior over the topics $\beta$ is parameterized by
+The posterior over the per-word topic assignments $z$ is parametrized by
+$\phi$, the posterior over per-document topic weights $\theta$ is parametrized
+by $\gamma$, and the posterior over the topics $\beta$ is parametrized by
 $\lambda$.
@@
 website includes all public information held by the Commission (project
-factsheets, publishable reports and deliverables), editorial content to support
+fact sheets, publishable reports and deliverables), editorial content to support
 communication and exploitation (news, events, success stories, magazines) and
@@
 	\begin{description}
-	\item Audiovisual and media, Culture, Education training and youth, Multiligualism
+	\item Audiovisual and media, Culture, Education training and youth, Multilingualism
 	\end{description}
@@
 research and technological development. For each project it is provided
-information, such as: reference, acronym, dates, funding, programmes,
+information, such as: reference, acronym, dates, funding, programs,
 participant countries, subjects and objectives.
@@
 The LDA model requires some basic input parameters; for both datasets we chose
-the number of topics $K=10$. The hyperparameter $\alpha$, which affects the
+the number of topics $K=10$. The hyper-parameter $\alpha$, which affects the
 sparsity of the document-topic distribution $\theta$, is by default a symmetric
@@
 
-In this section, we show our main results. We focus on finding differents
+In this section, we show our main results. We focus on finding differences
 between the two datasets in terms of topic distribution and later we 
@@
 Information systems. In our dataset we fount projects related to almost all
-kinds of information systems, and especially Quality managemest systems
+kinds of information systems, and especially Quality management systems
 (1994-2002), Management information systems, Network information systems and
@@
 universities and companies. Since technology has an impact in every aspect
-nowadays, it is normal to have such polularity over the years and it's becoming
+nowadays, it is normal to have such popularity over the years and it's becoming
 popular in education, as well. The same period of time, Innovation in Business
@@
 the projects related to material research are mostly related to the discovery
-and design of new materials, with an emphasis on solids. Matelials properties
-and performace are used in many disciplines, like chemistry, physics and
+and design of new materials, with an emphasis on solids. Materials properties
+and performance are used in many disciplines, like chemistry, physics and
 engineering.
 
-The third most polular subject is Molecular biology and Genetics. These projects
+The third most popular subject is Molecular biology and Genetics. These projects
 are related to the cellular molecules that carry out the biological processes
@@
 our lives, including evolution, nutrition and the spread of diseases. Especially
-from 1998 up to day, there is a focus in Healthcare and Diagnostics, and fot the
+from 1998 up to day, there is a focus in Health care and Diagnostics, and for the
 last decade researchers are studying the cancer detection and treatment, which
@@
 European Union is considered by some to have the most extensive environmental
-laws of any international organisation, started by the  European Economic
+laws of any international organization, started by the  European Economic
 Community (EEC), which is the beginning of the EU's environmental policy. Social
-and Econimic policies are also popular in the EU region over the last decate.
+and Economic policies are also popular in the EU region over the last decade.
 Also, the last two decades there is a focus on the Green energy production, like
@@
 The National Science Foundation mostly supports fundamental research and
-education in the non-medicalin science and engineering. Its medical counterpart
+education in the non-medical science and engineering. Its medical counterpart
 is the National Institutes of Health.\footnote{\url{https://en.wikipedia.org/wik
@@
 
-While NSF promotes the progress of science, it also enhances the effords to
+While NSF promotes the progress of science, it also enhances the efforts to
 maintain the national health, prosperity, and welfare. Over the last 22 years,
@@
 materials' properties and applications in engineering. The last 3 years,
-researchers from the USA focus on materials applications and desing in
+researchers from the USA focus on materials applications and design in
 mechanical engineering, bioengineering and chemical \& transport systems. In
@@
 order to give some insights to researchers and scientists regarding potential
-trends. Fot this analysis, we run the model for the whole dataset, instead of
+trends. For this analysis, we run the model for the whole dataset, instead of
 running the model per FP), for the EU and the USA, respectively. The outcome was
@@
 small compared to the other years and it was affecting the result of the trend
-for eact topic.}
+for each topic.}
 
@@
 is in proportion to each probability; the bigger the word, the higher the
-probability. Each wordcloud describes a topic, which we can find intuitevely.
+probability. Each wordcloud describes a topic, which we can find intuitively.
 Below are listed the topics that we found corresponding to the words that
@@
 \item[] Topic 0: Molecular biology
-\item[] Topic 1: Marerials \& Manufacturing
+\item[] Topic 1: Materials \& Manufacturing
 \item[] Topic 2: Social policy
@@
 the FP equals to the sum of the number of the documents assigned to this 
-topic during the FP, nomralized by the number of the documents-projects 
-occuring in this FP. In figure X we plot the results of the topic proportion 
+topic during the FP, normalized by the number of the documents-projects 
+occurring in this FP. In figure X we plot the results of the topic proportion 
 over time.
@@
 topic proportion of each topic per year equals to the sum of the number of the
-documents assigned to this topic during the year, nomralized by the number of
-the documents-projects  occuring in this year.
-
-In figure X we plot the topic distribition over time. We can easily observe that
+documents assigned to this topic during the year, normalized by the number of
+the documents-projects  occurring in this year.
+
+In figure X we plot the topic distribution over time. We can easily observe that
 the topic 6, which refers to STEM education, is becoming a trend in the United
 States over the years, while most of the other topics' evolution doesn't show up
-such a high increace. Topics 5 and 8, which refer to Chemistry \& Materials
-science and Molecular biology, respectively, show a small decreace over the
-years. Topics 9 and 0 (Mechanical Engineering, Materiac Science and High energy
+such a high increase. Topics 5 and 8, which refer to Chemistry \& Materials
+science and Molecular biology, respectively, show a small decrease over the
+years. Topics 9 and 0 (Mechanical Engineering, Material Science and High energy
 physics) show a small increase over the last 5 years. Mathematics' evolution
@@
 3 and 4) show a small decrease over the last 3 years.  Molecular biology and
-Genetics (Topic 2) has an increasing polularity from 1994 to 2001 and later is
+Genetics (Topic 2) has an increasing popularity from 1994 to 2001 and later is
 starting to stabilize. Climatology, Atmospheric and Ocean sciences look stable
@@
 \subfloat[Quality control systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
-\subfloat[Healthcare / Medical genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
+\subfloat[Health care / Medical genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
 \subfloat[Environmental sustainability and policies]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\

### 2017-06-23 thesis_report/draft_thesis.tex
EU evolution of topics over time & added code in the appendix

@@
 \usepackage{subfig}
+\usepackage{listings}
+\usepackage[utf8]{inputenc}
+\usepackage{color}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{magenta},
+    numberstyle=\tiny\color{codegray},
+    stringstyle=\color{codepurple},
+    basicstyle=\footnotesize,
+    breakatwhitespace=false,         
+    breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                 
+    numbers=left,                    
+    numbersep=5pt,                  
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+
+\lstset{style=mystyle}
 
@@
 \centering
-\includegraphics[width=0.6\textwidth, natwidth=548,natheight=201]{figs/PLSI_plate_notation.png}
+\includegraphics[width=0.6\textwidth]{figs/PLSI_plate_notation.png}
 \caption{Plate notation representing the PLSI model. \textbf{w} is the document 
@@
 \centering
-\includegraphics[width=0.6\textwidth, natwidth=561,natheight=197]{figs/LDA_standard_model.png}
+\includegraphics[width=0.6\textwidth]{figs/LDA_standard_model.png}
 \caption{Plate notation of the standard LDA model}
@@
 The implementation was run on a computer with an Intel® Xeon® Processor E5-1410
-(10MB Cache, 2.8 GHz, 4 cores, 8 threads) and RAM=12 GB.
+(10MB Cache, 2.8 GHz, 4 cores, 8 threads) and RAM=12 GB. Check the Appendix for 
+the actual implementation.
 
@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic0_all.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic1_all.png}} &
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic2_all.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic3_all.png}} &
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic4_all.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic5_all.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic6_all.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic7_all.png}} &
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic8_all.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic9_all.png}} &
-\subfloat[Topic 10]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic10_all.png}} &
-\subfloat[Topic 11]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/EU_topic11_all.png}}\\
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic0_all.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic1_all.png}} &
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic2_all.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic3_all.png}} &
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic4_all.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic5_all.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic6_all.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic7_all.png}} &
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic8_all.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic9_all.png}} &
+\subfloat[Topic 10]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic10_all.png}} &
+\subfloat[Topic 11]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic11_all.png}}\\
 \end{tabular}
@@
 
+Based on this plot, topic 10, which refers to International Research, has an
+interesting evolution; During the years 1994-1998 is appears as less popular
+topic, compared to other topics. However, this state changes drastically in
+1998-2002 ($+14\%$) and in 2002-2006 it is at its peak ($+18\% since 1994$).
+This period many activities and projects where initialized in order to support
+and promote international education and conferences to attract researchers from
+all over the world. Strangely, this trend has a significant decrease the last 10
+years, compared to other topics ($-12\%$). We already know that in Horizon 2020
+there is an agreement between EU and USA for supporting the cooperation of the
+two regions.Our hypothesis for the evolution of the International Research is
+that the EU successfully managed to create the foundation for supporting
+international people and there is no need to invest more on projects that
+attempt to promote cooperation between international researchers, because it is
+already considered as a common practice nowadays.
+
+Materials and Manufacturing was a hot topic in 1994-1998, but it also appears a
+big decrease during the years 1998-2006 and it has a stable trend since then.
+Materials Science/Chemistry \& Physics' popularity (topic 4) line has an
+increase during 2002-2013 and the last 3 years a small decrease of $2-3\%$.
+Topics 2 and 3 (Social policy, Disease detection \& treatment) follow the same
+linear trend as Materials science \& Physics. Energy production (topic 11) was
+less popular in 1994-2002 and is becoming slightly popular the last 15 years.
+
+Topic 9, which refers to Information systems in general, is a subject that has a
+stable trend and it appears as a popular topic the last 22 years compared to
+other topics, with a percentage of $12.5\%$ of the projects in EU on average.
+
+Biology and the study of molecular mechanisms have a small decrease of
+popularity on average. This may happen because the projects related to medical
+fields are supported by another institute, National Institutes of Health. Also,
+research in Climate change and Environmental science is another subject that
+paradoxically appears as a topic that is gradually losing its popularity over
+the last years.
+
+Finally, topic 6, which is related to Business \& Innovation, has a huge
+increase the last 3 years. We can assume that the EU is very interested in
+supporting the economy by funding projects about businesses and monetary
+affairs.
 \begin{center}
 \begin{figure}
-\includegraphics[width=1.0\textwidth, natwidth=707,natheight=483]
+\includegraphics[width=1.0\textwidth]
 {figs/eu-topic-evolution.png}
@@
 \end{center}
-
 \subparagraph{Trends in the USA	}
@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic0_12000_all_docs.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic1_12000_all_docs.png}} &
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic2_12000_all_docs.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic3_12000_all_docs.png}} &
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic4_12000_all_docs.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic5_12000_all_docs.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic6_12000_all_docs.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic7_12000_all_docs.png}} &
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic8_12000_all_docs.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/USA_topic9_12000_all_docs.png}} &
+\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic0_12000_all_docs.png}} &
+\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic1_12000_all_docs.png}} &
+\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic2_12000_all_docs.png}}\\
+\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic3_12000_all_docs.png}} &
+\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic4_12000_all_docs.png}} &
+\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic5_12000_all_docs.png}}\\
+\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic6_12000_all_docs.png}} &
+\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic7_12000_all_docs.png}} &
+\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic8_12000_all_docs.png}}\\
+\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic9_12000_all_docs.png}} &
 \end{tabular}
@@
 division.
-
 \begin{center}
 \begin{figure}
-\includegraphics[width=1.0\textwidth, natwidth=707,natheight=483]
+\includegraphics[width=1.0\textwidth]
 {figs/topic-evolution-usa.png}
@@
 \centering
-\includegraphics[width=0.8\textwidth, natwidth=1080,natheight=720]
+\includegraphics[width=0.8\textwidth]
 {figs/heatmaps/heatmapFP4.png}
@@
 \centering
-\includegraphics[width=0.8\textwidth, natwidth=1080,natheight=720]
+\includegraphics[width=0.8\textwidth]
 {figs/heatmaps/heatmapFP5.png}
@@
 \centering
-\includegraphics[width=0.8\textwidth, natwidth=1080,natheight=720]
+\includegraphics[width=0.8\textwidth]
 {figs/heatmaps/heatmapFP6.png}
@@
 \centering
-\includegraphics[width=0.8\textwidth, natwidth=1080,natheight=720]
+\includegraphics[width=0.8\textwidth]
 {figs/heatmaps/heatmapFP7.png}
@@
 \centering
-\includegraphics[width=0.8\textwidth, natwidth=1080,natheight=720]
+\includegraphics[width=0.8\textwidth]
 {figs/heatmaps/heatmapH2020.png}
@@
 \clearpage
-\appendix
-
-\begin{center}
-\begin{figure}
+\section{Appendix}
+
+\textbf{eu iterations.py}
+
+\lstinputlisting[language=Python]{code/eu_iterations.py}
+
+\textbf{usa iterations.py}
+
+\lstinputlisting[language=Python]{code/usa_iterations.py}
+
+\begin{center}
+\begin{figure}[h]
 \begin{tabular}{rcl}
-\subfloat[Quality Management Systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic0_7000.png}} &
-\subfloat[Agriculture, Fisheries and Food]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic1_7000.png}}&
-\subfloat[Molecular biology, Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic2_7000.png}}\\
-\subfloat[EU transport]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic3_7000.png}}&
-\subfloat[Digital systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic4_7000.png}} &
-\subfloat[Materials processing]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic5_7000.png}}\\
-\subfloat[Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic6_7000.png}} &
-\subfloat[Policy for environmental sustainability]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic7_7000.png}}&
-\subfloat[Energy technologies]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic8_7000.png}}\\
-\subfloat[Applications in mobile networks]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic9_7000.png}}&
+\subfloat[Quality Management Systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic0_7000.png}} &
+\subfloat[Agriculture, Fisheries and Food]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic1_7000.png}}&
+\subfloat[Molecular biology, Genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic2_7000.png}}\\
+\subfloat[EU transport]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic3_7000.png}}&
+\subfloat[Digital systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic4_7000.png}} &
+\subfloat[Materials processing]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic5_7000.png}}\\
+\subfloat[Genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic6_7000.png}} &
+\subfloat[Policy for environmental sustainability]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic7_7000.png}}&
+\subfloat[Energy technologies]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic8_7000.png}}\\
+\subfloat[Applications in mobile networks]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic9_7000.png}}&
 \end{tabular}
@@
 \begin{center}
-\begin{figure}
+\begin{figure}[h]
 \begin{tabular}{rcl}
-\subfloat[Management software]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic0_7000.png}} &
-\subfloat[Hydropower / Energy production]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic1_7000.png}}&
-\subfloat[Information technologies]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic2_7000.png}}\\
-\subfloat[Quality control systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
-\subfloat[Health care / Medical genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
-\subfloat[Environmental sustainability and policies]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\
-\subfloat[Molecular biology (genes)]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic6_7000.png}} &
-\subfloat[Optical quantum computing]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic7_7000.png}}&
-\subfloat[Education in Nuclear physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic8_7000.png}}\\
-\subfloat[Education, training]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic9_7000.png}}&
+\subfloat[Management software]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic0_7000.png}} &
+\subfloat[Hydropower / Energy production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic1_7000.png}}&
+\subfloat[Information technologies]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic2_7000.png}}\\
+\subfloat[Quality control systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
+\subfloat[Health care / Medical genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
+\subfloat[Environmental sustainability and policies]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\
+\subfloat[Molecular biology (genes)]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic6_7000.png}} &
+\subfloat[Optical quantum computing]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic7_7000.png}}&
+\subfloat[Education in Nuclear physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic8_7000.png}}\\
+\subfloat[Education, training]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic9_7000.png}}&
 \end{tabular}
@@
 \begin{center}
-\begin{figure}
+\begin{figure}[h]
 \begin{tabular}{rcl}
-\subfloat[International research]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic0_7000.png}} &
-\subfloat[Biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic1_7000.png}}&
-\subfloat[Embedded systems design]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic2_7000.png}}\\
-\subfloat[Molecular biology, genes]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic3_7000.png}}&
-\subfloat[Evolution / Formation]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic4_7000.png}} &
-\subfloat[Sustainable production / Energy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic5_7000.png}}\\
-\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic6_7000.png}} &
-\subfloat[Environmental management services]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic7_7000.png}}&
-\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic8_7000.png}}\\
-\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic9_7000.png}}&
+\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic0_7000.png}} &
+\subfloat[Biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic1_7000.png}}&
+\subfloat[Embedded systems design]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic2_7000.png}}\\
+\subfloat[Molecular biology, genes]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic3_7000.png}}&
+\subfloat[Evolution / Formation]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic4_7000.png}} &
+\subfloat[Sustainable production / Energy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic5_7000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic6_7000.png}} &
+\subfloat[Environmental management services]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic7_7000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic8_7000.png}}\\
+\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic9_7000.png}}&
 \end{tabular}
@@
 \begin{center}
-\begin{figure}
+\begin{figure}[h]
 \begin{tabular}{rcl}
-\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic0_7000.png}} &
-\subfloat[(High energy) physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic1_7000.png}}&
-\subfloat[Energy production]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic2_7000.png}}\\
-\subfloat[Social Sciences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic3_7000.png}}&
-\subfloat[Molecular Biology / Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic4_7000.png}} &
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic5_7000.png}}\\
-\subfloat[International research]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic6_7000.png}} &
-\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic7_7000.png}}&
-\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic8_7000.png}}\\
-\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic9_7000.png}}&
+\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic0_7000.png}} &
+\subfloat[(High energy) physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic1_7000.png}}&
+\subfloat[Energy production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic2_7000.png}}\\
+\subfloat[Social Sciences]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic3_7000.png}}&
+\subfloat[Molecular Biology / Genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic4_7000.png}} &
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic5_7000.png}}\\
+\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic6_7000.png}} &
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic7_7000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic8_7000.png}}\\
+\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic9_7000.png}}&
 \end{tabular}
@@
 \begin{center}
-\begin{figure}
+\begin{figure}[h]
 \begin{tabular}{rcl}
-\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic0_20000.png}} &
-\subfloat[Environmental sustainability \& food production]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic1_20000.png}}&
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic2_20000.png}}\\
-\subfloat[?]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic3_20000.png}}&
-\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic4_20000.png}} &
-\subfloat[Environmental sustainability / Green energy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic5_20000.png}}\\
-\subfloat[Physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic6_20000.png}} &
-\subfloat[Business \& Innovation]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic7_20000.png}}&
-\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic8_20000.png}}\\
-\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic9_20000.png}}&
+\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic0_20000.png}} &
+\subfloat[Environmental sustainability \& food production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic1_20000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic2_20000.png}}\\
+\subfloat[?]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic3_20000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic4_20000.png}} &
+\subfloat[Environmental sustainability / Green energy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic5_20000.png}}\\
+\subfloat[Physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic6_20000.png}} &
+\subfloat[Business \& Innovation]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic7_20000.png}}&
+\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic8_20000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic9_20000.png}}&
 \end{tabular}
@@
 \begin{center}
-\begin{figure}
+\begin{figure}[h]
 \begin{tabular}{rcl}
-\subfloat[Software engineering]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
-\subfloat[Climate change]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
-\subfloat[International research \& Education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
-\subfloat[Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
-\subfloat[Economic \& Social science]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
-\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
-\subfloat[Molecular biology / Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
-\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
-\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
-\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
+\subfloat[Software engineering]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
+\subfloat[Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
+\subfloat[International research \& Education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
+\subfloat[Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
+\subfloat[Economic \& Social science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
+\subfloat[Molecular biology / Genetics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
+\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
+\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
 \end{tabular}
@@
 \begin{center}
-\begin{figure}
+\begin{figure}[h]
 \begin{tabular}{rcl}
-\subfloat[Applied Sciences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic0_8000.png}} &
-\subfloat[Environment \& Climate change]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic1_8000.png}}&
-\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic2_8000.png}}\\
-\subfloat[Biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic3_8000.png}}&
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic4_8000.png}} &
-\subfloat[STEM education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic5_8000.png}}\\
-\subfloat[Systems ?]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic6_8000.png}} &
-\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic7_8000.png}}&
-\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic8_8000.png}}\\
-\subfloat[International conferences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic9_8000.png}}&
+\subfloat[Applied Sciences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic0_8000.png}} &
+\subfloat[Environment \& Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic1_8000.png}}&
+\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic2_8000.png}}\\
+\subfloat[Biology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic3_8000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic4_8000.png}} &
+\subfloat[STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic5_8000.png}}\\
+\subfloat[Systems ?]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic6_8000.png}} &
+\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic7_8000.png}}&
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic8_8000.png}}\\
+\subfloat[International conferences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic9_8000.png}}&
 \end{tabular}
@@
 \begin{center}
-\begin{figure}
+\begin{figure}[h]
 \begin{tabular}{rcl}
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic0_8000.png}} &
-\subfloat[Education (in engineering)]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic1_8000.png}}&
-\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic2_8000.png}}\\
-\subfloat[International conferences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic3_8000.png}}&
-\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic4_8000.png}} &
-\subfloat[Green transportation]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic5_8000.png}}\\
-\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic6_8000.png}} &
-\subfloat[Climate change]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic7_8000.png}}&
-\subfloat[Materials]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic8_8000.png}}\\
-\subfloat[Physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic9_8000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic0_8000.png}} &
+\subfloat[Education (in engineering)]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic1_8000.png}}&
+\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic2_8000.png}}\\
+\subfloat[International conferences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic3_8000.png}}&
+\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic4_8000.png}} &
+\subfloat[Green transportation]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic5_8000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic6_8000.png}} &
+\subfloat[Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic7_8000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic8_8000.png}}\\
+\subfloat[Physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic9_8000.png}}&
 \end{tabular}
@@
 \begin{center}
-\begin{figure}
+\begin{figure}[h]
 \begin{tabular}{rcl}
-\subfloat[STEM education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic0_9000.png}} &
-\subfloat[Computer \& Networking systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic1_9000.png}}&
-\subfloat[Chemistry \& Materials science]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic2_9000.png}}\\
-\subfloat[Climate change \ Environmental science]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic3_9000.png}}&
-\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic4_9000.png}} &
-\subfloat[Atmospheric \& Ocean sciences]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic5_9000.png}}\\
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic6_9000.png}} &
-\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic7_9000.png}}&
-\subfloat[(Molecular) biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic8_9000.png}}\\
-\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic9_9000.png}}&
+\subfloat[STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic0_9000.png}} &
+\subfloat[Computer \& Networking systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic1_9000.png}}&
+\subfloat[Chemistry \& Materials science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic2_9000.png}}\\
+\subfloat[Climate change \ Environmental science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic3_9000.png}}&
+\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic4_9000.png}} &
+\subfloat[Atmospheric \& Ocean sciences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic5_9000.png}}\\
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic6_9000.png}} &
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic7_9000.png}}&
+\subfloat[(Molecular) biology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic8_9000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic9_9000.png}}&
 \end{tabular}
@@
 \begin{center}
-\begin{figure}
+\begin{figure}[h]
 \begin{tabular}{rcl}
-\subfloat[Biology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic0_8000.png}} &
-\subfloat[Climate Change / Geology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic1_8000.png}}&
-\subfloat[Sociology]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic2_8000.png}}\\
-\subfloat[STEM education]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic3_8000.png}}&
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic4_8000.png}} &
-\subfloat[Chemical \& transport systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic5_8000.png}}\\
-\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic6_8000.png}} &
-\subfloat[Materials \& Mechanical engineering]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic7_8000.png}}&
-\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic8_8000.png}}\\
-\subfloat[International research]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic9_8000.png}}&
+\subfloat[Biology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic0_8000.png}} &
+\subfloat[Climate Change / Geology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic1_8000.png}}&
+\subfloat[Sociology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic2_8000.png}}\\
+\subfloat[STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic3_8000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic4_8000.png}} &
+\subfloat[Chemical \& transport systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic5_8000.png}}\\
+\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic6_8000.png}} &
+\subfloat[Materials \& Mechanical engineering]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic7_8000.png}}&
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic8_8000.png}}\\
+\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic9_8000.png}}&
 \end{tabular}

### 2017-06-23 thesis_report/code/eu_iterations.py

@@ -1,0 +1,126 @@
+# coding: utf-8
+
+import pandas as pd
+import numpy as np
+import re
+import pickle
+import gensim
+import json
+import string
+import logging
+import argparse
+
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+from wordcloud import WordCloud
+from gensim import corpora
+from gensim import models
+from gensim.corpora.dictionary import Dictionary
+from collections import defaultdict
+from gensim.parsing.preprocessing import STOPWORDS
+from time import time
+
+logging.basicConfig(format='%(levelname)s : %(message)s', level=logging.INFO)
+
+# Choose for which dataset you want to run the model and how many iterations
+parser = argparse.ArgumentParser()
+parser.add_argument('dataset',
+                    action='store',
+                    choices=['FP4', 'FP5', 'FP6', 'FP7', 'H2020'],
+                    help='input dataset')
+
+parser.add_argument('-i', '--iterations',
+                    type=int,
+                    default=7000,
+                    help='number of iterations')
+
+args = parser.parse_args()
+df_name = args.dataset
+
+# Read the oandas dataframe, using pickle, keep only the title and the objective
+df = pd.read_pickle('dfs/' + df_name)
+df1 = df[['title','objective']]
+# Drop the rows that have a None value
+df1 = df1.dropna(how='any')
+# Merge the two columns to have one column with all the available text - objectives
+df1['merged'] = df1['title'] + ' ' + df1['objective']
+objectives = df1['merged']
+
+# Remove punctuation
+RE_PUNCTUATION = '|'.join([re.escape(x) for x in string.punctuation])
+objectives = objectives.str.lower().str.replace('%l', '').str.replace(RE_PUNCTUATION, ' ')
+
+# Split objectives, remove words with length <2 and numbers
+objectives_split = objectives.str.strip().str.split()
+objectives_split = objectives_split.apply(lambda tokens: [token for token in tokens if len(token) > 2])
+objectives_split = objectives_split.apply(lambda tokens: [token for token in tokens if not(token.isdigit())])
+
+# Remove stopwords
+list_stopwords = ['data','will', 'develop', 'development', 'project', 'research', 'new', 'use', 'europe', 'european', 'based']
+if df_name == 'FP4':
+    list_stopwords.append('des')
+additional_stopwords = set(list_stopwords)
[…]

### 2017-06-23 thesis_report/code/usa_iterations.py

@@ -1,0 +1,118 @@
+# coding: utf-8
+
+import pandas as pd
+import numpy as np
+import re
+import pickle
+import gensim
+import json
+import string
+import logging
+import argparse
+
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+
+from wordcloud import WordCloud
+from gensim import corpora
+from gensim import models
+from gensim.corpora.dictionary import Dictionary
+from collections import defaultdict
+from gensim.parsing.preprocessing import STOPWORDS
+from time import time
+
+logging.basicConfig(format='%(levelname)s : %(message)s', level=logging.INFO)
+
+# Choose for which dataset you want to run the model and how many iterations
+parser = argparse.ArgumentParser()
+parser.add_argument('dataset',
+                    action='store',
+                    choices=['FP4', 'FP5', 'FP6', 'FP7', 'H2020'],
+                    help='input dataset')
+
+parser.add_argument('-i', '--iterations',
+                    type=int,
+                    default=8000,
+                    help='number of iterations')
+
+args = parser.parse_args()
+df_name = args.dataset
+
+# Read the oandas dataframe, using pickle, keep only the title and the objective
+df = pd.read_pickle('pickle_data/usa' + df_name)
+df1 = df[['title','objective']]
+df1 = df1.dropna(how='any')
+# Merge the two columns to have one column with all the available text - objectives
+df1['merged'] = df1['title'] + ' ' + df1['objective']
+objectives = df1['merged']
+
+# Remove punctuation
+RE_PUNCTUATION = '|'.join([re.escape(x) for x in string.punctuation])
+objectives = objectives.str.lower().str.replace(RE_PUNCTUATION, ' ')
+
+# Split objectives, remove words with length <2 and numbers
+objectives_split = objectives.str.strip().str.split()
+objectives_split = objectives_split.apply(lambda tokens: [token for token in tokens if len(token) > 2])
+objectives_split = objectives_split.apply(lambda tokens: [token for token in tokens if not(token.isdigit())])
+
+# Remove stopwords
+list_stopwords = ['data', 'work', 'based', 'new', 'project', 'university', 'student', 'students', 'research', 'study', 'program', 'development', 'study', 'studies', 'provide', 'use', 'understanding', 'important', 'support', 'proposed']
+additional_stopwords = set(list_stopwords)
+stopwords = set(STOPWORDS) | additional_stopwords
[…]

### 2017-06-24 thesis_report/draft_thesis.tex
Title page & Abstract

@@
 \setcounter{tocdepth}{4}
-
 \setlength{\parskip}{1em}
+
 \usepackage[justification=centering]{caption}
@@
 \usepackage{color}
+\usepackage{geometry}
 
@@
 
-\maketitle
+\begin{titlepage}
+	\centering
+	\includegraphics[width=0.8\textwidth]{figs/logo.jpg}\par\vspace{4cm}
+	{\scshape\Large MSc thesis\par}
+	\vspace{1.5cm}
+	{\Large\bfseries Topic modeling on EU and the USA research projects\par}
+	\vspace{2cm}
+	{\Large Maria Iliadi\par}
+	\vfill
+	supervised by\par
+	Prof.~Panos Louridas
+
+	\vfill
+
+% Bottom of the page
+	{\large \today\par}
+\end{titlepage}
 \tableofcontents
@@
 \begin{abstract}
-This is a simple paragraph at the beginning of the document. 
-A brief introduction about the main subject.
+The purpose of this work is to better identify, quantify and understand themes
+in research and innovation over the last 22 years, and to provide valuable
+knowledge about the research trends nowadays. A way to approach the issue is
+through the projects supported by funding agencies. In particular, public data
+are available for the projects funded under the European Union Framework
+Programmes, and for project funder by the NSF in the United States. The data
+include project descriptions, so it is possible to investigate, based on these
+textual data, the research topics that were actually funded over the last two
+decades. We first introduce the concept of Latent Dirichlet allocation and its
+application in topic modelling in projects funded in the two regions from 1994
+to 2017. We will then proceed to show the differences between the two regions in
+terms of topic similarity and topic evolution over time. We will discuss both
+policy implications, what has been funded over the years, as well as technical
+ones, how can one handle such datasets and extract information from them.
 \end{abstract}
@@
 It is important to note
-that the KL divergence is not symmetrical in $P$ and $Q$ so it’s not a metric.
+that the KL divergence is not symmetrical in $P$ and $Q$ so it's not a metric.
 
@@
 (PMFs)\footnote{If you roll 1000 dice, the theoretical odds of any particular
-number showing up (i.e. a 1, 2, 3, 4, 5, or 6) are 1/6. However, you won’t get
+number showing up (i.e. a 1, 2, 3, 4, 5, or 6) are 1/6. However, you won't get
 that exact distribution in a real experiment due to manufacturing defects. If
@@
 function (PMF) with unlimited options (e.g. an unlimited amount of dice in a
-bag). The process is similar Polya’s Urn\footnote{\url{http://www.statisticshowto.com/dirichlet-distribution/}}, only instead of having a set number
+bag). The process is similar Polya's Urn\footnote{\url{http://www.statisticshowto.com/dirichlet-distribution/}}, only instead of having a set number
 of ball colors you have an unlimited amount:
@@
 
-First, we’ll introduce some basic models for topic modeling. The Latent Semantic
+First, we'll introduce some basic models for topic modeling. The Latent Semantic
 Indexing, or LSI, was presented by Deerwester et al. in 1990. The model manages
@@
 2a). All the documents in the corpus share the same set of topics, but each
-document exhibits those topics with different proportion - that’s the
+document exhibits those topics with different proportion - that's the
 distinguishing characteristic of LDA. A more detailed explanation of the model
@@
 variables after observing training data. However, computing this distribution 
-is intractable, so we’re forced to approximate. One approximation approach is to 
+is intractable, so we're forced to approximate. One approximation approach is to 
 use an optimization method called Variational Bayes. In the original paper it's 
@@
 analyzing a chunk of documents at a time. A chunk could be a single document, 
-50 documents, or even the entire dataset. Let’s let a chunk be 1000 documents.
+50 documents, or even the entire dataset. Let's let a chunk be 1000 documents.
 
@@
 We can see that unlike variational LDA, in online LDA we only need to hold a
-small chunk of the data at a time, and once we’re done analyzing it, we never
-need it again. As with batch, once we’ve estimated $\lambda$, we can find the 
+small chunk of the data at a time, and once we're done analyzing it, we never
+need it again. As with batch, once we've estimated $\lambda$, we can find the 
 most probable words for each topic by looking at the word probabilities in 
@@
 	\end{description}
-\item Justice and Citizens’ rights
+\item Justice and Citizens' rights
 	\begin{description}
@@
 
-To obtain the collection of the documents, we consider as ‘documents’ in LDA the
+To obtain the collection of the documents, we consider as 'documents' in LDA the
 project objectives, which is an accurate description for the project. We also
-added the ‘title’ value of each project to the objectives-documents, to increase
+added the 'title' value of each project to the objectives-documents, to increase
 the probability of finding accurate topics. For the majority of the projects the
-‘start date’ and ‘end date’ value was null, so we kept the splitting of the
+'start date' and 'end date' value was null, so we kept the splitting of the
 dataset per framework, in order to keep the correlation to the time. We followed
@@
 Even the concept of STEM was first introduced by Judith A. Ramaley, the former
-director of the National Science Foundation’s education and human resources
+director of the National Science Foundation's education and human resources
 division.

### 2017-06-24 thesis_report/draft_thesis.tex
Conclusion

@@
 
+In this thesis, we have presented a work about discovering topics and their
+trends in the field of scientific research. We applied the LDA model in projects
+that got funded under the European Union Framework Programmes and the projects
+funded by the National Science Foundation in the United States, for research and
+innovation.
+
+We briefly describe the preprocessing of the abstracts-documents before applying
+the model. LDA, as an unsupervised learning algorithm, does not require any
+prior annotation of labeling the documents and the topics are resulted from the
+statistical structure of the words in the corpus. Using the posterior document-
+topic and topic-word distribution, we investigate the context of each topic per
+FP and the evolution of the topics in each of the two datasets over time.
+
+We found that most topics cover various topics, while some show well-defined
+scopes. Our work provides valuable knowledge about the research over the last
+two decades in the two regions and could benefit researchers to to identify the
+subjects that mostly get funded in the EU and USA. This research gives an
+interesting aspect about what kind of topics were actually funded over the last
+22 years.
+
+The results of our research have several interesting insights that can make it
+easier for people to understand the information contained in large datasets,
+including extracting topics and their dynamics. The evolution of the topics over
+time can also help researchers to find a set of promising topics to focus on and
+start a project based on this knowledge. This could potentially increase their
+chances to get a funding and have the opportunity to make their contribution in
+scientific research.
+
+Moreover, the information about what has been funded over the last years in
+these two regions show that the scope of scientific research has become more
+interdisciplinary and international as well. Even though we started analysing
+the abstracts of the projects quantitatively, we also tried to discuss the
+results and explain furtherthe evolution of the topics in research and potential
+trends.
+
+To sum up, discovering the topics in scientific research is a first step to
+understand the knowledge that the research offers to the community in these two
+regions, visualise the content and discover promising trends. We hore our work
+could help people realise the potential of scientific research and inspire them
+to identify meaningful topics to focus on.
+
 \section{Future work}

### 2017-06-24 thesis_report/draft_thesis.tex
Introduction

@@
 are available for the projects funded under the European Union Framework
-Programmes, and for project funder by the NSF in the United States. The data
+Programmes, and for project funded by the NSF in the United States. The data
 include project descriptions, so it is possible to investigate, based on these
@@
 decades. We first introduce the concept of Latent Dirichlet allocation and its
-application in topic modelling in projects funded in the two regions from 1994
+application in topic modeling in projects funded in the two regions from 1994
 to 2017. We will then proceed to show the differences between the two regions in
@@
 \section{Introduction}
-This is where you tell people why they should bother reading your article.
+Research is the foundation on which knowledge and new technologies emerge and
+support our welfare. Scientific research brings together observation, knowledge
+and data to solve problems, invent solutions and develop new products. In our
+globalized world, the shared commitment for excellence in science has a major
+impact to our well being and it's important to support research and development.
+Over the last years, many projects from different domains are getting funded for
+research and innovation.
+
+Nowadays, there are many funding opportunities for researchers. For instance,
+European Union countries are encouraged to invest 3\% of their GDP in research
+and development by 2020. EU's latest research programme, Horizon 2020, allows
+researchers to identify new opportunities and directions in almost any field of
+research. The programme's goals are to strengthen the EU's position in science,
+support industrial innovation and address social concerns, such as climate
+change, green transportation and energy.
+
+Another funding agency that actively promotes the progress of science is the
+National Science Foundation in the United States of America. NSF supports
+research in all the non medical fields of science \& engineering and aims to
+advance the national health and prosperity. It finds approximately 24\% of the
+federally supported research conducted by the USA's colleges and universities.
+
+With our work, we aim to investigate the evolution of scientific research in the
+EU and the US. In other words, we attempt to identify which subjects are more
+likely to get a funding, based on the previous focus the two regions in research
+fields. In order to answer these questions, we tried to gain some insights from
+the projects that got funded the last two decades under the EU Framework
+Programmes and the NSF in USA.
+
+When researchers apply for a funding, one of the first steps they do is to
+identify an interesting subject of the many possible topics of scientific
+investigation. The topic(s) of a project is always described in the project's
+abstract/description. Obtaining these abstracts, one can possibly investigate
+the topics of the projects and find the subjects that are being addressed and
+gain some information regarding the popularity of the topics among others.
+
+In this work, we discover topics and their evolution from 1994 to 2017, using
+the projects' abstracts that got funded this period. Using a topic model, we
+extract a set of topics and investigate the changes in the content per
+year/framework programme. These topics are used to gain insight into some of the
+research that occurs the last two decades. Our goal is to share these insights
+with researchers and encourage them to develop better strategies to establish
+themselves as more effective researchers globally, by choosing a subject that is
+more likely to get a funding.
+
+In section 2, we briefly talk about the papers that mostly influenced our study.
+Section 3 introduces some basic concepts in topic modeling and we describe the
+model that we used for topic extraction, Latent Dirichlet Allocation, which is a
+statistical generative model for documents. In section 4 we provide information
+about the dataset structure and the methodology that we followed in our
+analysis. In section 5 we interpret the results of our analysis, discuss the
+evolution of the topics over time and the differences between the two regions'
+topics based on their similarity. Finally, section 6 summarizes our work and
+section 7 suggests some future work.
 
@@
 these two regions show that the scope of scientific research has become more
-interdisciplinary and international as well. Even though we started analysing
+interdisciplinary and international as well. Even though we started analyzing
 the abstracts of the projects quantitatively, we also tried to discuss the
-results and explain furtherthe evolution of the topics in research and potential
+results and explain further evolution of the topics in research and potential
 trends.
@@
 understand the knowledge that the research offers to the community in these two
-regions, visualise the content and discover promising trends. We hore our work
-could help people realise the potential of scientific research and inspire them
+regions, visualize the content and discover promising trends. We hope our work
+could help people realize the potential of scientific research and inspire them
 to identify meaningful topics to focus on.

### 2017-06-25 thesis_report/draft_thesis.tex
Future work

@@
 	supervised by\par
-	Prof.~Panos Louridas
+	Assoc.Prof.~Panos Louridas
 
@@
 
+In future research, we intend to extend this work by exploring more complex
+models. In the standard LDA model, both the order of the words and the order of
+the documents are oblivious to the model. One future direction is to use a
+Dynamic Topic Model\cite{Blei:2006:DTM:1143844.1143859}, in which the order of
+the documents plays an important role. More precisely, the documents are grouped
+by time slice (e.g. years) and it is assumed that the documents of each group
+come from a set of topics that involved from the set of the previous slice.
+Moreover, we are planning to examine further the importance of corpus
+preprocessing in our dataset, in order to get higher quality topics.
+
+Another possible future direction is to integrate other data sources to further
+investigate the content and the evolution of the research topics. For example,
+we could add the projects that got funded by NIH in USA and/or find projects
+from other funding agencies, to measure the impact of new emerging topics.
+
+Last but not least, it would be interesting to explore the correlation of the
+topics with the countries/states that are involved in the projects, and address
+question like "which countries in EU are mostly collaborate? on which topics"
+and "which states of the US are getting more funding compared to others".
+
 \bibliography{references}{}

### 2017-06-25 thesis_report/draft_thesis.tex
Comparison of the two datasets with JSD

@@
 the documents-projects  occurring in this year.
-
-In figure X we plot the topic distribution over time. We can easily observe that
+\begin{center}
+\begin{figure}[h]
+\centering
+\includegraphics[width=1.0\textwidth]
+{figs/topic-evolution-usa.png}
+\caption{Topics over time in USA}
+\end{figure}
+\end{center}
+In figure 6 we plot the topic distribution over time. We can easily observe that
 the topic 6, which refers to STEM education, is becoming a trend in the United
@@
 division.
-\begin{center}
-\begin{figure}
-\includegraphics[width=1.0\textwidth]
-{figs/topic-evolution-usa.png}
-\caption{Topics over time in USA}
-\end{figure}
-\end{center}
 
@@
 
-\begin{figure}
+In LDA, a topic is represented as a probability distribution over words of the
+vocabulary. The words with the highest probability are the ones that most likely
+describe the topic, based on the model inference. In order to compare these
+topics quantitatively, one can apply measures that compare probability
+distributions, like KL-divergence or Jensen Shannon divergence (JSD). To make
+this computation more concrete, we will give a basic definition:
+
+Two topics (topic 1 and topic 2) are represented as normalized counts, or
+multinomial probability distributions.
+\begin{itemize}
+\item $P=(p_1, p_2, p_3,…, p_N)$ the probability distribution of the words in topic 1.
+\item $Q=(q_1, q_2, …, q_N)$ the multinomial distribution of the words in topic 2.
+\item $N = $total number of words in the vocabulary.
+\end{itemize}
+
+Since P and Q are probability distributions, it means that 
+$\sum_{i=1}^{N} p_i = \sum_{i=1}^{N} q_i = 1$. The The Jensen–Shannon 
+divergence (JSD) is a
+symmetrized and smoothed version of the Kullback–Leibler divergence
+$D(P \mid\mid Q)$. It quantifies how "distinguishable" two distributions are
+from each other. It is defined by
+
+\begin{equation}
+JSD(P \mid\mid Q) = \frac{1}{2}D(P \mid\mid M) + \frac{1}{2}D(Q \mid\mid M)
+\end{equation}
+where $M = \frac{1}{2}(P + Q)$ and $D(P \mid\mid Q) = \sum_{i}^{N} p_i \ln\frac{p_i}{q_i}$.
+
+In our case, we will use JSD cause is a symmetric formula, so that 
+$sim(Q,P) = sim(P,Q)$. we want to calculate the similarity of the topics of the 
+EU and the USA dataset per framework programme, one by one. Since the topics 
+come from different datasets, it means that their topic probability distributions 
+have different variables-words and different number of variables. To deal with this
+issue, we run the model for the two datasets separately and keep the topics as
+word probability distributions. Then for each pair of the two set of topics, we
+add to each of the topic-word distributions, the words that are missing and
+exist in the other distribution, with probability equals to zero. Then we apply
+the JSD to each pair of topics (see compare FPs.py in the Appendix, for the
+implementation).
+
+The figures 7-11 visualize the heatmaps of the similarity of the two regions
+during the FP4-H2020. Rows represent topics from the EU dataset and 
+columns topics from the USA dataset. The values of the JSD computation which are 
+close to zero (lighter color of the box) suggest more similarity within topics.
+According to the heatmaps, the topics that have high similarity between the 
+EU and the USA are:
+\begin{itemize}
+\item FP4 (1994-1997)
+\begin{itemize}
+\item[*] Software engineering
+\item[*] Materials
+\end{itemize}
+\item FP5 (1998-2001)
+\begin{itemize}
+\item[*] Energy production
+\item[*] Education in STEM
+\item[*] Mathematics
+\end{itemize}
+\item FP6 (2002 - 2006)
+\begin{itemize}
+\item[*] Information systems
+\item[*] Molecular biology / Genetics
+\item[*] Chemistry \& Materials
+\end{itemize}
+\item FP7 (2007-2013)
+\begin{itemize}
+\item[*] Chemistry \& Materials
+\item[*] High energy physics
+\item[*] Molecular biology / Genetics
+\end{itemize}
+\item H2020 (2014-2017)
+\begin{itemize}
+\item[*] Information systems
+\item[*] Materials
+\item[*] Physics
+\item[*] Economic \& Social policy
+\end{itemize}
+\end{itemize}
+\begin{figure}[h]
 \centering
@@
 \end{figure}
+\vfill
 
@@
 \lstinputlisting[language=Python]{code/usa_iterations.py}
+
+\textbf{compare FPs.py}
+
+\lstinputlisting[language=Python]{code/compare_FPs.py}
 
@@
 \end{center}
-
 \begin{center}

### 2017-06-25 thesis_report/code/compare_FPs.py

@@ -1,0 +1,68 @@
+# coding: utf-8
+import pandas as pd
+import numpy as np
+import gensim
+import argparse
+import pickle
+import scipy.stats as stats
+
+from gensim import corpora, models, similarities, matutils
+from gensim.corpora.dictionary import Dictionary
+from scipy.stats import entropy
+from numpy.linalg import norm
+
+parser = argparse.ArgumentParser()
+# Choose the Framework Programme
+parser.add_argument('dataset', action='store', choices=['FP4', 'FP5', 'FP6', 'FP7', 'H2020'], help='input dataset')
+args = parser.parse_args()
+df = args.dataset
+
+# Load the LDA model of the two datasets
+ldaEU = gensim.models.ldamodel.LdaModel.load('./eu_gensim/lda_saved/lda_eu' + df +'.model')
+ldaUSA = gensim.models.ldamodel.LdaModel.load('./usa_gensim/lda_saved/lda_usa' + df +'.model')
+
+def get_topic_vectors(topic_eu_id, topic_usa_id):
+    # get the words and their probabilities for the topic
+    eu_topic_terms_tuples = ldaEU.show_topic(topic_eu_id, topn=ldaEU.num_terms)
+    us_topic_terms_tuples = ldaUSA.show_topic(topic_usa_id, topn=ldaUSA.num_terms)
+
+    # keep the words in set
+    eu_topic_terms = { x[0] for x in eu_topic_terms_tuples }
+    us_topic_terms = { x[0] for x in us_topic_terms_tuples }
+
+    # add the words that don't exist in one of them, with probability = 0.0
+    for eu_missing in us_topic_terms - eu_topic_terms:
+        eu_topic_terms_tuples.append((eu_missing, 0.0))
+                    
+    for us_missing in eu_topic_terms - us_topic_terms:
+        us_topic_terms_tuples.append((us_missing, 0.0))
+
+    # sort the list of the tuples (word, probability) in alphabetic order
+    eu_topic_terms_tuples = sorted(eu_topic_terms_tuples, key=lambda x: x[0])
+    us_topic_terms_tuples = sorted(us_topic_terms_tuples, key=lambda x: x[0])
+
+    # get only the probabilities as vectors
+    eu_topic_probs = [x[1] for x in eu_topic_terms_tuples]
[…]

### 2017-06-26 thesis_report/draft_thesis.tex
add comments

@@
 \setlength{\parskip}{1em}
+
+\usepackage[textsize=tiny, textwidth=30mm]{todonotes}
+
+\usepackage{geometry}
+ \geometry{
+ a4paper,
+ right=40mm,
+ top=20mm,
+ }
 
@@
 
-Nowadays, there are many funding opportunities for researchers. For instance,
-European Union countries are encouraged to invest 3\% of their GDP in research
-and development by 2020. EU's latest research programme, Horizon 2020, allows
-researchers to identify new opportunities and directions in almost any field of
-research. The programme's goals are to strengthen the EU's position in science,
-support industrial innovation and address social concerns, such as climate
-change, green transportation and energy.
-
-Another funding agency that actively promotes the progress of science is the
-National Science Foundation in the United States of America. NSF supports
-research in all the non medical fields of science \& engineering and aims to
-advance the national health and prosperity. It finds approximately 24\% of the
-federally supported research conducted by the USA's colleges and universities.
-
-With our work, we aim to investigate the evolution of scientific research in the
-EU and the US. In other words, we attempt to identify which subjects are more
-likely to get a funding, based on the previous focus the two regions in research
-fields. In order to answer these questions, we tried to gain some insights from
-the projects that got funded the last two decades under the EU Framework
-Programmes and the NSF in USA.
-
-When researchers apply for a funding, one of the first steps they do is to
-identify an interesting subject of the many possible topics of scientific
-investigation. The topic(s) of a project is always described in the project's
-abstract/description. Obtaining these abstracts, one can possibly investigate
-the topics of the projects and find the subjects that are being addressed and
-gain some information regarding the popularity of the topics among others.
-
-In this work, we discover topics and their evolution from 1994 to 2017, using
-the projects' abstracts that got funded this period. Using a topic model, we
-extract a set of topics and investigate the changes in the content per
-year/framework programme. These topics are used to gain insight into some of the
-research that occurs the last two decades. Our goal is to share these insights
-with researchers and encourage them to develop better strategies to establish
-themselves as more effective researchers globally, by choosing a subject that is
-more likely to get a funding.
-
-In section 2, we briefly talk about the papers that mostly influenced our study.
-Section 3 introduces some basic concepts in topic modeling and we describe the
-model that we used for topic extraction, Latent Dirichlet Allocation, which is a
-statistical generative model for documents. In section 4 we provide information
-about the dataset structure and the methodology that we followed in our
-analysis. In section 5 we interpret the results of our analysis, discuss the
-evolution of the topics over time and the differences between the two regions'
-topics based on their similarity. Finally, section 6 summarizes our work and
-section 7 suggests some future work.
-
-\section{Related work}
-
-This chapter surveys previous work in topic modeling on scientific data. Topic
-modeling algorithms provides a suite of algorithms to discover hidden thematic
-structure in large collections of texts and can be adapted to many kinds of
-data. These algorithms can be used to summarize, visualize and explore a
-collection of documents. The papers listed below are applying a Latent Dirichlet
-Allocation model in an interesting approach on their corpus.
-
-D.Blei's research focuses on probabilistic topic models, Bayesian methods and
-approximate posterior inference. In his work "Introduction to Probabilistic
-Topic Models",\cite{Blei11introductionto} he describes the basic ideas behind
-LDA and applies the model to articles from the journal "Science". The model
-assumes that the topics are generated first, before the documents and that the
-documents exhibit multiple topics, but each one of them exhibit those topics in
-different proportion. In our implementation we also use the LDA model and we
-follow a similar approach, since we don't use any previous information about the
-subjects that run through our dataset and the documents are not labeled with
-keywords or topics. The topic distributions arise by computing the hidden
-structure that resembles the thematic structure of the collection.
+Nowadays, there are many \todo{ That sounds like a joke. Research
+  funding is extremely competitive. } funding opportunities for
+researchers. For instance, European Union countries are encouraged to
+invest 3\% of their GDP in research and development by 2020. EU's
+latest research programme, Horizon 2020, allows researchers to
+identify new opportunities and directions in almost any field of
+research. The programme's goals are to strengthen the EU's position in
+science, support industrial innovation and address social concerns,
+such as climate change, green transportation and energy.
+
+Another funding agency that actively promotes the progress of science
+is the National Science Foundation in the United States of America.
+NSF supports research in all the non medical fields of science \&
+engineering and aims to advance the national health and prosperity. It
+finds \todo{funds} approximately 24\% \todo{Where did you find this
+  number? Add reference.} of the federally supported research
+conducted by the USA's colleges and universities.
+
+With our work, we aim to investigate the evolution of scientific
+research in the EU and the US. In other words, we attempt to identify
+which subjects are more likely to get a funding, based on the previous
+focus the two regions in research fields \todo{Does not read right}.
+In order to answer these questions, we tried to gain some insights
+from the projects that got funded the last two decades under the EU
+Framework Programmes and the NSF in USA.
+
+When researchers apply for funding, one of the first steps they do is
+to identify an interesting subject of the many possible topics of
+scientific investigation. The topic(s) of a project is always
+described in the project's abstract/description. Obtaining
+\todo{Using} these abstracts, one can possibly investigate the topics
+of the projects and find the subjects that are being addressed and
+gain some information regarding the popularity of the topics among
+others.
+
+In this work, we discover topics and their evolution from 1994 to
+2017, using the projects' abstracts that got funded \todo{in} this
+period. Using a topic model, we extract a set of topics and
+investigate the changes in the content per year/framework programme.
+These topics are used to gain insight into some of the research that
+occurs the last two decades. Our goal is to share these insights with
+researchers and encourage them to develop better strategies to
+establish themselves as more effective researchers globally, by
+choosing a subject that is more likely to get a funding.
+
+In section 2 \todo{Throughout: never use hard-coded references. Always
+  use LaTeX cross-references.}, we briefly talk about the papers that
+mostly influenced our study. Section 3 introduces some basic concepts
+in topic modeling and we describe the model that we used for topic
+extraction, Latent Dirichlet Allocation, which is a statistical
+generative model for documents. In section 4 we provide information
+about the dataset structure and the methodology that we followed in
+our analysis. In section 5 we interpret the results of our analysis,
+\todo{and we}discuss the evolution of the topics over time and the
+differences between the two regions' topics based on their similarity.
+Finally, section 6 summarizes our work and section 7 suggests some
+future work.
+
+\section{Related work}\todo{Having this section here, before any
+  introduction to LDA, makes counter-intuitive reading. Better move it
+after.}
+
+This chapter \todo{section} surveys previous work in topic modeling on
+scientific data. Topic modeling algorithms provides \todo{provide} a
+suite of algorithms to discover hidden thematic structure
+\todo{structures} in large collections of texts and can be adapted to
+many kinds of data. These algorithms can be used to summarize,
+visualize and explore a collection of documents. The papers listed
+below are applying a Latent Dirichlet Allocation model in an
+interesting approach on their corpus.
+
+D.Blei's \todo{Throughout: separate initials with space from surname}
+research focuses on probabilistic topic models, Bayesian methods and
+approximate posterior inference. In his work "Introduction to
+Probabilistic Topic Models",\cite{Blei11introductionto}
+\todo{Throughout: Fix quotation marks; also citations are placed
+  before punctuation} he describes the basic ideas behind LDA and
+applies the model to articles from the journal "Science"
+\todo{\emph{Science}}. The model assumes that the topics are generated
+first, before the documents and that the documents exhibit multiple
+topics, but each one of them exhibit those topics in different
+proportion. In our implementation we also use the LDA model and we
+follow a similar approach, since we don't use any previous information
+about the subjects that run through our dataset and the documents are
+not labeled with keywords or topics. The topic distributions arise by
+computing the hidden structure that resembles the thematic structure
+of the collection.
 
@@
 
-Inspired by Griffiths and Steyvers, L.Sun and Y.Yin wrote a paper, "Discovering
-themes and trends in transportation research using topic modeling",
-\cite{Sun201749} about topic modeling in transportation research. 
-Considering approximately 17000 abstracts of articles published on 22 
-leading journals in transportation research as documents, they infer 50 
-topics by using LDA. Compared to "Finding scientific topics", Sun and 
-Yin use more than one journal (22 popular journals) and they
-investigate the journal-topic distribution and journal similarity. In our
-analysis, we identify the EU and the USA as 2 regions (like 2 different journals),
-with different proportions of documents-projects, and we visualize the topic
-similarity of the two regions per framework programme.
+Inspired by Griffiths and Steyvers, L.Sun and Y.Yin wrote a paper,
+"Discovering themes and trends in transportation research using topic
+modeling", \cite{Sun201749} about topic modeling in transportation
+research. Considering approximately 17000 abstracts of articles
+published on 22 leading journals in transportation research as
+documents, they infer 50 topics by using LDA. Compared to "Finding
+scientific topics", Sun and Yin use more than one journal (22 popular
+journals) and they investigate the journal-topic distribution and
+journal similarity. In our analysis, we identify the EU and the USA as
+2 regions (like 2 different journals), with different proportions of
+documents-projects, and we visualize the topic similarity of the two
+regions per framework programme.
 
@@
 
-In this chapter we will present some basic theoretic background about topic
-modeling. To deal with extensive text body, machine learning researchers have
-developed topic modeling: a suite of methods that analyze the words of the
-original text to discover the themes that run through the data and detect
-hidden semantic structures by analyzing a corpus. By marking up the documents
-using these topics and by using the resulting structure, the model can be used
-for organization, finding similar documents, or any other similar tasks. A
-topic is here defined as a probability distribution of words, meaning that
-certain words are more likely within a certain topic. Since the topics emerge
-from the analysis of the original texts, topic modeling algorithms do not
-require any prior annotations or labeling of the documents.\cite{Blei11introductionto}
+In this chapter we will present some basic theoretic background about
+topic modeling. To deal with extensive text body \todo{probably
+  plural}, machine learning researchers have developed topic modeling:
+a suite of methods that analyze the words of the original text to
+discover the themes that run through the data and detect hidden
+semantic structures by analyzing a corpus. By marking up the documents
+using these topics and by using the resulting structure, the model can
+be used for organization, finding similar documents, or any other
+similar tasks. A topic is here defined as a probability distribution
+of words, meaning that certain words are more likely within a certain
+topic. Since the topics emerge from the analysis of the original
+texts, topic modeling algorithms do not require any prior annotations
+or labeling of the documents.\cite{Blei11introductionto}
 
@@
 \begin{itemize}
-\item[] A \textit{word} is defined as an item from a vocabulary indexed from 
-${1, ..., V}$, where V is the size of the vocabulary. All words are 
-represented as unit-basis vectors with one component equal to one and 
-the rest equal to zero.
-\item[] A \textit{document} is a collection of words denoted by $w = {w_1, ..., w_N}$, 
-where $w_n$ is the $n$th word and $N$ is the total number of words in the 
-collection.
-\item[] A \textit{corpus} is a collection of documents in a dataset. It is denoted 
-$D = {w_1,..., w_M}$, where $w_m$ is the $m$th document in the corpus and 
-$M$ is the total number of documents.
+\item[] A \textit{word} is defined as an item from a vocabulary
+  indexed from ${1, ..., V}$, where V \todo{$V$} is the size of the
+  vocabulary. All words are represented as unit-basis vectors with one
+  component equal to one and the rest equal to zero.
+\item[] A \textit{document} is a collection of words denoted by
+  $w = {w_1, ..., w_N}$, where $w_n$ is the $n$th word and $N$ is the
+  total number of words in the collection.
+\item[] A \textit{corpus} is a collection of documents in a dataset.
+  It is denoted $D = {w_1,..., w_M}$, where $w_m$ is the $m$th
+  document in the corpus and $M$ is the total number of documents.
 \item[] \textit{Latent variables} are variables that may not be directly observed, 
@@
 
-When introducing the Latent Dirichlet Allocation in section 2.2.3, we 
-will be using the terms prior and posterior probabilities and 
-likelihood function:
+When introducing the Latent Dirichlet Allocation in section 2.2.3
+\todo{Cross reference}
+\todo{As you can see this is a disaster: always cross-reference with
+  LaTeX}, we will be using the terms prior and posterior probabilities
+and likelihood function:
 
 \begin{itemize}
-\item The prior probability distribution of and uncertain quantity is the 
-probability distribution that express the value of this quantity before 
-some evidence is taken into account.
+\item The prior probability distribution of and \todo{an} uncertain
+  quantity is the probability distribution that express the value of
+  this quantity before some evidence is taken into account.
 \item The posterior probability is the conditional probability after some 
@@
 
-In the context of probabilities, the Jensen Inequality is stated as follows: 
-If X is a random variable and f a convex function then:
+In the context of probabilities, the Jensen Inequality is stated as
+follows: If X \todo{$X$} is a random variable and f \todo{$f$} a
+convex function then \todo{What is $\mathbb{E}$?}:
 
@@
 
-And, if f is a concave function the inequality turns:
+And, if f \todo{f} is a concave function the inequality turns:
 
@@
 
-When formulating the optimization problem in Latent Dirichlet Allocation we 
-will use the KL divergence to express the optimization problem. The KL divergence 
-is a measure of the difference between two probability distributions $P$ and $Q$. 
-It is important to note
-that the KL divergence is not symmetrical in $P$ and $Q$ so it's not a metric.
+When formulating the optimization problem in Latent Dirichlet
+Allocation we will use the KL divergence to express the optimization
+problem. The KL divergence is a measure of the difference between two
+probability distributions $P$ and $Q$. It is important to note that
+the KL divergence is not symmetrical in $P$ and $Q$ so it's not a
+metric.
 
@@
 
-Given two continuous distributions $P$ and $Q$ the KL divergence is defined as follows:
+Given two continuous distributions $P$ and $Q$ the KL divergence is
+defined as follows:
 
@@
 D_{KL}(P \mid \mid Q) = \int_{-\infty}^{+\infty} p(x) log\frac{p(x)}{q(x)}dx
-\end{equation}
-
-This can also be expressed using the definition of expectation (and expressing the 
-log of a division as difference of log) as:
+\end{equation} \todo{ log in mathematics is $\log$}
+
+This can also be expressed using the definition of expectation (and
+expressing the log of a division as difference of log) as:
 
@@
   D_{KL}(P \mid \mid Q) = \mathbb{E}_{p}[log p(x)] - \mathbb{E}_{p}[log q(x)]
-\end{equation}
-
-This is the expression we will use later on instead of the definition. We present 
-now the two probability distributions we will be using when we define the different 
-models in this work: the \textbf{Multinomial} and the \textbf{Dirichlet} distributions.
+\end{equation} \todo{Smae with log; also, it is a function.}
+
+This is the expression we will use later on instead of the definition.
+We present now the two probability distributions we will be using when
+we define the different models in this work: the \textbf{Multinomial}
+and the \textbf{Dirichlet} distributions.
 
@@
 
-Once we have a representation for individual documents, the natural next step
-is to select a model for a set of documents. Given a training set of
-documents, we will choose values for the parameters of a probabilistic model
-that make the training documents have high probability. Then, given a test
-document, we can evaluate its probability according to the model. The higher
-this probability is, the more similar the test document is to the training set.
-
-The probability distribution that we use is the multinomial. In probability 
-theory, the multinomial distribution is a generalization of the binomial 
-distribution. For example, it models the probability of counts for rolling 
-a k-sided dice n times. For n independent trials each of which leads to a 
-success for exactly one of k categories, with each category having a given 
-fixed success probability, the multinomial distribution gives the 
-probability of any particular combination of numbers of successes for the 
-various categories\footnote{\url{https://en.wikipedia.org/wiki/Multinomial_distribution}}.
+Once we have a representation for individual documents, the natural
+next step is to select a model for a set of documents. Given a
+training set of documents, we will choose values for the parameters of
+a probabilistic model that make the training documents have high
+probability. Then, given a test document, we can evaluate its
+probability according to the model. The higher this probability is,
+the more similar the test document is to the training set. \todo{Is
+  this really what you use the multinomial distribution for? You use
+  the multinomial distribution because LDA assumes that this is the
+  distribution of topics in documents and words in topics.}
+
+The probability distribution that we use is the multinomial. In
+probability theory, the multinomial distribution is a generalization
+of the binomial distribution. For example, it models the probability
+of counts for rolling a k-sided dice n times. For n independent trials
+each of which leads to a success for exactly one of k categories, with
+each category having a given fixed success probability, the
+multinomial distribution gives the probability of any particular
+combination of numbers of successes for the various
+categories\footnote{\url{https://en.wikipedia.org/wiki/Multinomial_distribution}}.
+\todo{Variables like $k$, $n$, etc. should be in math mode.}
 
@@
 
-The Dirichlet distribution is a prior for the multinomial distribution. This
-means that if the prior distribution of the multinomial parameters is Dirichlet
-then the posterior distribution is also a Dirichlet distribution (with
-parameters different from those of the prior).
-
-The Dirichlet process is a way to model randomness of a probability mass
-function (PMF) with unlimited options (e.g. an unlimited amount of dice in a
-bag). The process is similar Polya's Urn\footnote{\url{http://www.statisticshowto.com/dirichlet-distribution/}}, only instead of having a set number
-of ball colors you have an unlimited amount:
+The Dirichlet distribution is a prior for the multinomial
+distribution. This means that if the prior distribution of the
+multinomial parameters is Dirichlet then the posterior distribution is
+also a Dirichlet distribution (with parameters different from those of
+the prior). \todo{ If the Dirichlet is the prior for the multinomial
+  then the posterior is the multinomial; in fact the Dirichlet is the
+  conjugate prior of the multinomial. It is the posterior distribution
+  of the \emph{parameters} that is still Dirichlet. }
+
+The Dirichlet process is a way to model randomness of a probability
+mass function (PMF) with unlimited options (e.g. an unlimited amount
+of dice in a bag). The process is similar Polya's
+Urn\footnote{\url{http://www.statisticshowto.com/dirichlet-distribution/}},
+only instead of having a set number of ball colors you have an
+unlimited amount: \todo{Why do we need to know that? }
 
@@
 
-First, we'll introduce some basic models for topic modeling. The Latent Semantic
-Indexing, or LSI, was presented by Deerwester et al. in 1990. The model manages
-to deal with the problem that multiple terms can refer to the same meaning,
-i.e. synonymy. However, it is not as successful regarding polysemy. The reason
-is that every term is represented as just one point in the so-called latent
-semantic space. Furthermore, a word that can mean two or more different things
-is represented as a weighted average of the different meanings.
-
-After LSI was introduced, Hofmann presented the Probabilistic Latent Semantic
-Indexing, or PLSI model. PLSI is a topic model where each word in a
-document is generated from a single topic which results in that each document
-in a corpus can be represented with a topic distribution. Later, in 2003 Blei et
-al. presented the Latent Dirichlet Allocation, or LDA. As opposed to PLSI, LDA
-is a statistically generative model for documents where each word in a document
-can be generated by all topics.
+First, we'll introduce some basic models for topic modeling. The
+Latent Semantic Indexing, or LSI, was presented by Deerwester et al.
+in 1990. \todo{Add reference.} The model manages to deal with the
+problem that multiple terms can refer to the same meaning, i.e.
+synonymy. However, it is not as successful regarding polysemy. The
+reason is that every term is represented as just one point in the
+so-called latent semantic space. Furthermore, a word that can mean two
+or more different things is represented as a weighted average of the
+different meanings.
+
+After LSI was introduced, Hofmann presented the Probabilistic Latent
+Semantic Indexing, or PLSI model \todo{Add reference}. PLSI is a topic
+model where each word in a document is generated from a single topic
+which results in that each document in a corpus can be represented
+with a topic distribution. Later, in 2003 Blei et al. presented the
+Latent Dirichlet Allocation, or LDA \todo{Add reference}. As opposed
+to PLSI, LDA is a statistically generative model for documents where
+each word in a document can be generated by all topics.
 
@@
 Latent Semantic Indexing was one of the earliest methods for finding
-relationships between documents and the words that occur in them.\cite{Deerwester90indexingby} In LSI a
-term-document matrix is created by analyzing the corpus, where the rows
-correspond to words and columns to documents. Each element in this sparse
-matrix describes the number of times a word occurs in a document but this term
-count can also be weighted with for instance TF-IDF. Letting each word
-represent a dimension in a very high dimensional space, a document can be seen
-as a vector with components corresponding to its weighted term counts.
-\cite{Salton:1988:TAA:54259.54260}
+relationships between documents and the words that occur in
+them.\cite{Deerwester90indexingby} In LSI a term-document matrix is
+created by analyzing the corpus, where the rows correspond to words
+and columns to documents. Each element in this sparse matrix describes
+the number of times a word occurs in a document but this term count
+can also be weighted with for instance TF-IDF \todo{Explain}. Letting
+each word represent a dimension in a very high dimensional space, a
+document can be seen as a vector with components corresponding to its
+weighted term counts. \cite{Salton:1988:TAA:54259.54260}
 
@@
 tries to solve this limitation by setting a Dirichlet prior on the topic
-distribution.\cite{blei2003latent}
+distribution.\cite{blei2003latent} \todo{In essence you repeat what
+  you said in the beginning of the paragraph.}
 
@@
 
-The basic idea in LDA is that we define a topic to be a Dirichlet distribution
-over a fixed vocabulary. Technically, the model assumes that the topics are
-generated first, before the documents.\cite{Blei11introductionto} Now for 
-each document in the collection, we generate the words in a two-stage process:
+The basic idea in LDA is that we define a topic to be a Dirichlet
+distribution over a fixed vocabulary. \todo{No, a topic is a
+  multinomial distribution.} Technically, the model assumes that the
+topics are generated first, before the
+documents.\cite{Blei11introductionto} Now for each document in the
+collection, we generate the words in a two-stage process:
 
@@
 
-This statistical model reflects the intuition that documents exhibit multiple
-topics. Each document exhibits the topics with different proportion (step 1);
-each word in each document is drawn from one of the topics (step 2b), where the
-selected topic is chosen from the per-document distribution over topics (step
-2a). All the documents in the corpus share the same set of topics, but each
-document exhibits those topics with different proportion - that's the
-distinguishing characteristic of LDA. A more detailed explanation of the model
-follows in section 2.2.3.1.
+This statistical model reflects the intuition that documents exhibit
+multiple topics. Each document exhibits the topics with different
+proportion (step 1); each word in each document is drawn from one of
+the topics (step 2b), where the selected topic is chosen from the
+per-document distribution over topics (step 2a). All the documents in
+the corpus share the same set of topics, but each document exhibits
+those topics with different proportion - that's the distinguishing
+characteristic of LDA. A more detailed explanation of the model
+follows in section 2.2.3.1. \todo{Again, fix cross-references}
 
@@
 
-LDA is a probabilistic model of text documents, which assumes a collection of 
-K topics. Each topic defines a multinomial distribution over the vocabulary 
-and is assumed to have been drawn from a Dirichlet 
-$\beta_k \sim Dirichlet(\eta)$.
-
-In LDA, each document is represented by a mixture of the topics, with weight
-$\theta_w^2$ for topic $z$ in document $w$. These weight have a Dirichlet prior,
-parametrized by a hyper-parameter $\alpha$. Each topic is a probability
-distribution over the vocabulary, with probability $\beta^w_z$ for word $w$ in
-topic $z$. We define the following variables and notation:
+LDA is a probabilistic model of text documents, which assumes a
+collection of K topics. Each topic defines a multinomial distribution
+over the vocabulary and is assumed to have been drawn from a Dirichlet
+$\beta_k \sim Dirichlet(\eta)$. \todo{What is $beta_k$ and what is
+  $\eta$? If you explain them later (which you do) this sentence
+  should follow the explanations.}
+
+In LDA, each document is represented by a mixture of the topics, with
+weight $\theta_w^2$ \todo{Where does the square come from?} for topic
+$z$ in document $w$. These weight \todo{weights} have a Dirichlet
+prior, parametrized by a hyper-parameter $\alpha$. Each topic is a
+probability distribution over the vocabulary, with probability
+$\beta^w_z$ for word $w$ in topic $z$. We define the following
+variables and notation:
 \begin{itemize}
@@
    drawn from a uniform Dirichlet distribution with parameter $\alpha$.
-  \item[] $z_{n}$ is a topic assignment for $word w_{n}$, sampled from 
-  $p(z_{n} = i|\theta) = \theta_{i}$.
+ \item[] $z_{n}$ is a topic assignment for $word w_{n}$ \todo{word
+     $w_n$}, sampled from $p(z_{n} = i|\theta) = \theta_{i}$.
   \item[] \textbf{w}$ = (w_{1}, ... , w_{N})$ is a document with $N$ words.
@@
 ~\cite{onlineLDAvb}. In our implementation, we're using the online variational
-LDA model, which is described in section 2.2.3.4.
+LDA model, which is described in section 2.2.3.4. \todo{Cross reference.}
 
@@
 one can use the parameters learned previously to estimate the topic
-distribution $\theta$ for this new document.
-
-A limitation with the standard LDA model is the fix vocabulary. This means that
-new words cannot enter the model and that you have to know a priori what words
-will model the corpus effectively. A setting where this could be problematic is
-when analyzing data where new words in the form of slang or names emerge over 
-time. Another limitation is the fact that one has to state
-the number of topics the model should use. This is not a big issue, but could
-lead to some of the resulting topics to be insignificant.
+distribution $\theta$ for this new document. \todo{You have already
+  said that many times.}
+
+A limitation with the standard LDA model is the fix \todo{fixed}
+vocabulary. This means that new words cannot enter the model and that
+you have to know a priori what words will model the corpus
+effectively. A setting where this could be problematic is when
+analyzing data where new words in the form of slang or names emerge
+over time. Another limitation is the fact that one has to state the
+number of topics the model should use. This is not a big issue, but
+could lead to some of the resulting topics to be insignificant.
 \begin{center}
@@
 
-In LDA, our ultimate goal is to find the posterior distribution of latent topic 
-variables after observing training data. However, computing this distribution 
-is intractable, so we're forced to approximate. One approximation approach is to 
-use an optimization method called Variational Bayes. In the original paper it's 
-being used a variational Bayes approximation of the posterior distribution;
-\cite{blei2003latent} alternative inference techniques use Gibbs sampling and
-expectation propagation. The goal of variational inference is to approximate an
-intractable probability distribution $p$, with a tractable one $q$, in a way
-that makes them as close as possible given a similarity measure. In this thesis,
-variational inference is used to approximate the posterior distribution of
-latent variables. A new distribution over the hidden variables $q(z, \beta)$
-(called the variational distribution) is  introduced. This new distribution has
-properties such that it can be efficiently computed.\cite{Fox2011ATO}
-
-In short, we approximate the true distribution by a simple distribution $q$, and 
-associate parameters $\phi$, $\gamma$, $\lambda$ with the original parameters 
-$z$, $\theta$, $\beta$ respectively. Recall that $z$ gives the topic assignments 
-for each word in each document, $\theta$ gives the topic composition of each 
-document, and $\beta$ gives the word-topic probabilities for each word and each 
-topic. The variational distribution is a function of a set of free parameters that 
-are optimized such that the variational distribution is as close as possible to 
-the actual target posterior distribution where closeness is measured in terms of 
-KL divergence.
+In LDA, our ultimate goal is to find the posterior distribution of
+latent topic variables after observing training data. However,
+computing this distribution is intractable, so we're forced to
+approximate. One approximation approach is to use an optimization
+method called Variational Bayes. In the original paper it's being used
+a variational Bayes approximation of the posterior distribution;
+\cite{blei2003latent} alternative inference techniques use Gibbs
+sampling and expectation propagation \todo{Cite these techniques.
+  AFAIK, if you do not use Variational Bayes, you use MCMC with Gibbs
+  sampling.}. The goal of variational
+inference is to approximate an intractable probability distribution
+$p$, with a tractable one $q$, in a way that makes them as close as
+possible given a similarity measure. In this thesis, variational
+inference is used to approximate the posterior distribution of latent
+variables. A new distribution over the hidden variables $q(z, \beta)$
+(called the variational distribution) is introduced. This new
+distribution has properties such that it can be efficiently
+computed.\cite{Fox2011ATO}
+
+In short, we approximate the true distribution by a simple
+distribution $q$, and associate parameters $\phi$, $\gamma$, $\lambda$
+with the original parameters $z$, $\theta$, $\beta$ respectively.
+Recall that $z$ gives the topic assignments for each word in each
+document, $\theta$ gives the topic composition of each document, and
+$\beta$ gives the word-topic probabilities for each word and each
+topic. The variational distribution is a function of a set of free
+parameters that are optimized such that the variational distribution
+is as close as possible to the actual target posterior distribution
+where closeness is measured in terms of KL divergence.
 
@@
 \end{algorithm}
+\todo{Update $\phi$ and $\gamma$ do not show as separate lines.}
 
@@
 \end{equation}
-Where $n_{d,word_{i}}$ is the number of occurrences of $word_{i}$ in document $d$.
-The algorithm above has constant memory requirements and empirically
-converges faster than collapsed Gibbs sampling. However, it still requires a
-full pass through the entire corpus in each iteration. It can be slow to apply
-to very large datasets.
+Where $n_{d,word_{i}}$ is the number of occurrences of $word_{i}$ in
+document $d$. The algorithm above has constant memory requirements and
+empirically converges faster than collapsed Gibbs sampling. However,
+it still requires a full pass through the entire corpus in each
+iteration. It can be slow to apply to very large datasets.
+\todo{Provide citation for the description you have given; I assume
+  it's the same blog post as for the following paragraph.}
 
@@
 dataset is made up of $\frac{numDocs}{chunkSize}$ copies of the current chunk. 
-Then $\lambda$ is updated using a weighted sum of $\lambda^{*}$ and $\lambda$:
+Then $\lambda$ is updated using a weighted sum of $\lambda^{*}$ and
+$\lambda$: \todo{As the algorithm is thrown on the next page, it looks
+  as if something is missing here.}
 
@@
 
-We can see that unlike variational LDA, in online LDA we only need to hold a
-small chunk of the data at a time, and once we're done analyzing it, we never
-need it again. As with batch, once we've estimated $\lambda$, we can find the 
-most probable words for each topic by looking at the word probabilities in 
-each row of $\lambda$.\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}
+We can see that unlike variational LDA, in online LDA we only need to
+hold a small chunk of the data at a time, and once we're done
+analyzing it, we never need it again. As with batch, once we've
+estimated $\lambda$, we can find the most probable words for each
+topic by looking at the word probabilities in each row of
+$\lambda$.\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}
 
@@
 
-In this section, we explain the procedure that we followed in n order to apply
-the LDA model in our dataset. The dataset consists of two datasets: the one that
-contains all the information about EU projects founded for research and
-innovation under the FP4-H2020 and the dataset from USA about the
-awards/projects that got approved from 1994-2017. We consider the projects'
-description/abstract as the documents in LDA.
+In this section, we explain the procedure that we followed in order to
+apply the LDA model in our dataset. The dataset consists of two
+datasets \todo{That reads funny.}: the one that contains all the
+information about EU projects founded for research and innovation
+under the FP4-H2020 \todo{Throughout: use dashes correctly. There are
+  hyphens (-), n-dashes (--) and m-dashes (---).} and the dataset from
+USA about the awards/projects that got approved from 1994-2017. We
+consider the projects' description/abstract as the documents in LDA.
 
@@
 
-The data that are provided by CORDIS (via the EU Open Data Portal) are open,
-free and can be used in research, applications, commercial or non-commercial
-purposes. The dataset that we chose for the following analysis contains
-information about all the projects funded by the European Union from 1994 to
-2017. These projects got approved under the framework programme (FP4-H2020) for
-research and technological development. For each project it is provided
-information, such as: reference, acronym, dates, funding, programs,
-participant countries, subjects and objectives.
-
-In the provided dataset, the information is splitted into CSV files, based on
-the framework program that each project belongs. The frameworks from 1994 to
-2020 are listed below:
+The data that are provided by CORDIS (via the EU Open Data Portal) are
+open, free and can be used in research, applications, commercial or
+non-commercial purposes. The dataset that we chose for the following
+analysis contains information about all the projects funded by the
+European Union from 1994 to 2017. These projects got approved under
+the framework programme (FP4-H2020) for research and technological
+development. For each project it is provided information \todo{Does
+  not read right}, such as: reference, acronym, dates, funding,
+programs, participant countries, subjects and objectives.
+
+In the provided dataset, the information is splitted \todo{split} into
+CSV files, based on the framework program that each project belongs.
+The frameworks from 1994 to 2020 are listed below:
 
@@
 
-To obtain the collection of the documents, we consider as 'documents' in LDA the
-project objectives, which is an accurate description for the project. We also
-added the 'title' value of each project to the objectives-documents, to increase
-the probability of finding accurate topics. For the majority of the projects the
-'start date' and 'end date' value was null, so we kept the splitting of the
-dataset per framework, in order to keep the correlation to the time. We followed
+To obtain the collection of the documents, we consider as 'documents'
+\todo{In the rest of the document you are using single quotation marks.}
+in LDA the project objectives, which is an accurate description for
+the project. We also added the 'title' value of each project to the
+objectives-documents, to increase the probability of finding accurate
+topics. For the majority of the projects the 'start date' and 'end
+date' value was null, so we kept the splitting of the dataset per
+framework, in order to keep the correlation to the time. We followed
 the same format in the dataset of USA awards.
@@
 words that appear less than 5 times in the collection. Finally, we obtained a
-smaller corpus per framework (see the table above)
-
-In this section, we explain the procedure that we followed in n order to apply
-the LDA model in our dataset. The dataset consists of two datasets: the one that
-contains all the information about EU projects founded for research and
-innovation under the FP4-H2020 and the dataset from USA about the
-awards/projects that got approved from 1994-2017. We consider the projects'
-description/abstract as the documents in LDA.
+smaller corpus per framework (see the table above).
+
+In this section, we explain the procedure that we followed in n order
+to apply the LDA model in our dataset. The dataset consists of two
+datasets: the one that contains all the information about EU projects
+founded for research and innovation under the FP4-H2020 and the
+dataset from USA about the awards/projects that got approved from
+1994-2017. We consider the projects' description/abstract as the
+documents in LDA. \todo{Why is this paragraph here?}
 
@@
 
-The National Science Foundation (NSF) is a United States government agency that
-supports fundamental research and education in all the non-medical fields of
-science and engineering. Its medical counterpart is the National Institutes of
-Health. The NSF funds approximately 24\% of all federally supported basic
-research conducted by the United States' colleges and universities. In some
-fields, such as mathematics, computer science, economics, and the social
-sciences, the NSF is the major source of federal backing.
+The National Science Foundation (NSF) is a United States government
+agency that supports fundamental research and education in all the
+non-medical fields of science and engineering. Its medical counterpart
+is the National Institutes of Health \todo{Does your data include
+  material from NIH as well?}. The NSF funds approximately 24\% of all
+federally supported basic research conducted by the United States'
+colleges and universities. In some fields, such as mathematics,
+computer science, economics, and the social sciences, the NSF is the
+major source of federal backing.
 
@@
 
-In this section, we show our main results. We focus on finding differences
-between the two datasets in terms of topic distribution and later we 
-investigate the evolution of the topics over time of each dataset separately.
+In this section, we show our main results. We focus on finding
+differences between the two datasets in terms of topic distribution
+and later we investigate the evolution of the topics over time of each
+dataset separately.\todo{Although in the preceding material you have
+  listed the areas of interest in the EU, as listed in the EU Open
+  Data Portal, and the areas of interest in the US, through its
+  directorates, you do not discuss whether the topics you found have
+  any relationship to these thematic areas and divisions. So you do
+  not answer the question: ``did you find something we did not already
+  know by checking the descriptions on the web sites?''}
 
@@
 
-In general, the most popular subject in European Union over the years is
-Information systems. In our dataset we fount projects related to almost all
-kinds of information systems, and especially Quality management systems
-(1994-2002), Management information systems, Network information systems and
-Information systems as a service to all kinds of organizations, including
-universities and companies. Since technology has an impact in every aspect
-nowadays, it is normal to have such popularity over the years and it's becoming
-popular in education, as well. The same period of time, Innovation in Business
-emerged as a trending topic, with projects related to new technologies and
-software systems in the industry and how they assist the businesses and the
-market. In addition, until 2002 a very popular subject related to Information
-systems, was Applications in mobile networks, embedded and broadband systems,
-which nowadays has lost part of its popularity in research.
+\todo{This is the heart of the thesis, but it is difficult to make
+  sense of it. Make sure that when you mention a topic, the topic
+  stands out of the text. It could be in italics, or some other font.
+  Right now it is not easy to detect it in the discussion. From what I
+  understand, the topics you mention are the top topics over all the
+  years. You should then list them all in a table, in decreasing order
+  of popularity. Also you should show the wordclouds. Right now there
+  is only a reference to a figure at the appendix, which is not at the
+  appendix at all.
+}
+
+In general, the most popular subject in European Union over the years
+is Information systems. In our dataset we fount \todo{found} projects
+related to almost all kinds of information systems, and especially
+Quality management systems (1994-2002), Management information
+systems, Network information systems and Information systems as a
+service to all kinds of organizations, including universities and
+companies. Since technology has an impact in every aspect nowadays, it
+is normal to have such popularity over the years and it's becoming
+popular in education, as well. The same period of time, Innovation in
+Business emerged as a trending topic, with projects related to new
+technologies and software systems in the industry and how they assist
+the businesses and the market. In addition, until 2002 a very popular
+subject related to Information systems, was Applications in mobile
+networks, embedded and broadband systems, which nowadays has lost part
+of its popularity in research.
 
@@
 
-The third most popular subject is Molecular biology and Genetics. These projects
-are related to the cellular molecules that carry out the biological processes
-essential for the cell's functions and maintenance. These affect many aspects of
-our lives, including evolution, nutrition and the spread of diseases. Especially
-from 1998 up to day, there is a focus in Health care and Diagnostics, and for the
-last decade researchers are studying the cancer detection and treatment, which
-is a common cause of death in EU and the second most common cause of death in
-USA.
-
-Moreover, Environmental, Social and Economic Sustainability is a subject very
-important to the research community and many researchers work on this up to day.
-In short, sustainability takes into account how we might live in harmony with
-the natural world around us, protecting it from damage and destruction. Many
-projects are related to one of the Three Pillars of Sustainability\footnote{http
-://www.thwink.org/sustain/glossary/ThreePillarsOfSustainability.htm}. The
-European Union is considered by some to have the most extensive environmental
-laws of any international organization, started by the  European Economic
-Community (EEC), which is the beginning of the EU's environmental policy. Social
-and Economic policies are also popular in the EU region over the last decade.
-Also, the last two decades there is a focus on the Green energy production, like
-hydropower, solar and nuclear energy.
+The third most popular subject is Molecular biology and Genetics.
+These projects are related to the cellular molecules that carry out
+the biological processes essential for the cell's functions and
+maintenance. These affect many aspects of our lives, including
+evolution, nutrition and the spread of diseases. \todo{This is not an
+  essay, remove.} Especially from 1998 up to day, there is a focus in
+Health care and Diagnostics, and for the last decade researchers are
+studying the cancer detection and treatment, which is a common cause
+of death in EU and the second most common cause of death in USA.
+\todo{It seems now that you are discussing topics that are not popular
+  throughout the period, but in the latest frameworks?}
+
+Moreover, Environmental, Social and Economic Sustainability is a
+subject very important to the research community and many researchers
+work on this up to day. In short, sustainability takes into account
+how we might live in harmony with the natural world around us,
+protecting it from damage and destruction. \todo{This is not an essay,
+  remove.} Many projects are related to one of the Three Pillars of
+Sustainability\footnote{http
+  ://www.thwink.org/sustain/glossary/ThreePillarsOfSustainability.htm}.
+The European Union is considered by some to have the most extensive
+environmental laws of any international organization, started by the
+European Economic Community (EEC), which is the beginning of the EU's
+environmental policy. Social and Economic policies are also popular in
+the EU region over the last decade. Also, the last two decades there
+is a focus on the Green energy production, like hydropower, solar and
+nuclear energy.
 
@@
 
-The National Science Foundation mostly supports fundamental research and
-education in the non-medical science and engineering. Its medical counterpart
-is the National Institutes of Health.\footnote{\url{https://en.wikipedia.org/wik
-i/National_Science_Foundation}} With STEM being the top priority in USA, most of
-the projects founded by NSF are related to engineering, computer science,
-mathematics and information systems, in general. The subjects STEM \& Education,
-Software engineering, Information systems and Mathematics, arise as topics in
-all these years, from 1994-2017.
+\todo{The same comments as in the previous subsection apply here. Make
+  sure you explain how you picked the topics you discuss here. Make
+  sure they stand out.}
+
+The National Science Foundation mostly supports fundamental research
+and education in the non-medical science and engineering. Its medical
+counterpart is the National Institutes of Health \todo{You have said
+  so before.}.\footnote{\url{https://en.wikipedia.org/wik
+    i/National_Science_Foundation}} With STEM being the top priority
+in USA, \todo{How do you know that?} most of the projects founded by
+NSF are related to engineering, computer science, mathematics and
+information systems, in general. The subjects STEM \& Education,
+Software engineering, Information systems and Mathematics, arise as
+topics in all these years, from 1994-2017.
 
@@
 
-From 1994-2006 and the last three years, International Research and conferences
-came up as a trending topic. Re- searchers have a great interest to collaborate
-with other colleagues from all over the world and share their knowledge. A big
-part of the projects funded by the EU that is related to international research,
-is also related to Physics, in general, and High energy physics in EU (see
-Appendix: Wordclouds of topics of the EU).
-
-NSF shows a great interest in international activities across all NSF supported
-disciplines. The goal of these projects is to support high quality research and
-education, which could not occur without international collaboration. NSF seeks
-to catalyze a higher level of international engagement in the U.S. science and
-engineering community by promoting International conferences and university
-projects and partnerships. An interesting fact regarding international
-partnerships is that the European Commission and the Government of the United
-States of America concluded on 17 October 2016 an Implementing Arrangement that
-simplifies the cooperation between Horizon 2020 projects and US entities.
-European and American researchers will be able to work together more closely on
-projects funded under Horizon 2020, the European Union's research and innovation
+From 1994-2006 and the last three years, International Research and
+conferences came up as a trending topic. Re- searchers \todo{Re-
+  searchers} have a great interest to collaborate with other
+colleagues from all over the world and share their knowledge. A big
+part of the projects funded by the EU that is related to international
+research, is also related to Physics, in general, and High energy
+physics in EU (see Appendix: Wordclouds of topics of the EU).
+\todo{Are you talking about the EU, or the US here?}
+
+NSF shows a great interest in international activities across all NSF
+supported disciplines. The goal of these projects is to support high
+quality research and education, which could not occur without
+international collaboration. NSF seeks to catalyze a higher level of
+international engagement in the US science and engineering community
+by promoting international conferences and university projects and
+partnerships \todo{You have said the same in the previous paragraph.}.
+An interesting fact regarding international partnerships is that the
+European Commission and the Government of the United States of America
+concluded on 17 October 2016 an Implementing Arrangement that
+simplifies the cooperation between Horizon 2020 projects and US
+entities. European and American researchers will be able to work
+together more closely on projects funded under Horizon 2020, the
+European Union's research and innovation
 programme.\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}
@@
 
-One of our goals is to identify trends in scientific research in EU and USA, in
-order to give some insights to researchers and scientists regarding potential
-trends. For this analysis, we run the model for the whole dataset, instead of
-running the model per FP), for the EU and the USA, respectively. The outcome was
-10 topics for each region from 1994 to 2017 for the EU and from 1994 to 2016 for
-the USA.\footnote{in this implementation we removed the projects of the year
-2017 from the USA dataset, because the amount of projects-documents was too
-small compared to the other years and it was affecting the result of the trend
-for each topic.}
+One of our goals is to identify trends in scientific research in EU
+and USA, in order to give some insights to researchers and scientists
+regarding potential trends. For this analysis, we run the model for
+the whole dataset, instead of running the model per FP), for the EU
+and the USA, respectively. The outcome was 10 topics for each region
+from 1994 to 2017 for the EU and from 1994 to 2016 for the
+USA.\footnote{in this implementation we removed the projects of the
+  year 2017 from the USA dataset, because the amount of
+  projects-documents was too small compared to the other years and it
+  was affecting the result of the trend for each topic.}
 
@@
 
-In figure x we show the 10 topics that consists of the 20 top words with the
-highest posterior probability of belonging to the topic. The size of each word
-is in proportion to each probability; the bigger the word, the higher the
-probability. Each wordcloud describes a topic, which we can find intuitively.
-Below are listed the topics that we found corresponding to the words that
+In figure x \todo{What?} we show the 10 topics that consists \todo{You
+  mean that you show the top 20 words; the topics consist of more.} of
+the 20 top words with the highest posterior probability of belonging
+to the topic. The size of each word is in proportion to each
+probability; the bigger the word, the higher the probability. Each
+wordcloud describes a topic, which we can find intuitively. Below are
+listed the topics that we found corresponding to the words that
 describe them:
@@
 \end{center}
+\todo{Why
+  don't you put the name of each topic in each topic's caption?}
+
 In order to find the topic distribution over time, we need the topic
-distribution of each project-document. As we mentioned before, LDA assumes that
-each document exhibits multiple topics. After running the model to our dataset,
-we get the document-topic distribution and we keep the topic with the highest
-probability (the one that most likely belongs to this document). Then, we
-calculate the proportion of each topic per FP, using the following equation:
+distribution of each project-document. As we mentioned before, LDA
+assumes that each document exhibits multiple topics. After running the
+model to our dataset, we get the document-topic distribution and we
+keep the topic with the highest probability (the one that most likely
+belongs to this document). Then, we calculate the proportion of each
+topic per FP, using the following equation:
 \begin{equation}
@@
 \end{equation}
-where $k$ is the number of the topic id, $fp$ is the framework programme,
-$fp \in [FP4, FP5, FP6, FP7, H2020]$. The topic proportion of each topic in 
-the FP equals to the sum of the number of the documents assigned to this 
-topic during the FP, normalized by the number of the documents-projects 
-occurring in this FP. In figure X we plot the results of the topic proportion 
-over time.
-
-Based on this plot, topic 10, which refers to International Research, has an
-interesting evolution; During the years 1994-1998 is appears as less popular
-topic, compared to other topics. However, this state changes drastically in
-1998-2002 ($+14\%$) and in 2002-2006 it is at its peak ($+18\% since 1994$).
-This period many activities and projects where initialized in order to support
-and promote international education and conferences to attract researchers from
-all over the world. Strangely, this trend has a significant decrease the last 10
-years, compared to other topics ($-12\%$). We already know that in Horizon 2020
-there is an agreement between EU and USA for supporting the cooperation of the
-two regions.Our hypothesis for the evolution of the International Research is
-that the EU successfully managed to create the foundation for supporting
-international people and there is no need to invest more on projects that
-attempt to promote cooperation between international researchers, because it is
-already considered as a common practice nowadays.
-
-Materials and Manufacturing was a hot topic in 1994-1998, but it also appears a
-big decrease during the years 1998-2006 and it has a stable trend since then.
-Materials Science/Chemistry \& Physics' popularity (topic 4) line has an
-increase during 2002-2013 and the last 3 years a small decrease of $2-3\%$.
-Topics 2 and 3 (Social policy, Disease detection \& treatment) follow the same
-linear trend as Materials science \& Physics. Energy production (topic 11) was
-less popular in 1994-2002 and is becoming slightly popular the last 15 years.
+where $k$ is the number of the topic id, $fp$ is the framework
+programme, $fp \in [FP4, FP5, FP6, FP7, H2020]$. The topic proportion
+of each topic in the FP equals the sum of the number of the documents
+assigned to this topic during the FP, normalized by the number of the
+documents-projects occurring in this FP. In figure X \todo{what?} we
+plot the results of topic proportions over time.
+
+Based on this plot, topic 10, which refers to International Research,
+has an interesting evolution; uring the years 1994-1998 is appears as
+less popular topic, compared to other topics. However, this changes
+drastically in 1998-2002 ($+14\%$) and in 2002-2006 it is at its peak
+($+18\% since 1994$ \todo{that should not be in math}). This period
+many activities and projects where initialized in order to support and
+promote international education and conferences to attract researchers
+from all over the world. Strangely, this trend has a significant
+decrease the last 10 years, compared to other topics ($-12\%$). We
+already know that in Horizon 2020 there is an agreement between EU and
+USA for supporting the cooperation of the two regions.Our hypothesis
+for the evolution of the International Research is that the EU
+successfully managed to create the foundation for supporting
+international people and there is no need to invest more on projects
+that attempt to promote cooperation between international researchers,
+because it is already considered as a common practice nowadays.
+
+Materials and Manufacturing was a hot topic in 1994-1998, but it also
+appears a big decrease during the years 1998-2006 and it has a stable
+trend since then. Materials Science/Chemistry \& Physics' popularity
+(topic 4) line has an increase during 2002-2013 and the last 3 years a
+small decrease of $2-3\%$. Topics 2 and 3 (Social policy, Disease
+detection \& treatment) follow the same linear trend as Materials
+science \& Physics. Energy production (topic 11) was less popular in
+1994-2002 and is becoming slightly \todo{more?} popular the last 15
+years.
 
@@
 Biology and the study of molecular mechanisms have a small decrease of
-popularity on average. This may happen because the projects related to medical
-fields are supported by another institute, National Institutes of Health. Also,
-research in Climate change and Environmental science is another subject that
-paradoxically appears as a topic that is gradually losing its popularity over
-the last years.
+popularity on average. This may happen because the projects related to
+medical fields are supported by another institute, National Institutes
+of Health \todo{Are you talking about the US or the EU?}. Also,
+research in Climate change and Environmental science is another
+subject that paradoxically appears as a topic that is gradually losing
+its popularity over the last years.
 
@@
 
-Just like the EU dataset, we found the 10 topics of the USA dataset from 1994 to
-2016. Since, we're looking for the topic distribution over time, in this
-implementation we took the projects per year (instead of using the separation of
-the dataset per FP), to visualize the evolution of each topic per year. We ran
-the LDA model with 12000 iterations and the dame value of the rest of the
-parameters, as described in section 4.3.
-
-Each one of the wordclouds in figure X represents a topic. The topics that are
-described in the wordclouds are listed below:
+Just like the EU dataset, we found the 10 topics of the USA dataset
+from 1994 to 2016. Since, we're looking for the topic distribution
+over time, in this implementation we took the projects per year
+(instead of using the separation of the dataset per FP), to visualize
+the evolution of each topic per year. We ran the LDA model with 12000
+iterations and the dame \todo{same} value of the rest of the
+parameters, as described in section 4.3. \todo{You should probably
+  explain the same for the Trends in the EU.}
+
+Each one of the wordclouds in figure X \todo{what?}represents a topic.
+The topics that are described in the wordclouds are listed below:
 
@@
 \end{center}
-In figure 6 we plot the topic distribution over time. We can easily observe that
-the topic 6, which refers to STEM education, is becoming a trend in the United
-States over the years, while most of the other topics' evolution doesn't show up
-such a high increase. Topics 5 and 8, which refer to Chemistry \& Materials
-science and Molecular biology, respectively, show a small decrease over the
-years. Topics 9 and 0 (Mechanical Engineering, Material Science and High energy
-physics) show a small increase over the last 5 years. Mathematics' evolution
-over time (Topic 1) looks stable on average and shows up as a popular subject
-over the last 22 years, while Social Sciences and International Research (Topic
-3 and 4) show a small decrease over the last 3 years.  Molecular biology and
-Genetics (Topic 2) has an increasing popularity from 1994 to 2001 and later is
-starting to stabilize. Climatology, Atmospheric and Ocean sciences look stable
-the first years, while from 2006 up to date it is gradually becoming less
+In figure 6 we plot the topic distribution over time. We can easily
+observe that the topic 6, which refers to STEM education, is becoming
+a trend in the United States over the years, while most of the other
+topics' evolution doesn't show up such a high increase. Topics 5 and
+8, which refer to Chemistry \& Materials science and Molecular
+biology, respectively, show a small decrease over the years. Topics 9
+and 0 (Mechanical Engineering, Material Science and High energy
+physics) show a small increase over the last 5 years. Mathematics'
+evolution over time (Topic 1) looks stable on average and shows up as
+a popular subject over the last 22 years, while Social Sciences and
+International Research (Topic 3 and 4) show a small decrease over the
+last 3 years. Molecular biology and Genetics (Topic 2) has an
+increasing popularity from 1994 to 2001 and later is starting to
+stabilize. Climatology, Atmospheric and Ocean sciences look stable the
+first years, while from 2006 up to date it is gradually becoming less
 popular over the years.
 
-In general, the STEM (science, technology, engineering and math) related
-research and education is becoming more and more popular, which is not
-surprising, since the National Science Foundation itself estimates that 80/% of
-the jobs available during the next decade will require math and science skills.
-Even the concept of STEM was first introduced by Judith A. Ramaley, the former
-director of the National Science Foundation's education and human resources
-division.
+In general, the STEM (science, technology, engineering and math)
+related research and education is becoming more and more popular,
+which is not surprising, since the National Science Foundation itself
+estimates that 80/%
+\todo{you mean percent} of the jobs available during the next decade
+will require math and science skills \todo{Cite that.}. Even the
+concept of STEM was first introduced by Judith A. Ramaley, the former
+director of the National Science Foundation's education and human
+resources division \cite{Cite that.}.
 
@@
 
-In our case, we will use JSD cause is a symmetric formula, so that 
-$sim(Q,P) = sim(P,Q)$. we want to calculate the similarity of the topics of the 
-EU and the USA dataset per framework programme, one by one. Since the topics 
-come from different datasets, it means that their topic probability distributions 
-have different variables-words and different number of variables. To deal with this
-issue, we run the model for the two datasets separately and keep the topics as
-word probability distributions. Then for each pair of the two set of topics, we
-add to each of the topic-word distributions, the words that are missing and
-exist in the other distribution, with probability equals to zero. Then we apply
-the JSD to each pair of topics (see compare FPs.py in the Appendix, for the
-implementation).
-
-The figures 7-11 visualize the heatmaps of the similarity of the two regions
-during the FP4-H2020. Rows represent topics from the EU dataset and 
-columns topics from the USA dataset. The values of the JSD computation which are 
-close to zero (lighter color of the box) suggest more similarity within topics.
-According to the heatmaps, the topics that have high similarity between the 
-EU and the USA are:
+In our case, we will use JSD cause \todo{because} is a symmetric
+formula, so that $sim(Q,P) = sim(P,Q)$. we want to calculate the
+similarity of the topics of the EU and the USA dataset per framework
+programme, one by one. Since the topics come from different datasets,
+it means that their topic probability distributions have different
+variables-words and different number of variables. To deal with this
+issue, we run the model for the two datasets separately and keep the
+topics as word probability distributions. Then for each pair of the
+two set of topics we add to each of the topic-word distributions, the
+words that are missing and exist in the other distribution, with
+probability equals to zero. Then we apply the JSD to each pair of
+topics (see compare FPs.py in the Appendix, for the implementation).
+
+The figures 7-11 \todo{Use cross-references} visualize the heatmaps of
+the similarity of the two regions during the FP4-H2020. Rows represent
+topics from the EU dataset and columns topics from the USA dataset.
+The values of the JSD computation which are close to zero (lighter
+color of the box) suggest more similarity within topics. According to
+the heatmaps, the topics that have high similarity between the EU and
+the USA are: \todo{To be able to make sense of it, you must list
+  somewhere what are topics eu0--eu9 and usa0--usa9. Right not it is
+  impossible to understand whether, for example, there were Software
+  Engineering topics in both the EU and the US, or only in one of the
+  two, and that was similar to Materials in the other regions, or
+  perhaps you mean something else entirely.}
 \begin{itemize}
@@
 
-We briefly describe the preprocessing of the abstracts-documents before applying
-the model. LDA, as an unsupervised learning algorithm, does not require any
-prior annotation of labeling the documents and the topics are resulted from the
-statistical structure of the words in the corpus. Using the posterior document-
-topic and topic-word distribution, we investigate the context of each topic per
-FP and the evolution of the topics in each of the two datasets over time.
-
-We found that most topics cover various topics, while some show well-defined
-scopes. Our work provides valuable knowledge about the research over the last
-two decades in the two regions and could benefit researchers to to identify the
-subjects that mostly get funded in the EU and USA. This research gives an
-interesting aspect about what kind of topics were actually funded over the last
-22 years.
+We briefly describe \todo{described} the preprocessing of the
+abstracts-documents before applying the model. LDA, as an unsupervised
+learning algorithm, does not require any prior annotation of labeling
+the documents and the topics are resulted from the statistical
+structure of the words in the corpus. Using the posterior document-
+topic and topic-word distribution, we investigate the context of each
+topic per FP and the evolution of the topics in each of the two
+datasets over time.
+
+We found that most topics cover various topics \todo{That reads
+  funny}, while some show well-defined scopes. Our work provides
+valuable knowledge about the research over the last two decades in the
+two regions and could benefit researchers to to identify the subjects
+that mostly get funded in the EU and USA. This research gives an
+interesting aspect about what kind of topics were actually funded over
+the last 22 years. \todo{In general, you should not praise your own
+  work. The reader may praise it.}
 
@@
 
-Last but not least, it would be interesting to explore the correlation of the
-topics with the countries/states that are involved in the projects, and address
-question like "which countries in EU are mostly collaborate? on which topics"
-and "which states of the US are getting more funding compared to others".
+Last but not least, it would be interesting to explore the correlation
+of the topics with the countries/states that are involved in the
+projects, and address question like "which countries in EU are mostly
+collaborate? on which topics" and "which states of the US are getting
+more funding compared to others".
 

### 2017-06-26 thesis_report/draft_thesis.tex
Fixed: mistakes in the report (Introduction-Methodology)

@@
 
-Nowadays, there are many \todo{ That sounds like a joke. Research
-  funding is extremely competitive. } funding opportunities for
-researchers. For instance, European Union countries are encouraged to
+Nowadays, there are some funding opportunities for researchers, but are 
+really competitive. The European Union countries are encouraged to
 invest 3\% of their GDP in research and development by 2020. EU's
@@
 engineering and aims to advance the national health and prosperity. It
-finds \todo{funds} approximately 24\% \todo{Where did you find this
-  number? Add reference.} of the federally supported research
-conducted by the USA's colleges and universities.
+funds approximately 24\% of the federally supported research
+conducted by the USA's colleges and universities.\footnote{\url{https://www.nsf.gov/about/}}
 
 With our work, we aim to investigate the evolution of scientific
-research in the EU and the US. In other words, we attempt to identify
-which subjects are more likely to get a funding, based on the previous
-focus the two regions in research fields \todo{Does not read right}.
-In order to answer these questions, we tried to gain some insights
-from the projects that got funded the last two decades under the EU
-Framework Programmes and the NSF in USA.
+research in the EU and the US. In order to gain some insights  regarding
+the research development, we used as a dataset the projects that got funded 
+the last two decades under the EU Framework Programmes and the NSF in USA.
 
@@
 scientific investigation. The topic(s) of a project is always
-described in the project's abstract/description. Obtaining
-\todo{Using} these abstracts, one can possibly investigate the topics
-of the projects and find the subjects that are being addressed and
-gain some information regarding the popularity of the topics among
-others.
+described in the project's abstract/description. Using these abstracts, 
+one can possibly investigate the topics of the projects and find the 
+subjects that are being addressed and gain some information regarding 
+the popularity of the topics among others.
 
 In this work, we discover topics and their evolution from 1994 to
-2017, using the projects' abstracts that got funded \todo{in} this
+2017, using the projects' abstracts that got funded in this
 period. Using a topic model, we extract a set of topics and
@@
 
-In section 2 \todo{Throughout: never use hard-coded references. Always
-  use LaTeX cross-references.}, we briefly talk about the papers that
-mostly influenced our study. Section 3 introduces some basic concepts
+In section \ref{theoretic} introduces some basic concepts
 in topic modeling and we describe the model that we used for topic
 extraction, Latent Dirichlet Allocation, which is a statistical
-generative model for documents. In section 4 we provide information
+generative model for documents. In section \ref{relatedwork}, 
+we briefly talk about the papers that mostly influenced our study. 
+In section \ref{methodology} we provide information
 about the dataset structure and the methodology that we followed in
-our analysis. In section 5 we interpret the results of our analysis,
-\todo{and we}discuss the evolution of the topics over time and the
+our analysis. In section \ref{analysis} we interpret the results of 
+our analysis, and we discuss the evolution of the topics over time and the
 differences between the two regions' topics based on their similarity.
-Finally, section 6 summarizes our work and section 7 suggests some
-future work.
-
-\section{Related work}\todo{Having this section here, before any
-  introduction to LDA, makes counter-intuitive reading. Better move it
-after.}
-
-This chapter \todo{section} surveys previous work in topic modeling on
-scientific data. Topic modeling algorithms provides \todo{provide} a
-suite of algorithms to discover hidden thematic structure
-\todo{structures} in large collections of texts and can be adapted to
-many kinds of data. These algorithms can be used to summarize,
-visualize and explore a collection of documents. The papers listed
-below are applying a Latent Dirichlet Allocation model in an
-interesting approach on their corpus.
-
-D.Blei's \todo{Throughout: separate initials with space from surname}
-research focuses on probabilistic topic models, Bayesian methods and
-approximate posterior inference. In his work "Introduction to
-Probabilistic Topic Models",\cite{Blei11introductionto}
-\todo{Throughout: Fix quotation marks; also citations are placed
-  before punctuation} he describes the basic ideas behind LDA and
-applies the model to articles from the journal "Science"
-\todo{\emph{Science}}. The model assumes that the topics are generated
-first, before the documents and that the documents exhibit multiple
-topics, but each one of them exhibit those topics in different
-proportion. In our implementation we also use the LDA model and we
-follow a similar approach, since we don't use any previous information
-about the subjects that run through our dataset and the documents are
-not labeled with keywords or topics. The topic distributions arise by
-computing the hidden structure that resembles the thematic structure
-of the collection.
-
-The paper that mostly influenced our work is "Finding Scientific Topics", by
-T.Griffiths and M.Steyvers.\cite{griffiths_steyvers04} They investigated
-abstract data from articles published in the Proceedings of the National Academy
-of Sciences (PNAS) from 1991 to 2001 and compared research topics obtained from
-topic modeling with existing categories. In our implementation, we also use 
-the abstracts of the projects as documents for the model.
-
-Griffiths and Steyvers describe LDA and present a Markov Chain Monte Carlo
-algorithm for inference in the model, illustrating the operation of the
-suggested algorithm on a small dataset, and then on a larger corpus of PNAS
-abstracts. Finally, they define the dynamics of the topics as a means of gaining
-insight into the dynamics of science. As "hot" topics are identified the topics
-that appear more frequently over the years (positive linear trend), and as
-"cold" the ones that appear less frequently (negative linear trends over time).
-We also analyze the topics over time, in order to highlight potential trends in
-scientific research in EU and USA.
-
-Inspired by Griffiths and Steyvers, L.Sun and Y.Yin wrote a paper,
-"Discovering themes and trends in transportation research using topic
-modeling", \cite{Sun201749} about topic modeling in transportation
-research. Considering approximately 17000 abstracts of articles
-published on 22 leading journals in transportation research as
-documents, they infer 50 topics by using LDA. Compared to "Finding
-scientific topics", Sun and Yin use more than one journal (22 popular
-journals) and they investigate the journal-topic distribution and
-journal similarity. In our analysis, we identify the EU and the USA as
-2 regions (like 2 different journals), with different proportions of
-documents-projects, and we visualize the topic similarity of the two
-regions per framework programme.
-
-To best of our knowledge, there is no work done in the field of topic modeling
-on scientific projects between EU and USA. There is limited information from
-European Commission about the evolution and the results of the projects provided
-by the official website.
+Finally, section \ref{conclusion} summarizes our work and section 
+\ref{future} suggests some future work.
 
 \section{Theoretic background}
-
+\label{theoretic}
 In this chapter we will present some basic theoretic background about
@@
 \item[] A \textit{word} is defined as an item from a vocabulary
-  indexed from ${1, ..., V}$, where V \todo{$V$} is the size of the
+  indexed from ${1, ..., V}$, where $V$ is the size of the
   vocabulary. All words are represented as unit-basis vectors with one
@@
 manufacturing process takes place.
-\item[] \textit{Synonymy} is the capacity for several words to have similar meanings such as
-the words “buy” and “purchase”.
+\item[] \textit{Synonymy} is the capacity for several words to have similar meanings such as the words “buy” and “purchase”.
 \end{itemize}
@@
 
-When introducing the Latent Dirichlet Allocation in section 2.2.3
-\todo{Cross reference}
-\todo{As you can see this is a disaster: always cross-reference with
-  LaTeX}, we will be using the terms prior and posterior probabilities
+When introducing the Latent Dirichlet Allocation in section \ref{LDAexplained}, 
+we will be using the terms prior and posterior probabilities
 and likelihood function:
@@
 \begin{itemize}
-\item The prior probability distribution of and \todo{an} uncertain
+\item The prior probability distribution of an uncertain
   quantity is the probability distribution that express the value of
@@
 In the context of probabilities, the Jensen Inequality is stated as
-follows: If X \todo{$X$} is a random variable and f \todo{$f$} a
-convex function then \todo{What is $\mathbb{E}$?}:
+follows: If $X$ is a random variable and $f$ a
+convex function then:
 
@@
 
-And, if f \todo{f} is a concave function the inequality turns:
+And, if $f$ is a concave function the inequality turns:
 
@@
 \end{equation}
+
+where $\mathbb{E}$ is the expectation of the random variable $X$.
+\footnote{Suppose random variable $X$ can take value $x_{1}$ with 
+probability $p_{1}$, value $x_{2}$ with probability $p_{2}$, 
+and so on, up to value $x_{k}$ with probability $p_{k}$. 
+Then the expectation of this random variable $X$ is defined as
+$\mathbb{E}[X] = x_{1}p_{1} + x_{2}p_{2} + ... + x_{k}p_{k}$.}
 
@@
 \begin{equation}
-D_{KL}(P \mid \mid Q) = \int_{-\infty}^{+\infty} p(x) log\frac{p(x)}{q(x)}dx
-\end{equation} \todo{ log in mathematics is $\log$}
+D_{KL}(P \mid \mid Q) = \int_{-\infty}^{+\infty} p(x) \log\frac{p(x)}{q(x)}dx
+\end{equation}
 
 This can also be expressed using the definition of expectation (and
-expressing the log of a division as difference of log) as:
+expressing the $\log$ of a division as difference of $\log$) as:
 
 \begin{equation}
-  D_{KL}(P \mid \mid Q) = \mathbb{E}_{p}[log p(x)] - \mathbb{E}_{p}[log q(x)]
-\end{equation} \todo{Smae with log; also, it is a function.}
+D_{KL}(P \mid \mid Q) = \mathbb{E}_{p}[\log{p(x)}] - \mathbb{E}_{p}[\log{q(x)}]
+\end{equation}
 
@@
 
-Once we have a representation for individual documents, the natural
-next step is to select a model for a set of documents. Given a
-training set of documents, we will choose values for the parameters of
-a probabilistic model that make the training documents have high
-probability. Then, given a test document, we can evaluate its
-probability according to the model. The higher this probability is,
-the more similar the test document is to the training set. \todo{Is
-  this really what you use the multinomial distribution for? You use
-  the multinomial distribution because LDA assumes that this is the
-  distribution of topics in documents and words in topics.}
-
-The probability distribution that we use is the multinomial. In
-probability theory, the multinomial distribution is a generalization
+The probability distribution that the model uses is the multinomial, 
+because it assumes that this is the distribution of topics in 
+documents and words in topics (read Latent Dirichlet Allocation in section \ref{LDAexplained}). 
+In probability theory, the multinomial distribution is a generalization
 of the binomial distribution. For example, it models the probability
-of counts for rolling a k-sided dice n times. For n independent trials
-each of which leads to a success for exactly one of k categories, with
+of counts for rolling a $k$-sided dice $n$ times. For $n$ independent trials
+each of which leads to a success for exactly one of $k$ categories, with
 each category having a given fixed success probability, the
@@
 categories\footnote{\url{https://en.wikipedia.org/wiki/Multinomial_distribution}}.
-\todo{Variables like $k$, $n$, etc. should be in math mode.}
 
@@
 
-The Dirichlet distribution is a prior for the multinomial
+The Dirichlet distribution is the conjugate prior of the multinomial
 distribution. This means that if the prior distribution of the
-multinomial parameters is Dirichlet then the posterior distribution is
-also a Dirichlet distribution (with parameters different from those of
-the prior). \todo{ If the Dirichlet is the prior for the multinomial
-  then the posterior is the multinomial; in fact the Dirichlet is the
-  conjugate prior of the multinomial. It is the posterior distribution
-  of the \emph{parameters} that is still Dirichlet. }
-
-The Dirichlet process is a way to model randomness of a probability
-mass function (PMF) with unlimited options (e.g. an unlimited amount
-of dice in a bag). The process is similar Polya's
-Urn\footnote{\url{http://www.statisticshowto.com/dirichlet-distribution/}},
-only instead of having a set number of ball colors you have an
-unlimited amount: \todo{Why do we need to know that? }
-
-\begin{itemize}
-\item Start out with an empty urn.
-\item Randomly pick a colored ball and place it in the urn.
-\item Then choose one option:
-\begin{enumerate}
-\item Randomly pick a colored ball and place it in the urn.
-\item Randomly remove a colored ball from the urn, then put it back with another 
-ball of the same color.
-\end{enumerate}
-\end{itemize}
-
-As the number of balls in the urn increase, the probability of picking a new
-color decreases. The proportion of balls in the urn after an infinite amount of
-draws is a Dirichlet process.
+multinomial parameters is Dirichlet then the posterior distribution of the
+parameters is still a Dirichlet distribution.
 
@@
 Latent Semantic Indexing, or LSI, was presented by Deerwester et al.
-in 1990. \todo{Add reference.} The model manages to deal with the
+in 1990.\cite{Deerwester90indexingby} The model manages to deal with the
 problem that multiple terms can refer to the same meaning, i.e.
@@
 After LSI was introduced, Hofmann presented the Probabilistic Latent
-Semantic Indexing, or PLSI model \todo{Add reference}. PLSI is a topic
-model where each word in a document is generated from a single topic
-which results in that each document in a corpus can be represented
-with a topic distribution. Later, in 2003 Blei et al. presented the
-Latent Dirichlet Allocation, or LDA \todo{Add reference}. As opposed
-to PLSI, LDA is a statistically generative model for documents where
-each word in a document can be generated by all topics.
+Semantic Indexing, or PLSI model\cite{Hofmann:1999:PLS:312624.312649}. 
+PLSI is a topic model where each word in a document is generated 
+from a single topic which results in that each document in a corpus 
+can be represented with a topic distribution. Later, in 2003 Blei et al. 
+presented the Latent Dirichlet Allocation, or LDA\cite{blei2003latent}. 
+As opposed to PLSI, LDA is a statistically generative model for documents 
+where each word in a document can be generated by all topics.
 
@@
 the number of times a word occurs in a document but this term count
-can also be weighted with for instance TF-IDF \todo{Explain}. Letting
+can also be weighted with for instance TF-IDF.\footnote{TF-IDF stands 
+for term frequency - inverse document frequency, and the tf-idf weight is 
+a weight often used in information retrieval and text mining. This weight 
+is a statistical measure used to evaluate how important a word is to 
+a document in a collection or corpus. The importance increases
+proportionally to the number of times a word appears in the document (TF) but
+is offset by the frequency of the word in the corpus (IDF).} Letting
 each word represent a dimension in a very high dimensional space, a
@@
 \subsubsection{Latent Dirichlet Allocation (LDA)}
-
+\label{LDAexplained}
 LDA is a topic model that was first presented as a graphical model for topic
@@
 
-This is similar to PLSI, except
-that in LDA the topic distribution is assumed to have a Dirichlet prior. 
-In practice, this results in more reasonable mixtures of topics in a
-document. The reduced document description result in PLSI is a vector where
-each element describes the mixing proportion for a topic. A limitation with
-PLSI is that there is no generative model for these proportions, making it
-difficult to handle unseen documents. The Latent Dirichlet Allocation model
-tries to solve this limitation by setting a Dirichlet prior on the topic
-distribution.\cite{blei2003latent} \todo{In essence you repeat what
-  you said in the beginning of the paragraph.}
+A limitation with PLSI is that there is no generative model for these
+proportions, making it difficult to handle unseen documents. The reduced
+document description result in PLSI is a vector where each element describes the
+mixing proportion for a topic. The Latent Dirichlet Allocation model tries to
+solve this limitation by setting a Dirichlet prior on the topic
+distribution.\cite{blei2003latent} In practice, this results in more reasonable
+mixtures of topics in a document.
 
@@
 
-The basic idea in LDA is that we define a topic to be a Dirichlet
-distribution over a fixed vocabulary. \todo{No, a topic is a
-  multinomial distribution.} Technically, the model assumes that the
-topics are generated first, before the
+The basic idea in LDA is that we define a topic to be a multinomial
+distribution over a fixed vocabulary. Technically, the model assumes 
+that the topics are generated first, before the
 documents.\cite{Blei11introductionto} Now for each document in the
@@
 characteristic of LDA. A more detailed explanation of the model
-follows in section 2.2.3.1. \todo{Again, fix cross-references}
+follows in section \ref{LDAmodel}.
 
 \paragraph{Model}
-
+\label{LDAmodel}
 LDA is a probabilistic model of text documents, which assumes a
@@
 over the vocabulary and is assumed to have been drawn from a Dirichlet
-$\beta_k \sim Dirichlet(\eta)$. \todo{What is $beta_k$ and what is
-  $\eta$? If you explain them later (which you do) this sentence
-  should follow the explanations.}
+$\beta_k \sim Dirichlet(\eta)$, where $beta_k$ is the posterior 
+distribution of the topic $k$.
 
 In LDA, each document is represented by a mixture of the topics, with
-weight $\theta_w^2$ \todo{Where does the square come from?} for topic
-$z$ in document $w$. These weight \todo{weights} have a Dirichlet
+weight $\theta_w$ for topic
+$z$ in document $w$. These weights have a Dirichlet
 prior, parametrized by a hyper-parameter $\alpha$. Each topic is a
@@
    drawn from a uniform Dirichlet distribution with parameter $\alpha$.
- \item[] $z_{n}$ is a topic assignment for $word w_{n}$ \todo{word
-     $w_n$}, sampled from $p(z_{n} = i|\theta) = \theta_{i}$.
+ \item[] $z_{n}$ is a topic assignment for word $w_{n}$, 
+ sampled from $p(z_{n} = i|\theta) = \theta_{i}$.
   \item[] \textbf{w}$ = (w_{1}, ... , w_{N})$ is a document with $N$ words.
@@
 matrix $\beta$. Then, we can analyze a corpus of documents with LDA by 
-examining $\beta$, which is the posterior distribution of topics, $\theta$ 
+examining $\beta$, $\theta$ 
 and $z$ conditioned on the documents. This reveals latent structure in
@@
 ~\cite{onlineLDAvb}. In our implementation, we're using the online variational
-LDA model, which is described in section 2.2.3.4. \todo{Cross reference.}
-
-The key difference in LDA compared to PLSI is that the process outlined above
-actually is generative for documents. This means that, given a new document,
-one can use the parameters learned previously to estimate the topic
-distribution $\theta$ for this new document. \todo{You have already
-  said that many times.}
-
-A limitation with the standard LDA model is the fix \todo{fixed}
+LDA model, which is described in section \ref{oLDAvb}.
+
+A limitation with the standard LDA model is the fixed 
 vocabulary. This means that new words cannot enter the model and that
@@
 a variational Bayes approximation of the posterior distribution;
-\cite{blei2003latent} alternative inference techniques use Gibbs
-sampling and expectation propagation \todo{Cite these techniques.
-  AFAIK, if you do not use Variational Bayes, you use MCMC with Gibbs
-  sampling.}. The goal of variational
+\cite{blei2003latent} alternative inference techniques use 
+MCMC with Gibbs sampling\cite{Griffiths02gibbssampling} and expectation 
+propagation.\cite{Minka:2002:EGA:2073876.2073918} The goal of variational
 inference is to approximate an intractable probability distribution
@@
         update $\phi$
+
         update $\gamma$ 
@@
 \end{algorithm}
-\todo{Update $\phi$ and $\gamma$ do not show as separate lines.}
 
@@
 iteration. It can be slow to apply to very large datasets.
-\todo{Provide citation for the description you have given; I assume
-  it's the same blog post as for the following paragraph.}
+\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}
 
 \paragraph{Online variational LDA}
-
+\label{oLDAvb}
 An online variational inference algorithm is proposed by Hoffman et all.\cite{onlineLDAvb} for fitting $\lambda$, the parameters to the variational
@@
 Then $\lambda$ is updated using a weighted sum of $\lambda^{*}$ and
-$\lambda$: \todo{As the algorithm is thrown on the next page, it looks
-  as if something is missing here.}
-
+$\lambda$:
 \begin{algorithm}
@@
 
+\section{Related work}
+\label{relatedwork}
+This section surveys previous work in topic modeling on
+scientific data. Topic modeling algorithms provide a
+suite of algorithms to discover hidden thematic structures 
+in large collections of texts and can be adapted to
+many kinds of data. These algorithms can be used to summarize,
+visualize and explore a collection of documents. The papers listed
+below are applying a Latent Dirichlet Allocation model in an
+interesting approach on their corpus.
+
+D. Blei's research focuses on probabilistic topic models, Bayesian methods and
+approximate posterior inference. In his work \emph{Introduction to
+Probabilistic Topic Models}\cite{Blei11introductionto} 
+he describes the basic ideas behind LDA and
+applies the model to articles from the journal \emph{Science}. 
+The model assumes that the topics are generated
+first, before the documents and that the documents exhibit multiple
+topics, but each one of them exhibit those topics in different
+proportion. In our implementation we also use the LDA model and we
+follow a similar approach, since we don't use any previous information
+about the subjects that run through our dataset and the documents are
+not labeled with keywords or topics. The topic distributions arise by
+computing the hidden structure that resembles the thematic structure
+of the collection.
+
+The paper that mostly influenced our work is \emph{Finding Scientific Topics}, by
+T. Griffiths and M. Steyvers.\cite{griffiths_steyvers04} They investigated
+abstract data from articles published in the Proceedings of the National Academy
+of Sciences (PNAS) from 1991 to 2001 and compared research topics obtained from
+topic modeling with existing categories. In our implementation, we also use 
+the abstracts of the projects as documents for the model.
+
+Griffiths and Steyvers describe LDA and present a Markov Chain Monte Carlo
+algorithm for inference in the model, illustrating the operation of the
+suggested algorithm on a small dataset, and then on a larger corpus of PNAS
+abstracts. Finally, they define the dynamics of the topics as a means of gaining
+insight into the dynamics of science. As \emph{hot} topics are identified the topics
+that appear more frequently over the years (positive linear trend), and as
+\emph{cold} the ones that appear less frequently (negative linear trends over time).
+We also analyze the topics over time, in order to highlight potential trends in
+scientific research in EU and USA.
+
+Inspired by Griffiths and Steyvers, L. Sun and Y. Yin wrote a paper,
+\emph{Discovering themes and trends in transportation research using topic
+modeling}, \cite{Sun201749} about topic modeling in transportation
+research. Considering approximately 17000 abstracts of articles
+published on 22 leading journals in transportation research as
+documents, they infer 50 topics by using LDA. Compared to \emph{Finding
+scientific topics}, Sun and Yin use more than one journal (22 popular
+journals) and they investigate the journal-topic distribution and
+journal similarity. In our analysis, we identify the EU and the USA as
+2 regions (like 2 different journals), with different proportions of
+documents-projects, and we visualize the topic similarity of the two
+regions per framework programme.
+
+To best of our knowledge, there is no work done in the field of topic modeling
+on scientific projects between EU and USA. There is limited information from
+European Commission about the evolution and the results of the projects provided
+by the official website.
+
 \section{Methodology}
-
+\label{methodology}
 In this section, we explain the procedure that we followed in order to
-apply the LDA model in our dataset. The dataset consists of two
-datasets \todo{That reads funny.}: the one that contains all the
-information about EU projects founded for research and innovation
-under the FP4-H2020 \todo{Throughout: use dashes correctly. There are
-  hyphens (-), n-dashes (--) and m-dashes (---).} and the dataset from
-USA about the awards/projects that got approved from 1994-2017. We
+apply the LDA model in our dataset. It consists of information about 
+EU projects funded for research and innovation under the FP4 - H2020 
+and the awards/projects that got funded by NSF from 1994 - 2017 in USA. We
 consider the projects' description/abstract as the documents in LDA.
@@
 the framework programme (FP4-H2020) for research and technological
-development. For each project it is provided information \todo{Does
-  not read right}, such as: reference, acronym, dates, funding,
-programs, participant countries, subjects and objectives.
-
-In the provided dataset, the information is splitted \todo{split} into
+development. Grant information is provided for each project, 
+including reference, acronym, dates, funding, programmes, 
+participant countries, subjects and objectives.
+
+In the provided dataset, the information is split into
 CSV files, based on the framework program that each project belongs.
@@
 \item FP4: fourth framework programme (1994-1998)
-\item FP5: fifth framework programme (1998–2002)
-\item FP6: sixth framework programme (2002–2006)
-\item FP7: seventh framework programme (2007–2013)
+\item FP5: fifth framework programme (1998-2002)
+\item FP6: sixth framework programme (2002-2006)
+\item FP7: seventh framework programme (2007-2013)
 \item H2020: Horizon 2020 framework programme (2014-2020)
@@
 
-To obtain the collection of the documents, we consider as 'documents'
-\todo{In the rest of the document you are using single quotation marks.}
+To obtain the collection of the documents, we consider as ``documents''
 in LDA the project objectives, which is an accurate description for
-the project. We also added the 'title' value of each project to the
+the project. We also added the ``title' value of each project to the
 objectives-documents, to increase the probability of finding accurate
-topics. For the majority of the projects the 'start date' and 'end
+topics. For the majority of the projects the ``start date' and ``end
 date' value was null, so we kept the splitting of the dataset per
@@
 library\footnote{http://radimrehurek.com/gensim/} and we added following very
-common words in the existing dataset: 'data', 'based', 'new', 'project',
-'university', 'student', 'students', 'research', 'study', 'program',
-'development', 'study', 'studies', 'provide', 'use'. We also removed the rare
-words that appear less than 5 times in the collection. Finally, we obtained a
-smaller corpus per framework (see the table above).
-
-In this section, we explain the procedure that we followed in n order
-to apply the LDA model in our dataset. The dataset consists of two
-datasets: the one that contains all the information about EU projects
-founded for research and innovation under the FP4-H2020 and the
-dataset from USA about the awards/projects that got approved from
-1994-2017. We consider the projects' description/abstract as the
-documents in LDA. \todo{Why is this paragraph here?}
+common words in the existing dataset: ``data'', ``based'', ``new'', ``project'',
+``university'', ``student'', ``students'', ``research'', ``study'', ``program'',
+``development'', ``study'', ``studies'', ``provide'', ``use''. We also removed 
+the rare words that appear less than 5 times in the collection. 
+Finally, we obtained a smaller corpus per framework (see the table above).
 
@@
 non-medical fields of science and engineering. Its medical counterpart
-is the National Institutes of Health \todo{Does your data include
-  material from NIH as well?}. The NSF funds approximately 24\% of all
+is the National Institutes of Health (ur data does not include 
+material from NIH). The NSF funds approximately 24\% of all
 federally supported basic research conducted by the United States'
@@
 Python library and we removed following very common words in the existing
-dataset: 'data', 'work', 'based', 'new', 'project', 'university', 'student',
-'students', 'research', 'study', 'program', 'development', 'study', 'studies',
-'provide', 'use', 'understanding', 'important', 'support', 'proposed'. We also
-removed the rare words that appear less than 5 times in the collection. Finally,
-we obtained a smaller corpus per framework (see Table below).
+dataset: ``data', ``work', ``based'', ``new'', ``project'', ``university'', ``student'',
+``students'', ``research'', ``study'', ``program'', ``development'', ``study'', ``studies'', ``provide'', ``use'', ``understanding'', ``important'', ``support'', ``proposed''.
+We also removed the rare words that appear less than 5
+times in the collection. Finally, we obtained a smaller corpus per framework 
+(see Table below).
 
@@
 extract the topics of a given corpus. Gensim uses a fast implementation of
-online LDA parameter estimation based on "Online Learning for Latent Dirichlet
-Allocation".\cite{onlineLDAvb} The algorithm runs in constant memory, which
+online LDA parameter estimation based on \emph{Online Learning for Latent Dirichlet
+Allocation}.\cite{onlineLDAvb} The algorithm runs in constant memory, which
 means that the size of the training corpus does not affect memory footprint, so
@@
 \section{Analysis and results}
-
+\label{analysis}
 In this section, we show our main results. We focus on finding
@@
 and later we investigate the evolution of the topics over time of each
-dataset separately.\todo{Although in the preceding material you have
-  listed the areas of interest in the EU, as listed in the EU Open
-  Data Portal, and the areas of interest in the US, through its
-  directorates, you do not discuss whether the topics you found have
-  any relationship to these thematic areas and divisions. So you do
-  not answer the question: ``did you find something we did not already
-  know by checking the descriptions on the web sites?''}
+dataset separately.
 
@@
 \section{Conclusion}
-
+\label{conclusion}
 In this thesis, we have presented a work about discovering topics and their
@@
 \section{Future work}
-
+\label{future}
 In future research, we intend to extend this work by exploring more complex

### 2017-06-26 thesis_report/draft_thesis.tex
Fixed: mistakes in the report (all except Analysis)

@@
 funds approximately 24\% of the federally supported research
-conducted by the USA's colleges and universities.\footnote{\url{https://www.nsf.gov/about/}}
+conducted by the USA's colleges and universities\footnote{\url{https://www.nsf.gov/about/}}.
 
@@
 In this chapter we will present some basic theoretic background about
-topic modeling. To deal with extensive text body \todo{probably
-  plural}, machine learning researchers have developed topic modeling:
+topic modeling. To deal with extensive texts body, machine learning 
+researchers have developed topic modeling:
 a suite of methods that analyze the words of the original text to
@@
 texts, topic modeling algorithms do not require any prior annotations
-or labeling of the documents.\cite{Blei11introductionto}
+or labeling of the documents\cite{Blei11introductionto}.
 
@@
 
-where $\mathbb{E}$ is the expectation of the random variable $X$.
+where $\mathbb{E}$ is the expectation of the random variable $X$
 \footnote{Suppose random variable $X$ can take value $x_{1}$ with 
@@
 Then the expectation of this random variable $X$ is defined as
-$\mathbb{E}[X] = x_{1}p_{1} + x_{2}p_{2} + ... + x_{k}p_{k}$.}
+$\mathbb{E}[X] = x_{1}p_{1} + x_{2}p_{2} + ... + x_{k}p_{k}$.}.
 
@@
 is over all possible data points. Here, a data point is a document containing
-$n$ words.\cite{Huang_maximumlikelihood}
+$n$ words\cite{Huang_maximumlikelihood}.
 
@@
 Latent Semantic Indexing, or LSI, was presented by Deerwester et al.
-in 1990.\cite{Deerwester90indexingby} The model manages to deal with the
+in 1990\cite{Deerwester90indexingby}. The model manages to deal with the
 problem that multiple terms can refer to the same meaning, i.e.
@@
 relationships between documents and the words that occur in
-them.\cite{Deerwester90indexingby} In LSI a term-document matrix is
+them\cite{Deerwester90indexingby}. In LSI a term-document matrix is
 created by analyzing the corpus, where the rows correspond to words
@@
 the number of times a word occurs in a document but this term count
-can also be weighted with for instance TF-IDF.\footnote{TF-IDF stands 
+can also be weighted with for instance TF-IDF\footnote{TF-IDF stands 
 for term frequency - inverse document frequency, and the tf-idf weight is 
@@
 proportionally to the number of times a word appears in the document (TF) but
-is offset by the frequency of the word in the corpus (IDF).} Letting
+is offset by the frequency of the word in the corpus (IDF).}. Letting
 each word represent a dimension in a very high dimensional space, a
 document can be seen as a vector with components corresponding to its
-weighted term counts. \cite{Salton:1988:TAA:54259.54260}
+weighted term counts\cite{Salton:1988:TAA:54259.54260}.
 
@@
 matrix. The difference is that instead of being based on linear algebra, PLSI
-is based on a mixture decomposition using a latent class model.
-~\cite{Hofmann:1999:PLS:312624.312649} PLSI associates an unobserved class 
+is based on a mixture decomposition using a latent class model
+~\cite{Hofmann:1999:PLS:312624.312649}. PLSI associates an unobserved class 
 variable $z$ with each document-word observation pair (\textbf{w},$
@@
 there is no clear way of assigning probability to a document that is not part
-of the training data.\cite{blei2003latent} Another problem is that the number 
+of the training data\cite{blei2003latent}. Another problem is that the number 
 of parameters in the model grows linearly with the number of documents.
@@
 is a mixture of a small number of topics and that each word's occurrence is
-attributable to one of the document's topics.\cite{Blei11introductionto}
+attributable to one of the document's topics\cite{Blei11introductionto}.
 
@@
 solve this limitation by setting a Dirichlet prior on the topic
-distribution.\cite{blei2003latent} In practice, this results in more reasonable
+distribution\cite{blei2003latent}. In practice, this results in more reasonable
 mixtures of topics in a document.
@@
 that the topics are generated first, before the
-documents.\cite{Blei11introductionto} Now for each document in the
+documents\cite{Blei11introductionto}. Now for each document in the
 collection, we generate the words in a two-stage process:
@@
 For each document $w$, in corpus $D$, the LDA generative process is as follows, 
-with corresponding plate notation in Figure 2:
+with corresponding plate notation in Figure \ref{figLDA}:
 
@@
 \caption{Plate notation of the standard LDA model}
+\label{figLDA}
 \end{figure}
@@
 partial derivatives of the likelihood function with respect to all variables,
-setting these derivatives to zero and solving the equations simultaneously.
-\cite{Myung:2003}
+setting these derivatives to zero and solving the equations simultaneously
+\cite{Myung:2003}.
 
@@
 MCMC with Gibbs sampling\cite{Griffiths02gibbssampling} and expectation 
-propagation.\cite{Minka:2002:EGA:2073876.2073918} The goal of variational
+propagation\cite{Minka:2002:EGA:2073876.2073918}. The goal of variational
 inference is to approximate an intractable probability distribution
@@
 distribution has properties such that it can be efficiently
-computed.\cite{Fox2011ATO}
+computed\cite{Fox2011ATO}.
 
@@
 it still requires a full pass through the entire corpus in each
-iteration. It can be slow to apply to very large datasets.
-\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}
+iteration. It can be slow to apply to very large datasets
+\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}.
 
@@
 An online variational inference algorithm is proposed by Hoffman et all.\cite{onlineLDAvb} for fitting $\lambda$, the parameters to the variational
-posterior over the topic distributions $\beta$. The "online LDA" is nearly as
+posterior over the topic distributions $\beta$. The \emph{online LDA} is nearly as
 simple as the variational algorithm, but converges much faster for large
@@
 topic by looking at the word probabilities in each row of
-$\lambda$.\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}
+$\lambda$\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}.
 
@@
 The paper that mostly influenced our work is \emph{Finding Scientific Topics}, by
-T. Griffiths and M. Steyvers.\cite{griffiths_steyvers04} They investigated
+T. Griffiths and M. Steyvers\cite{griffiths_steyvers04}. They investigated
 abstract data from articles published in the Proceedings of the National Academy
@@
 \emph{Discovering themes and trends in transportation research using topic
-modeling}, \cite{Sun201749} about topic modeling in transportation
+modeling}\cite{Sun201749}, about topic modeling in transportation
 research. Considering approximately 17000 abstracts of articles
@@
 apply the LDA model in our dataset. It consists of information about 
-EU projects funded for research and innovation under the FP4 - H2020 
-and the awards/projects that got funded by NSF from 1994 - 2017 in USA. We
+EU projects funded for research and innovation under the FP4-H2020 
+and the awards/projects that got funded by NSF from 1994-2017 in USA. We
 consider the projects' description/abstract as the documents in LDA.
@@
 in LDA the project objectives, which is an accurate description for
-the project. We also added the ``title' value of each project to the
+the project. We also added the ``title'' value of each project to the
 objectives-documents, to increase the probability of finding accurate
-topics. For the majority of the projects the ``start date' and ``end
-date' value was null, so we kept the splitting of the dataset per
+topics. For the majority of the projects the ``start date'' and ``end
+date'' value was null, so we kept the splitting of the dataset per
 framework, in order to keep the correlation to the time. We followed
@@
 \end{tabular}
+\label{eutable}
 \end{center}
@@
 the rare words that appear less than 5 times in the collection. 
-Finally, we obtained a smaller corpus per framework (see the table above).
+Finally, we obtained a smaller corpus per framework (see table \ref{eutable}).
 
@@
 non-medical fields of science and engineering. Its medical counterpart
-is the National Institutes of Health (ur data does not include 
+is the National Institutes of Health (our data does not include 
 material from NIH). The NSF funds approximately 24\% of all
@@
 In the provided dataset, the information is splitted into XML files, separated
-per year, from 1994 - 2017. In order to keep the correlation to time and be able
+per year, from 1994-2017. In order to keep the correlation to time and be able
 to compare the two datasets later, we splitted the projects based on the year
-they were initialized (see Table below).
+they were initialized (see table \ref{usatable}).
 
@@
 Python library and we removed following very common words in the existing
-dataset: ``data', ``work', ``based'', ``new'', ``project'', ``university'', ``student'',
-``students'', ``research'', ``study'', ``program'', ``development'', ``study'', ``studies'', ``provide'', ``use'', ``understanding'', ``important'', ``support'', ``proposed''.
+dataset: ``data'', ``work'', ``based'', ``new'', ``project'', ``university'', ``student'', ``students'', ``research'', ``study'', ``program'', ``development'', ``study'', ``studies'', ``provide'', ``use'', ``understanding'', ``important'', ``support'', ``proposed''.
 We also removed the rare words that appear less than 5
 times in the collection. Finally, we obtained a smaller corpus per framework 
-(see Table below).
+(see Table \ref{usatable}).
 
@@
 \end{tabular}
+\label{usatable}
 \end{center}
@@
 In general, the most popular subject in European Union over the years
-is Information systems. In our dataset we fount \todo{found} projects
+is Information systems. In our dataset we found projects
 related to almost all kinds of information systems, and especially
@@
 the biological processes essential for the cell's functions and
-maintenance. These affect many aspects of our lives, including
-evolution, nutrition and the spread of diseases. \todo{This is not an
-  essay, remove.} Especially from 1998 up to day, there is a focus in
+maintenance. Especially from 1998 up to day, there is a focus in
 Health care and Diagnostics, and for the last decade researchers are
@@
 subject very important to the research community and many researchers
-work on this up to day. In short, sustainability takes into account
-how we might live in harmony with the natural world around us,
-protecting it from damage and destruction. \todo{This is not an essay,
-  remove.} Many projects are related to one of the Three Pillars of
-Sustainability\footnote{http
-  ://www.thwink.org/sustain/glossary/ThreePillarsOfSustainability.htm}.
+work on this up to day. 
 The European Union is considered by some to have the most extensive
@@
 
-The National Science Foundation mostly supports fundamental research
-and education in the non-medical science and engineering. Its medical
-counterpart is the National Institutes of Health \todo{You have said
-  so before.}.\footnote{\url{https://en.wikipedia.org/wik
-    i/National_Science_Foundation}} With STEM being the top priority
-in USA, \todo{How do you know that?} most of the projects founded by
+With STEM being the top priority in USA, since this topic shows up in all the years
+and according to the plot in figure \ref{usatrend} STEM is the topic with the highest proportion
+of projects compared to the other topics (read section ), 
+most of the projects founded by
 NSF are related to engineering, computer science, mathematics and
@@
 From 1994-2006 and the last three years, International Research and
-conferences came up as a trending topic. Re- searchers \todo{Re-
-  searchers} have a great interest to collaborate with other
+conferences came up as a trending topic. Researchers have a great 
+interest to collaborate with other
 colleagues from all over the world and share their knowledge. A big
@@
 European Union's research and innovation
-programme.\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}
+programme\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}.
 
@@
 from 1994 to 2017 for the EU and from 1994 to 2016 for the
-USA.\footnote{in this implementation we removed the projects of the
+USA\footnote{in this implementation we removed the projects of the
   year 2017 from the USA dataset, because the amount of
   projects-documents was too small compared to the other years and it
-  was affecting the result of the trend for each topic.}
-
-\subparagraph{Trends in the EU}
-
-In figure x \todo{What?} we show the 10 topics that consists \todo{You
-  mean that you show the top 20 words; the topics consist of more.} of
+  was affecting the result of the trend for each topic.}.
+
+\subsection{Trends in the EU}
+
+In figure \ref{totaltopicsEU} we show the 10 topics described by
 the 20 top words with the highest posterior probability of belonging
@@
 \begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic0_all.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic1_all.png}} &
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic2_all.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic3_all.png}} &
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic4_all.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic5_all.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic6_all.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic7_all.png}} &
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic8_all.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic9_all.png}} &
-\subfloat[Topic 10]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic10_all.png}} &
-\subfloat[Topic 11]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic11_all.png}}\\
+\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic0_all.png}} &
+\subfloat[Materials \& Manufacturing]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic1_all.png}} &
+\subfloat[Social policy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic2_all.png}}\\
+\subfloat[Disease detection \& treatment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic3_all.png}} &
+\subfloat[Materials science / Physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic4_all.png}} &
+\subfloat[Transport \& Energy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic5_all.png}}\\
+\subfloat[Business \& Innovation]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic6_all.png}} &
+\subfloat[Climate change / Environment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic7_all.png}} &
+\subfloat[Molecular mechanisms]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic8_all.png}}\\
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic9_all.png}} &
+\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic10_all.png}} &
+\subfloat[Energy production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/EU_topic11_all.png}}\\
 \end{tabular}
 \caption{Wordclouds of topics of the EU dataset (1994-2017)}
+\label{totaltopicsEU}
 \end{figure}
 \end{center}
-\todo{Why
-  don't you put the name of each topic in each topic's caption?}
 
@@
 assigned to this topic during the FP, normalized by the number of the
-documents-projects occurring in this FP. In figure X \todo{what?} we
+documents-projects occurring in this FP. In figure \ref{eutrend} we
 plot the results of topic proportions over time.
@@
 drastically in 1998-2002 ($+14\%$) and in 2002-2006 it is at its peak
-($+18\% since 1994$ \todo{that should not be in math}). This period
+($+18\%$ since 1994). This period
 many activities and projects where initialized in order to support and
@@
 science \& Physics. Energy production (topic 11) was less popular in
-1994-2002 and is becoming slightly \todo{more?} popular the last 15
+1994-2002 and is becoming slightly more popular the last 15
 years.
@@
 \caption{Topics over time in EU}
+\label{eutrend}
 \end{figure}
 \end{center}
-\subparagraph{Trends in the USA	}
-
+
+\subsection{Trends in the USA}
+\label{usaevolution}
 Just like the EU dataset, we found the 10 topics of the USA dataset
@@
 the evolution of each topic per year. We ran the LDA model with 12000
-iterations and the dame \todo{same} value of the rest of the
+iterations and the same value of the rest of the
 parameters, as described in section 4.3. \todo{You should probably
@@
 
-Each one of the wordclouds in figure X \todo{what?}represents a topic.
+Each one of the wordclouds in figure \ref{usatotal} represents a topic.
 The topics that are described in the wordclouds are listed below:
@@
 \caption{Wordclouds of topics of the USA dataset (1994-2016)}
+\label{usatotal}
 \end{figure}
@@
 \end{figure}
+\label{usatrend}
 \end{center}
@@
 which is not surprising, since the National Science Foundation itself
-estimates that 80/%
-\todo{you mean percent} of the jobs available during the next decade
-will require math and science skills \todo{Cite that.}. Even the
-concept of STEM was first introduced by Judith A. Ramaley, the former
-director of the National Science Foundation's education and human
-resources division \cite{Cite that.}.
+estimates that 80\%
+ of the jobs available during the next decade
+will require math and science skills \footnote{\url{http://www.cvent.com/events/steam-ing-up-stem-academy-2017-2018/event-summary-e3e3f0c4087e43b99d23f4e4d95b6837.aspx}}.
+Even the acronym STEM arose in common use shortly after an interagency meeting on
+science education held at the US National Science Foundation chaired by the then 
+NSF director Rita Colwell\footnote{\url{https://en.wikipedia.org/wiki/Science,_technology,_engineering,_and_mathematics}}.
 
@@
 
-In our case, we will use JSD cause \todo{because} is a symmetric
+In our case, we will use JSD because is a symmetric
 formula, so that $sim(Q,P) = sim(P,Q)$. we want to calculate the
@@
 
-The figures 7-11 \todo{Use cross-references} visualize the heatmaps of
+The figures \ref{heatmap4}-\ref{heatmap20} visualize the heatmaps of
 the similarity of the two regions during the FP4-H2020. Rows represent
@@
 \caption{Heatmap of the similarity of the two regions during 1994-1997}
+\label{heatmap4}
 \end{figure}
@@
 \caption{Heatmap of the similarity of the two regions during 1998-2001}
+\label{heatmap5}
 \end{figure}
@@
 \caption{Heatmap of the similarity of the two regions during 2002-2006}
+\label{heatmap6}
 \end{figure}
@@
 \caption{Heatmap of the similarity of the two regions during 2007-2013}
+\label{heatmap7}
 \end{figure}
@@
 \caption{Heatmap of the similarity of the two regions during 2014-2017}
+\label{heatmap20}
 \end{figure}
@@
 
-We briefly describe \todo{described} the preprocessing of the
+We briefly described the preprocessing of the
 abstracts-documents before applying the model. LDA, as an unsupervised
@@
 
-We found that most topics cover various topics \todo{That reads
-  funny}, while some show well-defined scopes. Our work provides
+We found that most topics cover various subjects, while some show 
+well-defined scopes. Our work provides
 valuable knowledge about the research over the last two decades in the
 two regions and could benefit researchers to to identify the subjects
-that mostly get funded in the EU and USA. This research gives an
-interesting aspect about what kind of topics were actually funded over
-the last 22 years. \todo{In general, you should not praise your own
-  work. The reader may praise it.}
+that mostly get funded in the EU and USA. This research gives an aspect 
+about what kind of topics were actually funded over
+the last 22 years.
 
@@
 of the topics with the countries/states that are involved in the
-projects, and address question like "which countries in EU are mostly
-collaborate? on which topics" and "which states of the US are getting
-more funding compared to others".
+projects, and address question like ``which countries in EU are mostly
+collaborate? on which topics'' and ``which states of the US are getting
+more funding compared to others''.
 

### 2017-06-27 thesis_report/draft_thesis.tex
Report: fixed all mistakes

@@
 \usepackage{geometry} 
+\usepackage{float}
 
@@
 
-Nowadays, there are some funding opportunities for researchers, but are 
-really competitive. The European Union countries are encouraged to
+Today most research is funded by competitive open calls. 
+The European Union countries are encouraged to
 invest 3\% of their GDP in research and development by 2020. EU's
@@
 can also be weighted with for instance TF-IDF\footnote{TF-IDF stands 
-for term frequency - inverse document frequency, and the tf-idf weight is 
+for term frequency - inverse document frequency, and the TF-IDF weight is 
 a weight often used in information retrieval and text mining. This weight 
@@
 \subsection{EU dataset}
-
+\label{EUdataset}
 CORDIS (Community Research and Development Information Service) is the European
@@
 Finally, we obtained a smaller corpus per framework (see table \ref{eutable}). 
+For the actual implementation, see \emph{eu iterations.py} in the Appendix.
 
@@
 
-The NSF organizes its research and education support through seven 
-directorates, each encompassing several disciplines:
-
-\begin{itemize}
-\item Biological Sciences
-\begin{description}
-\item Molecular, Cellular and Organismal biology, Environmental science
-\end{description}
-\item Computer and Information Science and Engineering
-\begin{description}
-\item Fundamental computer science, Computer and networking systems, 
-Artificial Intelligence
-\end{description}
-\item Engineering
-\begin{description}
-\item Bioengineering, Environmental systems, Civil and Mechanical systems, 
-Chemical and Transport systems, Electrical and Communications systems, Design
- and Manufacturing
-\end{description}
-\item Geosciences
-\begin{description}
-\item Geological, Atmospheric and Ocean sciences
-\end{description}
-\item Mathematical and Physical Sciences
-\begin{description}
-\item Mathematics, Astronomy, Physics, Chemistry and Materials science
-\end{description}
-\item Social, Behavioral and Economic Sciences
-\begin{description}
-\item Neuroscience, Management, Psychology, Sociology, Anthropology, 
-Linguistics, Science of science policy and economics
-\end{description}
-\item Education and Human Resources
-\begin{description}
-\item Science, Technology, Engineering and mathematics education at every level
-\end{description}
-\end{itemize}
-
+NSF is divided into the following seven directorates that support science and
+engineering research and education: Biological Sciences, Computer and
+Information Science and Engineering, Engineering, Geosciences, Mathematical and
+Physical Sciences, Social, Behavioral and Economic Sciences, and Education and
+Human Resources. Each is headed by an assistant director and each is further
+subdivided into divisions like materials research, ocean sciences and behavioral
+and cognitive sciences. Within NSF's Office of the Director, the Office of
+Integrative Activities also supports research and researchers. Other sections of
+NSF are devoted to financial management, award processing and monitoring, legal
+affairs, outreach and other functions \footnote{\url{https://www.nsf.gov/about/research_areas.jsp}}. The directorates and their divisions are listed below:
+\begin{itemize}
+\item Biological Sciences (BIO)
+\begin{itemize}
+\item[] Biological Infrastructure (DBI)
+\item[] Environmental Biology (DEB)
+\item[] Emerging Frontiers (EF)
+\item[] Integrative Organismal Systems (IOS)
+\item[] Molecular and Cellular Biosciences (MCB)
+\end{itemize}
+\item Computer and Information Science and Engineering (CISE)
+\begin{itemize}
+\item[] Office of Advanced Cyberinfrastructure (OAC)
+\item[] Computing and Communication Foundations (CCF)
+\item[] Computer and Network Systems (CNS)
+\item[] Information and Intelligent Systems (IIS)
+\end{itemize}
+\item Education and Human Resources (EHR)
+\begin{itemize}
+\item[] Graduate Education (DGE)
+\item[] Research on Learning in Formal and Informal Settings (DRL)
+\item[] Undergraduate Education (DUE)
+\item[] Human Resource Development (HRD)
+\end{itemize}
+\item Engineering (ENG)
+\begin{itemize}
+\item[] Chemical, Bioengineering, Environmental and Transport Systems (CBET)
+\item[] Civil, Mechanical and Manufacturing Innovation (CMMI)
+\item[] Electrical, Communications and Cyber Systems (ECCS)
+\item[] Engineering Education and Centers (EEC)
+\item[] Emerging Frontiers and Multidisciplinary Activities (EFMA)
+\item[] Industrial Innovation and Partnerships (IIP)
+\end{itemize}
+\item Environmental Research and Education (ERE)
+\item Geosciences (GEO)
+\begin{itemize}
+\item[] Atmospheric and Geospace Sciences (AGS)
+\item[] Earth Sciences (EAR)
+\item[] Ocean Sciences (OCE)
+\item[] Office of Polar Programs (OPP)
+\end{itemize}
+\item Integrative Activities (OIA)
+\item International Science and Engineering (OISE)
+\item Mathematical and Physical Sciences (MPS)
+\begin{itemize}
+\item[] Astronomical Sciences (AST)
+\item[] Chemistry (CHE)
+\item[] Materials Research (DMR)
+\item[] Mathematical Sciences (DMS)
+\item[] Physics (PHY)
+\item[] Office of Multidisciplinary Activities (OMA)
+\end{itemize}
+\item Social, Behavioral and Economic Sciences (SBE)
+\begin{itemize}
+\item[] Behavioral and Cognitive Sciences (BCS)
+\item[] National Center for Science and Engineering Statistics (NCSES)
+\item[] Social and Economic Sciences (SES)
+\item[] SBE Office of Multidisciplinary Activities (SMA)
+\end{itemize}
+\end{itemize}
 The data about the awards
@@
 
-In the provided dataset, the information is splitted into XML files, separated
+In the provided dataset, the information is split into XML files, separated
 per year, from 1994-2017. In order to keep the correlation to time and be able
-to compare the two datasets later, we splitted the projects based on the year
+to compare the two datasets later, we split the projects based on the year
 they were initialized (see table \ref{usatable}).
@@
 (see Table \ref{usatable}). 
+For the actual implementation, see \emph{usa iterations.py} in the Appendix.
 
@@
 \subsection{Model inference}
-
+\label{modelinference}
 For the implementation, we used the Gensim package (Radim Řehůřek,
@@
 the actual implementation.
+\pagebreak
 
@@
 
-\todo{This is the heart of the thesis, but it is difficult to make
-  sense of it. Make sure that when you mention a topic, the topic
-  stands out of the text. It could be in italics, or some other font.
-  Right now it is not easy to detect it in the discussion. From what I
-  understand, the topics you mention are the top topics over all the
-  years. You should then list them all in a table, in decreasing order
-  of popularity. Also you should show the wordclouds. Right now there
-  is only a reference to a figure at the appendix, which is not at the
-  appendix at all.
-}
-
+In figures \ref{wordcloudEU4} - \ref{wordcloudEU20} we show the 10 topics from FP4 to H2020 of the EU dataset, described by
+the 20 top words with the highest posterior probability of belonging
+to the topic. The size of each word is in proportion to each
+probability; the bigger the word, the higher the probability. 
+Each wordcloud describes a topic, which we can find intuitively (the label 
+of each wordcloud corresponds to the title of the topic).
+
+By comparing the thematic areas suggested by the EU
+\footnote{\url{https://europa.eu/european-union/topics_en}} and the topics that
+we found with our implementation, one can easily observe that the majority of
+these topics are included in the wider categories of ``Science \& Technology''
+and its subcategory ``Research and Innovation''. For instance, the topics
+\emph{Molecular Biology} and \emph{Genetics} belong to the category ``Science \&
+Technology'', \emph{Cancer detection \& treatment} to the category ``Health''
+and ``Science'', \emph{Mathematics}, \emph{High energy physics}, \emph{Materials
+\& Chemistry} and \emph{Information Systems} belong to ``Science \&
+Technology''. Even though the topics that we listed above stand out as distinct
+thematic areas, they are not listed in the EU's website.
+
+The topics that we are going to discuss in this section are the ones that
+stand out in most of the Framework Programmes.
 In general, the most popular subject in European Union over the years
-is Information systems. In our dataset we found projects
+is \emph{Information systems}. In our dataset we found projects
 related to almost all kinds of information systems, and especially 
-Quality management systems (1994-2002), Management information
-systems, Network information systems and Information systems as a
-service to all kinds of organizations, including universities and
+\emph{Management information
+systems}, \emph{Network information systems} and \emph{Information systems as a
+service} to all kinds of organizations, including universities and
 companies. Since technology has an impact in every aspect nowadays, it
 is normal to have such popularity over the years and it's becoming
-popular in education, as well. The same period of time, Innovation in
-Business emerged as a trending topic, with projects related to new
+popular in education, as well. The same period of time, \emph{Innovation in
+Business} emerged as a trending topic, with projects related to new
 technologies and software systems in the industry and how they assist
 the businesses and the market. In addition, until 2002 a very popular
-subject related to Information systems, was Applications in mobile
-networks, embedded and broadband systems, which nowadays has lost part
+subject related to \emph{Information systems}, was \emph{Applications in mobile
+networks}, \emph{embedded and broadband systems}, which nowadays has lost part
 of its popularity in research.
 
-Another popular subject that appears the last 22 years is Materials research;
+Another popular subject that appears the last 22 years is \emph{Materials research};
 the projects related to material research are mostly related to the discovery
@@
 
-The third most popular subject is Molecular biology and Genetics.
+The third most popular subject is \emph{Molecular biology \& Genetics}.
 These projects are related to the cellular molecules that carry out
@@
 Health care and Diagnostics, and for the last decade researchers are
-studying the cancer detection and treatment, which is a common cause
+studying the \emph{Cancer detection \& treatment}, which is a common cause
 of death in EU and the second most common cause of death in USA.
-\todo{It seems now that you are discussing topics that are not popular
-  throughout the period, but in the latest frameworks?}
-
-Moreover, Environmental, Social and Economic Sustainability is a
+
+Moreover, \emph{Environmental, Social and Economic Sustainability} is a
 subject very important to the research community and many researchers
@@
 European Economic Community (EEC), which is the beginning of the EU's
-environmental policy. Social and Economic policies are also popular in
+environmental policy. \emph{Social and Economic policies} are also popular in
 the EU region over the last decade. Also, the last two decades there
-is a focus on the Green energy production, like hydropower, solar and
+is a focus on the \emph{Green energy production}, like hydropower, solar and
 nuclear energy.
 
-During the 6th and the 7th framework programme, International Research and
-conferences came up in our dataset as a trending topic. Researchers have a great
+During the 6th and the 7th framework programme, \emph{International Research \& 
+conferences} came up in our dataset as a trending topic. Researchers have a great
 interest to collaborate with other colleagues from all over the world and share
 their knowledge. A big part of the projects funded by the EU that is related to
-international research, is also related to Physics, in general, and High energy
-physics in EU (see Appendix: Wordclouds of topics of the EU).
-
+\emph{international research}, is also related to \emph{Physics}, in general, 
+and \emph{High energy physics}.
+
+\begin{figure}[H]
+\begin{tabular}{rcl}
+\subfloat[Management Systems \& Software engineering]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic0_7000.png}} &
+\subfloat[Agriculture, Fisheries and Food]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic1_7000.png}}&
+\subfloat[Molecular biology, Genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic2_7000.png}}\\
+\subfloat[EU transport]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic3_7000.png}}&
+\subfloat[Digital systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic4_7000.png}} &
+\subfloat[Materials processing]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic5_7000.png}}\\
+\subfloat[Genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic6_7000.png}} &
+\subfloat[Policy for environmental sustainability]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic7_7000.png}}&
+\subfloat[Energy technologies]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic8_7000.png}}\\
+\subfloat[Applications in mobile networks]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic9_7000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the EU FP4 (1994-1998)}
+\label{wordcloudEU4}
+\end{figure}
+
+\begin{figure}[H]
+\begin{tabular}{rcl}
+\subfloat[Management software]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic0_7000.png}} &
+\subfloat[Hydropower / Energy production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic1_7000.png}}&
+\subfloat[Information technologies]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic2_7000.png}}\\
+\subfloat[Quality control systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
+\subfloat[Health care / Medical genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
+\subfloat[Environmental sustainability and policies]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\
+\subfloat[Molecular biology (genes)]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic6_7000.png}} &
+\subfloat[Optical quantum computing]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic7_7000.png}}&
+\subfloat[Education in Nuclear physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic8_7000.png}}\\
+\subfloat[Education, training]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic9_7000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the EU FP5 (1998-2002)}
+\label{wordcloudEU5}
+\end{figure}
+
+\begin{figure}[H]
+\begin{tabular}{rcl}
+\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic0_7000.png}} &
+\subfloat[Biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic1_7000.png}}&
+\subfloat[Embedded systems design]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic2_7000.png}}\\
+\subfloat[Molecular biology, genes]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic3_7000.png}}&
+\subfloat[Evolution / Formation]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic4_7000.png}} &
+\subfloat[Sustainable production / Energy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic5_7000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic6_7000.png}} &
+\subfloat[Environmental management services]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic7_7000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic8_7000.png}}\\
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic9_7000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the EU FP6 (2002-2006)}
+\label{wordcloudEU6}
+\end{figure}
+
+\begin{figure}[H]
+\begin{tabular}{rcl}
+\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic0_7000.png}} &
+\subfloat[(High energy) physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic1_7000.png}}&
+\subfloat[Energy production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic2_7000.png}}\\
+\subfloat[Social Sciences]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic3_7000.png}}&
+\subfloat[Molecular Biology / Genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic4_7000.png}} &
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic5_7000.png}}\\
+\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic6_7000.png}} &
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic7_7000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic8_7000.png}}\\
+\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic9_7000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the EU FP7 (2007-2013)}
+\label{wordcloudEU7}
+\end{figure}
+
+\begin{figure}[H]
+\begin{tabular}{rcl}
+\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic0_20000.png}} &
+\subfloat[Environmental sustainability \& food production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic1_20000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic2_20000.png}}\\
+\subfloat[Training]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic3_20000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic4_20000.png}} &
+\subfloat[Environmental sustainability / Green energy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic5_20000.png}}\\
+\subfloat[Physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic6_20000.png}} &
+\subfloat[Business \& Innovation]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic7_20000.png}}&
+\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic8_20000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic9_20000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the EU H2020 (2014-2020)}
+\label{wordcloudEU20}
+\end{figure}
+
+\vfill
 \subsection{Discovering topics on the USA projects}
 
-\todo{The same comments as in the previous subsection apply here. Make
-  sure you explain how you picked the topics you discuss here. Make
-  sure they stand out.}
-
-With STEM being the top priority in USA, since this topic shows up in all the years
-and according to the plot in figure \ref{usatrend} STEM is the topic with the highest proportion
-of projects compared to the other topics (read section ), 
+In figures \ref{wordcloudUSA4} - \ref{wordcloudUSA20} we show the 10 topics 
+from 1994 to 2017 of the USA dataset, described by
+the 20 top words with the highest posterior probability of belonging
+to the topic.
+By comparing the the areas of interest in the US, through its directorates, 
+and our topics, we see that all the topics that we found correspond to either 
+a directorate or one of the divisions. Below, we discuss the topics that
+stand out in most of the years.
+
+With \emph{STEM} being the top priority in USA, since this topic shows up in all the years
+and according to the plot in figure \ref{usatrend} \emph{STEM} is the topic with the highest proportion
+of projects compared to the other topics (read section \ref{usaevolution}), 
 most of the projects founded by
 NSF are related to engineering, computer science, mathematics and
-information systems, in general. The subjects STEM \& Education,
-Software engineering, Information systems and Mathematics, arise as
+information systems, in general. The subjects \emph{STEM \& Education},
+\emph{Software engineering}, \emph{Information systems} and \emph{Mathematics}, arise as
 topics in all these years, from 1994-2017.
@@
 many projects are related to the environment effects of climate change. Topics
-like Environmental Science, Atmospheric \& Ocean sciences, Geology, Climate
-change and its impact in the United States emerge during all these years. The
-last three years there is a focus on the Green energy production, like
+like \emph{Environmental Science, Atmospheric \& Ocean sciences, Geology, Climate
+change} and its impact in the United States emerge during all these years. The
+last three years there is a focus on the \emph{Green energy production}, like
 hydropower and wind power. Among with climate change, there is many research
-related to Biology and Evolution. A less popular subject that appears during the
-years 1994-1997 and 2007-2013 is Molecular, Cellular \& Organismal biology and
-Genetics. These projects mostly refer to applied genetics, as well as cell
+related to \emph{Biology and Evolution}. A less popular subject that appears during the
+years 1994-1997 and 2007-2013 is \emph{Molecular, Cellular \& Organismal biology and
+Genetics}. These projects mostly refer to applied genetics, as well as cell
 functionality. Topics include receptor biology, regulation of gene expression,
@@
 
-Another popular subject that appears the last 22 years is Materials and
-Chemistry; the projects related to material research are mostly refer to the
+Another popular subject that appears the last 22 years is \emph{Materials and
+Chemistry}; the projects related to material research are mostly refer to the
 materials' properties and applications in engineering. The last 3 years,
@@
 mechanical engineering, bioengineering and chemical \& transport systems. In
-2002-2006 many projects are related to the subject of transport that is
-sustainable in the senses of social, environmental and climate impacts (Green
-transportation).
-
-From 1994-2006 and the last three years, International Research and
-conferences came up as a trending topic. Researchers have a great 
-interest to collaborate with other
-colleagues from all over the world and share their knowledge. A big
-part of the projects funded by the EU that is related to international
-research, is also related to Physics, in general, and High energy
-physics in EU (see Appendix: Wordclouds of topics of the EU).
-\todo{Are you talking about the EU, or the US here?}
-
-NSF shows a great interest in international activities across all NSF
+2002-2006 many projects are related to the subject of \emph{Transport} that is
+sustainable in the senses of social, environmental and climate impacts (\emph{Green
+transportation}).
+
+NSF shows a great interest in \emph{International activities} across all NSF
 supported disciplines. The goal of these projects is to support high
 quality research and education, which could not occur without
-international collaboration. NSF seeks to catalyze a higher level of
-international engagement in the US science and engineering community
-by promoting international conferences and university projects and
-partnerships \todo{You have said the same in the previous paragraph.}.
+international collaboration.
 An interesting fact regarding international partnerships is that the
@@
 together more closely on projects funded under Horizon 2020, the
-European Union's research and innovation
+European Union's \emph{Research and Innovation}
 programme\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}.
 
-From 2002 up to day, Economic and Social Sciences emerge as a topic in our
+From 2002 up to day, \emph{Economic and Social Sciences} emerge as a topic in our
 dataset. Researchers show a great interest in identifying policies which help
@@
 Finally, a topic that used to be popular in the past, in 1994-1997 and
-2007-2013, is High energy Physics in USA, which has lost its popularity
+2007-2013, is \emph{High energy Physics} in USA, which has lost its popularity
 nowadays. The last 5 years, there is an interest around STEM and its
-applications in manufacturing and engineering.
-
+applications in \emph{manufacturing and engineering}.
+
+\begin{figure}[H]
+\begin{tabular}{rcl}
+\subfloat[Software engineering]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
+\subfloat[Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
+\subfloat[International research \& Education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
+\subfloat[Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
+\subfloat[Economic \& Social science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
+\subfloat[Molecular biology / Genetics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
+\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
+\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the USA (1994-1997)}
+\label{wordcloudUSA4}
+\end{figure}
+
+\begin{figure}[H]
+\begin{tabular}{rcl}
+\subfloat[Applied Sciences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic0_8000.png}} &
+\subfloat[Environment \& Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic1_8000.png}}&
+\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic2_8000.png}}\\
+\subfloat[Biology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic3_8000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic4_8000.png}} &
+\subfloat[STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic5_8000.png}}\\
+\subfloat[Energy \& Technology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic6_8000.png}} &
+\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic7_8000.png}}&
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic8_8000.png}}\\
+\subfloat[International conferences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic9_8000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the USA (1998-2001)}
+\label{wordcloudUSA5}
+\end{figure}
+
+\begin{figure}[H]
+\begin{tabular}{rcl}
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic0_8000.png}} &
+\subfloat[Education (in engineering)]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic1_8000.png}}&
+\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic2_8000.png}}\\
+\subfloat[International conferences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic3_8000.png}}&
+\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic4_8000.png}} &
+\subfloat[Green transportation]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic5_8000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic6_8000.png}} &
+\subfloat[Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic7_8000.png}}&
+\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic8_8000.png}}\\
+\subfloat[Physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic9_8000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the USA (2002-2006)}
+\label{wordcloudUSA6}
+\end{figure}
+
+\begin{figure}[H]
+\begin{tabular}{rcl}
+\subfloat[STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic0_9000.png}} &
+\subfloat[Computer \& Networking systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic1_9000.png}}&
+\subfloat[Chemistry \& Materials science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic2_9000.png}}\\
+\subfloat[Climate change \ Environmental science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic3_9000.png}}&
+\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic4_9000.png}} &
+\subfloat[Atmospheric \& Ocean sciences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic5_9000.png}}\\
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic6_9000.png}} &
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic7_9000.png}}&
+\subfloat[(Molecular) biology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic8_9000.png}}\\
+\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic9_9000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the USA (2007-2013)}
+\label{wordcloudUSA7}
+\end{figure}
+
+\begin{figure}[H]
+\begin{tabular}{rcl}
+\subfloat[Biology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic0_8000.png}} &
+\subfloat[Climate Change / Geology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic1_8000.png}}&
+\subfloat[Social science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic2_8000.png}}\\
+\subfloat[STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic3_8000.png}}&
+\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic4_8000.png}} &
+\subfloat[Chemical \& transport systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic5_8000.png}}\\
+\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic6_8000.png}} &
+\subfloat[Materials \& Mechanical engineering]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic7_8000.png}}&
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic8_8000.png}}\\
+\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic9_8000.png}}&
+\end{tabular}
+\caption{Wordclouds of topics of the USA (2014-2017)}
+\label{wordcloudUSA20}
+\end{figure}
+
+\vfill
 \subsection{Topic evolution over time}
@@
 probability; the bigger the word, the higher the probability. Each
-wordcloud describes a topic, which we can find intuitively. Below are
+wordcloud describes a topic, which we can find intuitively. 
+We ran the LDA model with 7000
+iterations and the same value of the rest of the
+parameters, as described in section \ref{modelinference}. Below are
 listed the topics that we found corresponding to the words that
@@
 
-Based on this plot, topic 10, which refers to International Research,
-has an interesting evolution; uring the years 1994-1998 is appears as
+As we mentioned in section \ref{EUdataset}, most of the projects in the 
+EU dataset don't have information about the year that they were initialized, 
+and there's only information about the Framework Programme, where they got 
+approved. Therefore, in figure \ref{eutrend}, we illustrate the topic 
+evolution over time per FP.
+
+Based on this plot, topic 10, which refers to \emph{International Research},
+has an interesting evolution; during the years 1994-1998 is appears as
 less popular topic, compared to other topics. However, this changes
@@
 already know that in Horizon 2020 there is an agreement between EU and
-USA for supporting the cooperation of the two regions.Our hypothesis
-for the evolution of the International Research is that the EU
+USA for supporting the cooperation of the two regions. Our hypothesis
+for the evolution of the \emph{International Research} is that the EU
 successfully managed to create the foundation for supporting
@@
 
-Materials and Manufacturing was a hot topic in 1994-1998, but it also
+\emph{Materials and Manufacturing} was a hot topic in 1994-1998, but it also
 appears a big decrease during the years 1998-2006 and it has a stable
-trend since then. Materials Science/Chemistry \& Physics' popularity
+trend since then. \emph{Materials Science/Chemistry \& Physics'} popularity
 (topic 4) line has an increase during 2002-2013 and the last 3 years a
-small decrease of $2-3\%$. Topics 2 and 3 (Social policy, Disease
-detection \& treatment) follow the same linear trend as Materials
-science \& Physics. Energy production (topic 11) was less popular in
+small decrease of $2-3\%$. Topics 2 and 3 (\emph{Social policy, Disease
+detection \& treatment}) follow the same linear trend as \emph{Materials
+science \& Physics}. \emph{Energy production} (topic 11) was less popular in
 1994-2002 and is becoming slightly more popular the last 15
@@
 
-Topic 9, which refers to Information systems in general, is a subject that has a
+Topic 9, which refers to \emph{Information systems} in general, is a subject that has a
 stable trend and it appears as a popular topic the last 22 years compared to
@@
 
-Biology and the study of molecular mechanisms have a small decrease of
-popularity on average. This may happen because the projects related to
-medical fields are supported by another institute, National Institutes
-of Health \todo{Are you talking about the US or the EU?}. Also,
-research in Climate change and Environmental science is another
+\emph{Biology} and the study of \emph{molecular mechanisms} have a small decrease of
+popularity on average. Also,
+research in \emph{Climate change and Environmental science} is another
 subject that paradoxically appears as a topic that is gradually losing
@@
 
-Finally, topic 6, which is related to Business \& Innovation, has a huge
+Finally, topic 6, which is related to \emph{Business \& Innovation}, has a huge
 increase the last 3 years. We can assume that the EU is very interested in
@@
 iterations and the same value of the rest of the
-parameters, as described in section 4.3. \todo{You should probably
-  explain the same for the Trends in the EU.}
+parameters, as described in section \ref{modelinference}.
 
@@
 
-\begin{center}
-\begin{figure}
-\centering
-\begin{tabular}{rcl}
-\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic0_12000_all_docs.png}} &
-\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic1_12000_all_docs.png}} &
-\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic2_12000_all_docs.png}}\\
-\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic3_12000_all_docs.png}} &
-\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic4_12000_all_docs.png}} &
-\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic5_12000_all_docs.png}}\\
-\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic6_12000_all_docs.png}} &
-\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic7_12000_all_docs.png}} &
-\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic8_12000_all_docs.png}}\\
-\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic9_12000_all_docs.png}} &
-\end{tabular}
-\caption{Wordclouds of topics of the USA dataset (1994-2016)}
-\label{usatotal}
-\end{figure}
-\end{center}
-
 Just like the computation in the EU dataset, we calculate the topic 
@@
 the documents-projects  occurring in this year.
-\begin{center}
-\begin{figure}[h]
+
+\begin{figure}[H]
+\centering
+\begin{tabular}{rcl}
+\subfloat[Material science and High energy physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic0_12000_all_docs.png}} &
+\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic1_12000_all_docs.png}} &
+\subfloat[(Molecular) biology, Genetics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic2_12000_all_docs.png}}\\
+\subfloat[Science of social policy and economics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic3_12000_all_docs.png}} &
+\subfloat[International research and conferences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic4_12000_all_docs.png}} &
+\subfloat[Chemistry and Materials science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic5_12000_all_docs.png}}\\
+\subfloat[STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic6_12000_all_docs.png}} &
+\subfloat[Climatology, Atmospheric and Ocean sciences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic7_12000_all_docs.png}} &
+\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic8_12000_all_docs.png}}\\
+\subfloat[Mechanical engineering]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/USA_topic9_12000_all_docs.png}} &
+\end{tabular}
+\caption{Wordclouds of topics of the USA dataset (1994-2016)}
+\label{usatotal}
+\end{figure}
+
+\begin{figure}[H]
 \centering
@@
 \caption{Topics over time in USA}
-\end{figure}
 \label{usatrend}
-\end{center}
-In figure 6 we plot the topic distribution over time. We can easily
-observe that the topic 6, which refers to STEM education, is becoming
+\end{figure}
+
+In figure \ref{usatrend} we plot the topic distribution over time. We can easily
+observe that the topic 6, which refers to \emph{STEM education}, is becoming
 a trend in the United States over the years, while most of the other
 topics' evolution doesn't show up such a high increase. Topics 5 and
-8, which refer to Chemistry \& Materials science and Molecular
-biology, respectively, show a small decrease over the years. Topics 9
-and 0 (Mechanical Engineering, Material Science and High energy
-physics) show a small increase over the last 5 years. Mathematics'
+8, which refer to \emph{Chemistry \& Materials science} and \emph{Molecular
+biology}, respectively, show a small decrease over the years. Topics 9
+and 0 (\emph{Mechanical Engineering, Material Science and High energy
+physics}) show a small increase over the last 5 years.
+
+\emph{Mathematics}'
 evolution over time (Topic 1) looks stable on average and shows up as
-a popular subject over the last 22 years, while Social Sciences and
-International Research (Topic 3 and 4) show a small decrease over the
-last 3 years. Molecular biology and Genetics (Topic 2) has an
+a popular subject over the last 22 years, while \emph{Social Sciences} and
+\emph{International Research} (Topic 3 and 4) show a small decrease over the
+last 3 years. \emph{Molecular biology and Genetics} (Topic 2) has an
 increasing popularity from 1994 to 2001 and later is starting to
-stabilize. Climatology, Atmospheric and Ocean sciences look stable the
+stabilize. \emph{Climatology, Atmospheric and Ocean sciences} look stable the
 first years, while from 2006 up to date it is gradually becoming less
@@
 
-In general, the STEM (science, technology, engineering and math)
+In general, the \emph{STEM} (science, technology, engineering and math)
 related research and education is becoming more and more popular,
@@
 will require math and science skills \footnote{\url{http://www.cvent.com/events/steam-ing-up-stem-academy-2017-2018/event-summary-e3e3f0c4087e43b99d23f4e4d95b6837.aspx}}.
-Even the acronym STEM arose in common use shortly after an interagency meeting on
+Even the acronym STEM arose in common use shortly after an   meeting on
 science education held at the US National Science Foundation chaired by the then 
@@
 
-Since P and Q are probability distributions, it means that 
-$\sum_{i=1}^{N} p_i = \sum_{i=1}^{N} q_i = 1$. The The Jensen–Shannon 
+Since $P$ and $Q$ are probability distributions, it means that 
+$\sum_{i=1}^{N} p_i = \sum_{i=1}^{N} q_i = 1$. The Jensen–Shannon 
 divergence (JSD) is a
 symmetrized and smoothed version of the Kullback–Leibler divergence
-$D(P \mid\mid Q)$. It quantifies how "distinguishable" two distributions are
-from each other. It is defined by
-
+$D(P \mid\mid Q)$. It quantifies how ``distinguishable'' two distributions are
+from each other. It is defined by:
 \begin{equation}
@@
 topics from the EU dataset and columns topics from the USA dataset.
+The topics 0 - 9 of the EU dataset per FP (figures \ref{wordcloudEU4} -
+\ref{wordcloudEU20}) and the topics 0 - 9 of the USA dataset per FP (figures
+\ref{wordcloudUSA4} - \ref{wordcloudUSA20}) are declared in the heatmap plots as
+eu0 - eu9 and usa0 - usa9, respectively.
 The values of the JSD computation which are close to zero (lighter
 color of the box) suggest more similarity within topics. According to 
-the heatmaps, the topics that have high similarity between the EU and
-the USA are: \todo{To be able to make sense of it, you must list
-  somewhere what are topics eu0--eu9 and usa0--usa9. Right not it is
-  impossible to understand whether, for example, there were Software
-  Engineering topics in both the EU and the US, or only in one of the
-  two, and that was similar to Materials in the other regions, or
-  perhaps you mean something else entirely.}
+the boxes with the lightest color of the heatmaps, 
+the topics that have high similarity between the EU and the USA are:
+
 \begin{itemize}
@@
 \begin{itemize}
-\item[*] Software engineering
-\item[*] Materials
+\item[*] eu0: \emph{Management Systems \& Software engineering} $\sim$ usa0: \emph{Software engineering}
+\item[*] eu5: \emph{Materials processing} $\sim$ usa7: \emph{Materials}
 \end{itemize}
@@
 \begin{itemize}
-\item[*] Energy production
-\item[*] Education in STEM
-\item[*] Mathematics
-\end{itemize}
-\item FP6 (2002 - 2006)
-\begin{itemize}
-\item[*] Information systems
-\item[*] Molecular biology / Genetics
-\item[*] Chemistry \& Materials
+\item[*] eu1: \emph{Hydropower / Energy production} $\sim$ usa6: \emph{Energy production}
+\end{itemize}
+\item FP6 (2002 $\sim$ 2006)
+\begin{itemize}
+\item[*] eu9: \emph{Information systems} $\sim$ usa0: \emph{Information systems}
+\item[*] eu8: \emph{Materials} $\sim$ usa2: \emph{Materials \& Chemistry}
 \end{itemize}
@@
 \begin{itemize}
-\item[*] Chemistry \& Materials
-\item[*] High energy physics
-\item[*] Molecular biology / Genetics
+\item[*] eu8: \emph{Materials} $\sim$ usa2: \emph{Chemistry \& Materials Science}
+\item[*] eu1: \emph{High energy physics} $\sim$ usa4: \emph{High energy physics}
+\item[*] eu4: \emph{Molecular biology / Genetics} $\sim$ usa8: \emph{Molecular biology}
 \end{itemize}
@@
 \begin{itemize}
-\item[*] Information systems
-\item[*] Materials
-\item[*] Physics
-\item[*] Economic \& Social policy
-\end{itemize}
-\end{itemize}
-\begin{figure}[h]
+\item[*] eu2: \emph{Information systems} $\sim$ usa4: \emph{Information systems}
+\item[*] eu4: \emph{Materials} and eu6: \emph{Physics} $\sim$ usa7: \emph{Materials \& Mechanical engineering}
+\item[*] eu9: \emph{Economic \& Social policy} $\sim$ usa2: \emph{Social science}
+\end{itemize}
+\end{itemize}
+
+\begin{figure}[H]
 \centering
@@
 \end{figure}
-\begin{figure}
+
+\begin{figure}[H]
 \centering
@@
 
-\begin{center}
-\begin{figure}[h]
-\begin{tabular}{rcl}
-\subfloat[Quality Management Systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic0_7000.png}} &
-\subfloat[Agriculture, Fisheries and Food]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic1_7000.png}}&
-\subfloat[Molecular biology, Genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic2_7000.png}}\\
-\subfloat[EU transport]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic3_7000.png}}&
-\subfloat[Digital systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic4_7000.png}} &
-\subfloat[Materials processing]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic5_7000.png}}\\
-\subfloat[Genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic6_7000.png}} &
-\subfloat[Policy for environmental sustainability]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic7_7000.png}}&
-\subfloat[Energy technologies]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic8_7000.png}}\\
-\subfloat[Applications in mobile networks]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic9_7000.png}}&
-\end{tabular}
-\caption{Wordclouds of topics of the EU FP4 (1994-1998)}
-\end{figure}
-\end{center}
-\begin{center}
-\begin{figure}[h]
-\begin{tabular}{rcl}
-\subfloat[Management software]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic0_7000.png}} &
-\subfloat[Hydropower / Energy production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic1_7000.png}}&
-\subfloat[Information technologies]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic2_7000.png}}\\
-\subfloat[Quality control systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
-\subfloat[Health care / Medical genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
-\subfloat[Environmental sustainability and policies]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\
-\subfloat[Molecular biology (genes)]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic6_7000.png}} &
-\subfloat[Optical quantum computing]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic7_7000.png}}&
-\subfloat[Education in Nuclear physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic8_7000.png}}\\
-\subfloat[Education, training]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic9_7000.png}}&
-\end{tabular}
-\caption{Wordclouds of topics of the EU FP5 (1998-2002)}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}[h]
-\begin{tabular}{rcl}
-\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic0_7000.png}} &
-\subfloat[Biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic1_7000.png}}&
-\subfloat[Embedded systems design]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic2_7000.png}}\\
-\subfloat[Molecular biology, genes]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic3_7000.png}}&
-\subfloat[Evolution / Formation]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic4_7000.png}} &
-\subfloat[Sustainable production / Energy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic5_7000.png}}\\
-\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic6_7000.png}} &
-\subfloat[Environmental management services]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic7_7000.png}}&
-\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic8_7000.png}}\\
-\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP6_wordclouds/EUFP6_topic9_7000.png}}&
-\end{tabular}
-\caption{Wordclouds of topics of the EU FP6 (2002-2006)}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}[h]
-\begin{tabular}{rcl}
-\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic0_7000.png}} &
-\subfloat[(High energy) physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic1_7000.png}}&
-\subfloat[Energy production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic2_7000.png}}\\
-\subfloat[Social Sciences]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic3_7000.png}}&
-\subfloat[Molecular Biology / Genetics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic4_7000.png}} &
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic5_7000.png}}\\
-\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic6_7000.png}} &
-\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic7_7000.png}}&
-\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic8_7000.png}}\\
-\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_FP7_wordclouds/EUFP7_topic9_7000.png}}&
-\end{tabular}
-\caption{Wordclouds of topics of the EU FP7 (2007-2013)}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}[h]
-\begin{tabular}{rcl}
-\subfloat[Molecular biology]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic0_20000.png}} &
-\subfloat[Environmental sustainability \& food production]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic1_20000.png}}&
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic2_20000.png}}\\
-\subfloat[?]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic3_20000.png}}&
-\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic4_20000.png}} &
-\subfloat[Environmental sustainability / Green energy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic5_20000.png}}\\
-\subfloat[Physics]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic6_20000.png}} &
-\subfloat[Business \& Innovation]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic7_20000.png}}&
-\subfloat[Cancer detection \& treatment]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic8_20000.png}}\\
-\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/eu_topics/eu_H2020_wordclouds/EUH2020_topic9_20000.png}}&
-\end{tabular}
-\caption{Wordclouds of topics of the EU H2020 (2014-2020)}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}[h]
-\begin{tabular}{rcl}
-\subfloat[Software engineering]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
-\subfloat[Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&
-\subfloat[International research \& Education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic2_8000.png}}\\
-\subfloat[Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic3_8000.png}}&
-\subfloat[Economic \& Social science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic4_8000.png}} &
-\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic5_8000.png}}\\
-\subfloat[Molecular biology / Genetics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic6_8000.png}} &
-\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic7_8000.png}}&
-\subfloat[Cognitive neuroscience]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic8_8000.png}}\\
-\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic9_8000.png}}&
-\end{tabular}
-\caption{Wordclouds of topics of the USA (1994-1997)}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}[h]
-\begin{tabular}{rcl}
-\subfloat[Applied Sciences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic0_8000.png}} &
-\subfloat[Environment \& Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic1_8000.png}}&
-\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic2_8000.png}}\\
-\subfloat[Biology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic3_8000.png}}&
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic4_8000.png}} &
-\subfloat[STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic5_8000.png}}\\
-\subfloat[Systems ?]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic6_8000.png}} &
-\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic7_8000.png}}&
-\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic8_8000.png}}\\
-\subfloat[International conferences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP5_wordclouds/USAFP5_topic9_8000.png}}&
-\end{tabular}
-\caption{Wordclouds of topics of the USA (1998-2001)}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}[h]
-\begin{tabular}{rcl}
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic0_8000.png}} &
-\subfloat[Education (in engineering)]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic1_8000.png}}&
-\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic2_8000.png}}\\
-\subfloat[International conferences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic3_8000.png}}&
-\subfloat[Biology \& Evolution]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic4_8000.png}} &
-\subfloat[Green transportation]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic5_8000.png}}\\
-\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic6_8000.png}} &
-\subfloat[Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic7_8000.png}}&
-\subfloat[Materials]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic8_8000.png}}\\
-\subfloat[Physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP6_wordclouds/USAFP6_topic9_8000.png}}&
-\end{tabular}
-\caption{Wordclouds of topics of the USA (2002-2006)}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}[h]
-\begin{tabular}{rcl}
-\subfloat[STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic0_9000.png}} &
-\subfloat[Computer \& Networking systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic1_9000.png}}&
-\subfloat[Chemistry \& Materials science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic2_9000.png}}\\
-\subfloat[Climate change \ Environmental science]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic3_9000.png}}&
-\subfloat[High energy physics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic4_9000.png}} &
-\subfloat[Atmospheric \& Ocean sciences]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic5_9000.png}}\\
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic6_9000.png}} &
-\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic7_9000.png}}&
-\subfloat[(Molecular) biology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic8_9000.png}}\\
-\subfloat[Economic \& Social policy]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP7_wordclouds/USAFP7_topic9_9000.png}}&
-\end{tabular}
-\caption{Wordclouds of topics of the USA (2007-2013)}
-\end{figure}
-\end{center}
-
-\begin{center}
-\begin{figure}[h]
-\begin{tabular}{rcl}
-\subfloat[Biology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic0_8000.png}} &
-\subfloat[Climate Change / Geology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic1_8000.png}}&
-\subfloat[Sociology]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic2_8000.png}}\\
-\subfloat[STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic3_8000.png}}&
-\subfloat[Information systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic4_8000.png}} &
-\subfloat[Chemical \& transport systems]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic5_8000.png}}\\
-\subfloat[Materials \& Chemistry]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic6_8000.png}} &
-\subfloat[Materials \& Mechanical engineering]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic7_8000.png}}&
-\subfloat[Mathematics]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic8_8000.png}}\\
-\subfloat[International research]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_H2020_wordclouds/USAH2020_topic9_8000.png}}&
-\end{tabular}
-\caption{Wordclouds of topics of the USA (2014-2017)}
-\end{figure}
-\end{center}
-
 \end{document}

### 2017-06-27 thesis_report/draft_thesis.tex
Add acknowledgements

@@
 ones, how can one handle such datasets and extract information from them.
+\end{abstract}
+
+\renewcommand{\abstractname}{Acknowledgements}
+\begin{abstract}
+First of all, I would like to express my gratitude to my supervisor, Panos
+Louridas. Panos provided me with invaluable advice and help throughout my MSc
+thesis with his profound knowledge and a seemingly never-ending patience whilst
+allowing me to work in my own way. Panos’ positive outlook and methodic approach
+to solving problems has been a huge inspiration to me. He also helped me
+comprehend the right research practice making these months of study a real
+pleasure. Thank you.
+
+Many thanks to my colleagues from the IST Lab. It was an honour to have a chance
+to work together with such great people and brilliant researchers that helped me
+broaden my research interests. I would also like to thank all of my colleagues
+from the MSc in Computer Science and especially Artem Tsikiridis. I really
+appreciated helpful discussions and much needed coffee breaks. Finally, I would
+like to thank my family and my friends for their support and love all these
+years.
 \end{abstract}

### 2017-06-27 thesis_report/draft_thesis.tex
Fix 5.1

@@
 These topics are used to gain insight into some of the research that
-occurs the last two decades. Our goal is to share these insights with
+occurs the last two decades. We hope to share these insights with
 researchers and encourage them to develop better strategies to
@@
 In figures \ref{wordcloudEU4} - \ref{wordcloudEU20} we show the 10 topics from FP4 to H2020 of the EU dataset, described by
-the 20 top words with the highest posterior probability of belonging
+the 20 top words with the highest probability of belonging
 to the topic. The size of each word is in proportion to each
@@
 
-The topics that we are going to discuss in this section are the ones that
-stand out in most of the Framework Programmes.
-In general, the most popular subject in European Union over the years
-is \emph{Information systems}. In our dataset we found projects
-related to almost all kinds of information systems, and especially 
-\emph{Management information
-systems}, \emph{Network information systems} and \emph{Information systems as a
-service} to all kinds of organizations, including universities and
-companies. Since technology has an impact in every aspect nowadays, it
-is normal to have such popularity over the years and it's becoming
-popular in education, as well. The same period of time, \emph{Innovation in
-Business} emerged as a trending topic, with projects related to new
-technologies and software systems in the industry and how they assist
-the businesses and the market. In addition, until 2002 a very popular
-subject related to \emph{Information systems}, was \emph{Applications in mobile
-networks}, \emph{embedded and broadband systems}, which nowadays has lost part
-of its popularity in research.
-
-Another popular subject that appears the last 22 years is \emph{Materials research};
-the projects related to material research are mostly related to the discovery
-and design of new materials, with an emphasis on solids. Materials properties
-and performance are used in many disciplines, like chemistry, physics and
-engineering.
-
-The third most popular subject is \emph{Molecular biology \& Genetics}.
-These projects are related to the cellular molecules that carry out
-the biological processes essential for the cell's functions and
-maintenance. Especially from 1998 up to day, there is a focus in
-Health care and Diagnostics, and for the last decade researchers are
-studying the \emph{Cancer detection \& treatment}, which is a common cause
-of death in EU and the second most common cause of death in USA.
-
-Moreover, \emph{Environmental, Social and Economic Sustainability} is a
-subject very important to the research community and many researchers
-work on this up to day. 
-The European Union is considered by some to have the most extensive
-environmental laws of any international organization, started by the
+In order to obtain an overall view of th etopics in EU, we calculated for each
+one of the FPs the proportion of the documents-projects that are assigned to the
+topics of the FP, normalized by the total number of the documents of the FP. The
+topics that we are going to discuss in this section are the ones that either
+show up in most of the FPs or they have a high percentage in one of them.
+
+\emph{Molecular biology \& Genetics} is a popular topic that appears in all the
+FPs, from 1994 to 2017, where the 13\% of the projects on average belong to this
+category. These projects are related to the cellular molecules that carry out
+the biological processes essential for the cell's functions and maintenance.
+Another popular subject is \emph{Materials research}; the projects related to
+material research are mostly related to the discovery and design of new
+materials, with an emphasis on solids. Materials properties and performance are
+used in many disciplines, like chemistry, physics and engineering.
+\emph{Materials} as a topic covers the 13\% of the projects in FP4, while it
+doesn't stand out as a distinguish topic in FP5. However, in FP6 the 22\% of the
+projects refer to Materials, and since then it gradually loses its popularity,
+with 11\% of the projects in FP7 and only 6\% in H2020.
+
+\emph{Management software \& systems} is a subject that appears only in FP4 and
+FP5, with the 12\% of the projects. emph{Information systems \& technologies'}
+related projects cover the 8,5\% of the projects on average from FP5-H2020.
+Since technology has an impact in every aspect nowadays, it is normal to have a
+stable popularity over the years.
+
+Moreover, \emph{Environmental Sustainability and policies} is a popular subject
+in FP4, with the 12\% of the projects, while it gradually loses its popularity
+over the years. The European Union is considered by some to have the most
+extensive environmental laws of any international organization, started by the
 European Economic Community (EEC), which is the beginning of the EU's
-environmental policy. \emph{Social and Economic policies} are also popular in
-the EU region over the last decade. Also, the last two decades there
-is a focus on the \emph{Green energy production}, like hydropower, solar and
-nuclear energy.
-
-During the 6th and the 7th framework programme, \emph{International Research \& 
-conferences} came up in our dataset as a trending topic. Researchers have a great
-interest to collaborate with other colleagues from all over the world and share
-their knowledge. A big part of the projects funded by the EU that is related to
-\emph{international research}, is also related to \emph{Physics}, in general, 
-and \emph{High energy physics}.
+environmental policy. The \emph{Energy production} is a topic that shows up in
+FP4 with a 13\% of the projects, while in FP5 the number of the projects related
+to \emph{Green energy} (hydropower, solar, nuclear energy) is increasing up to
+17,5\% and since then it also loses its populariry. The last 3 years, only the
+3\% of the projects are related to \emph{Green energy production}.
+
+In FP6 and FP7, \emph{Social and Economic policies} appears with a small
+percentage of the projects (5\%). However, in H2020 it has a big increace, with
+the 17\% of the projects related to this topic. The last 3-4 years,
+\emph{Business \& Innovation} emerged as a trending topic, with 1 out of 4
+projects being related to the support of businesses and the market, with the
+assistance of new technologies and innovation.
+
+The last two decades, there is a 10\% of the projects related to \emph{Physics}
+and \emph{High energy physics}. Also, \emph{International Research} came up in
+our dataset as a trending topic, with a 16\% of projects in FP6 and FP7.
+Finally, the last decade, the 5\% of the projects are related to \emph{Cancer
+detection \& treatment}, which is a common cause of death in EU and the second
+most common cause of death in USA.
 
@@
 from 1994 to 2017 of the USA dataset, described by
-the 20 top words with the highest posterior probability of belonging
-to the topic.
+the 20 top words with the highest probability.
 By comparing the the areas of interest in the US, through its directorates, 
@@
 In figure \ref{totaltopicsEU} we show the 10 topics described by
-the 20 top words with the highest posterior probability of belonging
+the 20 top words with the highest probability of belonging
 to the topic. The size of each word is in proportion to each

### 2017-06-28 thesis_report/draft_thesis.tex
Fix 5.2

@@
 
-In order to obtain an overall view of th etopics in EU, we calculated for each
+In order to obtain an overall view of the topics in EU, we calculated for each
 one of the FPs the proportion of the documents-projects that are assigned to the
@@
 
-With \emph{STEM} being the top priority in USA, since this topic shows up in all the years
-and according to the plot in figure \ref{usatrend} \emph{STEM} is the topic with the highest proportion
-of projects compared to the other topics (read section \ref{usaevolution}), 
-most of the projects founded by
-NSF are related to engineering, computer science, mathematics and
-information systems, in general. The subjects \emph{STEM \& Education},
-\emph{Software engineering}, \emph{Information systems} and \emph{Mathematics}, arise as
-topics in all these years, from 1994-2017.
-
-While NSF promotes the progress of science, it also enhances the efforts to
-maintain the national health, prosperity, and welfare. Over the last 22 years,
-many projects are related to the environment effects of climate change. Topics
-like \emph{Environmental Science, Atmospheric \& Ocean sciences, Geology, Climate
-change} and its impact in the United States emerge during all these years. The
-last three years there is a focus on the \emph{Green energy production}, like
-hydropower and wind power. Among with climate change, there is many research
-related to \emph{Biology and Evolution}. A less popular subject that appears during the
-years 1994-1997 and 2007-2013 is \emph{Molecular, Cellular \& Organismal biology and
-Genetics}. These projects mostly refer to applied genetics, as well as cell
-functionality. Topics include receptor biology, regulation of gene expression,
-biomedical engineering, patterns of inheritance and molecular genetics.
+In order to obtain an overall view of the topics in USA, we calculated for each
+one of the FPs the proportion of the documents-projects that are assigned to the
+topics of the FP, normalized by the total number of the documents of the FP. The
+topics that we are going to discuss in this section are the ones that either
+show up in most of the FPs or they have a high percentage in one of them.
+
+\emph{Biology} is a topic that appears all over the last 22 years that we
+investigate, with a stable percentage of 10\% of the projects, on average. Some
+of these topics are related to emph{Biology and Evolution}. Also, a 5\%
+approximately of the projects are related to emph{Mathematics}, from 1994 to
+2017.
 
@@
 researchers from the USA focus on materials applications and design in
-mechanical engineering, bioengineering and chemical \& transport systems. In
-2002-2006 many projects are related to the subject of \emph{Transport} that is
-sustainable in the senses of social, environmental and climate impacts (\emph{Green
-transportation}).
+\emph{Mechanical engineering}, and \emph{Chemical \& transport systems}.
+
+With \emph{STEM} being the top priority in USA, since this topic shows up in all
+the years and according to the plot in figure \ref{usatrend} \emph{STEM} is the
+topic with the highest proportion of projects compared to the other topics (read
+section \ref{usaevolution}). Specifically, \emph{STEM education} has the 16,5\%
+of the projects from 1994-2006, 21\% in 2007-2013 (1 out of 5 projects is
+related to STEM) and the last 3 years it has lost its popularity by 10\%.
+
+Moreover, \emph{Information systems} is a very popular subject from 1998 to 2013, 
+covering the 13\% of the projects. The last 3 years, it became even more popular, 
+since 1 out of 5 projects is related to \emph{Information systems}.
+
+While NSF promotes the progress of science, it also enhances the efforts to
+maintain the national health, prosperity, and welfare. From 1994 to 2013,
+many projects are related to the environment effects of climate change. Topics
+like \emph{Environmental Science, Atmospheric \& Ocean sciences, Geology, Climate
+change} and its impact in the United States emerge during all these years in the 14\% 
+of the projects, on average. The last three years \emph{Climate change} 
+appears as a less popular subject (6\%).
 
 NSF shows a great interest in \emph{International activities} across all NSF
-supported disciplines. The goal of these projects is to support high
-quality research and education, which could not occur without
+supported disciplines (18\% of the projects in 1004-1998). The goal of these projects is 
+to support high quality research and education, which could not occur without
 international collaboration.
@@
 European Union's \emph{Research and Innovation}
-programme\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}.
+programme\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}. The last
+3 years, the projects related to \emph{International research} cover the 10\% of all the 
+projects this period.
 
 From 2002 up to day, \emph{Economic and Social Sciences} emerge as a topic in our
-dataset. Researchers show a great interest in identifying policies which help
-the communities and they also do lots of Qualitative and Quantitative research
-to investigate the size or extent of particular issues or trends in society.
+dataset (8\% of the projects, on average). Researchers show a great interest in identifying 
+policies which help the communities and they also do lots of Qualitative and Quantitative 
+research to investigate the size or extent of particular issues or trends in society.
 
 Finally, a topic that used to be popular in the past, in 1994-1997 and
-2007-2013, is \emph{High energy Physics} in USA, which has lost its popularity
-nowadays. The last 5 years, there is an interest around STEM and its
-applications in \emph{manufacturing and engineering}.
+2007-2013, covering the 10\% of the projects funded by NSF, is \emph{High energy Physics} 
+in USA, which has lost its popularity nowadays.
 
@@
 \begin{tabular}{rcl}
-\subfloat[Software engineering]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
+\subfloat[Software engineering / STEM education]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic0_8000.png}} &
 \subfloat[Climate change]{\includegraphics[width=0.35\textwidth]{figs/usa_topics/usa_FP4_wordclouds/USAFP4_topic1_8000.png}}&

### 2017-06-28 thesis_report/draft_thesis.tex
Minor fixes in 5.4 & 5.5

@@
 iterations and the same value of the rest of the
-parameters, as described in section \ref{modelinference}. Below are
-listed the topics that we found corresponding to the words that
-describe them:
+parameters, as described in section \ref{modelinference}. We assigned titles 
+to the topics, based on the words that describe them. Below are
+listed the titles of topics:
 \begin{itemize}
@@
 Each one of the wordclouds in figure \ref{usatotal} represents a topic.
-The topics that are described in the wordclouds are listed below:
+The titles of the topics that are described in the wordclouds are listed below:
 

### 2017-06-28 thesis_report/draft_thesis.tex
Final report

@@
 
-\title{Topic modeling on EU and the USA research projects}
+\title{Topic modeling on EU and USA research projects}
 \author{Maria Iliadi}
@@
 	supervised by\par
-	Assoc.Prof.~Panos Louridas
+	Assoc. Prof.~Panos Louridas
 
@@
 
-\renewcommand{\abstractname}{Acknowledgements}
+\renewcommand{\abstractname}{Acknowledgments}
 \begin{abstract}
@@
 thesis with his profound knowledge and a seemingly never-ending patience whilst
-allowing me to work in my own way. Panos’ positive outlook and methodic approach
+allowing me to work in my own way. Panos’s positive outlook and methodic approach
 to solving problems has been a huge inspiration to me. He also helped me
@@
 
-Many thanks to my colleagues from the IST Lab. It was an honour to have a chance
+Many thanks to my colleagues from the IST Lab. It was an honor to have a chance
 to work together with such great people and brilliant researchers that helped me
@@
 funds approximately 24\% of the federally supported research
-conducted by the USA's colleges and universities\footnote{\url{https://www.nsf.gov/about/}}.
+conducted by the USA's colleges and universities~\footnote{\url{https://www.nsf.gov/about/}}.
 
@@
 
-In section \ref{theoretic} introduces some basic concepts
+In section~\ref{theoretic} we introduce some basic concepts
 in topic modeling and we describe the model that we used for topic
 extraction, Latent Dirichlet Allocation, which is a statistical
-generative model for documents. In section \ref{relatedwork}, 
+generative model for documents. In section~\ref{relatedwork}, 
 we briefly talk about the papers that mostly influenced our study. 
-In section \ref{methodology} we provide information
+In section~\ref{methodology} we provide information
 about the dataset structure and the methodology that we followed in
-our analysis. In section \ref{analysis} we interpret the results of 
+our analysis. In section~\ref{analysis} we interpret the results of 
 our analysis, and we discuss the evolution of the topics over time and the
 differences between the two regions' topics based on their similarity.
-Finally, section \ref{conclusion} summarizes our work and section 
-\ref{future} suggests some future work.
+Finally, section~\ref{conclusion} summarizes our work and section~\ref{future} suggests some future work.
 
@@
 texts, topic modeling algorithms do not require any prior annotations
-or labeling of the documents\cite{Blei11introductionto}.
+or labeling of the documents~\cite{Blei11introductionto}.
 
@@
 
-When introducing the Latent Dirichlet Allocation in section \ref{LDAexplained}, 
+When introducing the Latent Dirichlet Allocation in section~\ref{LDAexplained}, 
 we will be using the terms prior and posterior probabilities
@@
 where $\mathbb{E}$ is the expectation of the random variable $X$
-\footnote{Suppose random variable $X$ can take value $x_{1}$ with 
+~\footnote{Suppose random variable $X$ can take value $x_{1}$ with 
 probability $p_{1}$, value $x_{2}$ with probability $p_{2}$, 
@@
 because it assumes that this is the distribution of topics in 
-documents and words in topics (read Latent Dirichlet Allocation in section \ref{LDAexplained}). 
+documents and words in topics (read Latent Dirichlet Allocation in section~\ref{LDAexplained}). 
 In probability theory, the multinomial distribution is a generalization
@@
 combination of numbers of successes for the various
-categories\footnote{\url{https://en.wikipedia.org/wiki/Multinomial_distribution}}.
+categories~\footnote{\url{https://en.wikipedia.org/wiki/Multinomial_distribution}}.
 
@@
 is over all possible data points. Here, a data point is a document containing
-$n$ words\cite{Huang_maximumlikelihood}.
+$n$ words~\cite{Huang_maximumlikelihood}.
 
@@
 The Dirichlet distribution is a way to model random probability mass functions
-(PMFs)\footnote{If you roll 1000 dice, the theoretical odds of any particular
+(PMFs)~\footnote{If you roll 1000 dice, the theoretical odds of any particular
 number showing up (i.e. a 1, 2, 3, 4, 5, or 6) are 1/6. However, you won't get
@@
 Latent Semantic Indexing, or LSI, was presented by Deerwester et al.
-in 1990\cite{Deerwester90indexingby}. The model manages to deal with the
+in 1990~\cite{Deerwester90indexingby}. The model manages to deal with the
 problem that multiple terms can refer to the same meaning, i.e.
@@
 After LSI was introduced, Hofmann presented the Probabilistic Latent
-Semantic Indexing, or PLSI model\cite{Hofmann:1999:PLS:312624.312649}. 
+Semantic Indexing, or PLSI model~\cite{Hofmann:1999:PLS:312624.312649}. 
 PLSI is a topic model where each word in a document is generated 
@@
 can be represented with a topic distribution. Later, in 2003 Blei et al. 
-presented the Latent Dirichlet Allocation, or LDA\cite{blei2003latent}. 
+presented the Latent Dirichlet Allocation, or LDA~\cite{blei2003latent}. 
 As opposed to PLSI, LDA is a statistically generative model for documents 
@@
 relationships between documents and the words that occur in
-them\cite{Deerwester90indexingby}. In LSI a term-document matrix is
+them~\cite{Deerwester90indexingby}. In LSI a term-document matrix is
 created by analyzing the corpus, where the rows correspond to words
@@
 the number of times a word occurs in a document but this term count
-can also be weighted with for instance TF-IDF\footnote{TF-IDF stands 
-for term frequency - inverse document frequency, and the TF-IDF weight is 
+can also be weighted with for instance TF-IDF~\footnote{TF-IDF stands 
+for term frequency-inverse document frequency, and the TF-IDF weight is 
 a weight often used in information retrieval and text mining. This weight 
@@
 document can be seen as a vector with components corresponding to its
-weighted term counts\cite{Salton:1988:TAA:54259.54260}.
+weighted term counts~\cite{Salton:1988:TAA:54259.54260}.
 
@@
 there is no clear way of assigning probability to a document that is not part
-of the training data\cite{blei2003latent}. Another problem is that the number 
+of the training data~\cite{blei2003latent}. Another problem is that the number 
 of parameters in the model grows linearly with the number of documents.
@@
 is a mixture of a small number of topics and that each word's occurrence is
-attributable to one of the document's topics\cite{Blei11introductionto}.
+attributable to one of the document's topics~\cite{Blei11introductionto}.
 
@@
 solve this limitation by setting a Dirichlet prior on the topic
-distribution\cite{blei2003latent}. In practice, this results in more reasonable
+distribution~\cite{blei2003latent}. In practice, this results in more reasonable
 mixtures of topics in a document.
@@
 that the topics are generated first, before the
-documents\cite{Blei11introductionto}. Now for each document in the
+documents~\cite{Blei11introductionto}. Now for each document in the
 collection, we generate the words in a two-stage process:
@@
 the corpus share the same set of topics, but each document exhibits
-those topics with different proportion - that's the distinguishing
+those topics with different proportion---that's the distinguishing
 characteristic of LDA. A more detailed explanation of the model
-follows in section \ref{LDAmodel}.
+follows in section~\ref{LDAmodel}.
 
@@
 For each document $w$, in corpus $D$, the LDA generative process is as follows, 
-with corresponding plate notation in Figure \ref{figLDA}:
+with corresponding plate notation in Figure~\ref{figLDA}:
 
@@
 ~\cite{onlineLDAvb}. In our implementation, we're using the online variational
-LDA model, which is described in section \ref{oLDAvb}.
+LDA model, which is described in section~\ref{oLDAvb}.
 
@@
 setting these derivatives to zero and solving the equations simultaneously
-\cite{Myung:2003}.
+~\cite{Myung:2003}.
 
@@
 a variational Bayes approximation of the posterior distribution;
-\cite{blei2003latent} alternative inference techniques use 
-MCMC with Gibbs sampling\cite{Griffiths02gibbssampling} and expectation 
-propagation\cite{Minka:2002:EGA:2073876.2073918}. The goal of variational
+~\cite{blei2003latent} alternative inference techniques use 
+MCMC with Gibbs sampling~\cite{Griffiths02gibbssampling} and expectation 
+propagation~\cite{Minka:2002:EGA:2073876.2073918}. The goal of variational
 inference is to approximate an intractable probability distribution
@@
 distribution has properties such that it can be efficiently
-computed\cite{Fox2011ATO}.
+computed~\cite{Fox2011ATO}.
 
@@
 iteration. It can be slow to apply to very large datasets
-\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}.
+~\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}.
 
@@
 \label{oLDAvb}
-An online variational inference algorithm is proposed by Hoffman et all.\cite{onlineLDAvb} for fitting $\lambda$, the parameters to the variational
+An online variational inference algorithm is proposed by Hoffman et all.~\cite{onlineLDAvb} for fitting $\lambda$, the parameters to the variational
 posterior over the topic distributions $\beta$. The \emph{online LDA} is nearly as
@@
 topic by looking at the word probabilities in each row of
-$\lambda$\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}.
+$\lambda$~\footnote{\url{https://wellecks.wordpress.com/2014/10/26/ldaoverflow-with-online-lda/}}.
 
@@
 approximate posterior inference. In his work \emph{Introduction to
-Probabilistic Topic Models}\cite{Blei11introductionto} 
+Probabilistic Topic Models}~\cite{Blei11introductionto} 
 he describes the basic ideas behind LDA and
@@
 The paper that mostly influenced our work is \emph{Finding Scientific Topics}, by
-T. Griffiths and M. Steyvers\cite{griffiths_steyvers04}. They investigated
+T. Griffiths and M. Steyvers~\cite{griffiths_steyvers04}. They investigated
 abstract data from articles published in the Proceedings of the National Academy
@@
 \emph{Discovering themes and trends in transportation research using topic
-modeling}\cite{Sun201749}, about topic modeling in transportation
+modeling}~\cite{Sun201749}, about topic modeling in transportation
 research. Considering approximately 17000 abstracts of articles
@@
 apply the LDA model in our dataset. It consists of information about 
-EU projects funded for research and innovation under the FP4-H2020 
-and the awards/projects that got funded by NSF from 1994-2017 in USA. We
+EU projects funded for research and innovation under the FP4--H2020 
+and the awards/projects that got funded by NSF from 1994--2017 in USA. We
 consider the projects' description/abstract as the documents in LDA.
@@
 Below, we provide the general topics of the EU projects as listed in the EU 
-Open Data Portal \footnote{https://data.europa.eu/euodp/en/data}:
+Open Data Portal~\footnote{https://data.europa.eu/euodp/en/data}:
 \begin{itemize}
@@
 European Union from 1994 to 2017. These projects got approved under
-the framework programme (FP4-H2020) for research and technological
+the framework programme (FP4--H2020) for research and technological
 development. Grant information is provided for each project, 
@@
 \begin{itemize}
-\item FP4: fourth framework programme (1994-1998)
-\item FP5: fifth framework programme (1998-2002)
-\item FP6: sixth framework programme (2002-2006)
-\item FP7: seventh framework programme (2007-2013)
-\item H2020: Horizon 2020 framework programme (2014-2020)
+\item FP4: fourth framework programme (1994--1998)
+\item FP5: fifth framework programme (1998--2002)
+\item FP6: sixth framework programme (2002--2006)
+\item FP7: seventh framework programme (2007--2013)
+\item H2020: Horizon 2020 framework programme (2014--2020)
 \end{itemize}
@@
 \hline
-FP4 & 1994-1998 & 14567 & 7293 & 364263 \\
-FP5 & 1998-2002 & 17202 & 15756 & 1617232 \\
-FP6 & 2002-2006 & 10091 & 15521 & 1437607 \\
-FP7 & 2007-2013 & 25607 & 26499 & 3789837 \\
-H2020 & 2014-2017 & 9055 & 15835 & 1342882 \\
+FP4 & 1994--1998 & 14567 & 7293 & 364263 \\
+FP5 & 1998--2002 & 17202 & 15756 & 1617232 \\
+FP6 & 2002--2006 & 10091 & 15521 & 1437607 \\
+FP7 & 2007--2013 & 25607 & 26499 & 3789837 \\
+H2020 & 2014--2017 & 9055 & 15835 & 1342882 \\
 \end{tabular}
@@
 As stopwords, we used the list that is provided by the Gensim Python
-library\footnote{http://radimrehurek.com/gensim/} and we added following very
+library~\footnote{http://radimrehurek.com/gensim/} and we added following very
 common words in the existing dataset: ``data'', ``based'', ``new'', ``project'',
@@
 the rare words that appear less than 5 times in the collection. 
-Finally, we obtained a smaller corpus per framework (see table \ref{eutable}). 
+Finally, we obtained a smaller corpus per framework (see table~\ref{eutable}). 
 For the actual implementation, see \emph{eu iterations.py} in the Appendix.
@@
 NSF are devoted to financial management, award processing and monitoring, legal
-affairs, outreach and other functions \footnote{\url{https://www.nsf.gov/about/research_areas.jsp}}. The directorates and their divisions are listed below:
+affairs, outreach and other functions~\footnote{\url{https://www.nsf.gov/about/research_areas.jsp}}. The directorates and their divisions are listed below:
 \begin{itemize}
@@
 The data about the awards
-\footnote{https://www.nsf.gov/awardsearch/download.jsp} are open, free and can
+~\footnote{https://www.nsf.gov/awardsearch/download.jsp} are open, free and can
 be used in research and applications. The dataset that we chose for the
@@
 In the provided dataset, the information is split into XML files, separated
-per year, from 1994-2017. In order to keep the correlation to time and be able
+per year, from 1994--2017. In order to keep the correlation to time and be able
 to compare the two datasets later, we split the projects based on the year
-they were initialized (see table \ref{usatable}).
+they were initialized (see table~\ref{usatable}).
 
@@
 times in the collection. Finally, we obtained a smaller corpus per framework 
-(see Table \ref{usatable}). 
+(see Table~\ref{usatable}). 
 For the actual implementation, see \emph{usa iterations.py} in the Appendix.
@@
 \hline
-FP4 & 1994-1997 & 36752 & 28038 & 4346604 \\
-FP5 & 1998-2001 & 37674 & 30728 & 5166316 \\
-FP6 & 2002-2006 & 54212 & 38476 & 8837298 \\
-FP7 & 2007-2013 & 87341 & 48277 & 15673424 \\
-H2020 & 2014-2017 & 35581 & 32268 & 7379219 \\
+FP4 & 1994--1997 & 36752 & 28038 & 4346604 \\
+FP5 & 1998--2001 & 37674 & 30728 & 5166316 \\
+FP6 & 2002--2006 & 54212 & 38476 & 8837298 \\
+FP7 & 2007--2013 & 87341 & 48277 & 15673424 \\
+H2020 & 2014--2017 & 35581 & 32268 & 7379219 \\
 \end{tabular}
@@
 For the implementation, we used the Gensim package (Radim Řehůřek,
-2009)\cite{rehurek_lrec} which implements an efficient online LDA algorithm, to
+2009)~\cite{rehurek_lrec} which implements an efficient online LDA algorithm, to
 extract the topics of a given corpus. Gensim uses a fast implementation of
 online LDA parameter estimation based on \emph{Online Learning for Latent Dirichlet
-Allocation}.\cite{onlineLDAvb} The algorithm runs in constant memory, which
+Allocation}~\cite{onlineLDAvb}. The algorithm runs in constant memory, which
 means that the size of the training corpus does not affect memory footprint, so
@@
 
-In figures \ref{wordcloudEU4} - \ref{wordcloudEU20} we show the 10 topics from FP4 to H2020 of the EU dataset, described by
+In figures \ref{wordcloudEU4}--\ref{wordcloudEU20} we show the 10 topics from FP4 to H2020 of the EU dataset, described by
 the 20 top words with the highest probability of belonging
@@
 Each wordcloud describes a topic, which we can find intuitively (the label 
-of each wordcloud corresponds to the title of the topic).
-
-By comparing the thematic areas suggested by the EU
-\footnote{\url{https://europa.eu/european-union/topics_en}} and the topics that
+of each wordcloud corresponds to the title of the topic)~\footnote{In figure~\ref{wordcloudEU4} the wordcloud (e), \emph{Digital systems}, is not very 
+clear which topic describes and in only appears in the 4\% of the projects 
+in this FP. Even though we tried with many iterations 
+until the model converges to find more distinguish topics, we didn't manage 
+to fetch better results.}.
+
+By comparing the thematic areas suggested by the EU~\footnote{\url{https://europa.eu/european-union/topics_en}} and the topics that
 we found with our implementation, one can easily observe that the majority of
@@
 \emph{Management software \& systems} is a subject that appears only in FP4 and
-FP5, with the 12\% of the projects. emph{Information systems \& technologies'}
-related projects cover the 8,5\% of the projects on average from FP5-H2020.
+FP5, with the 12\% of the projects. \emph{Information systems \& technologies'}
+related projects cover the 8,5\% of the projects on average from FP5--H2020.
 Since technology has an impact in every aspect nowadays, it is normal to have a
@@
 to \emph{Green energy} (hydropower, solar, nuclear energy) is increasing up to
-17,5\% and since then it also loses its populariry. The last 3 years, only the
+17,5\% and since then it also loses its popularity. The last 3 years, only the
 3\% of the projects are related to \emph{Green energy production}.
@@
 In FP6 and FP7, \emph{Social and Economic policies} appears with a small
-percentage of the projects (5\%). However, in H2020 it has a big increace, with
-the 17\% of the projects related to this topic. The last 3-4 years,
+percentage of the projects (5\%). However, in H2020 it has a big increase, with
+the 17\% of the projects related to this topic. The last 3--4 years,
 \emph{Business \& Innovation} emerged as a trending topic, with 1 out of 4
@@
 \end{tabular}
-\caption{Wordclouds of topics of the EU FP4 (1994-1998)}
+\caption{Wordclouds of topics of the EU FP4 (1994--1998)}
 \label{wordcloudEU4}
@@
 \end{tabular}
-\caption{Wordclouds of topics of the EU FP5 (1998-2002)}
+\caption{Wordclouds of topics of the EU FP5 (1998--2002)}
 \label{wordcloudEU5}
@@
 \end{tabular}
-\caption{Wordclouds of topics of the EU FP6 (2002-2006)}
+\caption{Wordclouds of topics of the EU FP6 (2002--2006)}
 \label{wordcloudEU6}
@@
 \end{tabular}
-\caption{Wordclouds of topics of the EU FP7 (2007-2013)}
+\caption{Wordclouds of topics of the EU FP7 (2007--2013)}
 \label{wordcloudEU7}
@@
 \end{tabular}
-\caption{Wordclouds of topics of the EU H2020 (2014-2020)}
+\caption{Wordclouds of topics of the EU H2020 (2014--2020)}
 \label{wordcloudEU20}
@@
 
-In figures \ref{wordcloudUSA4} - \ref{wordcloudUSA20} we show the 10 topics 
+In figures \ref{wordcloudUSA4}--\ref{wordcloudUSA20} we show the 10 topics 
 from 1994 to 2017 of the USA dataset, described by
@@
 and our topics, we see that all the topics that we found correspond to either 
-a directorate or one of the divisions. Below, we discuss the topics that
-stand out in most of the years.
+a directorate or one of the divisions.
 
@@
 investigate, with a stable percentage of 10\% of the projects, on average. Some
-of these topics are related to emph{Biology and Evolution}. Also, a 5\%
-approximately of the projects are related to emph{Mathematics}, from 1994 to
+of these topics are related to \emph{Biology and Evolution}. Also, a 5\%
+approximately of the projects are related to \emph{Mathematics}, from 1994 to
 2017.
@@
 With \emph{STEM} being the top priority in USA, since this topic shows up in all
-the years and according to the plot in figure \ref{usatrend} \emph{STEM} is the
+the years and according to the plot in figure~\ref{usatrend}, \emph{STEM} is the
 topic with the highest proportion of projects compared to the other topics (read
-section \ref{usaevolution}). Specifically, \emph{STEM education} has the 16,5\%
-of the projects from 1994-2006, 21\% in 2007-2013 (1 out of 5 projects is
+section~\ref{usaevolution}). Specifically, \emph{STEM education} has the 16,5\%
+of the projects from 1994--2006, 21\% in 2007--2013 (1 out of 5 projects is
 related to STEM) and the last 3 years it has lost its popularity by 10\%.
@@
 
-NSF shows a great interest in \emph{International activities} across all NSF
-supported disciplines (18\% of the projects in 1004-1998). The goal of these projects is 
+NSF also shows a great interest in \emph{International activities} across all NSF
+supported disciplines (18\% of the projects in 1994--1998). The goal of these projects is 
 to support high quality research and education, which could not occur without
@@
 European Union's \emph{Research and Innovation}
-programme\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}. The last
+programme~\footnote{\url{http://ec.europa.eu/research/iscp/index.cfm?pg=usa}}. The last
 3 years, the projects related to \emph{International research} cover the 10\% of all the 
@@
 
-Finally, a topic that used to be popular in the past, in 1994-1997 and
-2007-2013, covering the 10\% of the projects funded by NSF, is \emph{High energy Physics} 
+Finally, a topic that used to be popular in the past, in 1994--1997 and
+2007--2013, covering the 10\% of the projects funded by NSF, is \emph{High energy Physics} 
 in USA, which has lost its popularity nowadays.
@@
 \end{tabular}
-\caption{Wordclouds of topics of the USA (1994-1997)}
+\caption{Wordclouds of topics of the USA (1994--1997)}
 \label{wordcloudUSA4}
@@
 \end{tabular}
-\caption{Wordclouds of topics of the USA (1998-2001)}
+\caption{Wordclouds of topics of the USA (1998--2001)}
 \label{wordcloudUSA5}
@@
 \end{tabular}
-\caption{Wordclouds of topics of the USA (2002-2006)}
+\caption{Wordclouds of topics of the USA (2002--2006)}
 \label{wordcloudUSA6}
@@
 \end{tabular}
-\caption{Wordclouds of topics of the USA (2007-2013)}
+\caption{Wordclouds of topics of the USA (2007--2013)}
 \label{wordcloudUSA7}
@@
 \end{tabular}
-\caption{Wordclouds of topics of the USA (2014-2017)}
+\caption{Wordclouds of topics of the USA (2014--2017)}
 \label{wordcloudUSA20}
@@
 from 1994 to 2017 for the EU and from 1994 to 2016 for the
-USA\footnote{in this implementation we removed the projects of the
+USA~\footnote{in this implementation we removed the projects of the
   year 2017 from the USA dataset, because the amount of
@@
 
-\subsection{Trends in the EU}
-
-In figure \ref{totaltopicsEU} we show the 10 topics described by
+\subsubsection{Trends in the EU}
+
+In figure~\ref{totaltopicsEU} we show the 10 topics described by
 the 20 top words with the highest probability of belonging
@@
 iterations and the same value of the rest of the
-parameters, as described in section \ref{modelinference}. We assigned titles 
+parameters, as described in section~\ref{modelinference}. We assigned titles 
 to the topics, based on the words that describe them. Below are
@@
 \end{tabular}
-\caption{Wordclouds of topics of the EU dataset (1994-2017)}
+\caption{Wordclouds of topics of the EU dataset (1994--2017)}
 \label{totaltopicsEU}
@@
 assigned to this topic during the FP, normalized by the number of the
-documents-projects occurring in this FP. In figure \ref{eutrend} we
+documents-projects occurring in this FP. In figure~\ref{eutrend} we
 plot the results of topic proportions over time.
 
-As we mentioned in section \ref{EUdataset}, most of the projects in the 
+As we mentioned in section~\ref{EUdataset}, most of the projects in the 
 EU dataset don't have information about the year that they were initialized, 
 and there's only information about the Framework Programme, where they got 
-approved. Therefore, in figure \ref{eutrend}, we illustrate the topic 
+approved. Therefore, in figure~\ref{eutrend}, we illustrate the topic 
 evolution over time per FP.
@@
 Based on this plot, topic 10, which refers to \emph{International Research},
-has an interesting evolution; during the years 1994-1998 is appears as
+has an interesting evolution; during the years 1994--1998 is appears as
 less popular topic, compared to other topics. However, this changes
-drastically in 1998-2002 ($+14\%$) and in 2002-2006 it is at its peak
+drastically in 1998--2002 ($+14\%$) and in 2002--2006 it is at its peak
 ($+18\%$ since 1994). This period
@@
 
-\emph{Materials and Manufacturing} was a hot topic in 1994-1998, but it also
-appears a big decrease during the years 1998-2006 and it has a stable
+\emph{Materials and Manufacturing} was a hot topic in 1994--1998, but it also
+appears a big decrease during the years 1998--2006 and it has a stable
 trend since then. \emph{Materials Science/Chemistry \& Physics'} popularity
-(topic 4) line has an increase during 2002-2013 and the last 3 years a
-small decrease of $2-3\%$. Topics 2 and 3 (\emph{Social policy, Disease
+(topic 4) line has an increase during 2002--2013 and the last 3 years a
+small decrease of $2--3\%$. Topics 2 and 3 (\emph{Social policy, Disease
 detection \& treatment}) follow the same linear trend as \emph{Materials
 science \& Physics}. \emph{Energy production} (topic 11) was less popular in
-1994-2002 and is becoming slightly more popular the last 15
+1994--2002 and is becoming slightly more popular the last 15
 years.
@@
 other topics, with a percentage of $12.5\%$ of the projects in EU on average.
-
+\begin{figure}[H]
+\includegraphics[width=1.0\textwidth]
+{figs/eu-topic-evolution.png}
+\caption{Topics over time in EU}
+\label{eutrend}
+\end{figure}
 \emph{Biology} and the study of \emph{molecular mechanisms} have a small decrease of
@@
 affairs.
-\begin{center}
-\begin{figure}
-\includegraphics[width=1.0\textwidth]
-{figs/eu-topic-evolution.png}
-\caption{Topics over time in EU}
-\label{eutrend}
-\end{figure}
-\end{center}
-
-\subsection{Trends in the USA}
+
+\subsubsection{Trends in the USA}
 \label{usaevolution}
@@
 iterations and the same value of the rest of the
-parameters, as described in section \ref{modelinference}.
-
-Each one of the wordclouds in figure \ref{usatotal} represents a topic.
+parameters, as described in section~\ref{modelinference}.
+
+Each one of the wordclouds in figure~\ref{usatotal} represents a topic.
 The titles of the topics that are described in the wordclouds are listed below:
@@
 
-where $k$ is the number of the topic id, $y$ is the year between 1994-2016. The
+where $k$ is the number of the topic id, $y$ is the year between 1994--2016. The
 topic proportion of each topic per year equals to the sum of the number of the
@@
 \end{tabular}
-\caption{Wordclouds of topics of the USA dataset (1994-2016)}
+\caption{Wordclouds of topics of the USA dataset (1994--2016)}
 \label{usatotal}
 \end{figure}
-
 \begin{figure}[H]
@@
 \end{figure}
-
-In figure \ref{usatrend} we plot the topic distribution over time. We can easily
-observe that the topic 6, which refers to \emph{STEM education}, is becoming
+In figure~\ref{usatrend} we plot the topic distribution over time. We can easily
+observe that the topic 6, which refers to \emph{STEM education} (science, technology, engineering and math), is becoming
 a trend in the United States over the years, while most of the other
@@
 
-In general, the \emph{STEM} (science, technology, engineering and math)
-related research and education is becoming more and more popular,
-which is not surprising, since the National Science Foundation itself
-estimates that 80\%
- of the jobs available during the next decade
-will require math and science skills \footnote{\url{http://www.cvent.com/events/steam-ing-up-stem-academy-2017-2018/event-summary-e3e3f0c4087e43b99d23f4e4d95b6837.aspx}}.
+In general, the \emph{STEM} related research and education is becoming 
+more and more popular, which is not surprising, since the National 
+Science Foundation itself estimates that 80\% of the jobs available 
+during the next decade
+will require math and science skills~\footnote{\url{http://www.cvent.com/events/steam-ing-up-stem-academy-2017-2018/event-summary-e3e3f0c4087e43b99d23f4e4d95b6837.aspx}}.
 Even the acronym STEM arose in common use shortly after an meeting on
-science education held at the US National Science Foundation chaired by the then 
-NSF director Rita Colwell\footnote{\url{https://en.wikipedia.org/wiki/Science,_technology,_engineering,_and_mathematics}}.
+science education held at the US NSF chaired by the then 
+NSF director Rita Colwell~\footnote{\url{https://en.wikipedia.org/wiki/Science,_technology,_engineering,_and_mathematics}}.
 
@@
 
-The figures \ref{heatmap4}-\ref{heatmap20} visualize the heatmaps of
-the similarity of the two regions during the FP4-H2020. Rows represent
+The figures \ref{heatmap4}--\ref{heatmap20} visualize the heatmaps of
+the similarity of the two regions during the FP4--H2020. Rows represent
 topics from the EU dataset and columns topics from the USA dataset.
-The topics 0 - 9 of the EU dataset per FP (figures \ref{wordcloudEU4} -
-\ref{wordcloudEU20}) and the topics 0 - 9 of the USA dataset per FP (figures
-\ref{wordcloudUSA4} - \ref{wordcloudUSA20}) are declared in the heatmap plots as
-eu0 - eu9 and usa0 - usa9, respectively.
+The topics 0--9 of the EU dataset per FP (figures \ref{wordcloudEU4}--\ref{wordcloudEU20}) and the topics 0--9 of the USA dataset per FP (figures \ref{wordcloudUSA4}--\ref{wordcloudUSA20}) are declared in the heatmap plots as
+eu0--eu9 and usa0--usa9, respectively.
 The values of the JSD computation which are close to zero (lighter
@@
 \begin{itemize}
-\item FP4 (1994-1997)
+\item FP4 (1994--1997), with divergence < 0.3:
 \begin{itemize}
@@
 \end{itemize}
-\item FP5 (1998-2001)
+\item FP5 (1998--2001), with divergence < 0.25:
 \begin{itemize}
@@
 \end{itemize}
-\item FP6 (2002 $\sim$ 2006)
+\item FP6 (2002 $\sim$ 2006), , with divergence < 0.25:
 \begin{itemize}
@@
 \end{itemize}
-\item FP7 (2007-2013)
+\item FP7 (2007--2013), with divergence < 0.2:
 \begin{itemize}
@@
 \end{itemize}
-\item H2020 (2014-2017)
+\item H2020 (2014--2017), with divergence < 0.23:
 \begin{itemize}
@@
 \end{itemize}
+
+In order to find the similarities and the differences of the topics in research
+between the EU and the USA, we can also compare the two regions qualitatively by
+observing the corresponding titles of the topics during all these years (topics
+in figure~\ref{totaltopicsEU} for the EU and figure~\ref{usatotal} for the USA).
+
+Both the two regions are funding projects related to \emph{Molecular biology \&
+Genetics}, \emph{Materials \& Physics}, \emph{Social policies},
+\emph{International research} and \emph{Information systems}. Both also have
+many projects related to \emph{Climatology and Environmental Science}, but the
+USA also focuses on research in \emph{Atmospheric and Ocean sciences}.
+
+The are some notable differences in the two regions that are interesting from
+our point of view; In EU we find projects related to \emph{Energy production \&
+transportation}, which does not appear as a distinguish topic in USA. Moreover,
+\emph{Disease detection \& treatment} shows up only in EU, which is reasonable
+because in the dataset that we considered from the NSF, there are no projects 
+funded by the National Institute of Health. EU also focuses on the development of
+\emph{Business \& Innovation}, while USA doesn't. On the other hand, USA shows
+an interest in \emph{Mathematics} and a great focus in \emph{STEM education},
+while EU appears a wider interest in \emph{STEM}.
 
@@
 {figs/heatmaps/heatmapFP4.png}
-\caption{Heatmap of the similarity of the two regions during 1994-1997}
+\caption{Heatmap of the similarity of the two regions during 1994--1997}
 \label{heatmap4}
@@
 {figs/heatmaps/heatmapFP5.png}
-\caption{Heatmap of the similarity of the two regions during 1998-2001}
+\caption{Heatmap of the similarity of the two regions during 1998--2001}
 \label{heatmap5}
@@
 {figs/heatmaps/heatmapFP6.png}
-\caption{Heatmap of the similarity of the two regions during 2002-2006}
+\caption{Heatmap of the similarity of the two regions during 2002--2006}
 \label{heatmap6}
@@
 {figs/heatmaps/heatmapFP7.png}
-\caption{Heatmap of the similarity of the two regions during 2007-2013}
+\caption{Heatmap of the similarity of the two regions during 2007--2013}
 \label{heatmap7}
@@
 {figs/heatmaps/heatmapH2020.png}
-\caption{Heatmap of the similarity of the two regions during 2014-2017}
+\caption{Heatmap of the similarity of the two regions during 2014--2017}
 \label{heatmap20}
@@
 the documents are oblivious to the model. One future direction is to use a
-Dynamic Topic Model\cite{Blei:2006:DTM:1143844.1143859}, in which the order of
+Dynamic Topic Model~\cite{Blei:2006:DTM:1143844.1143859}, in which the order of
 the documents plays an important role. More precisely, the documents are grouped
